### 2024-07-01 test/main.tex
上传

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

\section{Why the S-matrix is so important?}
\begin{frame}{Locality and Unitarity}
    aa
\end{frame}
\section{Review of some pertinent results}
\begin{frame}{Gauge theory color structure}
    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
decomposed as
\textcolor{red}{\begin{equation*}
    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
\end{equation*}}

here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
\end{frame}
\begin{frame}
    Color-ordered partial amplitudes satisfy a set of well-known properties,
    \begin{itemize}
        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
    \end{itemize}
    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
    that matains the order of individual elements of each set.
\end{frame}
\begin{frame}
    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
\begin{equation*}
    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
\end{equation*}
The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
\\ \hspace*{\fill}\\
This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
\end{frame}
\begin{frame}{A Similar Structure}
    It can be proved that tree level amplitudes can also be decomposed like 
\begin{equation*}
    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
\end{equation*}
It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$}.
\end{frame}
\begin{frame}
    \begin{Large}
        \textcolor{red}{How can we realize the existence of this basis?}
    \end{Large}
\\ \hspace*{\fill}\\
We just need to notice the contribution from ladder diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{1.png}
\end{figure}
And any (three vertex) diagram, by using the Jacobbi identity like 
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{2.png}
\end{figure}
can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
\end{frame}
\begin{frame}{Color-Kinematics Duality and BCJ Relation}
The Color-Kinematics Duality here is not the complete version, but we can sketch some point from lower point case
\end{frame}

\section{CHY Formula}
\begin{frame}{Scattering equations}
    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
    \begin{equation*}
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
    \end{equation*}

    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
    \begin{equation*}
        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
    \end{equation*}
    and n-punctured Riemann sphere can be discribed by $SL(2,\mathbb{C})$ affine coordinates ${\sigma_1,\sigma_2,\ldots,\sigma_n}$, that is to say we have a equvilance relation
    \begin{align*}
        \{\sigma_1,\sigma_2,\ldots,\sigma_n\}\sim\{\psi(\sigma_1),\psi(\sigma_2),\ldots,\psi(\sigma_n)\},\\\psi(\sigma):=\frac{\alpha\sigma+\beta}{\gamma\sigma+\delta},\quad\alpha,\beta,\gamma,\delta\in\mathbb{C},\alpha\delta-\beta\gamma=1
    \end{align*}
    because of the redundancy of 
\end{frame}
\begin{frame}
    From this map, we can easily obtain the main ingredients of this report \\

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{n-3} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\begin{frame}{KLT Relation}
    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
    \begin{table}[]
        \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|}
        \hline
         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
        \end{tabular}
        }
        \end{table}
\end{frame}
\begin{frame}{KLT Orthogonality}
    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
    \begin{block}{Proposition 1}
        \begin{equation*}
            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
        \end{equation*}
    \end{block}

\end{frame}
\begin{frame}
    First we need to define the Jacobian matrix associated to the scattering equations

        \begin{equation*}
            \boxed{
            \label{jacobbi}
            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
            }
        \end{equation*}
    As mentioned above only n-3 of the scattering equations are independent so the matrix $\Phi$ has \alert{rank n-3}.  (This matrix was first encountered in the gravity amplitudes constructed from gauge theory using KLT relation ) 
\end{frame}
\begin{frame}
    Consider a generalization of $\Phi_{ab}$ 
    \begin{equation*}
        \Psi_{ab,a\neq b}\equiv\frac{s_{ab}}{(\sigma_a-\sigma_b)(\sigma_a^{\prime}-\sigma_b^{\prime})},\quad\Psi_{aa}\equiv-\sum_{c\neq a}\Psi_{ac}.
    \end{equation*}
    \begin{block}{Proposition 2}
        \begin{equation*}
            \operatorname{rank}\Psi(\{\sigma\},\{\sigma^{\prime}\})=\begin{cases}n-4, \{\sigma\}\neq\{\sigma^{\prime}\}\\n-3, \{\sigma\}=\{\sigma^{\prime}\}\end{cases}
        \end{equation*}
        $\sigma$ and $\sigma^\prime$ are assmused to be solutions to scattering equation.
    \end{block}
\end{frame}
\begin{frame}{Prove of KLT orthogonality}
    For the purpose of proving KLT orthogonality, we can construct a n! dimension vector for each solution
    \begin{equation*}
        \frac1{(\sigma_{\omega(1)}-\sigma_{\omega(2)})(\sigma_{\omega(2)}-\sigma_{\omega(3)})\cdots(\sigma_{\omega(n)}-\sigma_{\omega(1)})}
    \end{equation*}
    Not so obvious is the fact that we can fix the positon of 3 labels, which we choose 1,n-1,n, give rise to the KK relation and BCJ relation.
    \\ \hspace*{\fill}\\
    Now the vectors become (n-3)! dimension, and even aftering selecting three lables, we still have the freedom of where to put them. Here we only use two choices :
    \begin{equation*}
        \textcolor{red}{(1,\omega(2),\dots,\omega(n-2),n-1,n)\quad and \quad (1,\omega(2),\dots,\omega(n-2),n,n-1 )}
    \end{equation*}
\end{frame}
\begin{frame}
    The corresponding two vectors are 
    \begin{align*}V(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_{n-1})(\sigma_{n-1}-\sigma_n)(\sigma_n-\sigma_1)},\\U(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_n)(\sigma_n-\sigma_{n-1})(\sigma_{n-1}-\sigma_1)}.
    \end{align*}
    In this language, we can construct a bilinear form 
    \begin{equation*}
        S[\alpha|\beta]=\prod^{n-2}_{i=2}\left(s_{1,\alpha_i}+\sum_{j=2}^{i-1}
        \theta(\alpha(j),\alpha(i))_\beta s_{\alpha(j),\alpha(i)}\right)
    \end{equation*}
    where $\alpha,\beta\in S_{n-3}$,$\theta(i,j)_\beta=1$if the order of i,j is the same in both permutations 
    $\alpha(2,3,\dots,n-2)$ and $\beta(2,3,\dots,n-2)$, and 0 otherwise.
    S is usually called \alert{Momentum Kernel}.
\end{frame}
\begin{frame}
    Given any two solutions of scatering equations,
    \begin{equation*}
        \{\sigma_1^{(i)},\sigma_2^{(i)},\dots,\sigma_n^{(i)}\}\quad and \quad \{\sigma_1^{(j)},\sigma_2^{(j)},\dots,\sigma_n^{(j)}\}
    \end{equation*}
    define two vectors, $V(\alpha)^{(i)}$ and $U(\beta)^{(j)}$, i,j are choices of solutions and $\alpha,\beta$ are the choices of permutaions,
    the number of both is \alert{(n-3)!}.
    \\ \hspace*{\fill}\\
    A natural inner product can be defined as
    \begin{equation*}
        (i,j):=\sum_{\alpha,\beta\in S_{n-3}}V^{(i)}(\alpha)S[\alpha|\beta]U^{(j)}(\beta)
    \end{equation*}
    Knowing all definetions above, we can proceed to prove KLT orthogonality.
\end{frame}
\begin{frame}
    The starting point is to notice that
    \begin{equation*}
        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
    \end{equation*}
    is clearly invariant under $SL(2,\mathbb{C})\times SL(2,\mathbb{C})$. Partially fixing both $SL(2,\mathbb{C})$
    redundancies with convenient choice $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$
    and define 
    \begin{align*}
            K_n(\{\sigma\},\{\sigma'\})\equiv\sum_{\alpha,\beta\in S_{n-3}}&\frac1{\sigma_{1,\alpha(2)}\ldots\sigma_{\alpha(n-3),\alpha(n-2)}}S[\alpha|\beta]\\
            &\frac1{\sigma_{1,\beta(2)}^{\prime}\ldots\sigma_{\beta(n-3),\beta(n-2)}^{\prime}}
    \end{align*}
    The motivation for this definition is that $K_n$ appears in the numerator of KLT orthogonality.
\end{frame}
\begin{frame}
    It is also convenient to define an auxiliary co-rank one $(n-2)\times(n-2)$ matrix $\psi^{(n)}$
    \begin{equation*}
        \psi_{ab,a\neq b}=\frac{s_{ab}}{\sigma_{ab}\sigma_{ab}^{\prime}},\quad\psi_{aa}=-\sum_{b\neq a}\psi_{ab},\quad a,b=1,\ldots,n{-}2
    \end{equation*}
    It can be proven that any $(n-3)\times(n-3)$ minors of $\psi^{(n)}$ are the same, and we denote such a minor as
    ${\det}^\prime\psi^{(n)}$ , that is to say, the determinat of the matrix after removing any row and colum.
    \begin{block}{Proposition 3}
        The two functions defined above are identical up to a sign.
        \begin{equation*}
            K_n(\{\sigma\},\{\sigma'\})=(-1)^n{\det}^\prime\psi^{(n)}
        \end{equation*}
    \end{block}
\end{frame}
\begin{frame}
    The final step is put all pieces together. With the choice  $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$,
    we have 
    \begin{equation*}
        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}
    \end{equation*}
    In addition, one finds that the minor of $\psi$ obtained by removing the first row and colum is identical to 
    that of $\Psi(\{\sigma\},\{\sigma^{\prime}\})$ after removing rows and colums $\{1,n-1,n\}$. We denote them respectively
    $|\psi^{(n)}|^1_1$ and $|\Psi|^{1,n-1,n}_{1,n-1,n}$. Then,
    \begin{align*}
        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}&=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}\\
        &=\frac{(-1)^n|\psi^{(n)}|^1_1}{{(-1)^n|\psi^{(n)}|^1_1}^{\frac{1}{2}}{|\psi^{(n)}|^1_1}^{\frac{1}{2}}}\\
        &=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{(|\Psi(\{\sigma^{(i)},\sigma^{(i)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}(|\Psi(\{\sigma^{(j)}\},\{\sigma^{(j)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}}
    \end{align*}
\end{frame}
\begin{frame}
    Fianlly, we just need to use Proposition 2. 
    \begin{itemize}
        \item If $i=j$, the rank of matrix $\Psi$ is $n-3$ and the minor is nonzero, we obtain
        \begin{equation*}
            \frac{(i,i)}{(i,i)^{\frac12}(i,i)^{\frac12}}=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}=1
        \end{equation*}
        \item If $i\neq j$, the rank of matrix is $n-4$, so any minor with volume more than $n-4$ equals 0.
        \begin{equation*}
            |\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}=0\Rightarrow \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=0
        \end{equation*}
    \end{itemize}
    Up to now, we conclude the proof of KLT orthogonality.
\end{frame}
\begin{frame}
    \frametitle{Attempt to construct S-matrix --- Towards CHY}
    Thanks to the excellent properties of scattering equations, it is very tempting to propose that the solutions
    to scattering equations should be used to construct scattering amplitudes.
    \\ \hspace*{\fill}\\
    The first two constructed are YM and gravity amplitudes in any dimensions
    \begin{align*}
        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
        M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
    \end{align*}
    The measure is defined as following
    \begin{equation*}
        \prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}{:}=\sigma_{ij}\sigma_{jk}\sigma_{ki}\prod_{a\neq i,j,k}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}
    \end{equation*}
\end{frame}
\begin{frame}
    The reason we extract 3 indices from delta equation is the fact that only $n-3$ scattering equations are independent.
    This from can be proved to be \alert{independent of choice of $i,j,k$}, therefore permutaion invariant.
    We also have
    \begin{equation*}
        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
    \end{equation*}
    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
    \begin{equation*}
        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
    \end{equation*}
\end{frame}
\begin{frame}{The form of measure}
    It is worth to computed the measure explictly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 
    \begin{equation*}
        \int\prod_{c\neq p,q,r}d\sigma_c(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})\prod_{a\neq i,j,k}\delta\biggl(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\biggr)
    \end{equation*}
    The delta functions completely localize all integrals and the answer is evaluating a Jacobian defined above.
    \begin{equation*}
            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
    \end{equation*}
    Then, we obtain the measure
    \begin{equation*}
            \boxed{
            \sum_{\{\sigma\}\in\mathrm{solutions}}\frac{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}{|\Phi|_{pqr}^{ijk}}}
    \end{equation*}
\end{frame}
\begin{frame}
    Always denoted by 
    \begin{equation*}
        \boxed{
        \det{'}\Phi:=\frac{|\Phi|_{pqr}^{ijk}}{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}}
    \end{equation*}
    $|\Phi|_{pqr}^{ijk}$ means that we need to delete the rows $\{i,j,k\}$ and the colums $\{p,q,r\}$, of course it is free to choose which inedex refers
    to row or colum ($\Phi$ is a symmetric matrix).
\end{frame}
\begin{frame}
    \frametitle{The form of $E_n(\{k,\epsilon,\sigma\})$}
    In order to present the explict form of $E_n(\{k,\epsilon,\sigma\})$, first define the following $2n\times2n$ antisymmetric matrix 
    \begin{equation*}
        \Psi=\begin{pmatrix}
            A & -C^T \\
            C & B 
        \end{pmatrix}
    \end{equation*}
    where $A,B$ and $C$ are $n\times n$ matrices, defined as 
    \begin{equation*}
        A_{ab}=\begin{cases}\frac{s_{ab}}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b,\end{cases} \quad 
        B_{ab}=\begin{cases}\frac{\epsilon_a \cdot \epsilon_b}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b, \end{cases} \quad
    \end{equation*}
    \begin{equation*}
        C_{ab}=\begin{cases}\frac{\epsilon_a\cdot k_b}{\sigma_a-\sigma_b}&a\neq b,\\-\sum_{c\neq a}\frac{\epsilon_a\cdot k_c}{\sigma_a-\sigma_c}&a\neq b.\end{cases}
    \end{equation*}
\end{frame}
\begin{frame}
    The first important observation is that while the Pfaffian of $\Psi$ is 0, but after removing any rows $i,j$ and colums $i,j$
    with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
    \begin{equation*}
            \boxed{
            \mathrm{Pf}^{\prime}\Psi:=\frac{(-1)^{i+j}}{(\sigma_i-\sigma_j)}\mathrm{Pf}(\Psi_{ij}^{ij})}
    \end{equation*}
    It can be proved that the reduced Pfaffian is invariant under permutaion of \alert{particle labels}.

    \begin{alertblock}{Pfaffian}
        Pfaffian is defined for antisymmetric matrix, usually in two ways as following
        \begin{itemize}
            \item \begin{equation*}
                \mathrm{Pf}(A)^2=\det A
            \end{equation*}
            \item \begin{equation*}
                \mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}
            \end{equation*}
        \end{itemize}
    \end{alertblock}
\end{frame}
\begin{frame}
    Write down the proposal
    \alert{
    \begin{equation*}
        E_n(\{k,\epsilon,\sigma\})=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)
    \end{equation*}}
\end{frame}

\end{document}

### 2024-07-01 test/main.tex
最新

@@
     \end{equation*}}
+    Combine the measure and integrand, we conclude the formula for the tree-level S-matrix of Yang-Mills in any dimension
+    \begin{equation*}
+        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
+    \end{equation*}
+    And using the KLT constrution, we can construct the formula for tree-level S-matrix of gravity as double copy of that of Yang-Mills
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+    \end{equation*}
 \end{frame}

### 2024-07-02 test/main.tex
new
New

@@
     \begin{equation*}
-        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
     \end{equation*}
+\end{frame}
+\begin{frame}
+    We can also write the amplitude in another form
+    \begin{equation*}
+        M_n^{\mathrm{YM}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{1}{\sigma_{12}\cdots\sigma_{n1}}\frac{\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{\det{'}\Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    where we use the property of Pfaffian $\det{'}\Psi(k,\epsilon,\sigma)=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$\\$\times \mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$.
+\end{frame}
+\begin{frame}
+    \frametitle{Consistency check}
+    \begin{itemize}
+        \item \alert{Gauge invariance}\\
+        If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
+        \begin{equation*}
+            C_{ii}=-\sum_{c\neq i}\frac{\epsilon_i\cdot k_c}{\sigma_i-\sigma_c} \to -\sum_{c\neq i}\frac{k_i\cdot k_c}{\sigma_i-\sigma_c}=0
+        \end{equation*}
+        It is easy to discover that the $i$th and $i+n$th colums become identical, so the determinat and Pfaffian become 0.
+        \pause
+        \item \alert{Soft limit}
+        Using a special property of Pfaffian
+        \begin{equation*}
+            \mathrm{Pf} (E)=\sum_{q=1}^{2n}(-1)^q e_{pq}\mathrm{Pf}(E^{pq}_{pq})
+        \end{equation*}
+        we find the amplitude in the soft limit is 
+        \begin{equation*}
+            A_n\to\left(\frac{\epsilon_n\cdot k_{n-1}}{k_n\cdot k_{n-1}}+\frac{\epsilon_n\cdot k_1}{k_n\cdot k_!}\right)A_{n-1}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{CHY form of amplitudes}
 \end{frame}

### 2024-07-02 test/main.tex
New

--- 2024-07-01 test/main.tex
@@
     \end{equation*}}
+    Combine the measure and integrand, we conclude the formula for the tree-level S-matrix of Yang-Mills in any dimension
+    \begin{equation*}
+        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
+    \end{equation*}
+    And using the KLT constrution, we can construct the formula for tree-level S-matrix of gravity as double copy of that of Yang-Mills
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    We can also write the amplitude in another form
+    \begin{equation*}
+        M_n^{\mathrm{YM}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{1}{\sigma_{12}\cdots\sigma_{n1}}\frac{\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{\det{'}\Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    where we use the property of Pfaffian $\det{'}\Psi(k,\epsilon,\sigma)=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$\\$\times \mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$.
+\end{frame}
+\begin{frame}
+    \frametitle{Consistency check}
+    \begin{itemize}
+        \item \alert{Gauge invariance}\\
+        If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
+        \begin{equation*}
+            C_{ii}=-\sum_{c\neq i}\frac{\epsilon_i\cdot k_c}{\sigma_i-\sigma_c} \to -\sum_{c\neq i}\frac{k_i\cdot k_c}{\sigma_i-\sigma_c}=0
+        \end{equation*}
+        It is easy to discover that the $i$th and $i+n$th colums become identical, so the determinat and Pfaffian become 0.
+        \pause
+        \item \alert{Soft limit}
+        Using a special property of Pfaffian
+        \begin{equation*}
+            \mathrm{Pf} (E)=\sum_{q=1}^{2n}(-1)^q e_{pq}\mathrm{Pf}(E^{pq}_{pq})
+        \end{equation*}
+        we find the amplitude in the soft limit is 
+        \begin{equation*}
+            A_n\to\left(\frac{\epsilon_n\cdot k_{n-1}}{k_n\cdot k_{n-1}}+\frac{\epsilon_n\cdot k_1}{k_n\cdot k_1}\right)A_{n-1}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{CHY form of amplitudes}
+    Both formulas above can be written in this simplest form 
+    \alert{
+        \begin{equation*}
+            \!\!\!\!\mathcal{M}^{(s)}\!=\!\!\!\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)
+            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}{(\mathrm{Pf}^\prime\Psi)}^s
+        \end{equation*}}
+    with $s=1$ for Yang-Mills and $s=2$ for gravity.
+    \\ \hspace*{\fill}\\
+    Here we would like to consider that the formula above is not only a convenient way to write Yang-Mills and gravity amplitudes, but can be \alert{a definition of S-matrix
+    for spin s particles}.This means that 
+    \begin{equation*}
+        s=0\quad\to \quad \text{a corresponding sclar theory}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
+    \begin{equation*}
+        \left(\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\right)^2\to\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\mathrm{Pf}^\prime \Psi(k,\tilde{\epsilon},\sigma)
+    \end{equation*}
+    actually it gives amplitudes with gravitons coupled to dilatons and B-fields.
+    \\ \hspace*{\fill}\\
+    For the case $s=0$, the similar consequence is 
+    \begin{equation*}
+        \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)^2\to\left(\frac{\mathrm{Tr}(T^{a_1}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
+        \left(\frac{\mathrm{Tr}(\tilde{T}^{b_1}\dots \tilde{T}^{b_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
+    \end{equation*}
+    while the original color group is $U(N)$, the new factors are the product of two different color group \alert{$U(N)\times U(\tilde{N})$}.
+\end{frame}
+\begin{frame}
+    The simplest possibility is the theory with only cubic interaction
+    \begin{equation*}
+        -f_{abc}\tilde{f}_{a^\prime b^\prime c^\prime}\phi^{aa^\prime}\phi^{bb^\prime}\phi^{cc^\prime}
+    \end{equation*}
+    The conclusion of the factors above
+    \begin{equation*}
+        \mathcal{C}_{U(N)}\equiv \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)
+    \end{equation*}
+
 \end{frame}

### 2024-07-03 test/main.tex
New

@@
 \usefonttheme{professionalfonts}
+\usepackage{tikz}
 \AtBeginSection[]{
@@
 \end{equation*}
-It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$}.
+The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
 \end{frame}
@@
     \begin{equation*}
-        s=0\quad\to \quad \text{a corresponding sclar theory}
+        s=0\quad\to \quad \text{a corresponding scalar theory}
     \end{equation*}
@@
     \end{equation*}
-    The conclusion of the factors above
+    All of above leads to the conclusion that the factors 
     \begin{equation*}
-        \mathcal{C}_{U(N)}\equiv \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)
+        \mathcal{C}_{U(N)}\equiv \sum_{\sigma\in S_n/Z_n}\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)
     \end{equation*}
+    are interchangeable and this is a color-Kinematics corresopondence which is valid for individual solutions to scattering equations.
 
@@
 
+\begin{frame}
+    The connection of amplitudes between 3 theories can be described by the following diagram 
+    \begin{figure}[htb]
+        \centering
+        \includegraphics[width=1\linewidth]{main.png}
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \frametitle{Double partial amplitudes}
+    Because there are two color indices in this sclar theory, so it can be anticipateed that the amplitude
+    have double trace decomposition structure
+    \begin{align*}
+        \mathcal{M}_n^{(0)}&=\sum_{\alpha\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})M_n^{(0)}(\alpha(1),\alpha(2),\ldots,\alpha(n))\\
+        &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\text{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
+        &\times \alert{m_n^{(0)}(\alpha|\beta)}
+    \end{align*} 
+    where the last term $m_n^{(0)}(\alpha|\beta)$ is called \alert{double partial amplitude} and can be read off from the full amplitude
+    \begin{align*}
+    m_{n}^{(0)}(\alpha|\beta)&=\int\frac{d^{n}\sigma}{\operatorname{vol}\operatorname{SL}(2,\mathbb{C})}\frac{\prod_{a}{}^{\prime}\delta(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}})}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}\\
+    =&\sum_{\{\sigma\}\in\mathrm{solutions}}\frac1{\det^{\prime}\Phi}\frac{1}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}
+    \end{align*}
+
+\end{frame}
+\begin{frame}
+    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
+    \begin{equation*}
+        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
+    \end{equation*}
+    where $\alpha \in S_{n-2}$. The amplitude is 
+    \begin{equation*}
+        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    \frametitle{Examples}
+    \begin{itemize}
+        \item The simplest example is the 3 point case
+        \begin{equation*}
+            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
+        \end{equation*}
+        It actually gives the correct answer.
+        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
+        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
+        \begin{equation*}
+            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
+        \end{equation*}
+        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \begin{align*}
+        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
+        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
+        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
+    \end{align*}
+    \quad \quad as expected for a color-dressed cubic theory.
+    \begin{itemize}
+        \item For the five point, I just give the results of some double partial amplitudes.
+        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
+        \begin{equation*}
+            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
+                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \begin{align*}
+        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}s_{51}},\\
+        &m_5^{(0)}(I|P_5)=0
+    \end{align*}
+\end{frame}
+
 \end{document}

### 2024-07-03 test/main.tex
New

@@
 \usepackage{tikz}
+\usepackage{svg}
 \AtBeginSection[]{
@@
     \begin{align*}
-        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}s_{51}},\\
+        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_4)=-\frac{1}{s_{34}s_{51}},\\
         &m_5^{(0)}(I|P_5)=0
     \end{align*}
+    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
+    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
+    \\ \hspace*{\fill}\\
+    More explictly,
+
+    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+    %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+    %Straight Lines [id:da8455657796938298] 
+    \draw    (179.5,110) -- (212.5,142) ;
+    %Straight Lines [id:da5324594211620186] 
+    \draw    (212.5,142) -- (182.5,170) ;
+    %Straight Lines [id:da4643902351443361] 
+    \draw    (212.5,142) -- (254.5,142) ;
+    %Straight Lines [id:da8904360433186445] 
+    \draw    (280.5,111) -- (254.5,142) ;
+    %Straight Lines [id:da18000644921445508] 
+    \draw    (254.5,142) -- (281.5,171) ;
+    %Straight Lines [id:da29602344087941934] 
+    \draw    (320.5,109) -- (353.5,141) ;
+    %Straight Lines [id:da9975053882839713] 
+    \draw    (353.5,141) -- (323.5,169) ;
+    %Straight Lines [id:da5157442319090852] 
+    \draw    (353.5,141) -- (395.5,141) ;
+    %Straight Lines [id:da049884375007126946] 
+    \draw    (421.5,110) -- (395.5,141) ;
+    %Straight Lines [id:da9299487354359295] 
+    \draw    (395.5,141) -- (422.5,170) ;
+
+    % Text Node
+    \draw (111,135.4) node [anchor=north west][inner sep=0.75pt]    {$m_{4}^{(0)}(I,I) =$};
+    % Text Node
+    \draw (184.5,173) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (184.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (264.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (263.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (298,133.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (325.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (325.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (405.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (404.5,171) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+
+    \end{tikzpicture}
+
 \end{frame}
+\begin{frame}
+    Similarly,
 
+    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+    %uncomment if require: \path (0,350); %set diagram left start at 0, and has height of 350
+
+    %Straight Lines [id:da8963901965951664] 
+    \draw    (84,71) -- (108,93) ;
+    %Straight Lines [id:da07470927432540231] 
+    \draw    (108,93) -- (136,93) ;
+    %Straight Lines [id:da12245379377221366] 
+    \draw    (108,93) -- (85,111) ;
+    %Straight Lines [id:da6511432990080723] 
+    \draw    (136,93) -- (161,114) ;
+    %Straight Lines [id:da1430135957918477] 
+    \draw    (157,71) -- (136,93) ;
+    %Straight Lines [id:da8765002291973463] 
+    \draw    (157,71) -- (158,47) ;
+    %Straight Lines [id:da9623971067643409] 
+    \draw    (157,71) -- (178,87) ;
+    %Straight Lines [id:da5561877649988292] 
+    \draw    (214,70) -- (238,92) ;
+    %Straight Lines [id:da44100018812085007] 
+    \draw    (238,92) -- (266,92) ;
+    %Straight Lines [id:da05824517478761182] 
+    \draw    (238,92) -- (215,110) ;
+    %Straight Lines [id:da35334338456014613] 
+    \draw    (266,92) -- (291,113) ;
+    %Straight Lines [id:da9313767826880515] 
+    \draw    (287,70) -- (266,92) ;
+    %Straight Lines [id:da696534040519218] 
+    \draw    (287,70) -- (288,46) ;
+    %Straight Lines [id:da5526828548209644] 
+    \draw    (287,70) -- (308,86) ;
+    %Straight Lines [id:da19124382298581288] 
+    \draw    (359,64) -- (383,86) ;
+    %Straight Lines [id:da5237814153432139] 
+    \draw    (383,86) -- (411,86) ;
+    %Straight Lines [id:da7974585866426673] 
+    \draw    (383,86) -- (360,104) ;
+    %Straight Lines [id:da46316924534551385] 
+    \draw    (411,86) -- (436,107) ;
+    %Straight Lines [id:da37617479030606993] 
+    \draw    (432,64) -- (411,86) ;
+    %Straight Lines [id:da9834219129393018] 
+    \draw    (432,64) -- (433,40) ;
+    %Straight Lines [id:da7117622111604034] 
+    \draw    (432,64) -- (453,80) ;
+    %Straight Lines [id:da8760088009181417] 
+    \draw    (82,171) -- (106,193) ;
+    %Straight Lines [id:da7078786925271212] 
+    \draw    (106,193) -- (134,193) ;
+    %Straight Lines [id:da5389180018159456] 
+    \draw    (106,193) -- (83,211) ;
+    %Straight Lines [id:da26578622720899636] 
+    \draw    (134,193) -- (159,214) ;
+    %Straight Lines [id:da5989066756692625] 
+    \draw    (155,171) -- (134,193) ;
+    %Straight Lines [id:da13747441694892726] 
+    \draw    (155,171) -- (156,147) ;
+    %Straight Lines [id:da4119117050779677] 
+    \draw    (155,171) -- (176,187) ;
+    %Straight Lines [id:da5379584617019675] 
+    \draw    (221,169) -- (245,191) ;
+    %Straight Lines [id:da788296500370655] 
+    \draw    (245,191) -- (273,191) ;
+    %Straight Lines [id:da4136462405421193] 
+    \draw    (245,191) -- (222,209) ;
+    %Straight Lines [id:da37414431568833373] 
+    \draw    (273,191) -- (298,212) ;
+    %Straight Lines [id:da8232480161298765] 
+    \draw    (294,169) -- (273,191) ;
+    %Straight Lines [id:da7983669347123197] 
+    \draw    (294,169) -- (295,145) ;
+    %Straight Lines [id:da7903324165137171] 
+    \draw    (294,169) -- (315,185) ;
+
+    % Text Node
+    \draw (5,76.4) node [anchor=north west][inner sep=0.75pt]    {$m_{5}( I,I) =$};
+    % Text Node
+    \draw (87,114) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (86,68) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (159.5,56) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (180,84) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (163,111) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (198,73.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (217,113) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (216,67) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (289.5,55) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (310,83) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (293,110) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (335,72.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (362,107) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (361,61) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (434.5,49) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (455,77) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (438,104) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (65,184.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (85,214) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (84,168) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (157.5,156) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (178,184) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (161,211) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (201,181.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (224,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (226,172) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (296.5,154) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (317,182) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (300,209) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+
+    \end{tikzpicture}
+\end{frame}
+\begin{frame}
+    \frametitle{Trivalent graph expansion}
+    \begin{alertblock}{Proposition}
+        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
+    \end{alertblock}
+    \pause
+    More explictly, 
+    \begin{equation*}
+        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
+\end{equation*}
+where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
+$\beta$ ordering respectively. To make this expression more clear, see the following diagram
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{5.png}
+\end{figure}
+\end{frame}
+\begin{frame}
+    We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way
+    \begin{itemize}
+        \item First step, draw a disk with n nodes sitting on the boundary in the ordering $\alpha$, then link the n nodes with a loop of line segments according to
+              the ording $\beta$. The line segments from $\beta$ split the disk into some polygons, like the graph (b). We need to move the external points of every polygon
+              to make them have no common edges, like graph (c).
+        \item Second step, put a point in every polygon, named equivalant vertex, and connect this point to all external points in corresponding area. Lines that connect equivalent 
+              vertices in two regions with common vertices are called equivalent propagators. The resulting graph is an equivalent Feynman diagram, as shown in Figure (d).
+    \end{itemize}
+\end{frame}
 \end{document}

### 2024-07-04 test/main.tex
Newest

@@
 \section{Why the S-matrix is so important?}
-\begin{frame}{Locality and Unitarity}
-    aa
+\begin{frame}
+    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
+    unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
+    S-matrix can be constructed directly from a special kind of geometry object and we even have no need to introduce the Lagrangian
+    of the specific theory. Also the localty and unitarity can be the outcome from the request of positivity instead of input or previous constraints.
+    It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
+\end{frame}
+\begin{frame}{}
+    \begin{itemize}
+        \item BCFW recursion relation.
+        \begin{equation*}
+            \!\!\!\!A_n ~= \!\!\!\!\sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
+            \,\frac{1}{P_I^2}\,
+            \hat{A}_\text{R}(z_I)
+               ~~=
+               \!\!\!\!\sum_{\text{diagrams}~I}
+           \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1.pdf}}
+           \,.
+        \end{equation*}
+        \item Dual superconformal symmetry of $\mathcal{N}=4$ Super Yang-Mills amplitude.
+        \item Generalized unitarity
+        \item Positive geometry and Amplituhedra.
+        \item \dots
+    \end{itemize}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{Grassmanian-Image.jpg}
+    \end{figure}
 \end{frame}
@@
 \end{frame}
+\begin{frame}
+    \begin{itemize}
+        \item Third step, we can read off the corresponding amplitudes from the equivalent Feynman diagram. 
+    \end{itemize}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\linewidth]{7.png}
+    \end{figure}
+    In this example, we can obtain 
+    \begin{equation*}
+        m_8^{(0)}(I|54376218)=(-1)^?\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
+    \end{equation*}
+    As for the indefinite sign, there is also a procedure to determine it.
+\end{frame}
+\begin{frame}
+    \begin{itemize}
+        \item First step, determine the orientation of the disk by ordering $\alpha$, and define the loop segments by ordering $\beta$, which also determine the orientation of every polygon.
+        \item Second step, (1) each polygon with odd number vertices contributes a plus sign if the orientation is the same as disk, and a minus sign oppositely;
+              (2) each polygon with even number vertices contribute a minus sign; (3) each intersection point contributes a minus sign.
+    \end{itemize}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\linewidth]{6.png}
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \frametitle{Relation to KLT matrix}
+    It can be shown that the scalar double partial amplitudes are the same as the inverse of KLT matrix.
+    \begin{align*}
+        &(S_{\mathrm{KLT}}^{-1})_\beta^\alpha=(m_{\mathrm{scalar}})_\beta^\alpha\\
+        &\equiv m^{(0)}(1,\alpha(2),\ldots,\alpha(n-2),n-1,n|1,\beta(2),\ldots,\beta(n-2),n,n-1)
+    \end{align*}
+    The inverse of KLT matrix have been also discussed in other paper, in which it was related to field theory limit if string 
+    disk integrals, so it would be interesting to explore the connection further. 
+\end{frame}
 \end{document}

### 2024-07-05 test/main.tex
New

@@
 \usepackage{svg}
+\usepackage{graphics}
 \AtBeginSection[]{
@@
         \centering
-        \includegraphics[width=0.8\linewidth]{Grassmanian-Image.jpg}
+        \caption{Positive geometry}
+        \includegraphics[width=0.4\linewidth]{Grassmanian-Image.jpg}
     \end{figure}
@@
 \end{frame}
-\begin{frame}{Color-Kinematics Duality and BCJ Relation}
-The Color-Kinematics Duality here is not the complete version, but we can sketch some point from lower point case
+\begin{frame}{Color-Kinematics Duality }
+The Color-Kinematics Duality here is not the complete version, but we can catch some points.
+At four points we have
+\begin{equation*}
+    A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)=0.
+\end{equation*}
+%The decoupling identity does not rely on the specific polariazation and space-time, so the hold of this equation is 
+%entirely due to the amplitudes' dependence on Mandelstam variables.
+We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ 
+\begin{align*}
+    &A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)\\
+\quad&= (s+t+u)\chi=0
+\end{align*} 
+Considering that $A_4^{\mathrm{tree}}(1,2,3,4)$ treats $s$ and $t$ the same, and similar to the other two, we make the identification
+\begin{equation*}
+    A_4^{\mathrm{tree}}(1,2,3,4)=u\chi,\quad   A_4^{\mathrm{tree}}(1,3,2,4)=t\chi,\quad    A_4^{\mathrm{tree}}(1,4,2,3)=s\chi
+\end{equation*}
+\end{frame}
+\begin{frame}
+    We obtain
+    \begin{align*}
+        tA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,3,4,2),\\
+        sA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,4,2,3),\\
+        tA_4^{\mathrm{tree}}(1,2,3,4)=sA_4^{\mathrm{tree}}(1,3,4,2).\\
+    \end{align*}
+    And in order to obtain the knematic analog of Jacobbi identity, it is convenient to express the amplitudes in terms of poles
+\begin{align*}
+    &A_4^{\mathrm{tree}}(1,2,3,4)\equiv\frac{n_s}{s}+\frac{n_t}{t},\\
+    &A_4^{\mathrm{tree}}(1,3,4,2)\equiv-\frac{n_u}{u}-\frac{n_s}{s},\\
+    &A_4^{\mathrm{tree}}(1,4,2,3)\equiv-\frac{n_t}{t}+\frac{n_u}{u}.
+\end{align*}
+the relative sign here is just a convention.
+\end{frame}
+\begin{frame}
+    Combining the two relation above gives the desired identity
+    \begin{equation*}
+        \alert{n_u=n_s-n_t}
+    \end{equation*}
+    this is exactly the same form of Jacobbi identity for the color factors.
+    The full amplitude can be written like
+\begin{equation*}
+    \mathcal{A}_4^{\mathrm{tree}}=g^2\left(\frac{n_sc_s}{s}+\frac{n_uc_u}{u}+\frac{n_tc_t}{t}\right)
+\end{equation*}
+\end{frame}
+\begin{frame}
+    For the five point case, an example is 
+    \begin{figure}[htb]
+        \centering
+        \includegraphics[width=1\linewidth]{FivePtTwist2.eps}
+    \end{figure}
+    we have the corresponding color factor Jacobbi identities like
+    \begin{equation*}
+        c_3=c_5-c_8
+    \end{equation*}
+    so we need to have the knematic analog
+    \begin{equation*}
+        n_3=n_5-n_8
+    \end{equation*}
+    The explict forms of all these factors can be found in the original paper \textbf{New relations for gauge theory amplituds, PRD 78, 085011}
+\end{frame}
+\begin{frame}
+    Full amplitudes of 5 points are
+    \begin{eqnarray*}
+        \mathcal {A}^\mathrm{tree}_5& = & 
+        g^3\Biggl( {n_1 c_1\over s_{12}s_{45}}+{n_2 c_2\over s_{23}s_{51}}
+        +{n_3 c_3 \over s_{34}s_{12}}+{n_4 c_4\over s_{45}s_{23}}
+        +{n_5 c_5\over s_{51}s_{34}} +{n_{6} c_6\over s_{14}s_{25}}  \\
+        &&\null \hskip .3 cm 
+        + {n_7 c_7\over s_{32}s_{14}}+{n_{8} c_8\over s_{25}s_{43}}
+        +{n_{9} c_9\over s_{13}s_{25}}+{n_{10} c_{10}\over s_{42}s_{13}}
+        +{n_{11} c_{11}\over s_{51}s_{42}}+ {n_{12} c_{12}\over s_{12}s_{35}}  \\
+        &&\null \hskip .3 cm 
+        +{n_{13} c_{13}\over s_{35}s_{24}} 
+        +{n_{14} c_{14}\over s_{14}s_{35}}
+        +{n_{15} c_{15}\over s_{13}s_{45}}\Biggr)\,,
+        \end{eqnarray*}
+    This relation had been proved upto 8 points at the time and I think it has been improved to arbitrary points.  
 \end{frame}
@@
     \end{align*}
-    because of the redundancy of 
+    because of the redundancy of $\mathrm{SL}(2,\mathbb{C})$, only $n-3$ of them are independent.
 \end{frame}
@@
     \end{block}
-    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{n-3} of the equtions are independent, so we can rewrite the scattering equations as following 
+    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following
     \begin{equation*}
@@
 \end{frame}
+\iffalse
 \begin{frame}{KLT Relation}
@@
 \end{frame}
+\fi
 \begin{frame}{KLT Orthogonality}
@@
 \begin{frame}{The form of measure}
-    It is worth to computed the measure explictly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 
+    It is worth to computed the measure explicitly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 
     \begin{equation*}
@@
     \\ \hspace*{\fill}\\
-    More explictly,
+    More explicitly,
 
@@
     \pause
-    More explictly, 
+    More explicitly, 
     \begin{equation*}
@@
 \end{frame}
+\begin{frame}
+    \frametitle{Color-Kinematics Duality again}
+    At the begining, I mentioned that sclar-, gluon- and graviton- amplitudes can be related by simple transformations ($C\to E$ or $\tilde{C}\to\tilde{E}$ or both).
+    More explicitly,
+    \begin{equation*}
+        {\cal M}^{(0)}_n =\!\!\sum_{I=1}^{(n-3)!}\frac{C(\sigma^{(I)}){\tilde C}(\sigma^{(I)})}{{\rm det}'\Phi(\sigma^{(I)})},\quad {\cal M}^{(1)}_n = \!\!\sum_{I=1}^{(n-3)!}\frac{C(\sigma^{(I)}){\tilde E}(\sigma^{(I)})}{{\rm det}'\Phi(\sigma^{(I)})},
+    \end{equation*}
+    \begin{equation*}
+        {\cal M}^{(2)}_n = \!\!\sum_{I=1}^{(n-3)!}\frac{E(\sigma^{(I)}){\tilde E}(\sigma^{(I)})}{{\rm det}'\Phi(\sigma^{(I)})}.
+    \end{equation*}
+    If we expand the color factor like 
+    \begin{equation*}
+        C=\sum_{\gamma\in S_{n-2}}\frac{{\bf c}_{1\gamma(2)\cdots\gamma(n-1)n}}{\sigma_{1,\gamma(2)}\cdots\sigma_{\gamma(n-1),n}\sigma_{n,1}},
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    It hints the exsitence of similar form for $E$. More explicitly, there must functions, denoted as $\boldsymbol{n}$, which depends only on kinematic data $\{\epsilon^{\mu}_a,k^\mu_a \}$
+    \begin{equation*}
+        E = {\rm Pf}'\Psi(\epsilon,k,\sigma ) = \sum_{\gamma\in S_{n-2}}\frac{{\bf n}_{1\gamma(2)\cdots\gamma(n-1)n}}{\sigma_{1,\gamma(2)}\cdots\sigma_{\gamma(n-1),n}\sigma_{n,1}}.
+    \end{equation*}
+    Now we can unify $\bf c$ and $\bf n$ as e in all three theories, the full amplitude can be written in a unified form
+    \begin{equation*}
+       \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
+    \end{equation*}
+    and the factor satisfies the "BCJ" relation
+    \begin{equation*}
+        e_{g_t}=\pm(e_{g_s}-e_{g_u})
+    \end{equation*}
+    If we contentate on pure Yang-Mills theory, the realtion is just the one we list in the first second section.
+\end{frame}
 \end{document}

### 2024-07-05 test/main.tex
New

@@
 \section{Why the S-matrix is so important?}
+\iffalse
 \begin{frame}
@@
     It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
+    Most of the developments before have made for particular theories like $\mathcal{N}=4$ Super Yang-Mills theory or $\mathcal{N}=8$ Supergravity,
+    but this paper gives some hints to the construction of amplitudes for theories with less or no supersymmetry.
 \end{frame}
+\fi
 \begin{frame}{}
+    \frametitle{Some developments of amplitudes}
     \begin{itemize}
@@
         \centering
-        \caption{Positive geometry}
-        \includegraphics[width=0.4\linewidth]{Grassmanian-Image.jpg}
+        \includegraphics[width=0.25\linewidth]{Grassmannian.png}
+        \caption{Positive Grassmanian}
     \end{figure}
@@
     \end{itemize}
-    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
+    where the OP means ordered permutaions, that is all permutations of $\left\{\alpha\right\}$$\bigcup$$\left\{\beta\right\}^T$
     that matains the order of individual elements of each set.

### 2024-07-09 test/main.tex
New

@@
 \usepackage{graphics}
+\usepackage{appendixnumberbeamer}
 \AtBeginSection[]{
@@
 \end{frame}
+\begin{frame}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da04992460244937069] 
+\draw    (116,79) -- (116.49,163) ;
+\draw [shift={(116.5,165)}, rotate = 269.67] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da7393833245286348] 
+\draw    (218,134) -- (343.5,134) ;
+\draw [shift={(345.5,134)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da6514784763465036] 
+\draw    (447,76) -- (447.49,160) ;
+\draw [shift={(447.5,162)}, rotate = 269.67] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da8109804852164224] 
+\draw    (257,265) -- (320.5,265) ;
+\draw [shift={(322.5,265)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (79,46) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Lagrangian}$};
+% Text Node
+\draw (86,178) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{S-matrix}$};
+% Text Node
+\draw (391,49.4) node [anchor=north west][inner sep=0.75pt]    {$\mathrm{Amplituhedron}$};
+% Text Node
+\draw (417,173) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{S-matrix}$};
+% Text Node
+\draw (94,256) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Positivity}$ of $\mathrm{geometry}$ };
+% Text Node
+\draw (339,255) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Unitarity}$ and $\mathrm{Localty}$};
+
+\end{tikzpicture}
+
+\end{frame}
+\iffalse
 \section{Review of some pertinent results}
@@
 \end{frame}
-
+\fi
+\section{CHY Formula}
+\begin{frame}
+    \frametitle{Motivation}
+    %Most of the developments of amplitudes before have made for some specific theories, like N=4 super yang-mills theory and N=8 supergravity.
+    %The natural question is that what is the space of all field theories whose tree level S-matrix can be expressed in a compact form? 
+    \begin{itemize}
+        \item Compact form of amplitudes for sclar, pure Yang-Mills and gravity theories in any spacetime dimension.
+        %The author introduce a compact form of tree level amplitudes for three different theories, colored scalar theory, pure Yang-Mills and Einstein gravity.
+        %The concrete form of this formula implies that there is a relation between these three theories, and it may give some new insights of the connection between gravity and gauge theory.
+        \item A special amplitude --- Double partial amplitude
+        %Because of the special color structure of this scalar theory, the authors proposed a easy method to compute all scalar tree amplitudes, and then pure Yang-Mills and gravity can also be done using similar methods.
+        \item BCJ double copy at tree level
+        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation. It may give some implications for the construcion of nonpermubative BCJ double copy.
+        \item Related to other theories, such as EYM, EM, NLSM and so on.
+        %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{Scattering equations}
+    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
+    \begin{equation*}
+        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
+    \end{equation*}
+
+    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
+    \begin{equation*}
+        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
+    \end{equation*}
+    and n-punctured Riemann sphere can be discribed by $SL(2,\mathbb{C})$ affine coordinates ${\sigma_1,\sigma_2,\ldots,\sigma_n}$, that is to say we have a equvilance relation
+    \begin{align*}
+        \{\sigma_1,\sigma_2,\ldots,\sigma_n\}\sim\{\psi(\sigma_1),\psi(\sigma_2),\ldots,\psi(\sigma_n)\},\\\psi(\sigma):=\frac{\alpha\sigma+\beta}{\gamma\sigma+\delta},\quad\alpha,\beta,\gamma,\delta\in\mathbb{C},\alpha\delta-\beta\gamma=1
+    \end{align*}
+    because of the redundancy of $\mathrm{SL}(2,\mathbb{C})$, only $n-3$ of them are independent.
+\end{frame}
+\begin{frame}
+    From this map, we can easily obtain the main ingredients of this report \\
+
+    \begin{block}{\textcolor{red}{Scattering equations}}
+        \begin{equation*}
+            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
+        \end{equation*}
+    \end{block}
+    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following
+    \begin{equation*}
+        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
+    \end{equation*}
+\end{frame}
+\iffalse
 \section{CHY Formula}
@@
 \end{frame}
-\iffalse
-\begin{frame}{KLT Relation}
-    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
-    \begin{table}[]
-        \resizebox{\textwidth}{!}{
-        \begin{tabular}{|l|l|l|l|l|}
-        \hline
-         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
-         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
-         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
-         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
-         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
-         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
-         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
-         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
-         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
-         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
-        \end{tabular}
-        }
-        \end{table}
-\end{frame}
 \fi
-\begin{frame}{KLT Orthogonality}
-    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
-    \begin{block}{Proposition 1}
-        \begin{equation*}
-            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
-        \end{equation*}
-    \end{block}
-
-\end{frame}
-\begin{frame}
-    First we need to define the Jacobian matrix associated to the scattering equations
-
-        \begin{equation*}
-            \boxed{
-            \label{jacobbi}
-            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
-            }
-        \end{equation*}
-    As mentioned above only n-3 of the scattering equations are independent so the matrix $\Phi$ has \alert{rank n-3}.
-(This matrix was first encountered in the gravity amplitudes constructed from gauge theory using KLT relation )
-\end{frame}
-\begin{frame}
-    Consider a generalization of $\Phi_{ab}$ 
-    \begin{equation*}
-        \Psi_{ab,a\neq b}\equiv\frac{s_{ab}}{(\sigma_a-\sigma_b)(\sigma_a^{\prime}-\sigma_b^{\prime})},\quad\Psi_{aa}\equiv-\sum_{c\neq a}\Psi_{ac}.
-    \end{equation*}
-    \begin{block}{Proposition 2}
-        \begin{equation*}
-            \operatorname{rank}\Psi(\{\sigma\},\{\sigma^{\prime}\})=\begin{cases}n-4, \{\sigma\}\neq\{\sigma^{\prime}\}\\n-3, \{\sigma\}=\{\sigma^{\prime}\}\end{cases}
-        \end{equation*}
-        $\sigma$ and $\sigma^\prime$ are assmused to be solutions to scattering equation.
-    \end{block}
-\end{frame}
-\begin{frame}{Prove of KLT orthogonality}
-    For the purpose of proving KLT orthogonality, we can construct a n! dimension vector for each solution
-    \begin{equation*}
-        \frac1{(\sigma_{\omega(1)}-\sigma_{\omega(2)})(\sigma_{\omega(2)}-\sigma_{\omega(3)})\cdots(\sigma_{\omega(n)}-\sigma_{\omega(1)})}
-    \end{equation*}
-    Not so obvious is the fact that we can fix the positon of 3 labels, which we choose 1,n-1,n, give rise to the KK relation and BCJ relation.
-    \\ \hspace*{\fill}\\
-    Now the vectors become (n-3)! dimension, and even aftering selecting three lables, we still have the freedom of where to put them. Here we only use two choices :
-    \begin{equation*}
-        \textcolor{red}{(1,\omega(2),\dots,\omega(n-2),n-1,n)\quad and \quad (1,\omega(2),\dots,\omega(n-2),n,n-1 )}
-    \end{equation*}
-\end{frame}
-\begin{frame}
-    The corresponding two vectors are 
-    \begin{align*}V(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_{n-1})(\sigma_{n-1}-\sigma_n)(\sigma_n-\sigma_1)},\\U(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_n)(\sigma_n-\sigma_{n-1})(\sigma_{n-1}-\sigma_1)}.
-    \end{align*}
-    In this language, we can construct a bilinear form 
-    \begin{equation*}
-        S[\alpha|\beta]=\prod^{n-2}_{i=2}\left(s_{1,\alpha_i}+\sum_{j=2}^{i-1}
-        \theta(\alpha(j),\alpha(i))_\beta s_{\alpha(j),\alpha(i)}\right)
-    \end{equation*}
-    where $\alpha,\beta\in S_{n-3}$,$\theta(i,j)_\beta=1$if the order of i,j is the same in both permutations 
-    $\alpha(2,3,\dots,n-2)$ and $\beta(2,3,\dots,n-2)$, and 0 otherwise.
-    S is usually called \alert{Momentum Kernel}.
-\end{frame}
-\begin{frame}
-    Given any two solutions of scatering equations,
-    \begin{equation*}
-        \{\sigma_1^{(i)},\sigma_2^{(i)},\dots,\sigma_n^{(i)}\}\quad and \quad \{\sigma_1^{(j)},\sigma_2^{(j)},\dots,\sigma_n^{(j)}\}
-    \end{equation*}
-    define two vectors, $V(\alpha)^{(i)}$ and $U(\beta)^{(j)}$, i,j are choices of solutions and $\alpha,\beta$ are the choices of permutaions,
-    the number of both is \alert{(n-3)!}.
-    \\ \hspace*{\fill}\\
-    A natural inner product can be defined as
-    \begin{equation*}
-        (i,j):=\sum_{\alpha,\beta\in S_{n-3}}V^{(i)}(\alpha)S[\alpha|\beta]U^{(j)}(\beta)
-    \end{equation*}
-    Knowing all definetions above, we can proceed to prove KLT orthogonality.
-\end{frame}
-\begin{frame}
-    The starting point is to notice that
-    \begin{equation*}
-        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
-    \end{equation*}
-    is clearly invariant under $SL(2,\mathbb{C})\times SL(2,\mathbb{C})$. Partially fixing both $SL(2,\mathbb{C})$
-    redundancies with convenient choice $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$
-    and define 
-    \begin{align*}
-            K_n(\{\sigma\},\{\sigma'\})\equiv\sum_{\alpha,\beta\in S_{n-3}}&\frac1{\sigma_{1,\alpha(2)}\ldots\sigma_{\alpha(n-3),\alpha(n-2)}}S[\alpha|\beta]\\
-            &\frac1{\sigma_{1,\beta(2)}^{\prime}\ldots\sigma_{\beta(n-3),\beta(n-2)}^{\prime}}
-    \end{align*}
-    The motivation for this definition is that $K_n$ appears in the numerator of KLT orthogonality.
-\end{frame}
-\begin{frame}
-    It is also convenient to define an auxiliary co-rank one $(n-2)\times(n-2)$ matrix $\psi^{(n)}$
-    \begin{equation*}
-        \psi_{ab,a\neq b}=\frac{s_{ab}}{\sigma_{ab}\sigma_{ab}^{\prime}},\quad\psi_{aa}=-\sum_{b\neq a}\psi_{ab},\quad a,b=1,\ldots,n{-}2
-    \end{equation*}
-    It can be proven that any $(n-3)\times(n-3)$ minors of $\psi^{(n)}$ are the same, and we denote such a minor as
-    ${\det}^\prime\psi^{(n)}$ , that is to say, the determinat of the matrix after removing any row and colum.
-    \begin{block}{Proposition 3}
-        The two functions defined above are identical up to a sign.
-        \begin{equation*}
-            K_n(\{\sigma\},\{\sigma'\})=(-1)^n{\det}^\prime\psi^{(n)}
-        \end{equation*}
-    \end{block}
-\end{frame}
-\begin{frame}
-    The final step is put all pieces together. With the choice  $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$,
-    we have 
-    \begin{equation*}
-        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}
-    \end{equation*}
-    In addition, one finds that the minor of $\psi$ obtained by removing the first row and colum is identical to 
-    that of $\Psi(\{\sigma\},\{\sigma^{\prime}\})$ after removing rows and colums $\{1,n-1,n\}$. We denote them respectively
-    $|\psi^{(n)}|^1_1$ and $|\Psi|^{1,n-1,n}_{1,n-1,n}$. Then,
-    \begin{align*}
-        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}&=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}\\
-        &=\frac{(-1)^n|\psi^{(n)}|^1_1}{{(-1)^n|\psi^{(n)}|^1_1}^{\frac{1}{2}}{|\psi^{(n)}|^1_1}^{\frac{1}{2}}}\\
-        &=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{(|\Psi(\{\sigma^{(i)},\sigma^{(i)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}(|\Psi(\{\sigma^{(j)}\},\{\sigma^{(j)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}}
-    \end{align*}
-\end{frame}
-\begin{frame}
-    Fianlly, we just need to use Proposition 2. 
-    \begin{itemize}
-        \item If $i=j$, the rank of matrix $\Psi$ is $n-3$ and the minor is nonzero, we obtain
-        \begin{equation*}
-            \frac{(i,i)}{(i,i)^{\frac12}(i,i)^{\frac12}}=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}=1
-        \end{equation*}
-        \item If $i\neq j$, the rank of matrix is $n-4$, so any minor with volume more than $n-4$ equals 0.
-        \begin{equation*}
-            |\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}=0\Rightarrow \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=0
-        \end{equation*}
-    \end{itemize}
-    Up to now, we conclude the proof of KLT orthogonality.
-\end{frame}
 \begin{frame}
     \frametitle{Attempt to construct S-matrix --- Towards CHY}
-    Thanks to the excellent properties of scattering equations, it is very tempting to propose that the solutions
-    to scattering equations should be used to construct scattering amplitudes.
-    \\ \hspace*{\fill}\\
+    %Thanks to the excellent properties of scattering equations, it is very tempting to propose that the solutions
+    %to scattering equations should be used to construct scattering amplitudes.
     The first two constructed are YM and gravity amplitudes in any dimensions
     \begin{align*}
-        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
-        M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
+        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
+        M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
     \end{align*}
@@
 \begin{frame}
-    The reason we extract 3 indices from delta equation is the fact that only $n-3$ scattering equations are independent.
-    This from can be proved to be \alert{independent of choice of $i,j,k$}, therefore permutaion invariant.
-    We also have
-    \begin{equation*}
-        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
-    \end{equation*}
-    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
-    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
-    \begin{equation*}
-        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
-    \end{equation*}
-\end{frame}
-\begin{frame}{The form of measure}
-    It is worth to computed the measure explicitly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 
-    \begin{equation*}
-        \int\prod_{c\neq p,q,r}d\sigma_c(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})\prod_{a\neq i,j,k}\delta\biggl(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\biggr)
-    \end{equation*}
-    The delta functions completely localize all integrals and the answer is evaluating a Jacobian defined above.
-    \begin{equation*}
-            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
-    \end{equation*}
-    Then, we obtain the measure
+    \frametitle{The form of measure}
+    The measure can be written like
     \begin{equation*}
@@
     \end{equation*}
-\end{frame}
-\begin{frame}
-    Always denoted by 
+    where the determinant is that of the following Jacobbi matrix
+    \begin{equation*}
+        \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
+    \end{equation*}
+    Usually we take the notation as following
     \begin{equation*}
@@
     \end{equation*}
-    $|\Phi|_{pqr}^{ijk}$ means that we need to delete the rows $\{i,j,k\}$ and the colums $\{p,q,r\}$, of course it is free to choose which inedex refers
-    to row or colum ($\Phi$ is a symmetric matrix).
-\end{frame}
-\begin{frame}
-    \frametitle{The form of $E_n(\{k,\epsilon,\sigma\})$}
+\end{frame}
+
+\begin{frame}
+    \frametitle{The form of integrand}
     In order to present the explict form of $E_n(\{k,\epsilon,\sigma\})$, first define the following $2n\times2n$ antisymmetric matrix 
@@
 \begin{frame}
-    The first important observation is that while the Pfaffian of $\Psi$ is 0, but after removing any rows $i,j$ and colums $i,j$
-    with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
+    %The first important observation is that while the Pfaffian of $\Psi$ is 0, but after removing any rows $i,j$ and colums $i,j$
+    %with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
+    The Pfaffian of $\Psi$ is 0, but aftering removing any two rows and colums $i,j$ with $1\leq i< j\leq n$, 
+    the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as
     \begin{equation*}
@@
     \begin{equation*}
-        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
-    \end{equation*}
-    And using the KLT constrution, we can construct the formula for tree-level S-matrix of gravity as double copy of that of Yang-Mills
-    \begin{equation*}
-        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
+    \end{equation*}
+    and gravity amplitudes by using KLT construcion
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
     \end{equation*}
@@
         \end{equation*}
-        It is easy to discover that the $i$th and $i+n$th colums become identical, so the determinat and Pfaffian become 0.
+        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat and Pfaffian become 0.
         \pause
-        \item \alert{Soft limit}
+        \item \alert{Soft limit}\\
         Using a special property of Pfaffian
@@
     \\ \hspace*{\fill}\\
-    Here we would like to consider that the formula above is not only a convenient way to write Yang-Mills and gravity amplitudes, but can be \alert{a definition of S-matrix
-    for spin s particles}.This means that 
+    \begin{equation*}
+        \mathcal{M}^{(s)} \text{ as \alert{definition of S-matrix for spin s particles}}
+    \end{equation*}
     \begin{equation*}
@@
 \begin{frame}
-    In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
+    %In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
+    The general case is that we can choose different polariazation vector like 
     \begin{equation*}
@@
     We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way
+
+    %\begin{itemize}
+    %    \item First step, draw a disk with n nodes sitting on the boundary in the ordering $\alpha$, then link the n nodes with a loop of line segments according to
+    %          the ording $\beta$. The line segments from $\beta$ split the disk into some polygons, like the graph (b). We need to move the external points of every polygon
+    %          to make them have no common edges, like graph (c).
+    %    \item Second step, put a point in every polygon, named equivalant vertex, and connect this point to all external points in corresponding area. Lines that connect equivalent 
+    %          vertices in two regions with common vertices are called equivalent propagators. The resulting graph is an equivalent Feynman diagram, as shown in Figure (d).
+    %\end{itemize}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\linewidth]{7.png}
+    \end{figure}
+    In this example, we can obtain 
+    \begin{equation*}
+        m_8^{(0)}(I|54376218)=(-1)^?\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
+    \end{equation*}
+    As for the indefinite sign, there is also a procedure to determine it.
+
+\end{frame}
+
+\begin{frame}
+
+    %\begin{itemize}
+    %    \item Third step, we can read off the corresponding amplitudes from the equivalent Feynman diagram. 
+    %\end{itemize}
+    %\begin{itemize}
+    %\item First step, determine the orientation of the disk by ordering $\alpha$, and define the loop segments by ordering $\beta$, which also determine the orientation of every polygon.
+    %    \item Second step, (1) each polygon with odd number vertices contributes a plus sign if the orientation is the same as disk, and a minus sign oppositely;
+    %          (2) each polygon with even number vertices contribute a minus sign; (3) each intersection point contributes a minus sign.
+    %\end{itemize}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\linewidth]{6.png}
+    \end{figure}
+    The final answer is that
+    \begin{equation*}
+        m_8^{(0)}(I|54376218)=(-1)^6\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
+    \end{equation*}
+\end{frame}
+\section{Conclusion and Outlook}
+
+\section{Appendix}
+\begin{frame}{KLT Relation}
+    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
+    \begin{table}[]
+        \resizebox{\textwidth}{!}{
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
+         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
+         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
+         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
+         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
+         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
+         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
+         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
+         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
+         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
+        \end{tabular}
+        }
+        \end{table}
+\end{frame}
+
+\appendix
+\begin{frame}{KLT Orthogonality}
+    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
+    \begin{block}{Proposition 1}
+        \begin{equation*}
+            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
+        \end{equation*}
+    \end{block}
+
+\end{frame}
+\begin{frame}
+    First we need to define the Jacobian matrix associated to the scattering equations
+
+        \begin{equation*}
+            \boxed{
+            \label{jacobbi}
+            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
+            }
+        \end{equation*}
+    As mentioned above only n-3 of the scattering equations are independent so the matrix $\Phi$ has \alert{rank n-3}.
+(This matrix was first encountered in the gravity amplitudes constructed from gauge theory using KLT relation )
+\end{frame}
+\begin{frame}
+    Consider a generalization of $\Phi_{ab}$ 
+    \begin{equation*}
+        \Psi_{ab,a\neq b}\equiv\frac{s_{ab}}{(\sigma_a-\sigma_b)(\sigma_a^{\prime}-\sigma_b^{\prime})},\quad\Psi_{aa}\equiv-\sum_{c\neq a}\Psi_{ac}.
+    \end{equation*}
+    \begin{block}{Proposition 2}
+        \begin{equation*}
+            \operatorname{rank}\Psi(\{\sigma\},\{\sigma^{\prime}\})=\begin{cases}n-4, \{\sigma\}\neq\{\sigma^{\prime}\}\\n-3, \{\sigma\}=\{\sigma^{\prime}\}\end{cases}
+        \end{equation*}
+        $\sigma$ and $\sigma^\prime$ are assmused to be solutions to scattering equation.
+    \end{block}
+\end{frame}
+\begin{frame}{Prove of KLT orthogonality}
+    For the purpose of proving KLT orthogonality, we can construct a n! dimension vector for each solution
+    \begin{equation*}
+        \frac1{(\sigma_{\omega(1)}-\sigma_{\omega(2)})(\sigma_{\omega(2)}-\sigma_{\omega(3)})\cdots(\sigma_{\omega(n)}-\sigma_{\omega(1)})}
+    \end{equation*}
+    Not so obvious is the fact that we can fix the positon of 3 labels, which we choose 1,n-1,n, give rise to the KK relation and BCJ relation.
+    \\ \hspace*{\fill}\\
+    Now the vectors become (n-3)! dimension, and even aftering selecting three lables, we still have the freedom of where to put them. Here we only use two choices :
+    \begin{equation*}
+        \textcolor{red}{(1,\omega(2),\dots,\omega(n-2),n-1,n)\quad and \quad (1,\omega(2),\dots,\omega(n-2),n,n-1 )}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    The corresponding two vectors are 
+    \begin{align*}V(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_{n-1})(\sigma_{n-1}-\sigma_n)(\sigma_n-\sigma_1)},\\U(\omega)&=\frac1{(\sigma_1-\sigma_{\omega(2)})\cdots(\sigma_{\omega(n-2)}-\sigma_n)(\sigma_n-\sigma_{n-1})(\sigma_{n-1}-\sigma_1)}.
+    \end{align*}
+    In this language, we can construct a bilinear form 
+    \begin{equation*}
+        S[\alpha|\beta]=\prod^{n-2}_{i=2}\left(s_{1,\alpha_i}+\sum_{j=2}^{i-1}
+        \theta(\alpha(j),\alpha(i))_\beta s_{\alpha(j),\alpha(i)}\right)
+    \end{equation*}
+    where $\alpha,\beta\in S_{n-3}$,$\theta(i,j)_\beta=1$if the order of i,j is the same in both permutations 
+    $\alpha(2,3,\dots,n-2)$ and $\beta(2,3,\dots,n-2)$, and 0 otherwise.
+    S is usually called \alert{Momentum Kernel}.
+\end{frame}
+\begin{frame}
+    Given any two solutions of scatering equations,
+    \begin{equation*}
+        \{\sigma_1^{(i)},\sigma_2^{(i)},\dots,\sigma_n^{(i)}\}\quad and \quad \{\sigma_1^{(j)},\sigma_2^{(j)},\dots,\sigma_n^{(j)}\}
+    \end{equation*}
+    define two vectors, $V(\alpha)^{(i)}$ and $U(\beta)^{(j)}$, i,j are choices of solutions and $\alpha,\beta$ are the choices of permutaions,
+    the number of both is \alert{(n-3)!}.
+    \\ \hspace*{\fill}\\
+    A natural inner product can be defined as
+    \begin{equation*}
+        (i,j):=\sum_{\alpha,\beta\in S_{n-3}}V^{(i)}(\alpha)S[\alpha|\beta]U^{(j)}(\beta)
+    \end{equation*}
+    Knowing all definetions above, we can proceed to prove KLT orthogonality.
+\end{frame}
+\begin{frame}
+    The starting point is to notice that
+    \begin{equation*}
+        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
+    \end{equation*}
+    is clearly invariant under $SL(2,\mathbb{C})\times SL(2,\mathbb{C})$. Partially fixing both $SL(2,\mathbb{C})$
+    redundancies with convenient choice $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$
+    and define 
+    \begin{align*}
+            K_n(\{\sigma\},\{\sigma'\})\equiv\sum_{\alpha,\beta\in S_{n-3}}&\frac1{\sigma_{1,\alpha(2)}\ldots\sigma_{\alpha(n-3),\alpha(n-2)}}S[\alpha|\beta]\\
+            &\frac1{\sigma_{1,\beta(2)}^{\prime}\ldots\sigma_{\beta(n-3),\beta(n-2)}^{\prime}}
+    \end{align*}
+    The motivation for this definition is that $K_n$ appears in the numerator of KLT orthogonality.
+\end{frame}
+\begin{frame}
+    It is also convenient to define an auxiliary co-rank one $(n-2)\times(n-2)$ matrix $\psi^{(n)}$
+    \begin{equation*}
+        \psi_{ab,a\neq b}=\frac{s_{ab}}{\sigma_{ab}\sigma_{ab}^{\prime}},\quad\psi_{aa}=-\sum_{b\neq a}\psi_{ab},\quad a,b=1,\ldots,n{-}2
+    \end{equation*}
+    It can be proven that any $(n-3)\times(n-3)$ minors of $\psi^{(n)}$ are the same, and we denote such a minor as
+    ${\det}^\prime\psi^{(n)}$ , that is to say, the determinat of the matrix after removing any row and colum.
+    \begin{block}{Proposition 3}
+        The two functions defined above are identical up to a sign.
+        \begin{equation*}
+            K_n(\{\sigma\},\{\sigma'\})=(-1)^n{\det}^\prime\psi^{(n)}
+        \end{equation*}
+    \end{block}
+\end{frame}
+\begin{frame}
+    The final step is put all pieces together. With the choice  $\sigma_{n-1}^{(i)}=\sigma_n^{(j)}=\infty$ and $\sigma_n^{(i)}=\sigma_{n-1}^{(j)}=1$,
+    we have 
+    \begin{equation*}
+        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}
+    \end{equation*}
+    In addition, one finds that the minor of $\psi$ obtained by removing the first row and colum is identical to 
+    that of $\Psi(\{\sigma\},\{\sigma^{\prime}\})$ after removing rows and colums $\{1,n-1,n\}$. We denote them respectively
+    $|\psi^{(n)}|^1_1$ and $|\Psi|^{1,n-1,n}_{1,n-1,n}$. Then,
+    \begin{align*}
+        \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}&=\frac{K_n(\{\sigma^{(i)}\},\{\sigma^{(j)}\})}{K_n^{\frac12}(\{\sigma^{(i)}\},\{\sigma^{(i)}\})K_n^{\frac12}(\{\sigma^{(j)}\},\{\sigma^{(j)}\})}\\
+        &=\frac{(-1)^n|\psi^{(n)}|^1_1}{{(-1)^n|\psi^{(n)}|^1_1}^{\frac{1}{2}}{|\psi^{(n)}|^1_1}^{\frac{1}{2}}}\\
+        &=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{(|\Psi(\{\sigma^{(i)},\sigma^{(i)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}(|\Psi(\{\sigma^{(j)}\},\{\sigma^{(j)}\}|_{1,n-1,n}^{1,n-1,n})^{\frac12}}
+    \end{align*}
+\end{frame}
+\begin{frame}
+    Fianlly, we just need to use Proposition 2. 
+    \begin{itemize}
+        \item If $i=j$, the rank of matrix $\Psi$ is $n-3$ and the minor is nonzero, we obtain
+        \begin{equation*}
+            \frac{(i,i)}{(i,i)^{\frac12}(i,i)^{\frac12}}=\frac{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}{|\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}}=1
+        \end{equation*}
+        \item If $i\neq j$, the rank of matrix is $n-4$, so any minor with volume more than $n-4$ equals 0.
+        \begin{equation*}
+            |\Psi(\{\sigma^{(i)}\},\{\sigma^{(j)}\})|_{1,n-1,n}^{1,n-1,n}=0\Rightarrow \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=0
+        \end{equation*}
+    \end{itemize}
+    Up to now, we conclude the proof of KLT orthogonality.
+\end{frame}
+\begin{frame}
+    \frametitle{Attempt to construct S-matrix --- Towards CHY}
+    Thanks to the excellent properties of scattering equations, it is very tempting to propose that the solutions
+    to scattering equations should be used to construct scattering amplitudes.
+    \\ \hspace*{\fill}\\
+    The first two constructed are YM and gravity amplitudes in any dimensions
+    \begin{align*}
+        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
+        M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\text{vol SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
+    \end{align*}
+    The measure is defined as following
+    \begin{equation*}
+        \prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}{:}=\sigma_{ij}\sigma_{jk}\sigma_{ki}\prod_{a\neq i,j,k}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    The reason we extract 3 indices from delta equation is the fact that only $n-3$ scattering equations are independent.
+    This from can be proved to be \alert{independent of choice of $i,j,k$}, therefore permutaion invariant.
+    We also have
+    \begin{equation*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
+    \end{equation*}
+    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
+    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
+    \begin{equation*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
+    \end{equation*}
+\end{frame}
+\begin{frame}{The form of measure}
+    It is worth to computed the measure explicitly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 
+    \begin{equation*}
+        \int\prod_{c\neq p,q,r}d\sigma_c(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})\prod_{a\neq i,j,k}\delta\biggl(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\biggr)
+    \end{equation*}
+    The delta functions completely localize all integrals and the answer is evaluating a Jacobian defined above.
+    \begin{equation*}
+            \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
+    \end{equation*}
+    Then, we obtain the measure
+    \begin{equation*}
+            \boxed{
+            \sum_{\{\sigma\}\in\mathrm{solutions}}\frac{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}{|\Phi|_{pqr}^{ijk}}}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    Always denoted by 
+    \begin{equation*}
+        \boxed{
+        \det{'}\Phi:=\frac{|\Phi|_{pqr}^{ijk}}{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}}
+    \end{equation*}
+    $|\Phi|_{pqr}^{ijk}$ means that we need to delete the rows $\{i,j,k\}$ and the colums $\{p,q,r\}$, of course it is free to choose which inedex refers
+    to row or colum ($\Phi$ is a symmetric matrix).
+\end{frame}
+\begin{frame}
+    \frametitle{The form of $E_n(\{k,\epsilon,\sigma\})$}
+    In order to present the explict form of $E_n(\{k,\epsilon,\sigma\})$, first define the following $2n\times2n$ antisymmetric matrix 
+    \begin{equation*}
+        \Psi=\begin{pmatrix}
+            A & -C^T \\
+            C & B 
+        \end{pmatrix}
+    \end{equation*}
+    where $A,B$ and $C$ are $n\times n$ matrices, defined as 
+    \begin{equation*}
+        A_{ab}=\begin{cases}\frac{s_{ab}}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b,\end{cases} \quad 
+        B_{ab}=\begin{cases}\frac{\epsilon_a \cdot \epsilon_b}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b, \end{cases} \quad
+    \end{equation*}
+    \begin{equation*}
+        C_{ab}=\begin{cases}\frac{\epsilon_a\cdot k_b}{\sigma_a-\sigma_b}&a\neq b,\\-\sum_{c\neq a}\frac{\epsilon_a\cdot k_c}{\sigma_a-\sigma_c}&a\neq b.\end{cases}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    The first important observation is that while the Pfaffian of $\Psi$ is 0, but after removing any rows $i,j$ and colums $i,j$
+    with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
+    \begin{equation*}
+            \boxed{
+            \mathrm{Pf}^{\prime}\Psi:=\frac{(-1)^{i+j}}{(\sigma_i-\sigma_j)}\mathrm{Pf}(\Psi_{ij}^{ij})}
+    \end{equation*}
+    It can be proved that the reduced Pfaffian is invariant under permutaion of \alert{particle labels}.
+
+    \begin{alertblock}{Pfaffian}
+        Pfaffian is defined for antisymmetric matrix, usually in two ways as following
+        \begin{itemize}
+            \item \begin{equation*}
+                \mathrm{Pf}(A)^2=\det A
+            \end{equation*}
+            \item \begin{equation*}
+                \mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}
+            \end{equation*}
+        \end{itemize}
+    \end{alertblock}
+\end{frame}
+\begin{frame}
+    Write down the proposal
+    \alert{
+    \begin{equation*}
+        E_n(\{k,\epsilon,\sigma\})=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)
+    \end{equation*}}
+    Combine the measure and integrand, we conclude the formula for the tree-level S-matrix of Yang-Mills in any dimension
+    \begin{equation*}
+        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
+    \end{equation*}
+    And using the KLT constrution, we can construct the formula for tree-level S-matrix of gravity as double copy of that of Yang-Mills
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    We can also write the amplitude in another form
+    \begin{equation*}
+        M_n^{\mathrm{YM}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{1}{\sigma_{12}\cdots\sigma_{n1}}\frac{\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    \begin{equation*}
+        M_n^{\mathrm{gravity}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{\det{'}\Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
+    \end{equation*}
+    where we use the property of Pfaffian $\det{'}\Psi(k,\epsilon,\sigma)=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$\\$\times \mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$.
+\end{frame}
+\begin{frame}
+    \frametitle{Consistency check}
+    \begin{itemize}
+        \item \alert{Gauge invariance}\\
+        If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
+        \begin{equation*}
+            C_{ii}=-\sum_{c\neq i}\frac{\epsilon_i\cdot k_c}{\sigma_i-\sigma_c} \to -\sum_{c\neq i}\frac{k_i\cdot k_c}{\sigma_i-\sigma_c}=0
+        \end{equation*}
+        It is easy to discover that the $i$th and $i+n$th colums become identical, so the determinat and Pfaffian become 0.
+        \pause
+        \item \alert{Soft limit}
+        Using a special property of Pfaffian
+        \begin{equation*}
+            \mathrm{Pf} (E)=\sum_{q=1}^{2n}(-1)^q e_{pq}\mathrm{Pf}(E^{pq}_{pq})
+        \end{equation*}
+        we find the amplitude in the soft limit is 
+        \begin{equation*}
+            A_n\to\left(\frac{\epsilon_n\cdot k_{n-1}}{k_n\cdot k_{n-1}}+\frac{\epsilon_n\cdot k_1}{k_n\cdot k_1}\right)A_{n-1}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{CHY form of amplitudes}
+    Both formulas above can be written in this simplest form 
+    \alert{
+        \begin{equation*}
+            \!\!\!\!\mathcal{M}^{(s)}\!=\!\!\!\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)
+            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}{(\mathrm{Pf}^\prime\Psi)}^s
+        \end{equation*}}
+    with $s=1$ for Yang-Mills and $s=2$ for gravity.
+    \\ \hspace*{\fill}\\
+    Here we would like to consider that the formula above is not only a convenient way to write Yang-Mills and gravity amplitudes, but can be \alert{a definition of S-matrix
+    for spin s particles}.This means that 
+    \begin{equation*}
+        s=0\quad\to \quad \text{a corresponding scalar theory}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
+    \begin{equation*}
+        \left(\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\right)^2\to\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\mathrm{Pf}^\prime \Psi(k,\tilde{\epsilon},\sigma)
+    \end{equation*}
+    actually it gives amplitudes with gravitons coupled to dilatons and B-fields.
+    \\ \hspace*{\fill}\\
+    For the case $s=0$, the similar consequence is 
+    \begin{equation*}
+        \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)^2\to\left(\frac{\mathrm{Tr}(T^{a_1}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
+        \left(\frac{\mathrm{Tr}(\tilde{T}^{b_1}\dots \tilde{T}^{b_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
+    \end{equation*}
+    while the original color group is $U(N)$, the new factors are the product of two different color group \alert{$U(N)\times U(\tilde{N})$}.
+\end{frame}
+\begin{frame}
+    The simplest possibility is the theory with only cubic interaction
+    \begin{equation*}
+        -f_{abc}\tilde{f}_{a^\prime b^\prime c^\prime}\phi^{aa^\prime}\phi^{bb^\prime}\phi^{cc^\prime}
+    \end{equation*}
+    All of above leads to the conclusion that the factors 
+    \begin{equation*}
+        \mathcal{C}_{U(N)}\equiv \sum_{\sigma\in S_n/Z_n}\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)
+    \end{equation*}
+    are interchangeable and this is a color-Kinematics corresopondence which is valid for individual solutions to scattering equations.
+
+\end{frame}
+
+\begin{frame}
+    The connection of amplitudes between 3 theories can be described by the following diagram 
+    \begin{figure}[htb]
+        \centering
+        \includegraphics[width=1\linewidth]{main.png}
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \frametitle{Double partial amplitudes}
+    Because there are two color indices in this sclar theory, so it can be anticipateed that the amplitude
+    have double trace decomposition structure
+    \begin{align*}
+        \mathcal{M}_n^{(0)}&=\sum_{\alpha\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})M_n^{(0)}(\alpha(1),\alpha(2),\ldots,\alpha(n))\\
+        &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\text{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
+        &\times \alert{m_n^{(0)}(\alpha|\beta)}
+    \end{align*} 
+    where the last term $m_n^{(0)}(\alpha|\beta)$ is called \alert{double partial amplitude} and can be read off from the full amplitude
+    \begin{align*}
+    m_{n}^{(0)}(\alpha|\beta)&=\int\frac{d^{n}\sigma}{\operatorname{vol}\operatorname{SL}(2,\mathbb{C})}\frac{\prod_{a}{}^{\prime}\delta(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}})}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}\\
+    =&\sum_{\{\sigma\}\in\mathrm{solutions}}\frac1{\det^{\prime}\Phi}\frac{1}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}
+    \end{align*}
+
+\end{frame}
+\begin{frame}
+    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
+    \begin{equation*}
+        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
+    \end{equation*}
+    where $\alpha \in S_{n-2}$. The amplitude is 
+    \begin{equation*}
+        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    \frametitle{Examples}
+    \begin{itemize}
+        \item The simplest example is the 3 point case
+        \begin{equation*}
+            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
+        \end{equation*}
+        It actually gives the correct answer.
+        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
+        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
+        \begin{equation*}
+            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
+        \end{equation*}
+        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \begin{align*}
+        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
+        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
+        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
+    \end{align*}
+    \quad \quad as expected for a color-dressed cubic theory.
+    \begin{itemize}
+        \item For the five point, I just give the results of some double partial amplitudes.
+        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
+        \begin{equation*}
+            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
+                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \begin{align*}
+        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_4)=-\frac{1}{s_{34}s_{51}},\\
+        &m_5^{(0)}(I|P_5)=0
+    \end{align*}
+    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
+    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
+    \\ \hspace*{\fill}\\
+    More explicitly,
+
+    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+    %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+    %Straight Lines [id:da8455657796938298] 
+    \draw    (179.5,110) -- (212.5,142) ;
+    %Straight Lines [id:da5324594211620186] 
+    \draw    (212.5,142) -- (182.5,170) ;
+    %Straight Lines [id:da4643902351443361] 
+    \draw    (212.5,142) -- (254.5,142) ;
+    %Straight Lines [id:da8904360433186445] 
+    \draw    (280.5,111) -- (254.5,142) ;
+    %Straight Lines [id:da18000644921445508] 
+    \draw    (254.5,142) -- (281.5,171) ;
+    %Straight Lines [id:da29602344087941934] 
+    \draw    (320.5,109) -- (353.5,141) ;
+    %Straight Lines [id:da9975053882839713] 
+    \draw    (353.5,141) -- (323.5,169) ;
+    %Straight Lines [id:da5157442319090852] 
+    \draw    (353.5,141) -- (395.5,141) ;
+    %Straight Lines [id:da049884375007126946] 
+    \draw    (421.5,110) -- (395.5,141) ;
+    %Straight Lines [id:da9299487354359295] 
+    \draw    (395.5,141) -- (422.5,170) ;
+
+    % Text Node
+    \draw (111,135.4) node [anchor=north west][inner sep=0.75pt]    {$m_{4}^{(0)}(I,I) =$};
+    % Text Node
+    \draw (184.5,173) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (184.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (264.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (263.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (298,133.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (325.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (325.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (405.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (404.5,171) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+
+    \end{tikzpicture}
+
+\end{frame}
+\begin{frame}
+    Similarly,
+
+    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+    %uncomment if require: \path (0,350); %set diagram left start at 0, and has height of 350
+
+    %Straight Lines [id:da8963901965951664] 
+    \draw    (84,71) -- (108,93) ;
+    %Straight Lines [id:da07470927432540231] 
+    \draw    (108,93) -- (136,93) ;
+    %Straight Lines [id:da12245379377221366] 
+    \draw    (108,93) -- (85,111) ;
+    %Straight Lines [id:da6511432990080723] 
+    \draw    (136,93) -- (161,114) ;
+    %Straight Lines [id:da1430135957918477] 
+    \draw    (157,71) -- (136,93) ;
+    %Straight Lines [id:da8765002291973463] 
+    \draw    (157,71) -- (158,47) ;
+    %Straight Lines [id:da9623971067643409] 
+    \draw    (157,71) -- (178,87) ;
+    %Straight Lines [id:da5561877649988292] 
+    \draw    (214,70) -- (238,92) ;
+    %Straight Lines [id:da44100018812085007] 
+    \draw    (238,92) -- (266,92) ;
+    %Straight Lines [id:da05824517478761182] 
+    \draw    (238,92) -- (215,110) ;
+    %Straight Lines [id:da35334338456014613] 
+    \draw    (266,92) -- (291,113) ;
+    %Straight Lines [id:da9313767826880515] 
+    \draw    (287,70) -- (266,92) ;
+    %Straight Lines [id:da696534040519218] 
+    \draw    (287,70) -- (288,46) ;
+    %Straight Lines [id:da5526828548209644] 
+    \draw    (287,70) -- (308,86) ;
+    %Straight Lines [id:da19124382298581288] 
+    \draw    (359,64) -- (383,86) ;
+    %Straight Lines [id:da5237814153432139] 
+    \draw    (383,86) -- (411,86) ;
+    %Straight Lines [id:da7974585866426673] 
+    \draw    (383,86) -- (360,104) ;
+    %Straight Lines [id:da46316924534551385] 
+    \draw    (411,86) -- (436,107) ;
+    %Straight Lines [id:da37617479030606993] 
+    \draw    (432,64) -- (411,86) ;
+    %Straight Lines [id:da9834219129393018] 
+    \draw    (432,64) -- (433,40) ;
+    %Straight Lines [id:da7117622111604034] 
+    \draw    (432,64) -- (453,80) ;
+    %Straight Lines [id:da8760088009181417] 
+    \draw    (82,171) -- (106,193) ;
+    %Straight Lines [id:da7078786925271212] 
+    \draw    (106,193) -- (134,193) ;
+    %Straight Lines [id:da5389180018159456] 
+    \draw    (106,193) -- (83,211) ;
+    %Straight Lines [id:da26578622720899636] 
+    \draw    (134,193) -- (159,214) ;
+    %Straight Lines [id:da5989066756692625] 
+    \draw    (155,171) -- (134,193) ;
+    %Straight Lines [id:da13747441694892726] 
+    \draw    (155,171) -- (156,147) ;
+    %Straight Lines [id:da4119117050779677] 
+    \draw    (155,171) -- (176,187) ;
+    %Straight Lines [id:da5379584617019675] 
+    \draw    (221,169) -- (245,191) ;
+    %Straight Lines [id:da788296500370655] 
+    \draw    (245,191) -- (273,191) ;
+    %Straight Lines [id:da4136462405421193] 
+    \draw    (245,191) -- (222,209) ;
+    %Straight Lines [id:da37414431568833373] 
+    \draw    (273,191) -- (298,212) ;
+    %Straight Lines [id:da8232480161298765] 
+    \draw    (294,169) -- (273,191) ;
+    %Straight Lines [id:da7983669347123197] 
+    \draw    (294,169) -- (295,145) ;
+    %Straight Lines [id:da7903324165137171] 
+    \draw    (294,169) -- (315,185) ;
+
+    % Text Node
+    \draw (5,76.4) node [anchor=north west][inner sep=0.75pt]    {$m_{5}( I,I) =$};
+    % Text Node
+    \draw (87,114) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (86,68) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (159.5,56) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (180,84) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (163,111) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (198,73.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (217,113) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (216,67) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (289.5,55) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (310,83) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (293,110) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (335,72.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (362,107) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (361,61) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (434.5,49) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (455,77) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (438,104) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (65,184.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (85,214) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (84,168) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (157.5,156) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (178,184) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (161,211) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (201,181.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
+    % Text Node
+    \draw (224,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {5};
+    % Text Node
+    \draw (226,172) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (296.5,154) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (317,182) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
+    % Text Node
+    \draw (300,209) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
+
+    \end{tikzpicture}
+\end{frame}
+\begin{frame}
+    \frametitle{Trivalent graph expansion}
+    \begin{alertblock}{Proposition}
+        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
+    \end{alertblock}
+    \pause
+    More explicitly, 
+    \begin{equation*}
+        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
+\end{equation*}
+where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
+$\beta$ ordering respectively. To make this expression more clear, see the following diagram
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{5.png}
+\end{figure}
+\end{frame}
+\begin{frame}
+    We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way
     \begin{itemize}

### 2024-07-09 test/main.tex
New

@@
         \end{equation*}
-        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat and Pfaffian become 0.
+        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat and Pfaffian becomes 0.
         \pause
@@
 \section{Conclusion and Outlook}
+\begin{frame}
+    \begin{itemize}
+        \item A compact form of tree-level S-matrix in 3 different theories are introduced
+            \begin{equation*}
+                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
+             \end{equation*}
+        \item The computaion method for double partial amplitudes are given 
+            \begin{equation*}
+                    m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}
+            \end{equation*}
+        \item The CK duality and BCJ double-copy relation can be easily obtained
+            \begin{equation*}
+                e_{g_t}=\pm(e_{g_s}-e_{g_u})
+            \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{Connection between other theories}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{9.png}
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\linewidth]{4.png}
+    \end{figure}
+\end{frame}
 

### 2024-07-16 test/main.tex
New

@@
         %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
+        \item One-loop corrections to scattering amplitudes of scalars and gauge bosons can be obtained from tree amplitudes in one higher dimension. 
     \end{itemize}
@@
     \end{align*}
+    \pause
     The measure is defined as following
@@
     \frametitle{The form of measure}
-    The measure can be written like
+    The measure can be written like %the n-3 integral can be completely determined by n-3 delta function
     \begin{equation*}
@@
     \end{equation*}
+    \pause
     Usually we take the notation as following
@@
     It can be proved that the reduced Pfaffian is invariant under permutaion of \alert{particle labels}.
-
+    \pause
     \begin{alertblock}{Pfaffian}
@@
     \\ \hspace*{\fill}\\
+    \pause
     \begin{equation*}

### 2024-07-16 test/main.tex
New

@@
 \frame{\titlepage}
+\begin{frame}
+    This report is mainly based on the following works
+    \begin{itemize}
+        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1306.6575
+        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1307.2199
+        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1309.0885
+        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1412.3479
+        \item Z. Bern, J.J.M. Carrasco, H. Johansson, arxiv: 0805.3993
+    \end{itemize}
+\end{frame}
 
 \section{Why the S-matrix is so important?}
+
+\begin{frame}
+    \Large \alert{Scattering amplitude is one of the most important concepts in QFT}
+    \begin{itemize}
+        \pause
+        \item It is the bridge connecting experimental data and theoretical prediction.
+        \pause
+        \item It reveals various properties of theory, such as Lorentz symmetry, localty and unitarity.
+        \pause
+        \item Some recent work show that scattering amplitude contains many interesting mathematical structures.
+              Actually, this report introduces one of these structures.
+    \end{itemize}
+\end{frame}
 \iffalse
 \begin{frame}
-    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
+    I would like to emphasize two of them, BCFW recursion relations and Amplituhedron.
+    \bullet Generally, we would like to consider the scalar theory as the most basic theory in the Quantum field theory. But according to the BCFW, we
+            know that amplitudes in sclar theory can not be constructed recursively, but that of more complicated theory --- Yang-Mills, can be completely
+            constructed from 3 point amplitudes. So it may give us some new understandings of field theory.
+
+    \bullet It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
     unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
@@
     It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
-    Most of the developments before have made for particular theories like $\mathcal{N}=4$ Super Yang-Mills theory or $\mathcal{N}=8$ Supergravity,
+
+    \bullet Most of the developments before have made for particular theories like $\mathcal{N}=4$ Super Yang-Mills theory or $\mathcal{N}=8$ Supergravity,
     but this paper gives some hints to the construction of amplitudes for theories with less or no supersymmetry.
@@
         \item Generalized unitarity
-        \item Positive geometry and Amplituhedra.
+        \item Positive geometry and Amplituhedron.
         \item \dots
@@
 \end{frame}
-\iffalse
-\section{Review of some pertinent results}
-\begin{frame}{Gauge theory color structure}
-    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
-decomposed as
-\textcolor{red}{\begin{equation*}
-    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
-    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
-\end{equation*}}
-
-here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
-Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
-\end{frame}
-\begin{frame}
-    Color-ordered partial amplitudes satisfy a set of well-known properties,
-    \begin{itemize}
-        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
-        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
-        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
-        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
-        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
-    \end{itemize}
-    where the OP means ordered permutaions, that is all permutations of $\left\{\alpha\right\}$$\bigcup$$\left\{\beta\right\}^T$
-    that matains the order of individual elements of each set.
-\end{frame}
-\begin{frame}
-    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
-\begin{equation*}
-    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
-\end{equation*}
-The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
-\\ \hspace*{\fill}\\
-This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
-\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
-basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
-\end{frame}
-\begin{frame}{A Similar Structure}
-    It can be proved that tree level amplitudes can also be decomposed like 
-\begin{equation*}
-    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
-\end{equation*}
-The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
-\end{frame}
-\begin{frame}
-    \begin{Large}
-        \textcolor{red}{How can we realize the existence of this basis?}
-    \end{Large}
-\\ \hspace*{\fill}\\
-We just need to notice the contribution from ladder diagram
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=1\linewidth]{1.png}
-\end{figure}
-And any (three vertex) diagram, by using the Jacobbi identity like 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=1\linewidth]{2.png}
-\end{figure}
-can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
-\end{frame}
-\begin{frame}{Color-Kinematics Duality }
-The Color-Kinematics Duality here is not the complete version, but we can catch some points.
-At four points we have
-\begin{equation*}
-    A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)=0.
-\end{equation*}
-%The decoupling identity does not rely on the specific polariazation and space-time, so the hold of this equation is 
-%entirely due to the amplitudes' dependence on Mandelstam variables.
-We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ 
-\begin{align*}
-    &A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)\\
-\quad&= (s+t+u)\chi=0
-\end{align*} 
-Considering that $A_4^{\mathrm{tree}}(1,2,3,4)$ treats $s$ and $t$ the same, and similar to the other two, we make the identification
-\begin{equation*}
-    A_4^{\mathrm{tree}}(1,2,3,4)=u\chi,\quad   A_4^{\mathrm{tree}}(1,3,2,4)=t\chi,\quad    A_4^{\mathrm{tree}}(1,4,2,3)=s\chi
-\end{equation*}
-\end{frame}
-\begin{frame}
-    We obtain
-    \begin{align*}
-        tA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,3,4,2),\\
-        sA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,4,2,3),\\
-        tA_4^{\mathrm{tree}}(1,2,3,4)=sA_4^{\mathrm{tree}}(1,3,4,2).\\
-    \end{align*}
-    And in order to obtain the knematic analog of Jacobbi identity, it is convenient to express the amplitudes in terms of poles
-\begin{align*}
-    &A_4^{\mathrm{tree}}(1,2,3,4)\equiv\frac{n_s}{s}+\frac{n_t}{t},\\
-    &A_4^{\mathrm{tree}}(1,3,4,2)\equiv-\frac{n_u}{u}-\frac{n_s}{s},\\
-    &A_4^{\mathrm{tree}}(1,4,2,3)\equiv-\frac{n_t}{t}+\frac{n_u}{u}.
-\end{align*}
-the relative sign here is just a convention.
-\end{frame}
-\begin{frame}
-    Combining the two relation above gives the desired identity
-    \begin{equation*}
-        \alert{n_u=n_s-n_t}
-    \end{equation*}
-    this is exactly the same form of Jacobbi identity for the color factors.
-    The full amplitude can be written like
-\begin{equation*}
-    \mathcal{A}_4^{\mathrm{tree}}=g^2\left(\frac{n_sc_s}{s}+\frac{n_uc_u}{u}+\frac{n_tc_t}{t}\right)
-\end{equation*}
-\end{frame}
-\begin{frame}
-    For the five point case, an example is 
-    \begin{figure}[htb]
-        \centering
-        \includegraphics[width=1\linewidth]{FivePtTwist2.eps}
-    \end{figure}
-    we have the corresponding color factor Jacobbi identities like
-    \begin{equation*}
-        c_3=c_5-c_8
-    \end{equation*}
-    so we need to have the knematic analog
-    \begin{equation*}
-        n_3=n_5-n_8
-    \end{equation*}
-    The explict forms of all these factors can be found in the original paper \textbf{New relations for gauge theory amplituds, PRD 78, 085011}
-\end{frame}
-\begin{frame}
-    Full amplitudes of 5 points are
-    \begin{eqnarray*}
-        \mathcal {A}^\mathrm{tree}_5& = & 
-        g^3\Biggl( {n_1 c_1\over s_{12}s_{45}}+{n_2 c_2\over s_{23}s_{51}}
-        +{n_3 c_3 \over s_{34}s_{12}}+{n_4 c_4\over s_{45}s_{23}}
-        +{n_5 c_5\over s_{51}s_{34}} +{n_{6} c_6\over s_{14}s_{25}}  \\
-        &&\null \hskip .3 cm 
-        + {n_7 c_7\over s_{32}s_{14}}+{n_{8} c_8\over s_{25}s_{43}}
-        +{n_{9} c_9\over s_{13}s_{25}}+{n_{10} c_{10}\over s_{42}s_{13}}
-        +{n_{11} c_{11}\over s_{51}s_{42}}+ {n_{12} c_{12}\over s_{12}s_{35}}  \\
-        &&\null \hskip .3 cm 
-        +{n_{13} c_{13}\over s_{35}s_{24}} 
-        +{n_{14} c_{14}\over s_{14}s_{35}}
-        +{n_{15} c_{15}\over s_{13}s_{45}}\Biggr)\,,
-        \end{eqnarray*}
-    This relation had been proved upto 8 points at the time and I think it has been improved to arbitrary points.  
-\end{frame}
-\fi
+
 \section{CHY Formula}
@@
     \frametitle{Scattering equations}
-    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
+    It has been proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
     \begin{equation*}
@@
 \fi
+
 \begin{frame}
@@
     \begin{align*}
-        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
+        M_n^{\mathrm{YM}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},
         M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
@@
     \pause
-    The measure is defined as following
+    The delta function is defined as following
     \begin{equation*}
@@
     \frametitle{The form of measure}
-    The measure can be written like %the n-3 integral can be completely determined by n-3 delta function
+    The measure can be computed %the n-3 integral can be completely determined by n-3 delta function
     \begin{equation*}
@@
     \begin{equation*}
-        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
+        M_n^{\mathrm{YM}}=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
     \end{equation*}
@@
         \item \alert{Gauge invariance}\\
+        % The gauge invariance is just the statement that the amplitudes vanishes when we replace any polarization vector by the corressponding momentum vector.
         If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
@@
         \end{equation*}
-        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat and Pfaffian becomes 0.
+        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat becomes 0 and then Pfaffian becomes 0.
         \pause
@@
 \begin{frame}
-    \frametitle{CHY form of amplitudes}
+    \frametitle{The most general CHY form}
+    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
+    \begin{equation*}
+        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
+    \end{equation*}
+    \begin{itemize}
+        \item Each particle is represented by a puncture in Riemann sphere.
+        \item This form holds for general D-dimension.
+        \item The boxed part is \alert{universial for all theories}.
+        \item Only the integrand $\mathcal{I}$ determines the particular theory.
+    \end{itemize}
+\end{frame}
+%Since the Yang-Mills and gravity tree-level amplitudes can be written in a compact form, it is tempting to generalize it to other theories.
+\begin{frame}
+    \frametitle{CHY form for 3 specific theory}
     Both formulas above can be written in this simplest form 
@@
             \!\!\!\!\mathcal{M}^{(s)}\!=\!\!\!\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)
-            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}{(\mathrm{Pf}^\prime\Psi)}^s
+            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}\!{(\mathrm{Pf}^\prime\Psi)}^s
         \end{equation*}}
@@
 \end{frame}
-\section{Conclusion and Outlook}
-\begin{frame}
+\section{Summary and Outlook}
+\begin{frame}
+    \frametitle{Summary}
     \begin{itemize}
@@
             \begin{equation*}
-                e_{g_t}=\pm(e_{g_s}-e_{g_u})
+                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2,\quad e_{g_t}=\pm(e_{g_s}-e_{g_u})
             \end{equation*}
@@
 \section{Appendix}
+\appendix
+\begin{frame}{Gauge theory color structure}
+    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
+decomposed as
+\textcolor{red}{\begin{equation*}
+    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
+    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
+\end{equation*}}
+
+here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
+Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
+\end{frame}
+\begin{frame}
+    Color-ordered partial amplitudes satisfy a set of well-known properties,
+    \begin{itemize}
+        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
+        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
+        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
+        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
+        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
+    \end{itemize}
+    where the OP means ordered permutaions, that is all permutations of $\left\{\alpha\right\}$$\bigcup$$\left\{\beta\right\}^T$
+    that matains the order of individual elements of each set.
+\end{frame}
+\begin{frame}
+    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
+\begin{equation*}
+    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
+\end{equation*}
+The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
+\\ \hspace*{\fill}\\
+This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
+\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
+basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
+\end{frame}
+\begin{frame}{A Similar Structure}
+    It can be proved that tree level amplitudes can also be decomposed like 
+\begin{equation*}
+    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
+\end{equation*}
+The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
+\end{frame}
+\begin{frame}
+    \begin{Large}
+        \textcolor{red}{How can we realize the existence of this basis?}
+    \end{Large}
+\\ \hspace*{\fill}\\
+We just need to notice the contribution from ladder diagram
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=1\linewidth]{1.png}
+\end{figure}
+And any (three vertex) diagram, by using the Jacobbi identity like 
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=1\linewidth]{2.png}
+\end{figure}
+can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
+\end{frame}
+\begin{frame}{Color-Kinematics Duality }
+The Color-Kinematics Duality here is not the complete version, but we can catch some points.
+At four points we have
+\begin{equation*}
+    A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)=0.
+\end{equation*}
+%The decoupling identity does not rely on the specific polariazation and space-time, so the hold of this equation is 
+%entirely due to the amplitudes' dependence on Mandelstam variables.
+We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ 
+\begin{align*}
+    &A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)\\
+\quad&= (s+t+u)\chi=0
+\end{align*} 
+Considering that $A_4^{\mathrm{tree}}(1,2,3,4)$ treats $s$ and $t$ the same, and similar to the other two, we make the identification
+\begin{equation*}
+    A_4^{\mathrm{tree}}(1,2,3,4)=u\chi,\quad   A_4^{\mathrm{tree}}(1,3,2,4)=t\chi,\quad    A_4^{\mathrm{tree}}(1,4,2,3)=s\chi
+\end{equation*}
+\end{frame}
+\begin{frame}
+    We obtain
+    \begin{align*}
+        tA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,3,4,2),\\
+        sA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,4,2,3),\\
+        tA_4^{\mathrm{tree}}(1,2,3,4)=sA_4^{\mathrm{tree}}(1,3,4,2).\\
+    \end{align*}
+    And in order to obtain the knematic analog of Jacobbi identity, it is convenient to express the amplitudes in terms of poles
+\begin{align*}
+    &A_4^{\mathrm{tree}}(1,2,3,4)\equiv\frac{n_s}{s}+\frac{n_t}{t},\\
+    &A_4^{\mathrm{tree}}(1,3,4,2)\equiv-\frac{n_u}{u}-\frac{n_s}{s},\\
+    &A_4^{\mathrm{tree}}(1,4,2,3)\equiv-\frac{n_t}{t}+\frac{n_u}{u}.
+\end{align*}
+the relative sign here is just a convention.
+\end{frame}
+\begin{frame}
+    Combining the two relation above gives the desired identity
+    \begin{equation*}
+        \alert{n_u=n_s-n_t}
+    \end{equation*}
+    this is exactly the same form of Jacobbi identity for the color factors.
+    The full amplitude can be written like
+\begin{equation*}
+    \mathcal{A}_4^{\mathrm{tree}}=g^2\left(\frac{n_sc_s}{s}+\frac{n_uc_u}{u}+\frac{n_tc_t}{t}\right)
+\end{equation*}
+\end{frame}
+\begin{frame}
+    For the five point case, an example is 
+    \begin{figure}[htb]
+        \centering
+        \includegraphics[width=1\linewidth]{FivePtTwist2.eps}
+    \end{figure}
+    we have the corresponding color factor Jacobbi identities like
+    \begin{equation*}
+        c_3=c_5-c_8
+    \end{equation*}
+    so we need to have the knematic analog
+    \begin{equation*}
+        n_3=n_5-n_8
+    \end{equation*}
+    The explict forms of all these factors can be found in the original paper \textbf{New relations for gauge theory amplituds, PRD 78, 085011}
+\end{frame}
+\begin{frame}
+    Full amplitudes of 5 points are
+    \begin{eqnarray*}
+        \mathcal {A}^\mathrm{tree}_5& = & 
+        g^3\Biggl( {n_1 c_1\over s_{12}s_{45}}+{n_2 c_2\over s_{23}s_{51}}
+        +{n_3 c_3 \over s_{34}s_{12}}+{n_4 c_4\over s_{45}s_{23}}
+        +{n_5 c_5\over s_{51}s_{34}} +{n_{6} c_6\over s_{14}s_{25}}  \\
+        &&\null \hskip .3 cm 
+        + {n_7 c_7\over s_{32}s_{14}}+{n_{8} c_8\over s_{25}s_{43}}
+        +{n_{9} c_9\over s_{13}s_{25}}+{n_{10} c_{10}\over s_{42}s_{13}}
+        +{n_{11} c_{11}\over s_{51}s_{42}}+ {n_{12} c_{12}\over s_{12}s_{35}}  \\
+        &&\null \hskip .3 cm 
+        +{n_{13} c_{13}\over s_{35}s_{24}} 
+        +{n_{14} c_{14}\over s_{14}s_{35}}
+        +{n_{15} c_{15}\over s_{13}s_{45}}\Biggr)\,,
+        \end{eqnarray*}
+    This relation had been proved upto 8 points at the time and I think it has been improved to arbitrary points.  
+\end{frame}
 \begin{frame}{KLT Relation}
@@
 
-\appendix
 \begin{frame}{KLT Orthogonality}

### 2024-07-17 test/main.tex
New

@@
     \begin{align*}
-        M_n^{\mathrm{YM}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},
+        M_n^{\mathrm{YM}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
         M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
@@
     \frametitle{CHY form for 3 specific theory}
-    Both formulas above can be written in this simplest form 
+    Both formulas above can be written in this simplest form % This formula comes from the subsquent work of the same authors.
     \alert{
@@
     %In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
-    The general case is that we can choose different polariazation vector like 
+    The general case is that we can choose different polarization vector like 
     \begin{equation*}
@@
     \\ \hspace*{\fill}\\
+    \pause
     For the case $s=0$, the similar consequence is 
@@
     where the last term $m_n^{(0)}(\alpha|\beta)$ is called \alert{double partial amplitude} and can be read off from the full amplitude
+    \pause
     \begin{align*}
@@
 \begin{frame}
-    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
+    Here we choose a more usual way to write down the amplitudes by using the color basis
     \begin{equation*}
@@
     \end{equation*}
+    In conclusion, the amplitudes of this sclar theory can be written like the multiplication of two color factors and the double partial amplitudes.
 \end{frame}
@@
         It actually gives the correct answer.
+        \pause
         \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
@@
     \quad \quad as expected for a color-dressed cubic theory.
+    \pause
     \begin{itemize}
@@
     \end{align*}
-    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
+    From examples above, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
     trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
@@
 \end{frame}
+\begin{frame}
+    Now we can unify the color factor and kinematic factor as e in all three theories, so the full amplitude can be written in a unified form
+    \begin{equation*}
+       \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
+    \end{equation*}
+\end{frame}
 \section{Summary and Outlook}
@@
 %entirely due to the amplitudes' dependence on Mandelstam variables.
-We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ 
+We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ % Mandelstam variable
 \begin{align*}

### 2024-07-18 test/main.tex
New

@@
     \frametitle{Scattering equations}
+    % In the Witten-RSV formulation, tree-level field theory amplitudes are given as integrals that localize on generic spheres.
     It has been proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
@@
     \end{equation*}
+    each $\sigma_a$ represents a puncture located in the Riemann sphere.
+
+\end{frame}
+\iffalse
 and n-punctured Riemann sphere can be discribed by $SL(2,\mathbb{C})$ affine coordinates ${\sigma_1,\sigma_2,\ldots,\sigma_n}$, that is to say we have a equvilance relation
@@
 because of the redundancy of $\mathrm{SL}(2,\mathbb{C})$, only $n-3$ of them are independent.
-\end{frame}
+\fi
 \begin{frame}
@@
     \end{block}
-    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following
+    It can be shown that this equation is invariant under the $SL(2,\mathbb{C})$ transformation, that is to say
+    \begin{align*}
+        \{\sigma_1,\sigma_2,\ldots,\sigma_n\}\sim\{\psi(\sigma_1),\psi(\sigma_2),\ldots,\psi(\sigma_n)\},\\\psi(\sigma):=\frac{\alpha\sigma+\beta}{\gamma\sigma+\delta},\quad\alpha,\beta,\gamma,\delta\in\mathbb{C},\alpha\delta-\beta\gamma=1
+    \end{align*}
+    so only $\alert{n-3}$ of these equations are independent, and it has also been proved that these equations have $\alert{(n-3)!}$ solutions in any dimension. 
     \begin{equation*}
@@
         \prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}{:}=\sigma_{ij}\sigma_{jk}\sigma_{ki}\prod_{a\neq i,j,k}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}
+    \end{equation*}
+\end{frame}
+\begin{frame}
+    The reason we need to write down the measure as this form is that under $\mathrm{vol\,SL}(2,\mathbb{C})$
+    \begin{align*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad&\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\rightarrow\prod_{a}(\gamma\sigma_a+\delta)^{-2}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\\
+        \quad &d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
+    \end{align*}
+    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
+    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
+    \begin{equation*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
     \end{equation*}

### 2024-07-19 test/main.tex
New

@@
 \end{frame}
-\begin{frame}
-    The reason we need to write down the measure as this form is that under $\mathrm{vol\,SL}(2,\mathbb{C})$
-    \begin{align*}
-        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad&\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\rightarrow\prod_{a}(\gamma\sigma_a+\delta)^{-2}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\\
-        \quad &d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
-    \end{align*}
-    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
-    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
-    \begin{equation*}
-        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
-    \end{equation*}
-\end{frame}
+
 \begin{frame}
@@
     %with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
-    The Pfaffian of $\Psi$ is 0, but aftering removing any two rows and colums $i,j$ with $1\leq i< j\leq n$, 
-    the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as
+    %The Pfaffian of $\Psi$ is 0, but aftering removing any two rows and colums $i,j$ with $1\leq i< j\leq n$, 
+    %the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as
+    Because the $\mathrm{Pfaffian}$ of $\Psi$ equals to 0, so it is necessary to define the reduced $\mathrm{Pfaffian}$ like 
     \begin{equation*}
@@
     \end{equation*}
+    where $1\leq i< j\leq n$.
+    \\ \hspace*{\fill}\\
     It can be proved that the reduced Pfaffian is invariant under permutaion of \alert{particle labels}.
     \pause
-    \begin{alertblock}{Pfaffian}
+    \begin{alertblock}{$\mathrm{Pfaffian}$}
         Pfaffian is defined for antisymmetric matrix, usually in two ways as following
         \begin{itemize}
-            \item \begin{equation*}
-                \mathrm{Pf}(A)^2=\det A
-            \end{equation*}
-            \item \begin{equation*}
-                \mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}
-            \end{equation*}
+            \item  $\mathrm{Pf}(A)^2=\det A$
+            \item  $\mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}$
         \end{itemize}
@@
     \begin{equation*}
-        s=0\quad\to \quad \text{a corresponding scalar theory}
+        s=0\quad\to \quad \text{There should be a corresponding scalar theory}
     \end{equation*}
@@
     \end{equation*}
+    usually called bi-adjoint scalar theory.
+    \\ \hspace*{\fill}\\
     All of above leads to the conclusion that the factors 
@@
     \end{equation*}
-    are interchangeable and this is a color-Kinematics corresopondence which is valid for individual solutions to scattering equations.
+    are interchangeable and this is a Color-Kinematics corresopondence which is valid for individual solutions to scattering equations.
 
@@
 \begin{frame}
-    Here we choose a more usual way to write down the amplitudes by using the color basis
+    In practice, it is more convenient to use another color basis 
     \begin{equation*}
@@
     \end{align*}
-    From examples above, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
-    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
+    From the examples above, it is not hard to discover that 
+    \begin{align*}
+        &\text{if}\quad \alpha=\beta:\quad m_n^{(0)}(\alpha|\alpha)=\sum(\text{all color-orded trivalent diagrams})\\
+        &\text{if}\quad \alpha\neq\beta:\quad m_n^{(0)}(\alpha|\beta)=(\text{subset of}\; m_n^{(0)}(\alpha|\alpha))
+    \end{align*}
     \\ \hspace*{\fill}\\
@@
     \end{equation*}
+    and from the construcion of three type amplitudes, we can obtain
+    \begin{equation*}
+        {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
+    \end{equation*}
+
 \end{frame}
@@
 \appendix
+\begin{frame}
+    The reason we need to write down the measure as this form is that under $\mathrm{vol\,SL}(2,\mathbb{C})$
+    \begin{align*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad&\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\rightarrow\prod_{a}(\gamma\sigma_a+\delta)^{-2}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\\
+        \quad &d\mu_n\to\prod_{a=1}^n(\gamma\sigma_a+\delta)^{-4}d\mu_n
+    \end{align*}
+    $E_n(\{k,\epsilon,\sigma\})$ itself is permutaion invariant with resprct to $\sigma_a,k_a^\mu$ and $\epsilon_a^\mu$. The $SL(2,\mathbb{C})$ invariance of amplitude also 
+    constraints the form of $E_n(\{k,\epsilon,\sigma\})$
+    \begin{equation*}
+        \sigma_a\to\frac{\alpha\sigma_a+\beta}{\gamma\sigma_a+\delta}:\quad E_n(\{k,\epsilon,\sigma\})\to E_n(\{k,\epsilon,\sigma\})\prod_{a=1}^n(\gamma\sigma_a+\delta)^2
+    \end{equation*}
+\end{frame}
 \begin{frame}{Gauge theory color structure}

### 2024-07-21 test/main.tex
New

@@
 
-\section{Why the S-matrix is so important?}
+\section{Why the scattering amplitude is so important?}
 
@@
         \item Some recent work show that scattering amplitude contains many interesting mathematical structures.
-              Actually, this report introduces one of these structures.
     \end{itemize}
@@
         \item BCJ double copy at tree level
-        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation. It may give some implications for the construcion of nonpermubative BCJ double copy.
+        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation.
         \item Related to other theories, such as EYM, EM, NLSM and so on.
@@
         % The gauge invariance is just the statement that the amplitudes vanishes when we replace any polarization vector by the corressponding momentum vector.
-        If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
+        If we replace the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
         \begin{equation*}
@@
     \frametitle{Double partial amplitudes}
-    Because there are two color indices in this sclar theory, so it can be anticipateed that the amplitude
+    Because there are two color indices in this sclar theory, so it can be anticipated that the amplitude
     have double trace decomposition structure
@@
         \mathcal{M}_n^{(0)}&=\sum_{\alpha\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})M_n^{(0)}(\alpha(1),\alpha(2),\ldots,\alpha(n))\\
-        &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\text{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
+        &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\mathrm{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
         &\times \alert{m_n^{(0)}(\alpha|\beta)}
@@
     \end{equation*}
-    In conclusion, the amplitudes of this sclar theory can be written like the multiplication of two color factors and the double partial amplitudes.
+    In conclusion, the amplitudes of this scalar theory can be written like the multiplication of two color factors and the double partial amplitudes.
 \end{frame}

### 2024-07-22 test/main.tex
New

@@
         \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1307.2199
-        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1309.0885
+        \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1309.0885 (Title)
         \item F. Cachazo, S. He, E.Y. Yuan, arxiv: 1412.3479
@@
     \end{block}
+    \pause
     It can be shown that this equation is invariant under the $SL(2,\mathbb{C})$ transformation, that is to say
@@
     The delta function is defined as following
+    \begin{equation*}
+        \frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}{:}=\prod_{c\neq p,q,r}d\sigma_c(\sigma_{pq}\sigma_{qr}\sigma_{rp})
+    \end{equation*}
     \begin{equation*}
@@
     \begin{equation*}
-        M_n^{\mathrm{gravity}}=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
+        M_n^{\mathrm{gravity}}=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\Psi
     \end{equation*}
@@
         % The gauge invariance is just the statement that the amplitudes vanishes when we replace any polarization vector by the corressponding momentum vector.
-        If we replace the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
+        If we replace the ith polariazation vector $\epsilon_i^\mu$ by momentum $k_i^\mu$, we find that
         \begin{equation*}
@@
 \end{frame}
-\begin{frame}
-    \frametitle{The most general CHY form}
-    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
-    \begin{equation*}
-        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
-    \end{equation*}
-    \begin{itemize}
-        \item Each particle is represented by a puncture in Riemann sphere.
-        \item This form holds for general D-dimension.
-        \item The boxed part is \alert{universial for all theories}.
-        \item Only the integrand $\mathcal{I}$ determines the particular theory.
-    \end{itemize}
-\end{frame}
+
 %Since the Yang-Mills and gravity tree-level amplitudes can be written in a compact form, it is tempting to generalize it to other theories.
@@
             \!\!\!\!\mathcal{M}^{(s)}\!=\!\!\!\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)
-            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}\!{(\mathrm{Pf}^\prime\Psi)}^s
+            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}+\dots\right)^{(2-s)}\!{(\mathrm{Pf}^\prime\Psi)}^s
         \end{equation*}}
@@
     \end{equation*}
-    usually called bi-adjoint scalar theory.
+    usually called \alert{bi-adjoint} scalar theory.
     \\ \hspace*{\fill}\\
@@
         &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\mathrm{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
-        &\times \alert{m_n^{(0)}(\alpha|\beta)}
+        &\quad\times \alert{m_n^{(0)}(\alpha|\beta)}
     \end{align*} 
@@
     \end{equation*}
-    where $\alpha \in S_{n-2}$. The amplitude is 
+    where $\alpha \in S_{n-2}$, so in this case we can fix the position of two labels. The amplitude is 
     \begin{equation*}
@@
         \pause
-        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
+        \item The 4 point case is a little complicated. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
         $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
@@
     % Text Node
-    \draw (325.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
-    % Text Node
-    \draw (325.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
-    % Text Node
-    \draw (405.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-    % Text Node
-    \draw (404.5,171) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    \draw (325.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
+    % Text Node
+    \draw (325.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+    % Text Node
+    \draw (405.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+    % Text Node
+    \draw (404.5,171) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
 
@@
 \begin{frame}
-    We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way
+    We take $m_8^{(0)}(I|18543762)$ as an example to explain how to compute it in an systematic way
 
@@
     \begin{equation*}
+       \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha \tilde{e}_\beta m^{(0)}(\alpha|\beta)
+    \end{equation*}
+    and from the construcion of three type amplitudes, we can obtain
+    \begin{equation*}
+        {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
+    \end{equation*}
+    tree-level BCJ double copy relation.
+
+\end{frame}
+\section{Summary and Outlook}
+\begin{frame}
+    \frametitle{Summary}
+    \begin{itemize}
+        \item A compact form of tree-level S-matrix in 3 different theories are introduced
+            \begin{equation*}
                 \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
              \end{equation*}
-    and from the construcion of three type amplitudes, we can obtain
-    \begin{equation*}
-        {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
-    \end{equation*}
-
-\end{frame}
-\section{Summary and Outlook}
-\begin{frame}
-    \frametitle{Summary}
-    \begin{itemize}
-        \item A compact form of tree-level S-matrix in 3 different theories are introduced
-            \begin{equation*}
-                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
-             \end{equation*}
         \item The computaion method for double partial amplitudes are given 
@@
             \end{equation*}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{The most general CHY form}
+    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
+    \begin{equation*}
+        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
+    \end{equation*}
+    \begin{itemize}
+        \item Each particle is represented by a puncture in Riemann sphere.
+        \item This form holds for general D-dimension.
+        \item The boxed part is \alert{universial for all theories}.
+        \item Only the integrand $\mathcal{I}$ determines the particular theory.
     \end{itemize}
@@
 \begin{frame}
-    \begin{figure}
+    \begin{figure}[t]
         \centering
@@
     \end{figure}
-\end{frame}
-
+    \alert{arxiv: 1412.3479}
+\end{frame}
+\begin{frame}
+    \centering
+    \Huge Thanks for your attention!
+\end{frame}
+\appendix
 \section{Appendix}
-\appendix
-\begin{frame}
-    The reason we need to write down the measure as this form is that under $\mathrm{vol\,SL}(2,\mathbb{C})$
+
+\begin{frame}
+    The reason we need to write down the measure as this form is that under $\mathrm{SL}(2,\mathbb{C})$
     \begin{align*}

### 2024-07-22 test/main.tex
New

@@
 \end{equation*}
-where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
+where the $n_{\text{flip}}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
 $\beta$ ordering respectively. To make this expression more clear, see the following diagram
@@
 \begin{frame}
-    We take $m_8^{(0)}(I|18543762)$ as an example to explain how to compute it in an systematic way
+    I take $m_8^{(0)}(I|18543762)$ as an example to explain how to compute it in an tecnical way
 
@@
 \begin{frame}
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=1\linewidth]{4.png}
+    \end{figure}
+    \alert{arxiv: 1412.3479}
+\end{frame}
+\begin{frame}
     \frametitle{Connection between other theories}
@@
 \end{frame}
-\begin{frame}
-    \begin{figure}[t]
-        \centering
-        \includegraphics[width=1\linewidth]{4.png}
-    \end{figure}
-    \alert{arxiv: 1412.3479}
-\end{frame}
+
 \begin{frame}

### 2024-07-23 test/main.tex
New

@@
         %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation.
-        \item Related to other theories, such as EYM, EM, NLSM and so on.
+        \item Many other theories are related, such as EYM, EM, NLSM and so on.
         %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
@@
     \end{equation*}
-    each $\sigma_a$ represents a puncture located in the Riemann sphere.
+    all of the n punctured Riemann sphere actually compose a $\mathrm{n-3}$ dimension complex vector space $\mathfrak{m}_{0,n}$, 
+    and $\sigma_a$ is a set of coordinates of this space.
 
@@
     \end{figure}
-    The final answer is that
+    The final answer is 
     \begin{equation*}
@@
     and from the construcion of three type amplitudes, we can obtain
+
     \begin{equation*}
@@
             \end{equation*}
-        \item The CK duality and BCJ double-copy relation can be easily obtained
-            \begin{equation*}
-                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2,\quad e_{g_t}=\pm(e_{g_s}-e_{g_u})
+        \item The Color-Kinematic duality and BCJ double-copy relation can be easily obtained
+            \begin{equation*}
+                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2
             \end{equation*}

### 2024-09-13 Paper Category/main.tex
New

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\title{}
\author{}
\begin{document}
    \begin{itemize}
        \item %\cite{Arkani-Hamed:2019ymq}
        N.~Arkani-Hamed, Y.~t.~Huang and D.~O'Connell,
        ``Kerr black holes as elementary particles,''
        JHEP \textbf{01}, 046 (2020)
        doi:10.1007/JHEP01(2020)046
        [arXiv:1906.10100 [hep-th]].
        224 citations counted in INSPIRE as of 13 Sep 2024
    \end{itemize}
\section*{Hard to be catagorized}
\begin{itemize}
    \item %\cite{Jakobsen:2021zvh}
    G.~U.~Jakobsen, G.~Mogull, J.~Plefka and J.~Steinhoff,
    ``SUSY in the sky with gravitons,''
    JHEP \textbf{01}, 027 (2022)
    doi:10.1007/JHEP01(2022)027
    [arXiv:2109.04465 [hep-th]].
    114 citations counted in INSPIRE as of 13 Sep 2024\\
    Presents a study of the gravitational scattering of two massive, spinning compact bodies, showing that this astrophysical system enjoys a hidden N = 2 supersymmetry.
    \item 
\end{itemize}
\end{document}

### 2024-09-16 Paper Category/main.tex
New

@@
 \begin{itemize}
-    \item %\cite{Jakobsen:2021zvh}
-    G.~U.~Jakobsen, G.~Mogull, J.~Plefka and J.~Steinhoff,
-    ``SUSY in the sky with gravitons,''
-    JHEP \textbf{01}, 027 (2022)
-    doi:10.1007/JHEP01(2022)027
-    [arXiv:2109.04465 [hep-th]].
-    114 citations counted in INSPIRE as of 13 Sep 2024\\
-    Presents a study of the gravitational scattering of two massive, spinning compact bodies, showing that this astrophysical system enjoys a hidden N = 2 supersymmetry.
-    \item 
+    \item %\cite{Aoude:2020onz}
+    R.~Aoude, K.~Haddad and A.~Helset,
+    ``On-shell heavy particle effective theories,''
+    JHEP \textbf{05}, 051 (2020)
+    doi:10.1007/JHEP05(2020)051
+    [arXiv:2001.09164 [hep-th]].
+    163 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author introduce on-shell variables for HPETs with the aim to present such a formalism will allow the extension of
+    HBET to higher spins and to facilitate its application to higher loop orders. 
+    \item %\cite{Mazza:2021rgq}
+    J.~Mazza, E.~Franzin and S.~Liberati,
+    ``A novel family of rotating black hole mimickers,''
+    JCAP \textbf{04}, 082 (2021)
+    doi:10.1088/1475-7516/2021/04/082
+    [arXiv:2102.01105 [gr-qc]].
+    135 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author employ the Newman-Janis procedure to generalize SV metric, which generates the rotating blackhole mimickers. A method wowards the quantum theory of gravity.
+\end{itemize}
+\section*{Double copy relation}
+\begin{itemize}
+    \item %\cite{Johansson:2019dnu}
+    H.~Johansson and A.~Ochirov,
+    ``Double copy for massive quantum particles with spin,''
+    JHEP \textbf{09}, 040 (2019)
+    doi:10.1007/JHEP09(2019)040
+    [arXiv:1906.12292 [hep-th]].
+    161 citations counted in INSPIRE as of 16 Sep 2024\\
+    This paper explores the double copy structure of gravitational theories coupled to massive matter with spin, which is relevant for understanding black hole scattering and gravitational waves.
+    \item %\cite{Adamo:2022dcm}
+    T.~Adamo, J.~J.~M.~Carrasco, M.~Carrillo-Gonz\'alez, M.~Chiodaroli, H.~Elvang, H.~Johansson, D.~O'Connell, R.~Roiban and O.~Schlotterer,
+    ``Snowmass White Paper: the Double Copy and its Applications,''
+    [arXiv:2204.06547 [hep-th]].
+    92 citations counted in INSPIRE as of 16 Sep 2024\\
+    This Snowmass white paper provides a brief introduction to the double copy, its applications,
+    current research and future challenges.
+    \item %\cite{Chacon:2021wbr}
+    E.~Chac\'on, S.~Nagy and C.~D.~White,
+    ``The Weyl double copy from twistor space,''
+    JHEP \textbf{05}, 2239 (2021)
+    doi:10.1007/JHEP05(2021)239
+    [arXiv:2103.16441 [hep-th]].
+    72 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author show how
+    the current form and scope of the Weyl double copy can be derived from a certain procedure
+    in twistor space.
+    \item %\cite{Borsten:2021hua}
+    L.~Borsten, H.~Kim, B.~Jur\v{c}o, T.~Macrelli, C.~Saemann and M.~Wolf,
+    ``Double Copy from Homotopy Algebras,''
+    Fortsch. Phys. \textbf{69}, no.8-9, 2100075 (2021)
+    doi:10.1002/prop.202100075
+    [arXiv:2102.11390 [hep-th]].
+    76 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author give a detailed exposition of the BRST Lagrangian double copy and show that colour-kinematics duality and the BRST-Lagrangian double copy can be
+ elegantly articulated in terms of homotopy algebras.
+\end{itemize}
+\section*{Gravitational waves}
+\begin{itemize}
+    \item %\cite{DiVecchia:2023frv}
+    P.~Di Vecchia, C.~Heissenberg, R.~Russo and G.~Veneziano,
+    ``The gravitational eikonal: From particle, string and brane collisions to black-hole encounters,''
+    Phys. Rept. \textbf{1083}, 1-169 (2024)
+    doi:10.1016/j.physrep.2024.06.002
+    [arXiv:2306.16488 [hep-th]].
+    60 citations counted in INSPIRE as of 16 Sep 2024\\
+    Review paper. THe author discuss how the gravitational ekinoal approach can be applied invarious different physical
+    set ups involving particles,strings and branes and then we mainly concentrate on the most recent
+    developments.
+\end{itemize}
+\section*{Effective theories of BH}
+\begin{itemize}
+    \item %\cite{Cangemi:2022bew}
+    L.~Cangemi, M.~Chiodaroli, H.~Johansson, A.~Ochirov, P.~Pichini and E.~Skvortsov,
+    ``Kerr Black Holes From Massive Higher-Spin Gauge Symmetry,''
+    Phys. Rev. Lett. \textbf{131}, no.22, 221401 (2023)
+    doi:10.1103/PhysRevLett.131.221401
+    [arXiv:2212.06120 [hep-th]].
+    52 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author propose that the dynamics of Kerr black holes is strongly constrained by the principle of
+    gauge symmetry, and show that the known three-point Kerr amplitudes are uniquely
+    predicted using massive higher-spin gauge symmetry
+\end{itemize}
+\section*{Classical gravitational scattering versus Quantum part}
+\begin{itemize}
+    \item %\cite{Aoude:2022thd}
+    R.~Aoude, K.~Haddad and A.~Helset,
+    ``Classical Gravitational Spinning-Spinless Scattering at O(G2S\ensuremath{\infty}),''
+    Phys. Rev. Lett. \textbf{129}, no.14, 141102 (2022)\\
+    doi:10.1103/PhysRevLett.129.141102
+    [arXiv:2205.02809 [hep-th]].
+    73 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author calculate
+    the classical gravitational scattering amplitude for one spinning and one spinless object at $O(G^2)$
+    and all orders in spin, which exhibits the spin structure that has been
+    conjectured to describe Kerr black holes
+    \item %\cite{Alessio:2022kwv}
+    F.~Alessio and P.~Di Vecchia,
+    ``Radiation reaction for spinning black-hole scattering,''
+    Phys. Lett. B \textbf{832}, 137258 (2022)
+    doi:10.1016/j.physletb.2022.137258
+    [arXiv:2203.13272 [hep-th]].
+    54 citations counted in INSPIRE as of 16 Sep 2024\\
+    Starting from the leading soft term of the 5-point amplitude, involving a graviton and two Kerr black holes, the author determine the
+    radiative contribution to the real part of the two-loop eikonal.
+    \item %\cite{Jakobsen:2022fcj}
+    G.~U.~Jakobsen and G.~Mogull,
+    ``Conservative and Radiative Dynamics of Spinning Bodies at Third Post-Minkowskian Order Using Worldline Quantum Field Theory,''
+    Phys. Rev. Lett. \textbf{128}, no.14, 141102 (2022)
+    doi:10.1103/PhysRevLett.128.141102
+    [arXiv:2201.07778 [hep-th]].
+    96 citations counted in INSPIRE as of 16 Sep 2024\\
+    Using the spinning worldline quantum field theory formalism, the author compute the conservative scattering angle and the radiation-reaction effects.
+    \item %\cite{Cristofoli:2021jas}
+    A.~Cristofoli, R.~Gonzo, N.~Moynihan, D.~O'Connell, A.~Ross, M.~Sergola and C.~D.~White,
+    ``The uncertainty principle and classical amplitudes,''
+    JHEP \textbf{06}, 181 (2024)
+    doi:10.1007/JHEP06(2024)181
+    [arXiv:2112.07556 [hep-th]].
+    80 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author discussed how the classical limit is encoded in the quantum-first definition of field theory through scattering amplitudes
+    \item %\cite{Aoude:2021oqj}
+    R.~Aoude and A.~Ochirov,
+    ``Classical observables from coherent-spin amplitudes,''
+    JHEP \textbf{10}, 008 (2021)
+    doi:10.1007/JHEP10(2021)008
+    [arXiv:2108.01649 [hep-th]].
+    75 citations counted in INSPIRE as of 16 Sep 2024\\
+    The author promote the KMOC formalism  to describe general classical spinning objects by using coherent spin states. 
 \end{itemize}

### 2024-09-17 Paper Category/main.tex
New

@@
     \end{itemize}
-\section*{Hard to be catagorized}
+\section*{Related to Quantum Gravity}
 \begin{itemize}
@@
     135 citations counted in INSPIRE as of 16 Sep 2024\\
-    The author employ the Newman-Janis procedure to generalize SV metric, which generates the rotating blackhole mimickers. A method wowards the quantum theory of gravity.
+    The author employ the Newman-Janis procedure to generalize SV metric, which generates the rotating blackhole mimickers. A method towards the quantum theory of gravity.
 \end{itemize}
@@
     in twistor space.
+    \item%\cite{White:2020sfn}
+    C.~D.~White,
+    ``Twistorial Foundation for the Classical Double Copy,''
+    Phys. Rev. Lett. \textbf{126}, no.6, 061602 (2021)
+    doi:10.1103/PhysRevLett.126.061602
+    [arXiv:2012.02479 [hep-th]].
+    90 citations counted in INSPIRE as of 17 Sep 2024\\ 
+    The author
+    show that a particular incarnation- the Weyl double copy- can be derived using well-established
+    ideas from twistor theory.
     \item %\cite{Borsten:2021hua}
@@
  elegantly articulated in terms of homotopy algebras.
+    \item %\cite{Emond:2020lwi}
+    W.~T.~Emond, Y.~T.~Huang, U.~Kol, N.~Moynihan and D.~O'Connell,
+    ``Amplitudes from Coulomb to Kerr-Taub-NUT,''
+    JHEP \textbf{05}, 055 (2022)
+    doi:10.1007/JHEP05(2022)055
+    [arXiv:2010.07861 [hep-th]].
+    71 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author dentify the amplitudes corresponding to each of these solutions and con rm
+    that the amplitudes double-copy when the solutions are related by the classical double copy.
+    \item  %\cite{Godazgar:2020zbv}
+    H.~Godazgar, M.~Godazgar, R.~Monteiro, D.~Peinador Veiga and C.~N.~Pope,
+    ``Weyl Double Copy for Gravitational Waves,''
+    Phys. Rev. Lett. \textbf{126}, no.10, 101103 (2021)
+    doi:10.1103/PhysRevLett.126.101103
+    [arXiv:2010.02925 [hep-th]].
+    73 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author establish the status of the Weyl double copy relation for radiative solutions of the vacuum
+    Einstein equations.
+    \item %\cite{Bah:2019sda}
+    I.~Bah, R.~Dempsey and P.~Weck,
+    ``Kerr-Schild Double Copy and Complex Worldlines,''
+    JHEP \textbf{02}, 180 (2020)
+    doi:10.1007/JHEP02(2020)180
+    [arXiv:1910.04197 [hep-th]].
+    62 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author use the classical double copy to identify a necessary condition for Maxwell
+ theory sources to constitute single copies of Kerr-Schild solutions, and give a parameterization of the corresponding single copies in terms of Li´ enard-Wiechert fields of charges on complex worldlines.
+    \item %\cite{Elor:2020nqe}
+    G.~Elor, K.~Farnsworth, M.~L.~Graesser and G.~Herczeg,
+    ``The Newman-Penrose Map and the Classical Double Copy,''
+    JHEP \textbf{12}, 121 (2020)
+    doi:10.1007/JHEP12(2020)121
+    [arXiv:2006.08630 [hep-th]].
+    66 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author present a novel map, called Newman-Penrose map, between a certain class
+    of real, exact solutions of Einstein s equations and self-dual solutions of the at-space vacuum Maxwell equations.
+    \item %\cite{Borsten:2020xbt}
+    L.~Borsten and S.~Nagy,
+    ``The pure BRST Einstein-Hilbert Lagrangian from the double-copy to cubic order,''
+    JHEP \textbf{07}, 093 (2020)
+    doi:10.1007/JHEP07(2020)093
+    [arXiv:2004.14945 [hep-th]].
+    64 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author construct the pure gravity BRST Einstein Hilbert Lagrangian, to cubic order, using the BRST convolution product and BCJ double-copy.
+    \item  %\cite{Plefka:2019wyg}
+    J.~Plefka, C.~Shi and T.~Wang,
+    ``Double copy of massive scalar QCD,''
+    Phys. Rev. D \textbf{101}, no.6, 066004 (2020)
+    doi:10.1103/PhysRevD.101.066004
+    [arXiv:1911.06785 [hep-th]].
+    56 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author construct the gravitational theory emerging from the double-copy of massive scalar quantum
+    chromodynamics in general dimensions. 
 \end{itemize}
@@
     60 citations counted in INSPIRE as of 16 Sep 2024\\
-    Review paper. THe author discuss how the gravitational ekinoal approach can be applied invarious different physical
+    Review paper. The author discuss how the gravitational ekinoal approach can be applied to invarious different physical
     set ups involving particles,strings and branes and then we mainly concentrate on the most recent
     developments.
+
 \end{itemize}
@@
     gauge symmetry, and show that the known three-point Kerr amplitudes are uniquely
-    predicted using massive higher-spin gauge symmetry
+    predicted using massive higher-spin gauge symmetry.
 \end{itemize}
@@
     The author promote the KMOC formalism  to describe general classical spinning objects by using coherent spin states. 
+    \item %\cite{Cheung:2020gbf}
+    C.~Cheung, N.~Shah and M.~P.~Solon,
+    ``Mining the Geodesic Equation for Scattering Data,''
+    Phys. Rev. D \textbf{103}, no.2, 024030 (2021)
+    doi:10.1103/PhysRevD.103.024030
+    [arXiv:2010.08568 [hep-th]].
+    65 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author explore how the geodesic equation encodes conservative dynamics in the presence of an arbitrary
+    perturbative correction away from a non-spinning black hole binary system in general relativity.
+    \item %\cite{Luna:2023uwd}
+    A.~Luna, N.~Moynihan, D.~O'Connell and A.~Ross,
+    ``Observables from the spinning eikonal,''
+    JHEP \textbf{08}, 045 (2024)
+    doi:10.1007/JHEP08(2024)045
+    [arXiv:2312.09960 [hep-th]].
+    14 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author study the classical dynamics of spinning particles using scattering amplitudes
+ and eikonal exponentiation.
+\end{itemize}
+\section*{Holography}
+\begin{itemize}
+    \item %\cite{Pasterski:2020pdk}
+    S.~Pasterski and A.~Puhm,
+    ``Shifting spin on the celestial sphere,''
+    Phys. Rev. D \textbf{104}, no.8, 086020 (2021)
+    doi:10.1103/PhysRevD.104.086020
+    [arXiv:2012.15694 [hep-th]].
+    69 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author aims to  expand the existing framework surrounding conformal primary
+    states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.
+
 \end{itemize}

### 2024-09-17 Paper Category/main.tex
New

@@
     chromodynamics in general dimensions. 
+    \item  %\cite{Easson:2023dbk}
+    D.~A.~Easson, G.~Herczeg, T.~Manton and M.~Pezzelle,
+    ``Isometries and the double copy,''
+    JHEP \textbf{09}, 162 (2023)
+    doi:10.1007/JHEP09(2023)162
+    [arXiv:2306.13687 [gr-qc]].
+    18 citations counted in INSPIRE as of 17 Sep 2024\\
+    The authors show that the geodicity of the Kerr-Schild vector and the existence of a timelike Killing vector, are in fact consequences of the vacuum conditions instead of assumptions.
 \end{itemize}
@@
 \end{itemize}
-\section*{Classical gravitational scattering versus Quantum part}
+\section*{Classical and Quantum gravitational scattering}
 \begin{itemize}
@@
  and eikonal exponentiation.
+    \item %\cite{Kosmopoulos:2023bwc}
+    D.~Kosmopoulos and M.~P.~Solon,
+    ``Gravitational self force from scattering amplitudes in curved space,''
+    JHEP \textbf{03}, 125 (2024)
+    doi:10.1007/JHEP03(2024)125
+    [arXiv:2308.15304 [hep-th]].
+    18 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author employ scattering amplitudes in curved space to model the dynamics of a
+light probe particle orbiting in the background spacetime.
+    \item %\cite{Bern:2023ity}
+    Z.~Bern, D.~Kosmopoulos, A.~Luna, R.~Roiban, T.~Scheopner, F.~Teng and J.~Vines,
+    ``Quantum field theory, worldline theory, and spin magnitude change in orbital evolution,''
+    Phys. Rev. D \textbf{109}, no.4, 045011 (2024)
+    doi:10.1103/PhysRevD.109.045011
+    [arXiv:2308.14176 [hep-th]].
+    21 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author clarify the nature of additional Wilson coefficients appear compared to current worldline approaches.
+    \item %\cite{Gonzo:2023goe}
+    R.~Gonzo and C.~Shi,
+    ``Boundary to bound dictionary for generic Kerr orbits,''
+    Phys. Rev. D \textbf{108}, no.8, 084065 (2023)
+    doi:10.1103/PhysRevD.108.084065
+    [arXiv:2304.06066 [hep-th]].
+    20 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author establish a new relation between classical observables for scattering and bound orbits of a massive probe particle in a Kerr background.
+
 \end{itemize}
@@
     states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.
-
+    \item %\cite{Crawley:2023brz}
+    E.~Crawley, A.~Guevara, E.~Himwich and A.~Strominger,
+    ``Self-dual black holes in celestial holography,''
+    JHEP \textbf{09}, 109 (2023)
+    doi:10.1007/JHEP09(2023)109
+    [arXiv:2302.06661 [hep-th]].
+    19 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author use the celestial holography formalism to construct 2D quantum states for 4D linearized rotating self-dual black holes in (2,2) signature Klein space.
+\end{itemize}
+\section*{Formal Amplitude Method}
+\begin{itemize}
+    \item  %\cite{Chen:2023dcx}
+    A.~S.~K.~Chen, H.~Elvang and A.~Herderschee,
+    ``Bootstrapping the String Kawai-Lewellen-Tye Kernel,''
+    Phys. Rev. Lett. \textbf{131}, no.3, 031602 (2023)\\
+    doi:10.1103/PhysRevLett.131.031602
+    [arXiv:2302.04895 [hep-th]].\\
+    15 citations counted in INSPIRE as of 17 Sep 2024\\
+    This paper extends the minimal rank KLT bootstrap to 6-point, finding novel restrictions on the 4
+    and 5-point double-copy maps.
 \end{itemize}

### 2024-09-17 Paper Category/main.tex
New

@@
     \end{itemize}
-\section*{Related to Quantum Gravity}
+\section*{Towards Quantum Gravity}
 \begin{itemize}
@@
     The authors show that the geodicity of the Kerr-Schild vector and the existence of a timelike Killing vector, are in fact consequences of the vacuum conditions instead of assumptions.
+    \item %\cite{Bonezzi:2022bse}
+    R.~Bonezzi, C.~Chiaffrino, F.~Diaz-Jaramillo and O.~Hohm,
+    ``Gauge invariant double copy of Yang-Mills theory: The quartic theory,''
+    Phys. Rev. D \textbf{107}, no.12, 126015 (2023)
+    doi:10.1103/PhysRevD.107.126015
+    [arXiv:2212.04513 [hep-th]].
+    27 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author gives an explicit gauge invariant, off-shell and local double copy construction of
+    gravity
+    \item %\cite{Chawla:2022ogv}
+    S.~Chawla and C.~Keeler,
+    ``Aligned fields double copy to Kerr-NUT-(A)dS,''
+    JHEP \textbf{04}, 005 (2023)
+    doi:10.1007/JHEP04(2023)005
+    [arXiv:2209.09275 [hep-th]].
+    17 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author find a double copy relation between Abelian gauge fields and a large class of black
+ hole spacetimes with spherical horizon topology known as the Kerr-NUT-(A)dS family.
 \end{itemize}
@@
     The author establish a new relation between classical observables for scattering and bound orbits of a massive probe particle in a Kerr background.
+    \item %\cite{Bjerrum-Bohr:2022ows}
+    N.~E.~J.~Bjerrum-Bohr, L.~Plant\'e and P.~Vanhove,
+    ``Effective Field Theory and Applications: Weak Field Observables from Scattering Amplitudes in Quantum Field Theory,''
+    [arXiv:2212.08957 [hep-th]].
+    19 citations counted in INSPIRE as of 17 Sep 2024\\ 
+    The author discuss classical components
+    of perturbative weak-field scattering amplitudes until the fourth post-Minkowskian order based on an effective field theory extension of the Einstein-Hilbert action.
 
@@
     and 5-point double-copy maps.
+    \item %\cite{Cristofoli:2022phh}
+    A.~Cristofoli, A.~Elkhidir, A.~Ilderton and D.~O'Connell,
+    ``Large gauge effects and the structure of amplitudes,''
+    JHEP \textbf{06}, 204 (2023)
+    doi:10.1007/JHEP06(2023)204
+    [arXiv:2211.16438 [hep-th]].
+    12 citations counted in INSPIRE as of 17 Sep 2024\\
+    The author show that large gauge transformations modify the structure of momentum conservation.
 \end{itemize}

### 2024-09-24 Paper Category/main.tex
New

@@
 \end{itemize}
+%\cite{Bern:2019prr}
+Z.~Bern, J.~J.~Carrasco, M.~Chiodaroli, H.~Johansson and R.~Roiban,
+``The duality between color and kinematics and its applications,''
+J. Phys. A \textbf{57}, no.33, 333002 (2024)
+doi:10.1088/1751-8121/ad5fd0
+[arXiv:1909.01358 [hep-th]].
+455 citations counted in INSPIRE as of 23 Sep 2024
+\section*{CK duality in curved spacetime}
+\begin{itemize}
+    \item %\cite{Cheung:2022pdk}
+    C.~Cheung, J.~Parra-Martinez and A.~Sivaramakrishnan,
+    ``On-shell correlators and color-kinematics duality in curved symmetric spacetimes,''
+    JHEP \textbf{05}, 027 (2022)
+    doi:10.1007/JHEP05(2022)027
+    [arXiv:2201.05147 [hep-th]].
+    50 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author introduce a isometry frame on symmetric manifold to define a perturbatively calculable quantity—the on-shell correlator, which can be seen as 
+    the generalization of on-shell quantity to curved spacetime.
+    \item %\cite{Ben-Shahar:2021zww}
+    M.~Ben-Shahar and H.~Johansson,
+    ``Off-shell color-kinematics duality for Chern-Simons,''
+    JHEP \textbf{08}, 035 (2022)
+    doi:10.1007/JHEP08(2022)035
+    [arXiv:2112.11452 [hep-th]].
+    52 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author show that 3D Chern-Simons theory obeys off-shell color-kinematics duality and this holds both for gauge field and BRST ghosts.
+    \item %\cite{Cheung:2021zvb}
+    C.~Cheung and J.~Mangan,
+    ``Covariant color-kinematics duality,''
+    JHEP \textbf{11}, 069 (2021)
+    doi:10.1007/JHEP11(2021)069
+    [arXiv:2108.02276 [hep-th]].
+    65 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author construct an
+    explicit implementation of the double copy at the level of fields and equations of motion. They find that YM theory has a so-called "covariant 
+    double copy" property and can be related to GR.
+    \item %\cite{Chi:2021mio}
+    H.~H.~Chi, H.~Elvang, A.~Herderschee, C.~R.~T.~Jones and S.~Paranjape,
+    ``Generalizations of the double-copy: the KLT bootstrap,''
+    JHEP \textbf{03}, 077 (2022)
+    doi:10.1007/JHEP03(2022)077
+    [arXiv:2106.12600 [hep-th]].
+    50 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author formulate a new program to generalize the double-copy of tree amplitudes. They solve the KLT bootstrap equations perturbatively to find the most general higher-derivative
+    corrections to the 4- and 5-point field theory KLT kernel.
+    \item %\cite{Zhou:2021gnu}
+    X.~Zhou,
+    ``Double Copy Relation in AdS Space,''
+    Phys. Rev. Lett. \textbf{127}, no.14, 141601 (2021)
+    doi:10.1103/PhysRevLett.127.141601
+    [arXiv:2106.07651 [hep-th]].
+    58 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author present a double copy relation in Ad$\mathrm{S}_5$ which relates tree-level four-point amplitudes of supergravity, super Yang-Mills and bi-adjoint scalars.
+    \item %\cite{Campiglia:2021srh}
+    M.~Campiglia and S.~Nagy,
+    ``A double copy for asymptotic symmetries in the self-dual sector,''
+    JHEP \textbf{03}, 262 (2021)
+    doi:10.1007/JHEP03(2021)262
+    [arXiv:2102.01680 [hep-th]].
+    63 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author find an infinite set of double copy constructible symmetries the self-dual sectors
+    of Yang-Mills (YM) and gravity, in the light-cone formulation.
+    \item %\cite{Albayrak:2020fyp}
+    S.~Albayrak, S.~Kharel and D.~Meltzer,
+    ``On duality of color and kinematics in (A)dS momentum space,''
+    JHEP \textbf{03}, 249 (2021)
+    doi:10.1007/JHEP03(2021)249
+    [arXiv:2012.10460 [hep-th]].
+    80 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author explore color-kinematic duality for tree-level AdS/CFT correlators in momentum space, including the integrated correlator and the integrand.
+    \item %\cite{Armstrong:2020woi}
+    C.~Armstrong, A.~E.~Lipstein and J.~Mei,
+    ``Color/kinematics duality in AdS$_{4}$,''
+    JHEP \textbf{02}, 194 (2021)
+    doi:10.1007/JHEP02(2021)194
+    [arXiv:2012.02059 [hep-th]].
+    87 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author find analogous BCJ relations for Yang-Mills amplitudes in AdS4 and spell out the relation to 3d
+    conformal correlators in momentum space, and speculate on the double copy to graviton
+    amplitudes in AdS4.
+    \item %\cite{Casali:2020vuy}
+    E.~Casali and A.~Puhm,
+    ``Double Copy for Celestial Amplitudes,''
+    Phys. Rev. Lett. \textbf{126}, no.10, 101602 (2021)
+    doi:10.1103/PhysRevLett.126.101602
+    [arXiv:2007.15027 [hep-th]].
+    66 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author show that the celestial amplitudes persist the double copy relation by imposing a celestial double copy.
+\end{itemize}
+
+\section*{Gravitational scattering}
+\begin{itemize}
+    \item %\cite{Saketh:2021sri}
+    M.~V.~S.~Saketh, J.~Vines, J.~Steinhoff and A.~Buonanno,
+    ``Conservative and radiative dynamics in classical relativistic scattering and bound systems,''
+    Phys. Rev. Res. \textbf{4}, no.1, 013127 (2022)
+    doi:10.1103/PhysRevResearch.4.013127
+    [arXiv:2109.05994 [gr-qc]].
+    65 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author compute for the first time the changes in linear momentum and the total radiated linear momentum, in the relativistic classical scattering of two
+point-charges, at sixth order in the charge. 
+\end{itemize}
+\section*{Classical double copy}
+\begin{itemize}
+    \item %\cite{Monteiro:2020plf}
+    R.~Monteiro, D.~O'Connell, D.~Peinador Veiga and M.~Sergola,
+    ``Classical solutions and their double copy in split signature,''
+    JHEP \textbf{05}, 268 (2021)
+    doi:10.1007/JHEP05(2021)268
+    [arXiv:2012.11190 [hep-th]].
+    82 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author find a classical interpretation for the three-point amplitude in a split-signature and the double copy
+    of them give some implications of Lorentz signature.
+    spacetime
+    \item %\cite{delaCruz:2020bbn}
+    L.~de la Cruz, B.~Maybee, D.~O'Connell and A.~Ross,
+    ``Classical Yang-Mills observables from amplitudes,''
+    JHEP \textbf{12}, 076 (2020)
+    doi:10.1007/JHEP12(2020)076
+    [arXiv:2009.03842 [hep-th]].
+    73 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author study the classical Yang-Mills observables from the perspective of amplitudes, rather than equations of motion.
+    \item %\cite{Shi:2021qsb}
+    C.~Shi and J.~Plefka,
+    ``Classical double copy of worldline quantum field theory,''
+    Phys. Rev. D \textbf{105}, no.2, 026007 (2022)
+    doi:10.1103/PhysRevD.105.026007
+    [arXiv:2109.10345 [hep-th]].
+    50 citations counted in INSPIRE as of 23 Sep 2024\\
+    The author establish a classical double
+    copy relation of WQFT for classical observables (deflection, radiation).
+    \item %\cite{Easson:2020esh}
+    D.~A.~Easson, C.~Keeler and T.~Manton,
+    ``Classical double copy of nonsingular black holes,''
+    Phys. Rev. D \textbf{102}, no.8, 086015 (2020)
+    doi:10.1103/PhysRevD.102.086015
+    [arXiv:2007.16186 [gr-qc]].
+    53 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author apply the classical double copy procedure to a class of regular, non-singular black hole solutions, 
+    called T-dual-de sitter black hole. They also present the connection
+    between horizons on the gravity side and electric fields on the gauge theory side of the double copy.
+    \item %\cite{Keeler:2020rcv}
+    C.~Keeler, T.~Manton and N.~Monga,
+    ``From Navier-Stokes to Maxwell via Einstein,''
+    JHEP \textbf{08}, 147 (2020)
+    doi:10.1007/JHEP08(2020)147
+    [arXiv:2005.04242 [hep-th]].
+    56 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author build the single copy gauge fields which map to fluid-dual metrics, for two different classes of Navier-Stokes solutions.
+
+\end{itemize}
+\section*{Twistor method}
+\begin{itemize}
+    \item %\cite{White:2020sfn}
+    C.~D.~White,
+    ``Twistorial Foundation for the Classical Double Copy,''
+    Phys. Rev. Lett. \textbf{126}, no.6, 061602 (2021)
+    doi:10.1103/PhysRevLett.126.061602
+    [arXiv:2012.02479 [hep-th]].
+    90 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author show that a particular incarnation - the Weyl double copy - can be derived using well-established
+ideas from twistor theory and answer many questions about double copy.
+\end{itemize}
+\section*{Kinematics algebra}
+\begin{itemize}
+    \item %\cite{Chacon:2020fmr}
+    E.~Chac\'on, H.~Garc\'\i{}a-Compe\'an, A.~Luna, R.~Monteiro and C.~D.~White,
+    ``New heavenly double copies,''
+    JHEP \textbf{03}, 247 (2021)
+    doi:10.1007/JHEP03(2021)247
+    [arXiv:2008.09603 [hep-th]].
+    59 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author generalize the algebra of self-dual YM by  Moyal deformations, in which case the color-kinematic duality is manifest.
+    They also disscuss the classical integrability (or otherwise) of the gauge and gravity theories.
+\end{itemize}
+\section*{BRST double copy}
+\begin{itemize}
+    \item %\cite{Borsten:2020zgj}
+    L.~Borsten, B.~Jur\v{c}o, H.~Kim, T.~Macrelli, C.~Saemann and M.~Wolf,
+    ``Becchi-Rouet-Stora-Tyutin-Lagrangian Double Copy of Yang-Mills Theory,''
+    Phys. Rev. Lett. \textbf{126}, no.19, 191601 (2021)
+    doi:10.1103/PhysRevLett.126.191601
+    [arXiv:2007.13803 [hep-th]].
+    63 citations counted in INSPIRE as of 24 Sep 2024\\
+    The author show that the double copy of gauge theory amplitudes to N = 0 supergravity amplitudes extends from tree level to loop level.
+\end{itemize}
+%\cite{Momeni:2020vvr}
+A.~Momeni, J.~Rumbutis and A.~J.~Tolley,
+``Massive Gravity from Double Copy,''
+JHEP \textbf{12}, 030 (2020)
+doi:10.1007/JHEP12(2020)030
+[arXiv:2004.07853 [hep-th]].
+56 citations counted in INSPIRE as of 24 Sep 2024\\
+THe author explor the possibility of constructing an interacting massive spin-2 theory, i.e.
+massive gravity, as a double copy of massive Yang-Mills theory.
+
 \end{document}

### 2025-03-19 Note/Note.tex
New

\documentclass[12pt]{article}
\usepackage{times}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\begin{document}
\title{Note for scattering amplitude computation}
\author{Su Yingze}
\maketitle
\section{4-point case}
We can start from 4-point to compute the color-ordered amplitude.
\end{document}

### 2025-03-20 Note/Note.tex
New

@@
 \documentclass[12pt]{article}
-\usepackage{times}
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath,amsthm,amssymb}
+\usepackage{amsmath}
 \usepackage{graphicx}
+\setlength{\parindent}{0pt}
+% 使用系统字体，需要 XeLaTeX 或 LuaLaTeX 编译
+\usepackage{fontspec}
+\setmainfont{Times New Roman}
+\usepackage{xcolor}
+\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
+\newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
 \begin{document}
-\title{Note for scattering amplitude computation}
+
+\title{Note for Scattering Amplitude Computation}
 \author{Su Yingze}
 \maketitle
+
 \section{4-point case}
-We can start from 4-point to compute the color-ordered amplitude.
+For the four point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
+configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
+\begin{figure}[htbp]
+    \centering
+    \includegraphics{4pt.eps}
+    \caption{4pt.}
+    \label{fig:myfigure}
+\end{figure}
+
+For the first diagram, the residue equals to
+\begin{equation*}
+    \mathcal{R}es|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
+\end{equation*}
+Similarly, the second one is
+\begin{equation*}
+    \mathcal{R}es|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
+\end{equation*}
+
+Then we can conclude that the four-point color-ordered amplitude $A[1,2,3^+,4^-]$ equals to
+\begin{equation*}
+    A[1,2,3^+,4^-]=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23][42]\avg{24}}=\frac{\avg{24}\avg{14}}{\avg{13}\avg{23}}
+\end{equation*}
+
+\textcolor{red}{$\star Bonus$}
+
+It is still necessary to prove the color-ordered amplitude $A[1,2,3^+,4^+]$ equals to 0. Here we can use the color ordered Feynman rules to show the result.
+\begin{equation*}
+    A[1,2,3^+,4^+]\propto \frac{\left(\epsilon_3\cdot p_2\right)\left(\epsilon_4\cdot p_1\right)}{s_{23}}+\frac{\left(\epsilon_4\cdot p_2\right)\left(\epsilon_3\cdot p_1\right)}{s_{24}} 
+\end{equation*}
+Here we can utilize the spinor-helicity variable to express polarization vector
+\begin{equation*}
+    \epsilon_2^{+\mu}=\frac{\left <r_1|\gamma^\mu|3\right ]}{\sqrt{2}\avg{r_13}},\qquad \epsilon_4^{+\mu}=\frac{\left <r_2|\gamma^\mu|4\right ]}{\sqrt{2}\avg{r_24}}
+\end{equation*}
+here $r_1$ and $r_2$ represent the reference spinor.
+
+We can freely choose $r_1=r_2=1$ or 2, then $\avg{r_1 2}$,$\avg{r_2 1}$,$\avg{r_1 1}$,$\avg{r_2 2}$, two of them equal to 0, so we can conclude that
+\begin{equation*}
+    A[1,2,3^+,4^+]=0
+\end{equation*}
+\section{5-point case}
+For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
+we always consider the MHV (Maximal helicity violation) amplitude. 
+\par
+Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. 
 \end{document}

### 2025-03-21 Note/Note.tex
New

@@
 \usepackage{amsmath}
+\usepackage{cancel}
 \usepackage{graphicx}
+\setlength{\parskip}{0.3em}
 \setlength{\parindent}{0pt}
@@
 \usepackage{xcolor}
+\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
 \newcommand{\avg}[1]{\left\langle #1 \right\rangle}
 \newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
+\newcommand{\inavg}[2]{\langle #1 \rangle\! [#2]}
+\newcommand{\rinavg}[2]{[#1]\!\langle #2 \rangle}
+\newcommand{\aket}[1]{|#1\rangle}
 \begin{document}
@@
 \begin{equation*}
-    \epsilon_2^{+\mu}=\frac{\left <r_1|\gamma^\mu|3\right ]}{\sqrt{2}\avg{r_13}},\qquad \epsilon_4^{+\mu}=\frac{\left <r_2|\gamma^\mu|4\right ]}{\sqrt{2}\avg{r_24}}
+    \epsilon_2^{+\mu}=\frac{\langle r_1 | \gamma^\mu | 3 ]}{\sqrt{2}\avg{r_13}},\qquad \epsilon_4^{+\mu}=\frac{\left <r_2|\gamma^\mu|4\right ]}{\sqrt{2}\avg{r_24}}
 \end{equation*}
@@
 \par
-Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. 
+Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 
+of this kind of gauge theory, the color structure is invariant under the OPP (Order Preserving Permutation), in this case, for example,
+\begin{equation*}
+    (3_1^+,4_1^+,5_2^-)\qquad (3_1^+,5_2^-,4_1^+)\qquad(5_2^-,3_1^+,4_1^+)
+\end{equation*}
+give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude.
+\par
+The amplitude equals to
+\begin{align*}
+    A[1,2,3_1^+,4_1^+,5_2^-]&=A[1,2,\hat{I}^+,5^-]\times\frac{1}{s_{34}}\times A[\hat{3}^+,4^+,\hat{I}^-]\\
+    &=\frac{\doubleavg{15}{25}}{\mdavg{1\hat{I}}{2\hat{I}}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\\
+    &=\frac{\mdavg{15}{25}\bcancel{[34]^3}}{\mdavg{14}{23}\avg{43}\bcancel{[43][43][34]}}\\
+    &=\frac{\mdavg{15}{25}}{\mdavg{23}{34}\avg{41}}\\
+    &=\frac{(-1)\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align*}
+where we use the fact $|\hat{3}\rangle=|\hat{3}\rangle$ and following identities
+\begin{equation*}
+    \inavg{1\hat{I}}{\hat{I}3}=\inavg{14}{43},\quad \inavg{2\hat{I}}{\hat{I}3}=\inavg{24}{43}
+\end{equation*}
+and also
+\begin{align*}
+    \frac{[\hat{I}3]}{[4\hat{I}]}&=-\frac{\rinavg{3\hat{I}}{\hat{I}2}}{\rinavg{4\hat{I}}{\hat{I}2}}=-\frac{\rinavg{34}{42}}{\rinavg{43}{\hat{3}2}},\quad(\avg{\hat{3}2}=\avg{32}+z\avg{22}=\avg{32})\\
+    &=\frac{\avg{42}}{\avg{32}}
+\end{align*}
+here green refers to the particle with (-) helicity, red refers to particles belong to gauge group 1, red refers to particles belong to gauge group 2.
+\par
+Similarly, it is very easy to obtain another color-ordered amplitude $A[1,2,3_1^+,4_1^-,5_2^+]$
+\begin{align*}
+    A[1,2,3_1^+,4_1^-,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{4}}^2\!\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align*}
+and also $A[1,2,3_1^-,4_1^+,5_2^+]$ equals to
+\begin{equation*}
+    A[1,2,3_1^-,4_1^+,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{3}}^2\!\avg{1\textcolor{green}{3}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{equation*}
+But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5 \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
+\section{6-point case}
+Here we consider $(V_2V_2\Phi^\dagger V_1V_1 \Phi)$ case, the corresponding color-ordered amplitude is $A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]$.
+
 \end{document}

### 2025-03-24 Note/Note.tex
New

--- 2025-03-20 Note/Note.tex
@@
 \usepackage{xcolor}
+\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
 \newcommand{\avg}[1]{\left\langle #1 \right\rangle}
 \newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
+\newcommand{\inavg}[2]{\langle #1 \rangle\! [#2]}
+\newcommand{\rinavg}[2]{[#1]\!\langle #2 \rangle}
+\newcommand{\aket}[1]{|#1\rangle}
+\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
+\newcommand{\sket}[1]{|#1]}
 \begin{document}
@@
 \par
-Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. 
+Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 
+of this kind of gauge theory, the color structure is invariant under the OPP (Order Preserving Permutation), in this case, for example,
+\begin{equation*}
+    (3_1^+,4_1^+,5_2^-)\qquad (3_1^+,5_2^-,4_1^+)\qquad(5_2^-,3_1^+,4_1^+)
+\end{equation*}
+give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude.
+\par
+The amplitude equals to
+\begin{align*}
+    A[1,2,3_1^+,4_1^+,5_2^-]&=A[1,2,\hat{I}^+,5^-]\times\frac{1}{s_{34}}\times A[\hat{3}^+,4^+,\hat{I}^-]\\
+    &=\frac{\doubleavg{15}{25}}{\mdavg{1\hat{I}}{2\hat{I}}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\\
+    &=\frac{\mdavg{15}{25}\bcancel{[34]^3}}{\mdavg{14}{23}\avg{43}\bcancel{[43][43][34]}}\\
+    &=\frac{\mdavg{15}{25}}{\mdavg{23}{34}\avg{41}}\\
+    &=\frac{(-1)\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align*}
+where we use the fact $|\hat{3}\rangle=|\hat{3}\rangle$ and following identities
+\begin{equation*}
+    \inavg{1\hat{I}}{\hat{I}3}=\inavg{14}{43},\quad \inavg{2\hat{I}}{\hat{I}3}=\inavg{24}{43}
+\end{equation*}
+and also
+\begin{align*}
+    \frac{[\hat{I}3]}{[4\hat{I}]}&=-\frac{\rinavg{3\hat{I}}{\hat{I}2}}{\rinavg{4\hat{I}}{\hat{I}2}}=-\frac{\rinavg{34}{42}}{\rinavg{43}{\hat{3}2}},\quad(\avg{\hat{3}2}=\avg{32}+z\avg{22}=\avg{32})\\
+    &=\frac{\avg{42}}{\avg{32}}
+\end{align*}
+here green refers to the particle with (-) helicity, red refers to particles belong to gauge group 1, red refers to particles belong to gauge group 2.
+\par
+Similarly, it is very easy to obtain another color-ordered amplitude $A[1,2,3_1^+,4_1^-,5_2^+]$
+\begin{align*}
+    A[1,2,3_1^+,4_1^-,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{4}}^2\!\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align*}
+and also $A[1,2,3_1^-,4_1^+,5_2^+]$ equals to
+\begin{equation*}
+    A[1,2,3_1^-,4_1^+,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{3}}^2\!\avg{1\textcolor{green}{3}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{equation*}
+But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5 \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
+\section{6-point case}
+Here we consider $(V_2V_2\Phi^\dagger V_1V_1 \Phi)$ case, the corresponding color-ordered amplitude is $A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]$.
+Similarly, the fowwling orders all give us the same color factor
+\begin{gather*}
+    (3_1^+,4_1^+,5_2^+,6_2^-)\qquad(3_1^+,5_2^+,4_1^+,6_2^-)\qquad (3_1^+,5_2^+,6_2^-,4_1^+)\\
+    (5_2^+,3_1^+,4_1^+,6_2^-)\qquad(5_2^+,3_1^+,6_2^-,4_1^+)\qquad (5_2^+,6_2^-,3_1^+,4_1^+)
+\end{gather*}
+Only two diagrams have semmingly non-zero contributaion,
+\begin{align*}
+    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\\
+    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\\
+    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\\
+    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
+\end{align*}
+where we have used the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the following identities
+\begin{equation*}
+    \inavg{2\hat{I}}{\hat{I}3}=\inavg{24}{43}, \qquad \rinavg{4\hat{I}}{\hat{I}1}=\rinavg{43}{\hat{3}1}
+\end{equation*}
+The point here is that we first $\avg{\hat{3}1}$ which does not appear in 5-point case, so we nned to compute it carefully
+\begin{gather*}
+    \text{pole position}: \quad \hat{P_{34}}^2=0=2P_3\cdot P_4=\inavg{4\hat{3}}{34}\qquad\Rightarrow \qquad \avg{4\hat{3}}=0\\
+    \avg{43}+z\avg{42}=0\qquad \Rightarrow \qquad z=-\frac{43}{42}
+\end{gather*}
+then
+\begin{align*}
+    \avg{\hat{3}1}=\avg{31}+z\avg{21}&=\avg{31}-\frac{\avg{43}}{\avg{42}}\avg{21}\\
+    &=\frac{\mdavg{42}{31}-\mdavg{43}{21}}{42}\\
+    &=\frac{\mdavg{41}{32}}{\avg{42}}
+\end{align*}
+where we have used the Fierz identity
+\begin{equation*}
+    \mdavg{42}{31}+\mdavg{41}{23}+\mdavg{43}{12}=0.
+\end{equation*}
+Simiraly, we can compute the second diagram
+\begin{equation*}
+    A_2=\frac{[\hat{2}5][5\hat{I}]}{[\hat{I}\hat{2}]}\times\frac{1}{s_{25}}\times \frac{(-1)\asqu{16}\asqu{\hat{I}6}}{\mdavg{\hat{I}\hat{3}}{\hat{3}4}
+    \!\mdavg{41}{\hat{I}6}\!\avg{61}}
+\end{equation*}
+but from the pole position
+\begin{equation*}
+    \hat{P_{25}}^2=0=2P_2\cdot P_5=\inavg{52}{\hat{2}5}\qquad\Rightarrow \qquad [\hat{2}5]=0,
+\end{equation*}
+and simiraly
+\begin{equation*}
+    [\hat{2}\hat{I}]=[5\hat{I}]=0.
+\end{equation*}
+Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$.Finally, we obtain the color-ordered amplitude 
+\begin{equation*}
+    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
+\end{equation*}
+\section{n-point case}
+Here, we first propose a compact formula for the color-ordered amplitude
+\begin{equation*}
+    A
+\end{equation*}
 \end{document}

### 2025-03-25 Note/Note.tex
New

@@
 \usepackage{xcolor}
+\usepackage{float}
 \newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
@@
     \caption{4pt.}
-    \label{fig:myfigure}
+    \label{1}
 \end{figure}
@@
 \par
+If there is no special case, we always choose the following BCFW shift
+\begin{gather*}
+    \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\\
+    \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
+\end{gather*}
+where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.
+\par
 Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 
@@
 \end{equation*}
-give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude.
+give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude. We can draw all diagrams contributing to the BCFW process, the first two are following
 \par
-The amplitude equals to
+\begin{figure}[H]
+    \centering
+    \includegraphics{5pt1.eps}
+    \caption{5pt. 1}
+    \label{2}
+\end{figure}
+It is obvious that the second diagram in Figure 2 equals to 0, because there are no interaction between the two gauge bosons.
+\par
+Similarly, another two diagrams equal to 0 for the same reason
+\begin{figure}
+    \centering
+    \includegraphics{5pt2.eps}
+    \caption{5pt. 2}
+    \label{3}
+\end{figure}
+\par
+The last diagram still gives 0 contribution because it includes a subamplitude $A[1,\hat{I},\hat{3}^+,4^+]=0$.
+\par
+\begin{figure}[H]
+    \centering
+    \includegraphics{5pt3.eps}
+    \caption{5pt. 3}
+    \label{4}
+\end{figure}
+Above all. only the first diagram in Figure 1 has non-vanishing contributions, so the full color ordered amplitude equals to
 \begin{align*}
@@
 \end{equation*}
-But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5 \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
+But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5^+ \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
 \section{6-point case}
@@
 Only two diagrams have semmingly non-zero contributaion,
+\par
+\begin{figure}[H]
+    \centering
+    \includegraphics{6pt.eps}
+    \caption{6pt.}
+    \label{5}
+\end{figure}
+so the full color ordered amplitude equals to
 \begin{align*}
@@
 \end{equation*}
-Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$.Finally, we obtain the color-ordered amplitude 
+Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$. Finally, we obtain the color-ordered amplitude 
 \begin{equation*}
-    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
+    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=A_1+A_2=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
 \end{equation*}
@@
 \begin{equation*}
-    A
+    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
 \end{equation*}
+where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
+refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
+\par
+The usual way to prove this kind of compact formula is deduction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.
+And although there are $\frac{(n_1+n_2)!}{n_1!n_2!}$ OPP, we just need to consider some of them. 
 \end{document}

### 2025-04-03 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Amplication of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude, especially in Yang-Mills theory and gravity.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{From real to complex -- Analytic Continuation}
    \textbf{Why is analytic continuation valid?}
\begin{itemize}
  \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
  \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
  \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
\end{itemize}
    \begin{center}
    \tikz{
      \draw[double equal sign distance, -Implies, line width=1pt] (0,0) -- (0,-1.2);
    }
    \end{center}
\vspace{0.5em}
\centering
\textcolor{red}{Ampltudes can be shifted to complex plane}
\end{frame}

\begin{frame}
    \frametitle{Momentum Shift in BCFW}
    \textbf{What did BCFW do to make the shift?}

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. Then introduce $n$ complex-valued vectors $r_i^\mu$.
    \begin{enumerate}[label=(\roman*)]
        \item $\sum_{i=1}^n r_i^\mu=0$,
        \item $r_i\cdot r_j = 0$ for all $i,j=1, 2, \ldots, n.$ In particular $r_i^2=0$,
        \item $p_i \cdot r_i =0$ for each i (no sum). 
    \end{enumerate}

These vectors $r_i$ are used to define n shifted momenta
\begin{equation*}
    \hat{p}_i^\mu \equiv p_i^\mu + zr_i^\mu \qquad \text{with} z \in \mathcal{C}
\end{equation*}

\end{frame}
\begin{frame}
Note that,
    \begin{enumerate}[label=(\Alph*)]
    \item By property (i), momentum conservation holds for the shifted momenta: $\sum_{i=1}^{n} \hat{p}_i^\mu =0$,
    \item By (ii) and (iii), we have $\hat{p}_i^2=0$, so each shifted momentum is on-shell,
    \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$.
    \end{enumerate}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}
because the $z^2$ term vanishes by property (ii). We can write 
\begin{equation*}
    \hat{P}_I^2 = -\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=-\frac{P_I^2}{2P_I\cdot R_I}
\end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result of (A) and (B) (momentum conservation and on-shell), we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of
    original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    \textcolor{red}{$\bigstar$ The most important point is}
    \begin{equation*}
        \boxed{\color{red}A_n=\hat{A}_n(0)}
    \end{equation*}
\end{frame}

\end{document}

### 2025-04-03 Intermediate report/main.tex
New

@@
 \setmainfont{Times New Roman}
+\usepackage{amsmath}
 \usepackage{bm}
@@
     \par
-    \textcolor{red}{$\bigstar$ The most important point is}
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
+    \textcolor{red}{$\bigstar$ The most important point here is that}
     \begin{equation*}
-        \boxed{\color{red}A_n=\hat{A}_n(0)}
+        \boxed{\color{red}Res|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
+    \end{equation*}
+    It means that the orignal ampltude equals to the residue at orign.
+\end{frame}
+\begin{frame}
+    From Cauchy Theorem, we can ontain
+    \begin{equation*}
+        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
+
+    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
+    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
+    \begin{equation*}
+        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+    \end{equation*}
+    This makes it easy to evaluate the residue at $z=z_I$
+    \begin{equation*}
+        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=
     \end{equation*}

### 2025-04-07 Intermediate report/main.tex
New

@@
 \usepackage{enumitem}
+\usepackage[most]{tcolorbox}
+\tcbset{
+  thickitembox/.style={
+    colback=white,
+    colframe=white,
+    left=2mm,
+    before skip=4pt,
+    after skip=4pt,
+    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
+    enhanced,
+  }
+}
 \setlist[itemize]{label=\textbullet}
@@
 \setlength{\parskip}{0.3em}
+\newcommand{\aket}[1]{|#1\rangle}
+\newcommand{\sket}[1]{|#1]}
+\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
 \AtBeginSection[]{
@@
 }
-\title[Amplication of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
+\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
 \author{Su Yingze}
@@
     \end{equation*}
-    It means that the orignal ampltude equals to the residue at orign.
+    It means that the original amplitude equals to the residue at origin.
 \end{frame}
@@
 
+\begin{frame}
+\frametitle{Little Group}
+    In the context of relativistic QFT, particles are classified according to the unitary irreducible representations of the Poincaré group.
+
+    A crucial concept in this classification is the 
+    \begin{tcolorbox}[thickitembox]
+        \textbf{Little Group:} The subgroup of Lorentz transformations that leaves a given four-momentum invariant.
+    \end{tcolorbox}
+    \begin{itemize}
+        \item \textbf{Massless Case}\\
+        For a massless particle with representative momentum 
+        \begin{equation*}
+            p^\mu=(E,0,0,E)
+        \end{equation*}
+        the little group is $SO(2)\simeq U(1)$.\\
+        In terms of spinor-helicity variables, the massless momentum can be written as
+        \begin{equation*}
+            p_{\alpha \dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item[] The action of the little group is:
+        \begin{equation*}
+            \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
+        \end{equation*}
+        same as 
+        \begin{equation*}
+            \aket{\lambda}\rightarrow t\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+        \end{equation*}
+        The scattering amplitudes should transform covariantly under little group scaling:
+        \begin{equation*}
+            \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
+        \end{equation*}
+        \item \textbf{Massive Case}\\
+        It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{3-point can be completely determined}
+    $\bullet$ 3-particle special kinematics determines an on-shell 3-point amplitude with massless particles depends only on either angle or square brackets of the external momenta.
+
+    Let us suppose thet it depends only on angle brackets, then we can write down the general ansatz
+    \begin{equation*}
+        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
+    \end{equation*}
+    Little group scaling tells us that
+    \begin{equation*}
+        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
+    \end{equation*}
+    We can obtain
+    \begin{equation*}
+        2h_1=-x_{12}-x_{13}
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    Similarly, we can also obtain
+    \begin{equation*}
+        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
+    \end{equation*}
+    Then all index can be solved from this system of equations, so that
+    \begin{equation*}
+        A_3^{h_1h_2h_3}=c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}\quad h_1+h_2+h_3<0.
+    \end{equation*}
+    Also for square brackets case, we can obtain
+    \begin{equation*}
+        A_3^{h_1h_2h_3}=c^{'}[12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}\quad h_1+h_2+h_3>0.
+    \end{equation*}
+    \textbf{Example}: 3-gluon amplitude\\
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
+    \end{equation*}
+\end{frame}
+\section{Scattering in quiver gauge theory}
+\begin{frame}
+    \frametitle{Introduction to quiver gauge theory}
+    The lagrangian can be written like
+    \begin{equation*}
+        \mathcal{L}=-\sum_{i=1}^{k}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k-1}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
+    \end{equation*}
+    here $F_i$ refers to the ith field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
+    \begin{equation*}
+        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iV_{i\mu}\Phi_i+ig_{i+1}\Phi_i V_{i+1\mu}.
+    \end{equation*}
+    It is easy to confirm that this theory is invariant under $SU(N_1)\times SU(N_2)\times\cdots\times SU(N_k)$.
+    \begin{figure}
+        \centering
+        \includegraphics{test.eps}
+        \caption{Quiver gauge theory}
+        \label{1}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Classification of scattering amplitude}
+    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields and one scalar field.
+    The amplitudes in this theory can be classified to many types
+    \begin{columns}[T]
+        \begin{column}{0.48\textwidth}
+            \begin{itemize}
+                \item 3-point
+                    \begin{itemize}
+                        \item $\bm{V_1\Phi\Phi^\dagger}$
+                        \item $\bm{V_2\Phi\Phi^\dagger}$
+                        \item $\bm{V_1V_1V_1}$
+                        \item $\bm{V_2V_2V_2}$
+                    \end{itemize}
+            \end{itemize}
+        \end{column}
+        \begin{column}{0.48\textwidth}
+            \begin{itemize}
+                \item 4-point
+                \begin{itemize}
+                    \item $\bm{V_1V_1V_1V_1}$
+                    \item $\bm{V_2V_2V_2V_2}$
+                    \item $\bm{\Phi^\dagger V_1V_1\Phi}$
+                    \item $\bm{\Phi V_2V_2\Phi^\dagger}$
+                    \item $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$
+                \end{itemize}
+            \end{itemize}
+        \end{column}
+    \end{columns}
+\end{frame}
+
 \end{document}

### 2025-04-08 Intermediate report/main.tex
New

@@
 \usepackage{enumitem}
+\usepackage{subcaption}
 \usepackage[most]{tcolorbox}
@@
 
+\begin{frame}
+    \begin{columns}[T]
+        \begin{column}{0.6\textwidth}
+        \begin{itemize}
+            \item 5-point
+            \begin{itemize}
+                \item $\bm{V_1V_1V_1V_1V_1}$
+                \item $\bm{V_2V_2V_2V_2V_2}$
+                \item $\bm{\Phi^\dagger V_1V_1V_1\Phi}$
+                \item $\bm{\Phi V_2V_2V_2\Phi^\dagger}$
+                \item $\bm{V_2\Phi^\dagger V_1V_1\Phi}$
+                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1}$
+                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_1}$ (Not yet solved)
+                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_2}$ (Not yet solved)
+            \end{itemize}
+        \end{itemize}
+    \end{column}
+    \begin{column}{0.48\textwidth}
+        \begin{itemize}
+            \item 6-point
+            \begin{itemize}
+                \item $\bm{V_1V_1V_1V_1V_1V_1}$
+                \item $\bm{V_2V_2V_2V_2V_2V_2}$
+                \item $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$
+                \item $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$
+                \item $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$
+                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$\\
+                $\qquad$ $\vdots$\\
+                $\qquad$ $ \vdots$
+            \end{itemize}
+        \end{itemize}
+    \end{column}
+    \end{columns}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Color structure}
+    \begin{itemize}
+        \item n$ V_1$ or n$V_2$\\
+        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
+        existing results.
+        \begin{equation*}
+            \boxed{\text{Parke-Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+        \end{equation*}
+        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item $\Phi^\dagger V_1V_1\Phi$
+        \begin{figure}
+            \centering
+            \begin{subfigure}{0.3\textwidth}
+              \includegraphics[width=\linewidth]{sch.pdf}
+              \caption{s channel}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}{0.3\textwidth}
+              \includegraphics[width=\linewidth]{uch.pdf}
+              \caption{u channel}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}{0.3\textwidth}
+              \includegraphics[width=\linewidth]{tch.pdf}
+              \caption{t channel}
+            \end{subfigure}
+          \end{figure}
+        The color factor can be written respectively as following
+        \begin{equation*}
+            r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\,r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\,
+            r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
+        \end{equation*}
+        We can easily obtain a similar Jacobbi relation
+        \begin{equation*}
+            r_t=r_s-r_u
+        \end{equation*}
+        Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item[] For example, in the 4pt. case, the full amplitude can be decomposed to the following form
+        \begin{align*}
+            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\\
+            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\\
+            &=(A_s+A_t)r_s+(A_u-A_t)r_u
+        \end{align*}
+        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
+        \textcolor{red}{[1,2,4,3]} respectively.
+
+        \vspace{0.5em}
+        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
+        It should be noticed that the order only has the relation with the order of external gluon line.
+        \begin{equation*}
+            [1,2,\sigma(3),\sigma(4),\cdots,\sigma(n)]
+        \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item $V_2\Phi^\dagger V_1V_1\Phi$
+    \end{itemize}
+\end{frame}
+
 \end{document}

### 2025-04-09 Intermediate report/main.tex
New

@@
 \newcommand{\sket}[1]{|#1]}
-\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
+\newcommand{\avg}[1]{\langle #1 \rangle}
+\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
 \AtBeginSection[]{
@@
     \begin{equation*}
-        \boxed{\color{red}Res|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
+        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
     \end{equation*}
@@
 \end{frame}
-\section{Scattering in quiver gauge theory}
+\section{Color structure in quiver gauge theory}
 \begin{frame}
@@
     \end{equation*}
-    here $F_i$ refers to the ith field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
+    here $F_i$ refers to the ith gauge field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
     \begin{equation*}
@@
     \frametitle{Classification of scattering amplitude}
-    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields and one scalar field.
+    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields $V_1$, $V_2$ and one scalar field $\Phi$, $\Phi^\dagger$.
     The amplitudes in this theory can be classified to many types
@@
                     \item $\bm{\Phi V_2V_2\Phi^\dagger}$
+                    \item $\bm{\Phi V_2 \Phi^\dagger V_1}$
                     \item $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$
@@
         \begin{equation*}
-            \boxed{\text{Parke-Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
         \end{equation*}
@@
     \begin{itemize}
-        \item $V_2\Phi^\dagger V_1V_1\Phi$
+        \item $\Phi V_2 \Phi^\dagger V_1$\\
+        The color structure for this kind of amplitude has special form, like
+        \begin{equation*}
+            (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
+        \end{equation*}
+        It is more straightforward to observe the color structure in terms of double line notation as follows 
+        \vspace{0.5em}
+
+        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+        \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da7604191870446242] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
+%Straight Lines [id:da7895005569652712] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
+%Straight Lines [id:da19217218880843812] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
+%Straight Lines [id:da7866299736623521] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
+%Straight Lines [id:da5667542352395977] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
+%Straight Lines [id:da33701635654582174] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
+%Straight Lines [id:da7076492571881566] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
+%Straight Lines [id:da3803886589182971] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
+%Straight Lines [id:da696489944746132] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
+%Straight Lines [id:da24340791537710427] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
+%Straight Lines [id:da7298898466192736] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
+%Straight Lines [id:da3460055698725] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
+%Straight Lines [id:da4507056480848969] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
+%Straight Lines [id:da6544383915955476] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
+%Straight Lines [id:da03624471669725382] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
+%Straight Lines [id:da34280653261510274] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;
+
+% Text Node
+\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+% Text Node
+\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+
+        \end{tikzpicture}
+
     \end{itemize}
@@
 
+\begin{frame}
+    \frametitle{OPP(Order preserving permutation)}
+    From the 4 point case, we have known that the relative order between gauge boson 1 and gauge boson 2 does not affect the color structure. 
+    Thus, it is necessary to introduce the \textbf{OPP(Order preserving permutation)}. For example:
+    \begin{equation*}
+        (3_1,4_1,5_2) \quad (3_1,5_2,4_1) \quad (5_2,3_1,4_1)
+    \end{equation*}
+    These three permutations are different OPP for $(3_1,4_1,5_2)$, so that give us the same color factor.
+\end{frame}
+
+\section{Scattering amplitudes from BCFW}
+\begin{frame}
+    \frametitle{Basic building block -- 3-point}
+    From the previous section, we have known that there are only two kinds of 3 point amplitude
+    \begin{gather*}
+        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
+        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5_+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
+    \end{gather*}
+    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
+\end{frame}
+
+\begin{frame}
+    \frametitle{4 point from BCFW}
+    $\bullet \, \Phi^\dagger V_1V_1\Phi$\\
+    Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
+    \begin{gather*}
+        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
+        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
+    \end{gather*}
+    \begin{minipage}{0.5\textwidth}
+        \begin{equation*}
+        A[1,2,3^+,4^-] = \sum_{h}
+        \end{equation*}
+        \end{minipage}
+        \hspace{-3em}
+        \begin{minipage}{0.45\textwidth}
+        \scalebox{0.7}{\includegraphics{4pt1.pdf}}
+        \end{minipage}
+\end{frame}
+
+\begin{frame}
+    $\qquad =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$
+    \vspace{0.5em}
+
+    We denote these two different BCFW channels as $A_1$ and $A_2$, then 
+    \begin{align*}
+        A_1&=\frac{\avg{\hat{2}\hat{I}}\avg{\hat{I}1}}{\avg{1\hat{I}}}\times \frac{1}{s_{12}}\times \frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\\
+        &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+    \end{align*}
+    where we use the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the \textcolor{red}{Fierz Identity}
+    \begin{equation*}
+        [ij][kl]+[il][jk]+[ik][lj]=0
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    Similarly, we can obtain
+    \begin{equation*}
+        A[1,2,3^-,4^+]=(-1)\frac{\avg{13}^2\avg{23}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+    \end{equation*}
+    \textcolor{red}{$\bigstar$ Bonus relation}
+    \begin{equation*}
+        A[1,2,3^+,4^+]=A[1,2,3^-,4^-]=0
+    \end{equation*}
+\end{frame}
+
 \end{document}

### 2025-04-11 Intermediate report/main.tex
New

@@
 \usepackage{subcaption}
+\usepackage{comment}
 \usepackage[most]{tcolorbox}
@@
 \frame{\titlepage}
+\section{Why we need new method?}
+\begin{frame}
+    \frametitle{Why we need new method?}
+    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
+    \begin{itemize}
+        \item How to compute high multiplicity amplitudes, like n gluons scattering.
+        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
+        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
+        \item Is the local field theory the most basic discription for physics?
+    \end{itemize}
+    \includegraphics{Picture1.png}
+\end{frame}
+\begin{frame}
+    \frametitle{From Frynman diagram to On-shell method}
+    On-shell here means that all quantities we use are gauge invariant.
+    Specifically, there are many ingredients under this frame
+    \begin{itemize}
+        \item The analytic continuation for S-matrix.
+        \item The color-ordered amplitudes.
+        \item The BCFW recursion relation.
+        \item The spinor helicity discription for amplitudes.
+    \end{itemize}
+\end{frame}
 \section{Preliminary}
@@
     \frametitle{A brief introduction to BCFW}
-    BCFW recursion relation is a method to compute scattering amplitude, especially in Yang-Mills theory and gravity.
+    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
+    compute higher point amplitudes from lower point.
     \par
@@
  \end{itemize}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Flowchart: Connector [id:dp8833995378786028] 
+\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (100,151.75) ..
+controls (100,139.19) and (110.41,129) ..
+(123.25,129) ..
+controls (136.09,129) and (146.5,139.19) ..
+(146.5,151.75) ..
+controls (146.5,164.31) and (136.09,174.5) ..
+(123.25,174.5) ..
+controls (110.41,174.5) and (100,164.31) ..
+(100,151.75) -- cycle ;
+%Straight Lines [id:da4824712234334869] 
+\draw    (72.5,88.5) -- (107,134) ;
+%Straight Lines [id:da012324134018845356] 
+\draw    (146.5,151.75) -- (202.5,151.5) ;
+%Straight Lines [id:da08630319677446052] 
+\draw    (107,169.5) -- (74.5,207.5) ;
+%Right Arrow [id:dp15563446404618686] 
+\draw   (213,146.88) -- (234.3,146.88) -- (234.3,142) -- (248.5,151.75) -- (234.3,161.5) -- (234.3,156.63) -- (213,156.63) -- cycle ;
+%Flowchart: Connector [id:dp3078703826898672] 
+\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (285,152.75) ..
+controls (285,140.19) and (295.41,130) ..
+(308.25,130) ..
+controls (321.09,130) and (331.5,140.19) ..
+(331.5,152.75) ..
+controls (331.5,165.31) and (321.09,175.5) ..
+(308.25,175.5) ..
+controls (295.41,175.5) and (285,165.31) ..
+(285,152.75) -- cycle ;
+%Flowchart: Connector [id:dp8700788921830469] 
+\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (385,153.75) ..
+controls (385,141.19) and (395.41,131) ..
+(408.25,131) ..
+controls (421.09,131) and (431.5,141.19) ..
+(431.5,153.75) ..
+controls (431.5,166.31) and (421.09,176.5) ..
+(408.25,176.5) ..
+controls (395.41,176.5) and (385,166.31) ..
+(385,153.75) -- cycle ;
+%Straight Lines [id:da3777742197603755] 
+\draw    (331.5,152.75) -- (387.5,152.5) ;
+%Straight Lines [id:da01635751939547947] 
+\draw    (253.5,96.5) -- (288,142) ;
+%Straight Lines [id:da6633767687204817] 
+\draw    (287,165.5) -- (254.5,203.5) ;
+%Straight Lines [id:da3605859970876615] 
+\draw    (458.5,101.5) -- (426,139) ;
+%Straight Lines [id:da9887266785867475] 
+\draw    (427,168.5) -- (462.5,202.5) ;
+%Right Arrow [id:dp7496461117394901] 
+\draw   (477,146.88) -- (498.3,146.88) -- (498.3,142) -- (512.5,151.75) -- (498.3,161.5) -- (498.3,156.63) -- (477,156.63) -- cycle ;
+
+% Text Node
+\draw (516,143.4) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
+
+\end{tikzpicture}
+
 \end{frame}
@@
 \end{frame}
-\section{Color structure in quiver gauge theory}
+\section{Introduction of quiver gauge theory}
 \begin{frame}
-    \frametitle{Introduction to quiver gauge theory}
+    \frametitle{Introduction of Quiver of Moose gauge theory}
+    \begin{itemize}
+        \item Quiver: A container for carring arrows
+        \item Moose: A kind of deer with large horns 
+    \end{itemize}
+
+    In the language of field theories, quiver gauge theories contain gauge fields and fermions, summarized in a pictotial representaion.
+    \begin{figure}
+        \centering
+        \begin{minipage}{0.45\textwidth}
+            \centering
+            \includegraphics[width=0.6\textwidth]{Moosed.jpeg}
+            \caption*{Moose diagram}
+        \end{minipage}
+        \hspace{1em}
+        \begin{minipage}{0.3\textwidth}
+            \begin{gather*}
+                N-\text{sided polygon}\\
+                G: \text{gauge group} \quad SU(m)\\
+                \rightarrow : \text{Unitary scalar fields}\quad \Phi_{ij} 
+            \end{gather*}
+        \end{minipage}
+
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \frametitle{Why we foucs on quiver gauge theory?}
     The lagrangian can be written like
     \begin{equation*}
-        \mathcal{L}=-\sum_{i=1}^{k}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k-1}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
+        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
     \end{equation*}
@@
     \end{equation*}
-    It is easy to confirm that this theory is invariant under $SU(N_1)\times SU(N_2)\times\cdots\times SU(N_k)$.
+    Here, gauge field and scalar field transformed like
+    \begin{equation*}
+        \bm{A_{i\mu}}\rightarrow g_i(x) \bm{A_{i\mu}} g_i^-(x),\qquad \Phi_i\rightarrow g_i(x)\Phi_i g_{i+1}^-(x)
+    \end{equation*}
+    It is easy to confirm that this theory is invariant under $\prod_1^N SU(M)$ gauge group.
+\end{frame}
+\begin{frame}
+    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where the 
+    only the fifth dimension are latticed.
+    \begin{itemize}
+        \item If $SU(m)_1$ and $SU(m)_N$ are connected $\longrightarrow$ $S^2$ compactification
+        \item If not connected $\longrightarrow$ $\mathrm{Interval}$ compactification
+    \end{itemize}
+    After higgsing, we can obtain a spectrum
+    \begin{equation*}
+        M_k^2=4g^2g_s^2\sin^2\left(\frac{\pi k}{N}\right)
+    \end{equation*}
+    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification.
+\end{frame}
+\begin{frame}
+    {What is relation to scattering amplitude?}
+    The critical point is \textcolor{red}{locality}. 
+    \begin{itemize}
+        \item Space-Time Locality $\longrightarrow$ local field theories
+        \item Theory Space Locality $\longrightarrow$ Discretized theory space
+    \end{itemize}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
+\begin{center}
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+        %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+        %Shape: Ellipse [id:dp8504954329776364] 
+        \draw   (104,129.25) ..
+controls (104,123.31) and (108.57,118.5) ..
+(114.2,118.5) ..
+controls (119.84,118.5) and (124.4,123.31) ..
+(124.4,129.25) ..
+controls (124.4,135.19) and (119.84,140) ..
+(114.2,140) ..
+controls (108.57,140) and (104,135.19) ..
+(104,129.25) -- cycle ;
+        %Shape: Ellipse [id:dp885507200032482] 
+        \draw   (219.1,129.25) ..
+controls (219.1,123.31) and (223.66,118.5) ..
+(229.3,118.5) ..
+controls (234.93,118.5) and (239.5,123.31) ..
+(239.5,129.25) ..
+controls (239.5,135.19) and (234.93,140) ..
+(229.3,140) ..
+controls (223.66,140) and (219.1,135.19) ..
+(219.1,129.25) -- cycle ;
+        %Shape: Ellipse [id:dp7989991915217867] 
+        \draw   (180.38,129.25) ..
+controls (180.38,123.31) and (184.95,118.5) ..
+(190.58,118.5) ..
+controls (196.22,118.5) and (200.79,123.31) ..
+(200.79,129.25) ..
+controls (200.79,135.19) and (196.22,140) ..
+(190.58,140) ..
+controls (184.95,140) and (180.38,135.19) ..
+(180.38,129.25) -- cycle ;
+        %Shape: Ellipse [id:dp013562751387628191] 
+        \draw   (142.71,129.25) ..
+controls (142.71,123.31) and (147.28,118.5) ..
+(152.92,118.5) ..
+controls (158.55,118.5) and (163.12,123.31) ..
+(163.12,129.25) ..
+controls (163.12,135.19) and (158.55,140) ..
+(152.92,140) ..
+controls (147.28,140) and (142.71,135.19) ..
+(142.71,129.25) -- cycle ;
+        %Straight Lines [id:da15611587109210845] 
+        \draw    (124.4,129.25) -- (142.71,129.25) ;
+        %Straight Lines [id:da9794450917549196] 
+        \draw    (163.12,129.25) -- (181.43,129.25) ;
+        %Straight Lines [id:da4720621582644091] 
+        \draw    (200.79,129.25) -- (219.1,129.25) ;
+
+        % Text Node
+        \draw (103,93.4) node [anchor=north west][inner sep=0.75pt]    {$G_{1}$};
+        % Text Node
+        \draw (142,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
+        % Text Node
+        \draw (180,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
+        % Text Node
+        \draw (220,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{4}$};
+        % Text Node
+        \draw (124,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
+        % Text Node
+        \draw (164,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
+        % Text Node
+        \draw (203,141.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
+        \end{tikzpicture}
+\end{center}
+If we change this to a scattering diagram
 \begin{figure}
     \centering
-        \includegraphics{test.eps}
-        \caption{Quiver gauge theory}
-        \label{1}
+\begin{minipage}{0.4\textwidth}
+
+    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+    %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+    %Shape: Inductor (Air Core) [id:dp932367781299785] 
+    \draw   (274.98,130.32) -- (281.77,130.32) ..
+controls (281.87,128.3) and (282.81,126.57) ..
+(284.14,125.97) ..
+controls (285.47,125.36) and (286.92,126.01) ..
+(287.8,127.59) ..
+controls (288.47,128.82) and (288.75,130.41) ..
+(288.55,131.96) ..
+controls (288.55,132.56) and (288.21,133.05) ..
+(287.8,133.05) ..
+controls (287.38,133.05) and (287.04,132.56) ..
+(287.04,131.96) ..
+controls (286.85,130.41) and (287.12,128.82) ..
+(287.8,127.59) ..
+controls (288.58,126.27) and (289.67,125.53) ..
+(290.81,125.53) ..
+controls (291.95,125.53) and (293.05,126.27) ..
+(293.83,127.59) ..
+controls (294.5,128.82) and (294.78,130.41) ..
+(294.58,131.96) ..
+controls (294.58,132.56) and (294.24,133.05) ..
+(293.83,133.05) ..
+controls (293.41,133.05) and (293.07,132.56) ..
+(293.07,131.96) ..
+controls (292.88,130.41) and (293.16,128.82) ..
+(293.83,127.59) ..
+controls (294.61,126.27) and (295.7,125.53) ..
+(296.84,125.53) ..
+controls (297.99,125.53) and (299.08,126.27) ..
+(299.86,127.59) ..
+controls (300.53,128.82) and (300.81,130.41) ..
+(300.61,131.96) ..
+controls (300.61,132.56) and (300.28,133.05) ..
+(299.86,133.05) ..
+controls (299.44,133.05) and (299.11,132.56) ..
+(299.11,131.96) ..
+controls (298.91,130.41) and (299.19,128.82) ..
+(299.86,127.59) ..
+controls (300.73,126.01) and (302.18,125.36) ..
+(303.52,125.97) ..
+controls (304.85,126.57) and (305.79,128.3) ..
+(305.89,130.32) -- (312.67,130.32) ;
+    %Straight Lines [id:da12934086227313735] 
+    \draw    (239.95,129.92) -- (274.98,129.92) ;
+    %Straight Lines [id:da483410968594159] 
+    \draw    (274.98,130.32) -- (275.43,159.86) ;
+    %Shape: Inductor (Air Core) [id:dp1480868197800882] 
+    \draw   (339.72,130.32) -- (346.51,130.32) ..
+controls (346.6,128.3) and (347.55,126.57) ..
+(348.88,125.97) ..
+controls (350.21,125.36) and (351.66,126.01) ..
+(352.54,127.59) ..
+controls (353.21,128.82) and (353.48,130.41) ..
+(353.29,131.96) ..
+controls (353.29,132.56) and (352.95,133.05) ..
+(352.54,133.05) ..
+controls (352.12,133.05) and (351.78,132.56) ..
+(351.78,131.96) ..
+controls (351.59,130.41) and (351.86,128.82) ..
+(352.54,127.59) ..
+controls (353.32,126.27) and (354.41,125.53) ..
+(355.55,125.53) ..
+controls (356.69,125.53) and (357.78,126.27) ..
+(358.57,127.59) ..
+controls (359.24,128.82) and (359.52,130.41) ..
+(359.32,131.96) ..
+controls (359.32,132.56) and (358.98,133.05) ..
+(358.57,133.05) ..
+controls (358.15,133.05) and (357.81,132.56) ..
+(357.81,131.96) ..
+controls (357.62,130.41) and (357.89,128.82) ..
+(358.57,127.59) ..
+controls (359.35,126.27) and (360.44,125.53) ..
+(361.58,125.53) ..
+controls (362.72,125.53) and (363.81,126.27) ..
+(364.6,127.59) ..
+controls (365.27,128.82) and (365.55,130.41) ..
+(365.35,131.96) ..
+controls (365.35,132.56) and (365.01,133.05) ..
+(364.6,133.05) ..
+controls (364.18,133.05) and (363.84,132.56) ..
+(363.84,131.96) ..
+controls (363.65,130.41) and (363.92,128.82) ..
+(364.6,127.59) ..
+controls (365.47,126.01) and (366.92,125.36) ..
+(368.26,125.97) ..
+controls (369.59,126.57) and (370.53,128.3) ..
+(370.63,130.32) -- (377.41,130.32) ;
+    %Straight Lines [id:da6722655237119544] 
+    \draw    (311.79,129.92) -- (339.72,129.92) ;
+    %Straight Lines [id:da3803917060459867] 
+    \draw    (339.72,130.32) -- (340.17,159.86) ;
+    %Straight Lines [id:da9202776931220129] 
+    \draw    (377.41,130.32) -- (377.86,159.86) ;
+    %Straight Lines [id:da09703581803647143] 
+    \draw    (377.41,129.92) -- (412.44,129.92) ;
+
+    % Text Node
+    \draw (219.64,120.92) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
+    % Text Node
+    \draw (264.87,163) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
+    % Text Node
+    \draw (279.95,102.3) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
+    % Text Node
+    \draw (311.87,103.11) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
+    % Text Node
+    \draw (330.5,163) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
+    % Text Node
+    \draw (348.23,102.3) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
+    % Text Node
+    \draw (368.63,161.38) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
+    % Text Node
+    \draw (413.86,121.72) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
+
+    \end{tikzpicture}
+
+\end{minipage}
+\hspace{1em}
+\begin{minipage}{0.4\textwidth}
+    \begin{equation*}
+        \sim 1/z^{\textcolor{red}{\textcircled{\textcolor{black}{4}}}}
+    \end{equation*}
+\end{minipage}
 \end{figure}
 \end{frame}
-
 \begin{frame}

### 2025-04-12 Intermediate report/main.tex
New

@@
     \frametitle{From Frynman diagram to On-shell method}
-    On-shell here means that all quantities we use are gauge invariant.
+    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
     Specifically, there are many ingredients under this frame
@@
     \frametitle{From real to complex -- Analytic Continuation}
-    \textbf{Why is analytic continuation valid?}
+    \textbf{Why can we conduct analytic continuation?}
 \begin{itemize}
@@
 \begin{frame}
-\frametitle{Little Group}
-    In the context of relativistic QFT, particles are classified according to the unitary irreducible representations of the Poincaré group.
-
-    A crucial concept in this classification is the 
-    \begin{tcolorbox}[thickitembox]
-        \textbf{Little Group:} The subgroup of Lorentz transformations that leaves a given four-momentum invariant.
-    \end{tcolorbox}
+\frametitle{Spinor-helicity formalism}
+    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
+    Specifically
     \begin{itemize}
-        \item \textbf{Massless Case}\\
-        For a massless particle with representative momentum 
+        \item $\bm{\text{Massless Case}}$\\
     \begin{equation*}
-            p^\mu=(E,0,0,E)
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
+            p^0-p^3 & -p^1+ip^2\\
+            -p^1-ip^2 & p^0+p^3
+        \end{pmatrix*}
     \end{equation*}
-        the little group is $SO(2)\simeq U(1)$.\\
-        In terms of spinor-helicity variables, the massless momentum can be written as
+    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
     \begin{equation*}
-            p_{\alpha \dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}
+        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \end{equation*}
+    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
+    \begin{equation*}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
+    \end{equation*}
+    same as 
+    \begin{equation*}
+        \aket{\lambda}\rightarrow t^-\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
     \end{equation*}
@@
     \begin{itemize}
-        \item[] The action of the little group is:
-        \begin{equation*}
-            \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
-        \end{equation*}
-        same as 
-        \begin{equation*}
-            \aket{\lambda}\rightarrow t\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
-        \end{equation*}
+        \item[]  This redefinition just matches the $U(1)$ little group transformation.
+        \vspace{0.5em}
+
         The scattering amplitudes should transform covariantly under little group scaling:

### 2025-04-14 Intermediate report/main.tex
New

@@
 \usepackage{bm}
+\usepackage{booktabs}
 \usepackage{tikz}
@@
     \end{itemize}
-    \includegraphics{Picture1.png}
 \end{frame}
@@
 \end{equation*}
+Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
+\begin{equation*}
+    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
+\end{equation*}
 
@@
     \begin{equation*}
-        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=
+        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\raisebox{-1em}{\includegraphics[height=3em]{recrel1.pdf}}   
     \end{equation*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Large z behavior}
+    In the BCFW formula, the boundary term $B_n$ affects a lot
+    \begin{equation*}
+        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
+    \begin{equation*}
+        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
+    \end{equation*}
+    Here I show the large z behavior for gluon scattering 
+    \begin{center}
+        \begin{tabular}{lrc}
+            \toprule
+            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
+            \midrule
+            $+$ & $1/z$ & $z^3$ \\
+            $-$ & $1/z$ & $1/z$ \\
+            \bottomrule
+          \end{tabular}
+    \end{center}
+
 \end{frame}
@@
     \begin{equation*}
-        \aket{\lambda}\rightarrow t^-\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
     \end{equation*}
@@
 \begin{frame}
-    \frametitle{Introduction of Quiver of Moose gauge theory}
+    \frametitle{Introduction of Quiver or Moose gauge theory}
     \begin{itemize}

### 2025-04-14 Intermediate report/main.tex
New

@@
 \newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
+\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
 \AtBeginSection[]{
@@
 
-    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. Then introduce $n$ complex-valued vectors $r_i^\mu$.
-    \begin{enumerate}[label=(\roman*)]
-        \item $\sum_{i=1}^n r_i^\mu=0$,
-        \item $r_i\cdot r_j = 0$ for all $i,j=1, 2, \ldots, n.$ In particular $r_i^2=0$,
-        \item $p_i \cdot r_i =0$ for each i (no sum). 
-    \end{enumerate}
-
-These vectors $r_i$ are used to define n shifted momenta
+    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
     \begin{equation*}
-    \hat{p}_i^\mu \equiv p_i^\mu + zr_i^\mu \qquad \text{with} z \in \mathcal{C}
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
     \end{equation*}
-Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
+    satisfying 
     \begin{equation*}
-    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
     \end{equation*}
+    Note that,
+    \begin{itemize}
+        \item Momentum conservation holds for shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
+        \item Each shifted momentum is still on-shell: $\hat{p}_i^2=0$
+        \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
+              \begin{equation*}
+                \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=\frac{P_I^2}{2P_I\cdot k}
+              \end{equation*}
+    \end{itemize}
 
 \end{frame}
-\begin{frame}
-Note that,
-    \begin{enumerate}[label=(\Alph*)]
-    \item By property (i), momentum conservation holds for the shifted momenta: $\sum_{i=1}^{n} \hat{p}_i^\mu =0$,
-    \item By (ii) and (iii), we have $\hat{p}_i^2=0$, so each shifted momentum is on-shell,
-    \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$.
-    \end{enumerate}
-Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
-\begin{equation*}
-    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
-\end{equation*}
-because the $z^2$ term vanishes by property (ii). We can write 
-\begin{equation*}
-    \hat{P}_I^2 = -\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=-\frac{P_I^2}{2P_I\cdot R_I}
-\end{equation*}
-\end{frame}
+
 \begin{frame}
     \frametitle{Fantasitic result from Cauchy Theorem}
-    As a result of (A) and (B) (momentum conservation and on-shell), we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of
-    original real momentum. 
+    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
     \begin{equation*}
@@
     \begin{equation*}
-        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
     \end{equation*}
@@
     \end{equation*}
-    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
+    Here we can notice that there is an ambiguity for the definition, the momentum is invariant under the following redefinition
     \begin{equation*}
@@
             \begin{gather*}
-                N-\text{sided polygon}\\
+                N\text{-sided polygon}\\
                 G: \text{gauge group} \quad SU(m)\\
@@
     \begin{equation*}
-        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iV_{i\mu}\Phi_i+ig_{i+1}\Phi_i V_{i+1\mu}.
+        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iA_{i\mu}\Phi_i+ig_{i+1}\Phi_i A_{i+1\mu}.
     \end{equation*}
@@
     \end{equation*}
-    It is easy to confirm that this theory is invariant under $\prod_1^N SU(M)$ gauge group.
+    It is easy to confirm that this theory is invariant under $\prod_1^N SU(m)$ gauge group.
 \end{frame}
 \begin{frame}
-    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where the 
+    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
     only the fifth dimension are latticed.
@@
 \end{center}
-If we change this to a scattering diagram
+If we change this to a scattering diagram, and compute the large-z behavior
 \begin{figure}
@@
 \end{frame}
+\section{Scattering amplitudes from BCFW}
 \begin{frame}
@@
 \end{frame}
+\begin{frame}
+    \frametitle{Basic building block -- 3-point}
+    From the previous section, we have known that there are only two kinds of 3 point amplitude
+    \begin{gather*}
+        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
+        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
+    \end{gather*}
+    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
+\end{frame}
+\begin{frame}
+    \frametitle{Gauge boson sector}
+    \begin{itemize}
+        \item n$ V_1$ or n$V_2$\\
+        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
+        existing results.
+        \begin{equation*}
+            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+        \end{equation*}
+        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
+    \end{itemize}
+\end{frame}
 
+\begin{frame}
+    \frametitle{QCD like sector}
+    \begin{itemize}
+        \item $\Phi^\dagger V_1V_1\Phi$\\
+        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
+        \begin{gather*}
+        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
+        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
+        \end{gather*}
+        The amplitudes can be computed 
+        \begin{align*}
+            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+        \end{align*}
+        \item $\Phi^\dagger V_1V_1V_1\Phi$
+            \begin{equation*}
+                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+            \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item $\Phi^\dagger (nV_1)\Phi$
+            \begin{equation*}
+                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
+            \end{equation*}
+            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
+                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
+        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pure 2-site amplitude}
+    \begin{itemize}
+        \item $\Phi V_2 \Phi^\dagger V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+        \end{equation*}
+        \item $\Phi V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+        \end{equation*}
+        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
+        \end{equation*}
+
+    \end{itemize}
+\end{frame}
+
+\appendix
+\section{Appendix}
 \begin{frame}
@@
 \end{frame}
-
-\section{Scattering amplitudes from BCFW}
 \begin{frame}

### 2025-04-15 Intermediate report/main.tex
New

@@
 \usepackage{comment}
+\usepackage{slashed}
 \usepackage[most]{tcolorbox}
@@
 }
-\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
+\title[Application of BCFW]{Tree level scattering amplitude in (De)constructed gauge theory}
 \author{Su Yingze}
@@
         \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
-        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
-        \item Is the local field theory the most basic discription for physics?
+        \item Some symmetries are not manifest in the lagrangian level, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM, etc.
+        \item The unexpected simplicity of some amplitudes has led to the speculation that local QFT may not 
+        be the most fundamental framework.
     \end{itemize}
@@
 
+\begin{center}
+
  \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
@@
 
-%Flowchart: Connector [id:dp8833995378786028] 
-\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (100,151.75) ..
-controls (100,139.19) and (110.41,129) ..
-(123.25,129) ..
-controls (136.09,129) and (146.5,139.19) ..
-(146.5,151.75) ..
-controls (146.5,164.31) and (136.09,174.5) ..
-(123.25,174.5) ..
-controls (110.41,174.5) and (100,164.31) ..
-(100,151.75) -- cycle ;
-%Straight Lines [id:da4824712234334869] 
-\draw    (72.5,88.5) -- (107,134) ;
-%Straight Lines [id:da012324134018845356] 
-\draw    (146.5,151.75) -- (202.5,151.5) ;
-%Straight Lines [id:da08630319677446052] 
-\draw    (107,169.5) -- (74.5,207.5) ;
-%Right Arrow [id:dp15563446404618686] 
-\draw   (213,146.88) -- (234.3,146.88) -- (234.3,142) -- (248.5,151.75) -- (234.3,161.5) -- (234.3,156.63) -- (213,156.63) -- cycle ;
-%Flowchart: Connector [id:dp3078703826898672] 
-\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (285,152.75) ..
-controls (285,140.19) and (295.41,130) ..
-(308.25,130) ..
-controls (321.09,130) and (331.5,140.19) ..
-(331.5,152.75) ..
-controls (331.5,165.31) and (321.09,175.5) ..
-(308.25,175.5) ..
-controls (295.41,175.5) and (285,165.31) ..
-(285,152.75) -- cycle ;
-%Flowchart: Connector [id:dp8700788921830469] 
-\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (385,153.75) ..
-controls (385,141.19) and (395.41,131) ..
-(408.25,131) ..
-controls (421.09,131) and (431.5,141.19) ..
-(431.5,153.75) ..
-controls (431.5,166.31) and (421.09,176.5) ..
-(408.25,176.5) ..
-controls (395.41,176.5) and (385,166.31) ..
-(385,153.75) -- cycle ;
-%Straight Lines [id:da3777742197603755] 
-\draw    (331.5,152.75) -- (387.5,152.5) ;
-%Straight Lines [id:da01635751939547947] 
-\draw    (253.5,96.5) -- (288,142) ;
-%Straight Lines [id:da6633767687204817] 
-\draw    (287,165.5) -- (254.5,203.5) ;
-%Straight Lines [id:da3605859970876615] 
-\draw    (458.5,101.5) -- (426,139) ;
-%Straight Lines [id:da9887266785867475] 
-\draw    (427,168.5) -- (462.5,202.5) ;
-%Right Arrow [id:dp7496461117394901] 
-\draw   (477,146.88) -- (498.3,146.88) -- (498.3,142) -- (512.5,151.75) -- (498.3,161.5) -- (498.3,156.63) -- (477,156.63) -- cycle ;
-
-% Text Node
-\draw (516,143.4) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
+ %Shape: Ellipse [id:dp47704771803228196] 
+ \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (179.79,126.94) ..
+controls (179.79,120.82) and (184.73,115.86) ..
+(190.81,115.86) ..
+controls (196.89,115.86) and (201.82,120.82) ..
+(201.82,126.94) ..
+controls (201.82,133.06) and (196.89,138.02) ..
+(190.81,138.02) ..
+controls (184.73,138.02) and (179.79,133.06) ..
+(179.79,126.94) -- cycle ;
+ %Straight Lines [id:da8859462256956995] 
+ \draw    (163,96.75) -- (182.27,118.91) ;
+ %Straight Lines [id:da980370255241411] 
+ \draw    (201.82,126.94) -- (232.38,126.66) ;
+ %Straight Lines [id:da41368612060172827] 
+ \draw    (182.82,135.52) -- (165.75,153.25) ;
+ %Right Arrow [id:dp6770308298589597] 
+ \draw   (240.37,124.24) -- (254.74,124.24) -- (254.74,121.68) -- (264.32,126.8) -- (254.74,131.92) -- (254.74,129.36) -- (240.37,129.36) -- cycle ;
+ %Shape: Ellipse [id:dp9789947232756657] 
+ \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (277.26,126.94) ..
+controls (277.26,120.82) and (282.19,115.86) ..
+(288.27,115.86) ..
+controls (294.35,115.86) and (299.28,120.82) ..
+(299.28,126.94) ..
+controls (299.28,133.06) and (294.35,138.02) ..
+(288.27,138.02) ..
+controls (282.19,138.02) and (277.26,133.06) ..
+(277.26,126.94) -- cycle ;
+ %Straight Lines [id:da15853752019875] 
+ \draw    (263.22,98.41) -- (279.74,118.91) ;
+ %Straight Lines [id:da28595275955528565] 
+ \draw    (299.28,126.94) -- (329.84,126.66) ;
+ %Straight Lines [id:da7505788363123894] 
+ \draw    (280.29,135.52) -- (263.22,153.25) ;
+ %Shape: Ellipse [id:dp870376485686725] 
+ \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (351.87,126.66) ..
+controls (351.87,120.54) and (346.94,115.58) ..
+(340.86,115.58) ..
+controls (334.77,115.58) and (329.84,120.54) ..
+(329.84,126.66) ..
+controls (329.84,132.78) and (334.77,137.74) ..
+(340.86,137.74) ..
+controls (346.94,137.74) and (351.87,132.78) ..
+(351.87,126.66) -- cycle ;
+ %Straight Lines [id:da5791423310908868] 
+ \draw    (363.43,98.97) -- (349.94,118.91) ;
+ %Straight Lines [id:da5454664407915119] 
+ \draw    (349.43,134.42) -- (365.28,152.14) ;
+ %Right Arrow [id:dp848095583389827] 
+ \draw   (368.11,124.79) -- (382.49,124.79) -- (382.49,122.23) -- (392.07,127.35) -- (382.49,132.48) -- (382.49,129.92) -- (368.11,129.92) -- cycle ;
+
+ % Text Node
+ \draw (393.76,120.95) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
 
  \end{tikzpicture}
+\end{center}
 
@@
 \begin{frame}
+    \frametitle{Spinor-Helicity formalisim}
+In the part of introduction to BCFW
+\begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[height=4em]{recrel1.pdf} 
+    \end{minipage}
+    \hspace{0.01em}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \(
+        \vcenter{\hbox{$\rightarrow$}} \quad \text{No helicity appears here}
+        \)
+    \end{minipage}
+\end{figure}
+
+but the S-matrix is a function of moentum $p_i$ and helicity $h_i$
+\begin{center}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Circle [id:dp6973592945628315] 
+\draw  [color={rgb, 255:red, 248; green, 0; blue, 0 }  ,draw opacity=1 ] (302.8,146.93) ..
+controls (302.81,142.78) and (306.18,139.44) ..
+(310.32,139.45) ..
+controls (314.47,139.46) and (317.81,142.83) ..
+(317.8,146.97) ..
+controls (317.79,151.11) and (314.42,154.46) ..
+(310.28,154.45) ..
+controls (306.14,154.44) and (302.79,151.07) ..
+(302.8,146.93) -- cycle ;
+%Straight Lines [id:da7518027963985391] 
+\draw [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ]   (310.28,154.45) -- (296.03,178.04) ;
+\draw [shift={(295,179.75)}, rotate = 301.13] [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt]    {$\mathcal{M}( p_{i} ,h_{i})$};
+% Text Node
+\draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 247; green, 13; blue, 13 }  ,opacity=1 ] [align=left] {How can we catch the information of helicity?};
+
+\end{tikzpicture}
+\end{center}
+The answer is \textbf{Spinor-Helicity formalism} 
+\(
+\xrightarrow{\text{}} 
+\)
+Catch \(p_i\) and \(h_i\) at the same time.
+
+\end{frame}
+\begin{frame}
 \frametitle{Spinor-helicity formalism}
-    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
-    Specifically
-    \begin{itemize}
-        \item $\bm{\text{Massless Case}}$\\
-    \begin{equation*}
-        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
-            p^0-p^3 & -p^1+ip^2\\
-            -p^1-ip^2 & p^0+p^3
-        \end{pmatrix*}
-    \end{equation*}
-    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
-    \begin{equation*}
-        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
-    \end{equation*}
-    Here we can notice that there is an ambiguity for the definition, the momentum is invariant under the following redefinition
-    \begin{equation*}
-        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
+    \begin{itemize}
+        \item $\textbf{\text{Massless Case}}$\\
+    \begin{equation*}
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \end{equation*}
+    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
+    \begin{equation*}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
     \end{equation*}
@@
     \end{equation*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item[]  This redefinition just matches the $U(1)$ little group transformation.
-        \vspace{0.5em}
-
     The scattering amplitudes should transform covariantly under little group scaling:
@@
     \end{equation*}
+    \end{itemize}
+\vspace{-2em}
+    \begin{itemize}
     \item \textbf{Massive Case}\\
@@
 \begin{frame}
-    \frametitle{3-point can be completely determined}
-    $\bullet$ 3-particle special kinematics determines an on-shell 3-point amplitude with massless particles depends only on either angle or square brackets of the external momenta.
-
-    Let us suppose thet it depends only on angle brackets, then we can write down the general ansatz
+    \frametitle{ On-shell 3-point can be completely determined}
+    \textbf{On-shell 3-point for real momentum}
+
+    Because of the constrain from momentum conservation and on-shell condition
+    \begin{equation*}
+        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
+    \end{equation*}
+    All of the contribution 
+    \begin{equation*}
+        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
+    \end{equation*}
+    In terms of Spinor- Helicity variable, we have 
+    \begin{equation*}
+        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
+    \end{equation*}
+    \textcolor{red}{You can not obtain any notrvial thing from 3-point!}
+
+    Of coure, you can introduce non-minimal interaction
+    \begin{equation*}
+        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
+    \end{equation*}
+    but it still equals to 0 in the on-shell case.
+\end{frame}
+
+\begin{frame}
+    \textbf{Another necessarity to introduce complex momentum}
+
+    If the momentum is complexed, we have 
+    \begin{equation*}
+        \avg{12}\neq[21]^*
+    \end{equation*}
+    Then we can obtain
+    \begin{equation*}
+        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
+    \end{equation*}
+    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
     \begin{equation*}
@@
     \end{equation*}
-\end{frame}
-
-\begin{frame}
     Similarly, we can also obtain
@@
     \end{equation*}
+\end{frame}
+
+\begin{frame}
     Then all index can be solved from this system of equations, so that
-    \begin{equation*}
-        A_3^{h_1h_2h_3}=c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}\quad h_1+h_2+h_3<0.
-    \end{equation*}
-    Also for square brackets case, we can obtain
-    \begin{equation*}
-        A_3^{h_1h_2h_3}=c^{'}[12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}\quad h_1+h_2+h_3>0.
-    \end{equation*}
+    \[
+    \boxed{
+    \begin{aligned}
+        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+        \quad & h_1+h_2+h_3 > 0
+    \end{aligned}
+        }
+    \]
+
+    \textbf{\textcolor{red}{$\star$\,All massless 3-point ampltides are completely determined by little froup scalling!}}
+
     \textbf{Example}: 3-gluon amplitude\\
@@
     \end{equation*}
+    There's another possibility 
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
+    \end{equation*}
+    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
 \end{frame}
@@
         \end{equation*}       
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item Compact formula for general case
+        \begin{equation*}
+            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
+        \end{equation*} 
+        \begin{minipage}{0.7\textwidth}
+            \raggedright  % 或者 \centering 或 \raggedleft
+            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
+            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
+            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
+            $\star$: \,Order for gauge group 1\\
+            $\ast$: \,Order for gauge group 2 
+            \end{minipage}
 

### 2025-04-18 Intermediate report/main.tex
New

@@
     \frametitle{Why we need new method?}
-    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
-    \begin{itemize}
-        \item How to compute high multiplicity amplitudes, like n gluons scattering.
-        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
-        \item Some symmetries are not manifest in the lagrangian level, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM, etc.
-        \item The unexpected simplicity of some amplitudes has led to the speculation that local QFT may not 
-        be the most fundamental framework.
-    \end{itemize}
+Feynman diagram is a brilliant method without doubt, helping us compute the scattering process pertubatively.
+\begin{center}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Curve Lines [id:da3663218891074064] 
+\draw    (211.4,171.25) .. controls (275.46,64.25) and (285.26,224.75) .. (345.4,124.75) ;
+%Shape: Ellipse [id:dp631421347808582] 
+\draw  [color={rgb, 255:red, 134; green, 131; blue, 131 }  ,draw opacity=1 ][fill={rgb, 255:red, 133; green, 128; blue, 128 }  ,fill opacity=1 ] (241.14,136) ..
+controls (241.14,130.48) and (246.99,126) ..
+(254.21,126) ..
+controls (261.43,126) and (267.29,130.48) ..
+(267.29,136) ..
+controls (267.29,141.52) and (261.43,146) ..
+(254.21,146) ..
+controls (246.99,146) and (241.14,141.52) ..
+(241.14,136) -- cycle ;
+%Curve Lines [id:da0018479507229188785] 
+\draw    (345.4,124.75) .. controls (376.12,77.25) and (421.23,156.25) .. (458.49,170.25) ;
+%Shape: Ellipse [id:dp37806345751603687] 
+\draw  [color={rgb, 255:red, 128; green, 124; blue, 124 }  ,draw opacity=1 ][fill={rgb, 255:red, 133; green, 129; blue, 129 }  ,fill opacity=1 ] (355.53,113.5) ..
+controls (355.53,107.98) and (361.39,103.5) ..
+(368.61,103.5) ..
+controls (375.83,103.5) and (381.68,107.98) ..
+(381.68,113.5) ..
+controls (381.68,119.02) and (375.83,123.5) ..
+(368.61,123.5) ..
+controls (361.39,123.5) and (355.53,119.02) ..
+(355.53,113.5) -- cycle ;
+%Straight Lines [id:da7438579232631651] 
+\draw    (261.4,183.5) -- (426.42,182.76) ;
+\draw [shift={(428.42,182.75)}, rotate = 179.74] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Curve Lines [id:da40606602539843883] 
+\draw    (316.97,156) .. controls (355.02,142.32) and (265.25,67.01) .. (386.7,69.7) ;
+\draw [shift={(388.54,69.75)}, rotate = 181.61] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (215.9,175.75) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
+% Text Node
+\draw (219.25,90) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont Kinematic/Color}}\\{\small {\fontfamily{ptm}\selectfont  \ \ \ complexity}}};
+% Text Node
+\draw (344.1,86.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Gauge redundancies}}};
+% Text Node
+\draw (440.24,175.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
+% Text Node
+\draw (332.23,166.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textcolor[rgb]{1,0,0}{?}}}};
+% Text Node
+\draw (408.97,63) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.05,0.05}{Feynman diagrams}}}}};
+
+\end{tikzpicture}
+\end{center}
+\vspace{-2.3em}
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Spring [id:dp43786797179465176] 
+\draw   (216.4,104.97) ..
+controls (219.03,103.2) and (222.94,102.68) ..
+(226.33,106.02) ..
+controls (233.1,112.72) and (224.24,121.49) ..
+(220.86,118.14) ..
+controls (217.47,114.8) and (226.33,106.02) ..
+(233.1,112.72) ..
+controls (239.87,119.41) and (231.01,128.19) ..
+(227.63,124.84) ..
+controls (224.24,121.49) and (233.1,112.72) ..
+(239.87,119.41) ..
+controls (246.64,126.11) and (237.78,134.88) ..
+(234.4,131.53) ..
+controls (231.01,128.19) and (239.87,119.41) ..
+(246.64,126.11) ..
+controls (253.41,132.8) and (244.56,141.58) ..
+(241.17,138.23) ..
+controls (237.78,134.88) and (246.64,126.11) ..
+(253.41,132.8) ..
+controls (254.2,133.59) and (254.78,134.4) ..
+(255.18,135.22) ;
+%Shape: Ellipse [id:dp10564067273276767] 
+\draw  [fill={rgb, 255:red, 196; green, 189; blue, 189 }  ,fill opacity=1 ] (252.25,146.07) ..
+controls (252.25,135.17) and (261.17,126.33) ..
+(272.19,126.33) ..
+controls (283.2,126.33) and (292.12,135.17) ..
+(292.12,146.07) ..
+controls (292.12,156.97) and (283.2,165.8) ..
+(272.19,165.8) ..
+controls (261.17,165.8) and (252.25,156.97) ..
+(252.25,146.07) -- cycle ;
+%Shape: Spring [id:dp8051072896719512] 
+\draw   (202.57,146.94) ..
+controls (203.45,144.19) and (206.11,141.62) ..
+(210.87,142.09) ..
+controls (220.4,143.03) and (219.26,154.27) ..
+(214.5,153.79) ..
+controls (209.74,153.32) and (210.87,142.09) ..
+(220.4,143.03) ..
+controls (229.92,143.98) and (228.78,155.21) ..
+(224.02,154.74) ..
+controls (219.26,154.27) and (220.4,143.03) ..
+(229.92,143.98) ..
+controls (239.44,144.92) and (238.31,156.15) ..
+(233.54,155.68) ..
+controls (228.78,155.21) and (229.92,143.98) ..
+(239.44,144.92) ..
+controls (248.97,145.87) and (247.83,157.1) ..
+(243.07,156.63) ..
+controls (238.31,156.15) and (239.44,144.92) ..
+(248.97,145.87) ..
+controls (250.08,145.98) and (251.05,146.23) ..
+(251.89,146.59) ;
+%Shape: Spring [id:dp24229359788253813] 
+\draw   (291.38,147.82) ..
+controls (292.02,144.73) and (294.46,141.66) ..
+(299.24,141.73) ..
+controls (308.81,141.87) and (308.63,154.27) ..
+(303.84,154.2) ..
+controls (299.06,154.13) and (299.24,141.73) ..
+(308.81,141.87) ..
+controls (318.38,142.01) and (318.2,154.41) ..
+(313.41,154.34) ..
+controls (308.63,154.27) and (308.81,141.87) ..
+(318.38,142.01) ..
+controls (327.95,142.15) and (327.77,154.55) ..
+(322.98,154.48) ..
+controls (318.2,154.41) and (318.38,142.01) ..
+(327.95,142.15) ..
+controls (337.52,142.28) and (337.34,154.69) ..
+(332.55,154.62) ..
+controls (327.77,154.55) and (327.95,142.15) ..
+(337.52,142.28) ..
+controls (338.64,142.3) and (339.63,142.49) ..
+(340.49,142.8) ;
+%Shape: Spring [id:dp1840306550125722] 
+\draw   (290.58,139.13) ..
+controls (289.05,136.36) and (288.91,132.46) ..
+(292.6,129.45) ..
+controls (299.99,123.43) and (307.96,133) ..
+(304.26,136.01) ..
+controls (300.57,139.02) and (292.6,129.45) ..
+(299.99,123.43) ..
+controls (307.38,117.41) and (315.35,126.98) ..
+(311.65,129.99) ..
+controls (307.96,133) and (299.99,123.43) ..
+(307.38,117.41) ..
+controls (314.77,111.38) and (322.73,120.96) ..
+(319.04,123.97) ..
+controls (315.35,126.98) and (307.38,117.41) ..
+(314.77,111.38) ..
+controls (322.16,105.36) and (330.12,114.94) ..
+(326.43,117.95) ..
+controls (322.73,120.96) and (314.77,111.38) ..
+(322.16,105.36) ..
+controls (323.02,104.66) and (323.9,104.17) ..
+(324.76,103.85) ;
+%Shape: Spring [id:dp21851269782703253] 
+\draw   (271.73,127.44) ..
+controls (268.6,126.81) and (265.5,124.41) ..
+(265.56,119.67) ..
+controls (265.68,110.2) and (278.2,110.35) ..
+(278.14,115.09) ..
+controls (278.08,119.82) and (265.56,119.67) ..
+(265.68,110.2) ..
+controls (265.79,100.73) and (278.32,100.88) ..
+(278.26,105.61) ..
+controls (278.2,110.35) and (265.68,110.2) ..
+(265.79,100.73) ..
+controls (265.91,91.25) and (278.44,91.4) ..
+(278.38,96.14) ..
+controls (278.32,100.88) and (265.79,100.73) ..
+(265.91,91.25) ..
+controls (266.03,81.78) and (278.55,81.93) ..
+(278.5,86.67) ..
+controls (278.44,91.4) and (265.91,91.25) ..
+(266.03,81.78) ..
+controls (266.04,80.67) and (266.23,79.69) ..
+(266.54,78.84) ;
+%Shape: Spring [id:dp05024762380258474] 
+\draw   (224.2,195.95) ..
+controls (222.44,193.32) and (221.96,189.44) ..
+(225.37,186.13) ..
+controls (232.21,179.5) and (240.98,188.36) ..
+(237.56,191.68) ..
+controls (234.14,194.99) and (225.37,186.13) ..
+(232.21,179.5) ..
+controls (239.05,172.87) and (247.82,181.73) ..
+(244.4,185.05) ..
+controls (240.98,188.36) and (232.21,179.5) ..
+(239.05,172.87) ..
+controls (245.88,166.24) and (254.65,175.1) ..
+(251.24,178.42) ..
+controls (247.82,181.73) and (239.05,172.87) ..
+(245.88,166.24) ..
+controls (252.72,159.61) and (261.49,168.47) ..
+(258.07,171.79) ..
+controls (254.65,175.1) and (245.88,166.24) ..
+(252.72,159.61) ..
+controls (253.52,158.83) and (254.35,158.27) ..
+(255.18,157.88) ;
+%Shape: Spring [id:dp9217960437924791] 
+\draw   (283.39,161.81) ..
+controls (286.03,160.03) and (289.94,159.51) ..
+(293.32,162.86) ..
+controls (300.09,169.56) and (291.24,178.33) ..
+(287.85,174.98) ..
+controls (284.47,171.64) and (293.32,162.86) ..
+(300.09,169.56) ..
+controls (306.86,176.25) and (298.01,185.03) ..
+(294.62,181.68) ..
+controls (291.24,178.33) and (300.09,169.56) ..
+(306.86,176.25) ..
+controls (313.63,182.95) and (304.78,191.72) ..
+(301.39,188.37) ..
+controls (298.01,185.03) and (306.86,176.25) ..
+(313.63,182.95) ..
+controls (320.4,189.64) and (311.55,198.42) ..
+(308.17,195.07) ..
+controls (304.78,191.72) and (313.63,182.95) ..
+(320.4,189.64) ..
+controls (321.2,190.43) and (321.78,191.24) ..
+(322.17,192.06) ;
+
+% Text Node
+\draw (254.1,174.78) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
+% Text Node
+\draw (354,136) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Can we really compute this by hand?}};
+
+\end{tikzpicture}
+
 \end{frame}
@@
     \frametitle{From Frynman diagram to On-shell method}
+    The answer is On-shell method.
+    \begin{center}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da5445374886882226] 
+\draw    (276.25,137) -- (457.5,136.26) ;
+\draw [shift={(459.5,136.25)}, rotate = 179.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
+% Text Node
+\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
+% Text Node
+\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
+
+\end{tikzpicture}
+
+    \end{center}
+
     On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
@@
     \frametitle{A brief introduction to BCFW}
-    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
-    compute higher point amplitudes from lower point.
-    \par
- \begin{itemize}[label=\textbullet]
-    \item Ruth Britto
-    \item Freddy Cachazo
-    \item Bo Feng
-    \item Edward Witten
+BCFW helps us solve one of the problems
+\vspace{-1em}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{BCFW.png}
+\end{figure}
+\vspace{-1em}
+with the cost of introducing \textcolor{red}{complexed momentum}.
+
+BCFW is a method to compute amplitudes recursively, proposed by 
+\begin{itemize}
+    \item Britto, Cachazo, Feng, arXiv: hep-th/0412308
+    \item Britto, Cachazo, Feng, Witten, arXiv: hep-th/0501052
+
 \end{itemize}
@@
     \end{equation*}
-    Note that,
-    \begin{itemize}
-        \item Momentum conservation holds for shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
-        \item Each shifted momentum is still on-shell: $\hat{p}_i^2=0$
-        \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
-              \begin{equation*}
-                \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=\frac{P_I^2}{2P_I\cdot k}
-              \end{equation*}
-    \end{itemize}
-
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Circle [id:dp47058391497271046] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) ..
+controls (266.75,112.19) and (277.94,101) ..
+(291.75,101) ..
+controls (305.56,101) and (316.75,112.19) ..
+(316.75,126) ..
+controls (316.75,139.81) and (305.56,151) ..
+(291.75,151) ..
+controls (277.94,151) and (266.75,139.81) ..
+(266.75,126) -- cycle ;
+%Straight Lines [id:da8759716500759761] 
+\draw    (249,78.25) -- (273.5,109.25) ;
+%Straight Lines [id:da2121821831988906] 
+\draw    (233.5,103.25) -- (266.5,120.75) ;
+%Straight Lines [id:da6378763431676462] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
+%Straight Lines [id:da7508961107891289] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
+%Straight Lines [id:da06317949320750826] 
+\draw    (237,155.25) -- (271.5,140.75) ;
+%Straight Lines [id:da403008866951158] 
+\draw    (261.5,180.25) -- (281.5,149.25) ;
+%Straight Lines [id:da8334043101335312] 
+\draw    (423,119.25) -- (457.5,104.75) ;
+%Straight Lines [id:da03451573841415356] 
+\draw    (418.5,109.75) -- (438.5,78.75) ;
+%Straight Lines [id:da025418352459996796] 
+\draw    (420,140.25) -- (453,157.75) ;
+%Straight Lines [id:da22879254297825424] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
+%Straight Lines [id:da2355772127149045] 
+\draw    (410.5,148.75) -- (435,179.75) ;
+%Shape: Rectangle [id:dp6752662310096104] 
+\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
+%Straight Lines [id:da4580921639862495] 
+\draw    (316.75,126) -- (373.5,125.75) ;
+%Shape: Circle [id:dp8699671429684472] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) ..
+controls (373.5,111.94) and (384.69,100.75) ..
+(398.5,100.75) ..
+controls (412.31,100.75) and (423.5,111.94) ..
+(423.5,125.75) ..
+controls (423.5,139.56) and (412.31,150.75) ..
+(398.5,150.75) ..
+controls (384.69,150.75) and (373.5,139.56) ..
+(373.5,125.75) -- cycle ;
+
+% Text Node
+\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
+% Text Node
+\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
+% Text Node
+\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
+% Text Node
+\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
+% Text Node
+\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
+% Text Node
+\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};
+
+\end{tikzpicture}
+    \end{minipage}
+    \hspace{1em}
+    \begin{minipage}{0.45\textwidth}
+        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
+    \begin{equation*}
+        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
+    \end{equation*}
+
+    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
+    \end{minipage}
+\end{figure} 
 \end{frame}
@@
     \frametitle{Fantasitic result from Cauchy Theorem}
-    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
+    %First, I will show the most important part in this report.
+    \begin{block}{BCFW recursion relation}
+        \begin{equation*}
+            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
+        \end{equation*}
+    \end{block}
+    Brief proof:
+
+    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
     \begin{equation*}
@@
     \end{equation*}
-    and we have known the possible positions of single poles, $z_I$, different propagators give 
-    us different single poles in the z-plane. 
-    \par
+
     If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
@@
     where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
-
-    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
-    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
+    \vspace{-1em}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=0.3\textwidth]{CT.png}
+    \end{figure}
+    \vspace{-1.5em}
+    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
+    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
     \begin{equation*}
@@
     \begin{equation*}
-        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\raisebox{-1em}{\includegraphics[height=3em]{recrel1.pdf}}   
+        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
     \end{equation*}
@@
     \begin{equation*}
-        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
     \end{equation*}
@@
     \end{equation*}
-    same as 
+    same for
     \begin{equation*}
@@
     \end{equation*}
-    \textcolor{red}{You can not obtain any notrvial thing from 3-point!}
+    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}
 
@@
     \end{equation*}
-    but it still equals to 0 in the on-shell case.
+    but it still equals to 0 under the on-shell condition.
 \end{frame}
@@
 
-    \textbf{\textcolor{red}{$\star$\,All massless 3-point ampltides are completely determined by little froup scalling!}}
+    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
 
@@
     \frametitle{Introduction of Quiver or Moose gauge theory}
-    \begin{itemize}
-        \item Quiver: A container for carring arrows
-        \item Moose: A kind of deer with large horns 
-    \end{itemize}
-
-    In the language of field theories, quiver gauge theories contain gauge fields and fermions, summarized in a pictotial representaion.
+    \begin{figure}
+        \centering
+        \begin{minipage}{0.45\textwidth}
+        Quiver: A container for carring arrows\\
+        Moose: A kind of deer with large horns 
+    \end{minipage}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.3\linewidth]{Quiver.jpg}
+        \hspace{1em}
+        \includegraphics[width=0.3\textwidth]{Moose.jpeg}
+
+    \end{minipage}
+\end{figure}
+
+    In the language of field theories, quiver gauge theories contain gauge fields and bi-fundamental scalars, summarized in a pictotial representaion.
     \begin{figure}
@@
     \begin{equation*}
-        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{k}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
+        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{N}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
     \end{equation*}
@@
     \begin{equation*}
-        \bm{A_{i\mu}}\rightarrow g_i(x) \bm{A_{i\mu}} g_i^-(x),\qquad \Phi_i\rightarrow g_i(x)\Phi_i g_{i+1}^-(x)
+        \bm{A_{i\mu}}\rightarrow U_i(x) \bm{A_{i\mu}} U_i^-(x)-\frac{i}{g_i}(\partial\mu U)U^{-1},\qquad \Phi_i\rightarrow U_i(x)\Phi_i U_{i+1}^-(x)
     \end{equation*}
@@
     It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
-    only the fifth dimension are latticed.
+    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
     \begin{itemize}
@@
     \end{itemize}
-    After higgsing, we can obtain a spectrum
-    \begin{equation*}
-        M_k^2=4g^2g_s^2\sin^2\left(\frac{\pi k}{N}\right)
+    After higgsing the scalar field, we can obtain a spectrum
+    \begin{equation*}
+        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
     \end{equation*}
@@
 \begin{frame}
-    \frametitle{Classification of scattering amplitude}
-    For the simplicity, we started front the two-site gauge theory, means that there are only two gauge fields $V_1$, $V_2$ and one scalar field $\Phi$, $\Phi^\dagger$.
-    The amplitudes in this theory can be classified to many types
-    \begin{columns}[T]
-        \begin{column}{0.48\textwidth}
-            \begin{itemize}
-                \item 3-point
-                    \begin{itemize}
-                        \item $\bm{V_1\Phi\Phi^\dagger}$
-                        \item $\bm{V_2\Phi\Phi^\dagger}$
-                        \item $\bm{V_1V_1V_1}$
-                        \item $\bm{V_2V_2V_2}$
-                    \end{itemize}
-            \end{itemize}
-        \end{column}
-        \begin{column}{0.48\textwidth}
-            \begin{itemize}
-                \item 4-point
-                \begin{itemize}
-                    \item $\bm{V_1V_1V_1V_1}$
-                    \item $\bm{V_2V_2V_2V_2}$
-                    \item $\bm{\Phi^\dagger V_1V_1\Phi}$
-                    \item $\bm{\Phi V_2V_2\Phi^\dagger}$
-                    \item $\bm{\Phi V_2 \Phi^\dagger V_1}$
-                    \item $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$
-                \end{itemize}
-            \end{itemize}
-        \end{column}
-    \end{columns}
-\end{frame}
-
-\begin{frame}
-    \begin{columns}[T]
-        \begin{column}{0.6\textwidth}
-        \begin{itemize}
-            \item 5-point
-            \begin{itemize}
-                \item $\bm{V_1V_1V_1V_1V_1}$
-                \item $\bm{V_2V_2V_2V_2V_2}$
-                \item $\bm{\Phi^\dagger V_1V_1V_1\Phi}$
-                \item $\bm{\Phi V_2V_2V_2\Phi^\dagger}$
-                \item $\bm{V_2\Phi^\dagger V_1V_1\Phi}$
-                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1}$
-                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_1}$ (Not yet solved)
-                \item $\textcolor{red}{\Phi\Phi^\dagger\Phi\Phi^\dagger V_2}$ (Not yet solved)
-            \end{itemize}
-        \end{itemize}
-    \end{column}
-    \begin{column}{0.48\textwidth}
-        \begin{itemize}
-            \item 6-point
-            \begin{itemize}
-                \item $\bm{V_1V_1V_1V_1V_1V_1}$
-                \item $\bm{V_2V_2V_2V_2V_2V_2}$
-                \item $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$
-                \item $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$
-                \item $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$
-                \item $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$\\
-                $\qquad$ $\vdots$\\
-                $\qquad$ $ \vdots$
-            \end{itemize}
-        \end{itemize}
-    \end{column}
-    \end{columns}
+    \frametitle{Classification of Scattering Amplitudes}
+    \centering
+    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$. The amplitudes are classified by their multiplicity:
+
+    \vspace{1em}
+
+    \renewcommand{\arraystretch}{1.3}
+    \setlength{\tabcolsep}{6pt}
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
+        \hline
+        $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
+        $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
+        $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
+        $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
+        & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
+        & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
+        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
+        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
+        \hline
+    \end{tabular}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{QCD like sector}
+    \frametitle{SQCD like sector}
     \begin{itemize}
@@
 \end{frame}
-
+\section{Summary and Outlook}
+\begin{frame}
+    \frametitle{Summary}
+    \begin{itemize}
+        \item Introduce the on-shell method, including BCFW recursion relation, color-ordered amplitudes. etc.
+        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
+        \item The locality plays an important role to relate the spacetime locality and field space locality.
+        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas can be obtained.
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{Possible future work}
+
+\begin{center}
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Circle [id:dp9858548351804828] 
+\draw   (351.75,140.5) ..
+controls (351.75,130.84) and (359.59,123) ..
+(369.25,123) ..
+controls (378.91,123) and (386.75,130.84) ..
+(386.75,140.5) ..
+controls (386.75,150.16) and (378.91,158) ..
+(369.25,158) ..
+controls (359.59,158) and (351.75,150.16) ..
+(351.75,140.5) -- cycle ;
+%Straight Lines [id:da97880204376832] 
+\draw    (382.75,152.5) -- (418.61,189.81) ;
+\draw [shift={(420,191.25)}, rotate = 226.13] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da40380915410006823] 
+\draw    (381.25,128) -- (416.59,92.66) ;
+\draw [shift={(418,91.25)}, rotate = 135] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da3536680968554168] 
+\draw    (356.5,127.75) -- (312.17,98.36) ;
+\draw [shift={(310.5,97.25)}, rotate = 33.55] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da43484293892230164] 
+\draw    (356.75,154) -- (311.61,187.07) ;
+\draw [shift={(310,188.25)}, rotate = 323.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da7682811881365084] 
+\draw    (351.75,140.5) -- (298.5,140.26) ;
+\draw [shift={(296.5,140.25)}, rotate = 0.26] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da38096838344174566] 
+\draw    (386.75,140.5) -- (439.5,140.26) ;
+\draw [shift={(441.5,140.25)}, rotate = 179.74] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (353.25,133) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Now}};
+% Text Node
+\draw (371.25,194.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Including gravity?}};
+% Text Node
+\draw (370.25,69.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont BCJ double copy?}};
+% Text Node
+\draw (249.75,57) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Massive scalar or}\\{\fontfamily{ptm}\selectfont  gauge boson?}};
+% Text Node
+\draw (262.75,191) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 3 or 4 site?}};
+% Text Node
+\draw (276.75,132) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont ??}};
+% Text Node
+\draw (443.75,132.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont ??}};
+
+\end{tikzpicture}
+\end{center}
+\end{frame}
+\begin{frame}
+    \centering
+    \Huge Thanks for your attention!
+\end{frame}
 \appendix
@@
 \end{frame}
+\begin{frame}
+    \frametitle{Fantasitic result from Cauchy Theorem}
+    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
+    \begin{equation*}
+        A_n \longrightarrow \hat{A}_n(z)
+    \end{equation*}
+    and we have known the possible positions of single poles, $z_I$, different propagators give 
+    us different single poles in the z-plane. 
+    \par
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
+    \textcolor{red}{$\bigstar$ The most important point here is that}
+    \begin{equation*}
+        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
+    \end{equation*}
+    It means that the original amplitude equals to the residue at origin.
+\end{frame}
 

### 2025-04-19 Intermediate report/main.tex
New

@@
 
-    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the single pole at the origin. 
     \textcolor{red}{$\bigstar$ The most important point here is that}
@@
         \end{equation*}
-        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
+        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
     \end{itemize}
@@
         \begin{equation*}
-            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
+            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
         \end{equation*}       
@@
         \item The locality plays an important role to relate the spacetime locality and field space locality.
-        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas can be obtained.
+        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
     \end{itemize}

### 2025-04-20 Intermediate report/main.tex
New

@@
 \centering
-\textcolor{red}{Ampltudes can be shifted to complex plane}
+\textcolor{red}{Amplitudes can be shifted to complex plane}
 \end{frame}
@@
     \end{equation*}
-    The scattering amplitudes should transform covariantly under little group scaling:
+    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
     \begin{equation*}
@@
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\begin{tikzpicture}[scale=1.2,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
 %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
@@
 % Text Node
-\draw (353.25,133) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Now}};
+\draw (355.25,134) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Now}};
 % Text Node

### 2025-04-24 Note/Note.tex
New

@@
 \usepackage{float}
+\usepackage{caption}
 \newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
-\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
+\newcommand{\avg}[1]{\langle #1 \rangle}
 \newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
@@
 \maketitle
+
+\section{3-point building block}
+We have known that the on-shell 3-point amplitudes can be completely determined by the little group scaling, according to the following formulas
+\begin{align*}
+    A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+    \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+    \quad & h_1+h_2+h_3 > 0
+\end{align*}
+Because of the specialty of this kind of 2 site gauge theory, there are no direct interaction between gauge boson and scalar, so there are only two kinds of 3-point amplitudes.
+\begin{itemize}
+    \item 2 scalar 1 gauge boson
+    \begin{equation*}
+        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\mdavg{23}{31}}{\avg{12}}
+    \end{equation*}
+    \item 3 gauge boson
+    \begin{equation*}
+        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\mdavg{45}{53}}
+    \end{equation*}
+\end{itemize}
+If there are no exceptions, 1 and 2 always represent the antiscalar and scalar respectively, other number represent the gauge boson.
+
+\section{Gauge boson sector}
+In this section, we will show how to build the gauge boson scattering. Because there's no direct interaction between gauge boson 1 and gauge boson 2, so we only need to compute one of them.
+And although we have already known the formulas for MHV color-ordered amplitudes for gluon scattering -- Parke-Talyor Formula 
+\begin{equation*}
+    A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\mdavg{n-1,n}{n1}}
+\end{equation*}
+also for the anti-MHV amplitudes
+\begin{equation*}
+    A[\cdots,i^+,\cdots,j^+,\cdots]=\frac{[ij]^4}{[12][34]\cdots[n-1,n][n1]}
+\end{equation*}
+Here, we will give an concrete example to show how to use BCFW to compute the 4-point amplitudes $A[3^+,4^+,5^-,6^-]$
+
+\begin{figure}[H]
+    \centering
+    \includegraphics{4ptg.pdf}
+    \caption*{4pt gluon}
+\end{figure}
+We choose the $[3,4\rangle$ shift, and it has been proved that $[+,+\rangle$ shift is valid
+\begin{gather*}
+    \sket{\hat{3}}=\sket{3}-z\sket{4},\qquad \qquad \aket{\hat{4}}=\aket{4}+z\aket{3}\\
+    \aket{\hat{3}}=\aket{3}, \qquad \sket{\hat{4}}=\sket{4}.
+\end{gather*}
+The first diagram can be evaluated 
+\begin{equation*}
+    A_1=\frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}\times\frac{1}{s_{36}}\times\frac{\avg{5\hat{I}}^3}{\mdavg{\hat{I}\hat{4}}{\hat{4}5}}
+\end{equation*}
+The point here is that 
+\begin{equation*}
+    \text{Pole position}:\quad \hat{P}_{34}^2=0=\avg{36}[6\hat{3}]\quad \Rightarrow  \quad [6\hat{3}]=0,
+\end{equation*}
+for the similar reason, we can obtain $[\hat{I}6]=[6\hat{3}]=0$, so we conclude that the left part
+\begin{equation*}
+    \frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}=0
+\end{equation*}
+so the first channel is vanishing.
+
+The second diagram can be similarly evaluated
+\begin{align*}
+    A_2&=\frac{\avg{\hat{I}6}^3}{\mdavg{6\hat{3}}{\hat{3}\hat{I}}}\times\frac{1}{s_{36}}\times\frac{[\hat{I}\hat{4}]^3}{[\hat{4}5][5\hat{I}]}\\
+       &=\frac{[34]^3}{[34][45][56][61]}
+\end{align*}
+From this, we can conclude that the color-ordered amplitude equals to
+\begin{equation*}
+    A[3^+,4^+,5^-,6^-]=\frac{[34]^3}{[34][45][56][63]}.
+\end{equation*}
+and it can also be expressed by angle brackets interchangeably
+\begin{equation*}
+    A[3^+,4^+,5^-,6^-]=\frac{\avg{56}^3}{\mdavg{34}{45}\!\mdavg{56}{63}}
+\end{equation*}
+Then, 5-point , 6-point can be recursively computed by using BCFW recursion relation.
+
+\section{SQCD like sector}
+First we explain the color decomposition in this sector by 4 point amplitude $\Phi^\dagger V_1V_1\Phi$
+    \begin{figure}[htbp]
+        \centering
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{sch.pdf}
+            \caption*{s channel}
+        \end{minipage}
+        \hfill
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{uch.pdf}
+            \caption*{u channel}
+        \end{minipage}
+        \hfill
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{tch.pdf}
+            \caption*{t channel}
+        \end{minipage}
+    \end{figure}
+
+    The color factor can be written respectively as following
+    \begin{equation*}
+        r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\,r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\,
+        r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
+    \end{equation*}
+    We can easily obtain a similar Jacobbi relation
+    \begin{equation*}
+        r_t=r_s-r_u
+    \end{equation*}
+    Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.
+
+    For example, in the 4pt. case, the full amplitude can be decomposed to the following form
+        \begin{align*}
+            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\\
+            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\\
+            &=(A_s+A_t)r_s+(A_u-A_t)r_u
+        \end{align*}
+        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
+        \textcolor{red}{[1,2,4,3]} respectively.
+        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
+
+    We start from the 4-point color-ordered $A[1,2,3^+,4^-]$ again
+    \begin{center}
+    \begin{minipage}{0.45\textwidth}
+        \begin{align*}
+        A[1,2,3^+,4^-] &= \sum_{h}
+        \end{align*}
+        \end{minipage}
+        \hspace{-3em}
+        \begin{minipage}{0.45\textwidth}
+        \raisebox{-1em}{\scalebox{0.8}{\includegraphics{4pt1.pdf}}}
+        \end{minipage}
+    \end{center}
+
+    $\hspace{13.7em} =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$
 

### 2025-04-25 Note/Note.tex
New

@@
 \usepackage{cancel}
+\usepackage{tikz}
 \usepackage{graphicx}
@@
 \newcommand{\sket}[1]{|#1]}
+\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
+\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
 \begin{document}
@@
 \section{SQCD like sector}
+\subsection{4-point case}
 First we explain the color decomposition in this sector by 4 point amplitude $\Phi^\dagger V_1V_1\Phi$
@@
 
-\section{4-point case}
+    For the same reason, the contribution from the second diagram is vanishing, so we only need to compute the firt one
+    \begin{align*}
+        A_1&=\frac{\avg{\hat{2}\hat{I}}\avg{\hat{I}1}}{\avg{1\hat{I}}}\times \frac{1}{s_{12}}\times \frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\\
+        &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+    \end{align*}
+    where we use the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the \textcolor{red}{Fierz Identity}
+    \begin{equation*}
+        [ij][kl]+[il][jk]+[ik][lj]=0
+    \end{equation*}
+
+    Here we can prove a nonus relation $\textcolor{red}{A[1,2,3^+,4^+]=0}$. Because of the vanishing of 3 gluon amplitude $A[+,+,+]$, so we only have one channel
+    \begin{figure}[H]
+        \centering
+        \includegraphics{4pt+.pdf}
+        \caption*{all plus}
+    \end{figure}
+
+    Similarly, beacuse of the on-shell pole, we obtain
+    \begin{equation*}
+        [\hat{2}\hat{I}]=[\hat{I}1]=[1\hat{2}]=0,
+    \end{equation*}
+    so the contributaion from the left part
+    \begin{equation*}
+        \frac{[\hat{2}\hat{I}][\hat{I}1]}{[1\hat{2}]}=0,
+    \end{equation*}
+    then we can conclude that
+    \begin{equation*}
+        \textcolor{red}{A[1,2,3^+,4^+]=0}
+    \end{equation*}
+\subsection{5-point case}
+Still, from the 4-point amplitude, we can first obtain 
+\begin{equation*}
+    \textcolor{red}{A[1,2,3^+,4^+,5^+]}.
+\end{equation*}
+For the 5-point MHV case, here we only consider the $(+,+,-)$ case. 
+\begin{align*}
+    A[1,2,3^+,4^+,5^+]&=\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.1.pdf}}}+\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.2.pdf}}}\\
+    &=0+\frac{\avg{2\hat{5}}^2\avg{15}}{\avg{12}\!\mdavg{2\hat{I}}{\hat{I}5}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}3]}
+\end{align*}
+then we use
+\begin{equation*}
+    \cbrak{2\hat{I}}{\hat{I3}}=\cbrak{24}{43},\quad \acbrak{4\hat{I}}{\hat{I}5}=\acbrak{43}{\hat{3}5}
+\end{equation*}
+from the pole position
+\begin{gather*}
+    \hat{P}_{34}^2=0=\cbrak{\hat{3}4}{43}\quad \Rightarrow \quad \avg{\hat{3}4}=0\\
+    \avg{34}+z\avg{24}=0\qquad\Rightarrow\quad z=-\frac{\avg{34}}{\avg{24}}
+\end{gather*}
+so
+\begin{equation*}
+    \avg{\hat{3}5}=\frac{\mdavg{32}{54}}{\avg{24}}
+\end{equation*}
+Then the color-ordered amplitude equals to 
+\begin{equation*}
+    A[1,2,3^+,4^+,5^+]=\frac{\avg{15}^2\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+\end{equation*}
+\subsection{n-point case}
+It is not so hard to generallize these results to general case, here we only provide the compact formula, and the negligible sign are neglected
+\begin{equation*}
+    A[1,2,\cdots,n^-]=\frac{\avg{1,n}^2\avg{2,n}^2}{\mdavg{12}{23}\cdots\mdavg{n-1,1}{n,1}}
+\end{equation*} 
+\section{Pure 2-site sector}
+\subsection{4-point case}
+The color structure for this kind of amplitude has special form, like
+\begin{equation*}
+    (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
+\end{equation*}
+It is more straightforward to observe the color structure in terms of double line notation as follows 
+\vspace{0.5em}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
+\begin{center}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da7604191870446242] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
+%Straight Lines [id:da7895005569652712] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
+%Straight Lines [id:da19217218880843812] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
+%Straight Lines [id:da7866299736623521] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
+%Straight Lines [id:da5667542352395977] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
+%Straight Lines [id:da33701635654582174] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
+%Straight Lines [id:da7076492571881566] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
+%Straight Lines [id:da3803886589182971] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
+%Straight Lines [id:da696489944746132] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
+%Straight Lines [id:da24340791537710427] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
+%Straight Lines [id:da7298898466192736] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
+%Straight Lines [id:da3460055698725] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
+%Straight Lines [id:da4507056480848969] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
+%Straight Lines [id:da6544383915955476] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
+%Straight Lines [id:da03624471669725382] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
+%Straight Lines [id:da34280653261510274] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;
+
+% Text Node
+\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+% Text Node
+\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+
+\end{tikzpicture}
+\end{center}
 For the four point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
@@
 \end{equation*}
-\section{5-point case}
+\subsection{5-point case}
 For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
@@
 But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5^+ \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
-\section{6-point case}
+\subsection{6-point case}
 Here we consider $(V_2V_2\Phi^\dagger V_1V_1 \Phi)$ case, the corresponding color-ordered amplitude is $A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]$.
@@
 \end{equation*}
-\section{n-point case}
+\subsection{n-point case}
 Here, we first propose a compact formula for the color-ordered amplitude

### 2025-04-26 Note/Note.tex
New

@@
         Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
+
+    If there is no special case, we always choose the following BCFW shift
+        \begin{gather*}
+            \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\\
+            \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
+        \end{gather*}
+    where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.
 
@@
 \end{center}
-For the four point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
+For the 4-point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
 configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
@@
 
-For the first diagram, the residue equals to
+Because we choose $[2,3\rangle$ shift here, so there is only one valid BCFW channel
+\begin{align*}
+    A[1,2,3_1^+,4_2^-]&=\frac{\mdavg{\hat{2}4}{4\hat{I}}}{\avg{\hat{I}\hat{2}}}\times\frac{1}{s_{24}}\times\frac{[\hat{I}\hat{3}][\hat{3}1]}{[1\hat{I}]}\\
+    &=\frac{[13][23]}{[14][24]}
+\end{align*}
+it seems that this amplitude is different from others before, because it is expressed solely in terms of angle brackets, but of course it can be rewritten to another form.
+\begin{align*}
+    \frac{[13][23]}{[14][24]}&=\frac{\cbrak{23}{31}}{\cbrak{23}{41}}\times \frac{\acbrak{23}{31}}{\acbrak{24}{31}}\\
+    &=-\frac{\cbrak{24}{\bcancel{41}}}{\avg{23}\bcancel{[41]}}\times(-1)\frac{\bcancel{[24]}\avg{41}}{\bcancel{[24]}\avg{31}}\\
+    &=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+\end{align*}
+Also, we can compute it from direct gluing. For the first diagram, the residue equals to
 \begin{equation*}
-    \mathcal{R}es|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
+    \mathrm{Res}|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
 \end{equation*}
@@
 \begin{equation*}
-    \mathcal{R}es|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
+    \mathrm{Res}|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
 \end{equation*}
@@
 we always consider the MHV (Maximal helicity violation) amplitude.
-\par
-If there is no special case, we always choose the following BCFW shift
-\begin{gather*}
-    \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\\
-    \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
-\end{gather*}
-where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.
-\par
+
 Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 

### 2025-05-09 Master Thesis/main.tex
New

\documentclass[11pt]{JHEP}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Your Paper Title}
\author{Your Name\\
Your Institute\\
\email{your.email@domain}}

\abstract{
A short summary of your paper goes here. This includes background, results, and key findings.
}

\begin{document}

\section{Introduction}

This is the introduction to your JHEP-style article. You can cite as in~\cite{sample}.

\section{Main Results}

Equation example:
\begin{equation}
    E = mc^2
\end{equation}

\section{Conclusion}

Summarize what you found and its implications.

\bibliographystyle{JHEP}
\bibliography{references}

\end{document}

### 2025-05-09 Master Thesis/thesis.tex
New

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\onehalfspacing

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{2cm}

    {\LARGE \textbf{Tree Level Scattering Amplitudes in (De)Constructed Gauge Theory}}\\[1.5cm]

    \textbf{Author:} \\
    {\Large Su Yingze} \\[1cm]

    \textbf{Affiliation:} \\
    Department of Physics, Faculty of Science \\
    Nagoya University \\[1cm]

    \textbf{Major:} \\
    Theoretical Physics \\[1cm]

    \textbf{Degree:} \\
    Master of Science \\[1cm]

    \textbf{Submitted on:} \\
    June 2025 \\[2cm]

    \vfill
\end{titlepage}
\newpage
\begin{abstract}
\normalsize
This paper mainly show the computation for scattering amplitudes in a kind of (De)Constructed gauge theory, by using the so called on shell method. As we have known,
under the conventional quantum field theory frame, Feynman proposed a brilliant method -- Feynman diagrams, to help us perturbatively compute scattering amplitude by a
diagrammatic method. However, this method faces many challenges during the improvements of physical theory and complexity of construction for model building, there are many
amplitudes hard to compute by hand or even impossible to compute. Hence, it is quite necessary to introduce a new method.      
\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}
As we have known,
under the conventional quantum field theory frame, Richard Feynman proposed a brilliant method -- Feynman diagrams, to help us perturbatively compute scattering amplitude by a
diagrammatic method. However, this method faces many challenges during the improvements of physical theory and complexity of construction for model building, there are many
amplitudes hard to compute by hand or even impossible to compute. In gauge theory, there are huge number of gauge redundancies, making the computation quite complicated.
We need to address with this kind of unphysical degree of freedom, otherwise we can not obtain the correct physical quantities. Also, we have to address with kinematic factor and color factor simultaneously in the nonabelian gauge theory.
And it has been known that the amplitudes in $\mathcal{N}=4$ super Yang-Mills theory obtain the symmetry -- dual superconformal symmetry\cite{Drummond:2008vq}, which is not reflected in conventional Feynman diagram method.

Hence, all of these factors impetus physicists to propose something new, then the BCFW recursion relation is the first product as a new method to compute amplitudes . Historically, the original recursion relation is for gluon scattering amplitudes, coming from Britto, Cachazo and Feng \cite{Britto:2004ap},
and it can be seen as the first breakthrough for modern amplitude method. They explored the analytic properties of amplitudes when extended into complex momentum space. In particular, they considered deforming two external momenta by a complex parameter z, in such a way that the on-shell conditions and momentum conservation are preserved.
Through this deformation, they observed that tree-level amplitudes exhibit simple pole structures in the complex 
z-plane, corresponding to internal propagators going on-shell. This analytic structure allowed them to derive a recursion relation that expresses an 
n-point amplitude in terms of lower-point amplitudes. Edward Witten subsequently noticed that his Twistor String Theory\cite{Witten:2003nn}, which reveals the hidden symmetry and geometry structure of amplitude, implied that the scattering amplitudes has stronger 
analytic property. Their collaboration led to a general formulation of the recursion relations, now known as the BCFW recursion relations\cite{Britto:2005fq}, named after Ruth Britto, Freddy Cachazo, Bo Feng, and Edward Witten.
In particular, Witten helped clarify the large -- z behavior of the amplitudes under complex momentum shifts --- a crucial condition ensuring the validity of the recursion.

The starting point comes from the precise cancellation in scattering for longitudinal modes of massive spin-2 Kaluza-Klein(KK) states. While individual contributions grow as $\mathcal{O}(s^5)$, $\mathcal{O}(s^4)$, $\mathcal{O}(s^3)$ and $\mathcal{O}(s^2)$, it has been proved that these contributions are cancelled with
each other in a quite intricate way\cite{SekharChivukula:2019yul}, and the final results only grow as $\mathcal{O}(s)$. But it is quite difficult to compute this kind of scattering amplitudes, so if we can obtain some clues for this KK scattering amplitudes from other aspects, it may help us to
understand this cancellation in another way. This paper is motivated by a kind of (De)constructed gauge theory, proposed by Nima, Cohen and Georgi\cite{Arkani-Hamed:2001kyx}. They constructed a renormalizable, asymptotically free, four dimension gauge theories that dynamically generate a fifth dimension. 
In this paper, the authors proposed that the “ Condensed '' theory actually discretized a five dimension gauge theory with gauge group $SU(m)$. After higgsing, the Kaluza-Klein spectrum for $S^1$ compactification appears. It encourages to compute scattering amplitudes in this model. This paper mainly contributes to the 
computation for scattering amplitudes in the simplest 2-site model by utilizing BCFW recursion relation and other related method, such as color-ordered amplitudes, spinor-helicity formalism, etc.

\section{Review of BCFW recursion relation and others}
Traditionally, one relies on Feynman diagrams to calculate scattering amplitudes. Feynman diagrams
provide a clear picture of physics and a systematic procedure of calculations. They are in textbooks
and widely used. But Feynman diagrams are not efficient in complicated calculations for high energy physics. Increasing
the number of particles in a scattering, the number of Feynman diagrams increase exponentially. If gauge
fields are involved, one easily encounters thousands of diagrams. For example, for pure gluon case, the number
of Feynman diagrams for n-gluons at tree-level is given by
\begin{table}[htbp]
    \centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    n= & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
    \hline
       & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900   \\
    \hline
    \end{tabular}
\end{table}

\noindent
{
(These numbers are counted with the inclusion of 4 point interaction.)}

Not only with huge number
of diagrams, the expression for a single Feynman diagram can also be very complicated. For example, the
three-graviton vertex has almost 100 terms. It is almost impossible to calculate scattering amplitudes of
gravitons directly from Feynman diagrams. For gauge theories, single Feynman diagram usually depends
on the gauge. Many terms cancel with each other at the end of process of calculation. In practice, one does not
even know where to start most times.

BCFW are devised to solve some of these problems. So in the following part, I will give a systematic introduction to BCFW
recursion relation and other necessary tools. This section is mainly based on the excellent review by Elvang and Huang \cite{Elvang:2013cua}.
\subsection{Spinor-Helicity Formalisim for Massless Particles}
The spinor-helicity formalism just told us that a light-like Lorentz 4-vector can be decomposed to the product of 
two Weyl spinor. It is quite natural to see it from the representation of Lorentz group. A Lorentz 4-vector lives in $(\frac{1}{2},\frac{1}{2})$ representation,
which can be decomposed to $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$. We have known that the $(\frac{1}{2},0)$ and $(0,\frac{1}{2})$ correspond to left handed Weyl spinor and 
right handed Weyl spinor respectively.

Given a null momentum $p_\mu$ in four dimension spacetime, we can define a $2\times2$ matrix by sigma matrix 
\begin{equation*}
    p_{\alpha\dot{\alpha}}=p_\mu\sigma^\mu=\begin{pmatrix}
        p^0-p^3 & -p^1+ip^2\\
        -p^1-ip^2 & p^0+p^3
    \end{pmatrix}
\end{equation*}
note that det$p_{\alpha\dot{\alpha}}=0$ for massless particles, so it is always possible find two Weyl spinor(two components quantity) satsfying the following equation
\begin{equation}
    p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \label{2.1}
\end{equation}
For general complex momenta, the $\lambda_\alpha$ and $\tilde{\lambda}_{\dot{\alpha}}$ are independent two dimensional complex vectors. For real momenta, the matrix is Hermitian and 
so we have $\tilde{\lambda}_{\dot{\alpha}}=(\pm)(\lambda_\alpha)^*$.

Thet satisfy the following Weyl equation
\begin{equation}
    p_{\alpha\dot{\alpha}}\sket{p}^{\dot{\alpha}}=0,\quad [p|_{\dot{\alpha}}p^{\dot{\alpha}\alpha}=0,\quad p^{\dot{\alpha}\alpha}\aket{p}_\alpha,\quad \langle p|^\alpha p_{\alpha\dot{\alpha}}=0
\end{equation}
and we can use two-dimension antisymmetric tensor to raise or lower the indices
\begin{equation}
    [p|_{\dot{\alpha}}=\varepsilon _{\dot{\alpha}\dot{\beta}}\sket{p}^{\dot{\beta}},\qquad \langle p|^\alpha=\varepsilon^{\alpha\beta}\aket{p}_{\beta}
\end{equation}
\noindent
Then,

\boxed{\text{The angle and square spinors are the core of \textbf{spinor-helicity formalism}}.}

\vspace{1em}
Here, it is also necessary to introduce the \textbf{angle spinor bracket} $\avg{pq}$ and \textbf{square spinor bracket} $[pq]$, it is the key ingredient for writing amplitudes in terms of spinor-helicity variable.
\begin{equation}
    \avg{pq}=\langle p|^\alpha \aket{q}_\alpha,\qquad [pq]=[p|_{\dot{\alpha}}|q]^{\dot{\alpha}}.
\end{equation}
Since the indices are raised and lowed by antisymmetric tensor, so the brackets are antisymmetric:
\begin{equation}
    \avg{pq}=-\avg{qp},\qquad [pq]=-[qp].
\end{equation}
There are no $\langle pq]$ brackets, because the indices cannot contract with each other to form a Lorentz scalar.

It is very easy to derive the following important relation:
\begin{equation}
    \cbrak{pq}{pq}=2p\cdot q= (p+q)^2
\end{equation}
by using \eqref{2.1} and 
\begin{equation*}
    \mathrm{Tr}(\sigma^\mu \bar{\sigma}^\nu)=2\eta^{\mu\nu}.
\end{equation*}

In amplitude calculations, \textbf{momentum conservation} is imposed on n particles as $\sum_{i=1}^{n}p_i^\mu=0$(here we consider all particles ingoing). Translating by 
spinor-helicity variable, it becomes
\begin{equation}
   \sum_{i=1}^{n}\aket{i}[i|=0,\quad \text{i.e.}\quad \sum_{i=1}^{n}\cbrak{qi}{ik}=0,
\end{equation}
here q and k are arbitrary light-like vectors.

We end this subsection by introducing one more identity: \textbf{Schouten Identity}. It comes from a rather trivial fact: there are no three independent 2-dimensional vectors. So if we have three 2 components angle spinors $\aket{i}$, $\aket{j}$ and $\aket{k}$, we can write one of them as a linear combination of two others
\begin{equation}
    \aket{k}=a\aket{i}+b\aket{j},\qquad \text{for complex a and b}.
    \label{2.8}
\end{equation} 
One can contract a $\aket{i}$ and a $\aket{b}$ with the both sides, then a,b can be solved. \eqref{2.8} can be cast to the form
\begin{equation}
    \aket{i}\avg{jk}+\aket{k}\avg{ij}+\aket{j}\avg{ki}=0,
\end{equation}
This is Schouten identity and often written with a fourth spinor $\langle r|$
\begin{equation}
    \mdavg{ri}{jk}+\mdavg{rk}{ij}+\mdavg{rk}{ki}=0.
\end{equation}
We have a similar Schouten identity holding for square spinors
\begin{equation}
    [ri][jk]+[rk][ij]+[rj][ki]=0.
\end{equation}

\subsection{BCFW recursion relation}

\bibliographystyle{unsrt}
\bibliography{reference.bib}

\end{document}

### 2025-05-12 Master Thesis/thesis.tex
New

@@
 \subsection{Spinor-Helicity Formalisim for Massless Particles}
+\subsubsection{Brief introduction of spinor-helicity formalism}
 The spinor-helicity formalism just told us that a light-like Lorentz 4-vector can be decomposed to the product of 
@@
 \begin{equation}
-    \mdavg{ri}{jk}+\mdavg{rk}{ij}+\mdavg{rk}{ki}=0.
+    \cbrak{ri}{jk}+\mdavg{rk}{ij}+\mdavg{rk}{ki}=0.
 \end{equation}
@@
 
+There is also a important result can be obtained, the \textbf{3-particle soecial kinematics}. If we have three light-like vectors satisfying momentum conservation
+$p_1^\mu+p_2^\mu+p_3^\mu=0$. Then
+\begin{equation}
+    \mdavg{12}{21}=2p_1\cdot p_2=(p_1+p_2)^2=p_3^2=0,
+\end{equation}
+so either $\avg{12}$ or $[12]$ equals to 0. If we suppose $\avg{12}\neq0$, then from $\avg{12}[23]=\langle 1|p_2|3]=-\langle 1|p_1+p_3|3]=0$, we can conclude that
+$[23]=0$. Similarly, we can also obtain $[31]=0$. Thus, $[12]=[23]=[31]=0$, which means that the three square spinors are proportional with each other
+\begin{equation}
+    |1] \propto |2] \propto |3]
+\end{equation}
+or another possibility
+\begin{equation}
+    \aket{1}\propto\aket{2}\propto\aket{3}.
+\end{equation}
+As a consequence,
+\begin{enumerate}
+    \item A non-vanishing on-shell 3-particle amplitude depends only on square brackets or angle brackets.
+    \item Since for real momenta, angle brackets are complex conjugated with square brackets, so \textit{on-shell 3 point amplitudes are only meanful for complex momenta}(unless it is a constant, like $\phi^3$ theory).
+\end{enumerate}
+\subsubsection{Yang-Mills and Color-ordering}
+Let us consider the Yang-Mills lagrangian
+\begin{equation}
+    \mathcal{L}=-\frac{1}{4}F_{\mu\nu}F^{\mu\nu},
+\end{equation}
+with field strength $F_{\mu\nu}=\partial_\mu A_\nu -  \partial_\nu A_\mu - \frac{ig}{\sqrt{2}}[A_\mu,A_\nu]$, and $A_\mu=A_\mu^a T^a$.
+Gauge fields belong to adjoint representation, so the index a runs over $1,2 \cdots N^2-1$ in $SU(N)$ case.
+The generators are normalized like $\textrm{Tr}[T^aT^b]=\delta^{ab}$ and $[T^a,T^b]=i\tilde{f}^{abc}T^c$\footnote{In the usual QFT textbook,
+$\textrm{Tr}[T^aT^b]=\frac{1}{2}\delta^{ab}$ and $[T^a,T^b]=if^{abc}T^c$, with $\tilde{f}^{abc}=\sqrt{2}f^{abc}$ are common choice.  }.
+
+The amplitude-friendly gauge choice is \textit{Gervais-Neveu gauge } with gauge fixing term $\mathcal{L}_{gf}=-\frac{1}{2}\mathrm{Tr}(H_\mu^\mu)=0$, here $H_{\mu\nu}=\partial_\mu A_nu - \frac{ig}{\sqrt{2}}A_\mu A_\nu$.
+After gauge fixing, the lagrangian becomes 
+\begin{equation}
+    \mathcal{L}=\mathrm{Tr} \left(-\frac{1}{2}\partial_\mu A_\nu \partial^\mu A^\nu - i\sqrt{2}g\partial^\mu A^\nu A_\nu A_\mu+\frac{g^2}{4}A^\mu A^\nu A_\mu A_\nu \right)
+\end{equation}
+The 3- and 4-gluon vertices involve $\tilde{f}^{abc}$ and $\tilde{f}^{abi}\tilde{f}^{icd}$+permutations, respectively, each dressed up with kinematic factors.
+The amplitudes constructed from these rules can be organized into
+different group theory structures. For example, the
+color factors of the s-, t-, and u-channel diagram of the 4-gluon tree amplitude are
+\begin{equation}
+    c_s=\tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4},\quad c_t=\tilde{f}^{a_4a_1b}\tilde{f}^{ba_2a_3},\quad c_u=\tilde{f}^{a_1a_3b}\tilde{f}^{ba_2a_4}
+\end{equation}
+and the four point interaction just gives a sum of contributions from $c_s$, $c_t$ and $c_u$. And because of the Jacobi identity, we have
+\begin{equation}
+    c_s=c_t+c_u.
+\end{equation}
+
+And the color factor can be written by the trace of product of generators
+\begin{equation}
+    i\tilde{f}^{abc}=\mathrm{Tr}([T^a,T^b]T^c),
+\end{equation}
+where $T^a$ are generators of fundamental representation. Moreover, in $SU(N)$, we have a Fierz identity
+\begin{equation}
+    \sum_{a}T^a_{ij}T^a_{kl}=\delta_{il}\delta_{kj}-\frac{1}{N}\delta_{ij}\delta_{kl}.
+\end{equation}
+This identity is easier understood as matrix form like 
+\begin{equation}
+    \mathrm{Tr}\{T^aA\}\mathrm{Tr}\{T^aB\}=\mathrm{Tr}\{AB\}-\frac{1}{N}\{A\}\mathrm{Tr}\{B\},
+\end{equation}
+and
+\begin{equation}
+    \mathrm{Tr}\{AT^aBT^a\}=\mathrm{Tr}\{A\}\mathrm{Tr}\{B\}-\frac{1}{N}\mathrm{Tr}\{AB\}.
+\end{equation}
+Then it can be used to simplify the calculation.
+
+For example, the 4 gluon s-channel gives us
+\begin{equation}
+    \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}{a_3}).
+\end{equation}
+Similarly, three other diagrams can also be written in terms of single trace. Therefore, the full 4-point amplitude can be rewritten like
+\begin{equation}
+    \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})+\text{perms of } (234) )
+\end{equation}
+here the subamplitudes $A_4[1234],A_4[1243]$, etc. are called \textbf{color-ordereed ampltitudes}. This concept can be easily generalized to tree-level n-point case
+\begin{equation}
+    \mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})
+\end{equation}
+where the sun is taken over the $(n-1)!$ trace basis (considering the cyclic property of trace).
+Actually, the number of independent basis can be reduced to $(n-3)!$, called Del Duca-Dixon-Maltoni (DDM) color decomposition\cite{DelDuca:1999rs}.
+But it has no tight relation with this paper, so here we do not offer more detailed explanation for it.
+
+The color-ordered amplitude $A_n[1,2 ...
+n]$ is calculated in terms of diagrams with no lines crossing(planar diagrams) and the ordering of the external lines fixed as given 1, 2, 3,..., n.
+Here, we directly give the final result for 3-point color-ordered amplitudes without any intermediate calculating process.
+And in this full paper, we mainly consider the helicity amplitudes which will be explained later, so we need to clarify the helicity configuration.
+
+For 3-point, there are only two non-vanishing configurations
+\begin{equation}
+    A_3[1^-,2^-,3^+]=\frac{\avg{12}^3}{\mdavg{23}{31}}
+\end{equation}
+and 
+\begin{equation}
+    A_3[1^+,2^+,3^-]=\frac{[12]^3}{[23][31]}.
+\end{equation}
+
+It has been known that there is a compact formula for n-point gluon color-ordered amplitudes --- \textbf{\textit{Parke - Talyor Formula}}
+\begin{equation}
+    A_n[1^+\cdots i^-\cdots j^- \cdots n^+]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\avg{n1}}.
+\end{equation}
+We will prove this formula in the next subsection.
+
+The color-ordered amplitudes have a number of properties
+\begin{enumerate}
+    \item \textit{Cyclic}: It follows from the cyclic property for trace that $A_n[12\cdots n]=A_n[2n\cdots 1]$
+    \item \textit{Reflection}: $A_n[12\cdots n]=(-1)^nA_[n\cdots 21]$
+    \item The $U(1)$ \textit{decoupling identity}: 
+    \begin{equation}
+        A_n[123\cdots n]+A_n[213\cdots n]+A_n[231\cdots n]+\cdots + A_n[23\cdots 1n]=0
+    \end{equation}
+\end{enumerate}
 \subsection{BCFW recursion relation}

### 2025-05-13 Master Thesis/thesis.tex
New

@@
 \usepackage{cancel}
+\usepackage{xcolor}
 \numberwithin{equation}{section}
@@
 \newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
+\newcommand{\tif}[1]{\textit{\textbf{#1}}}
 \onehalfspacing
@@
 
-    {\LARGE \textbf{Tree Level Scattering Amplitudes in (De)Constructed Gauge Theory}}\\[1.5cm]
+    {\LARGE \textbf{On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}}\\[1.5cm]
 
@@
 \end{equation}
+and similarly we can obtain define
+\begin{equation}
+    p_\mu \bar{\sigma}^\mu=p^{\dot{\alpha}\alpha}=\tilde{\lambda}^{\dot{\alpha}}\lambda^\alpha=\sket{\lambda} \langle \lambda |,
+\end{equation}
 For general complex momenta, the $\lambda_\alpha$ and $\tilde{\lambda}_{\dot{\alpha}}$ are independent two dimensional complex vectors. For real momenta, the matrix is Hermitian and 
@@
     \cbrak{pq}{pq}=2p\cdot q= (p+q)^2
+    \label{2.7}
 \end{equation}
@@
 \end{equation*}
-
+Here, we list other identities without any provement
+\begin{align}
+    &[k|\gamma^\mu\aket{p}=\langle p|\gamma^\mu |k],\\
+    &{[k|\gamma^\mu\aket{p}}^*=[p|\gamma^\mu\aket{k} \qquad \text{(for real moemnta)}.
+\end{align}
+and \textbf{Fierz identity}
+\begin{equation}
+    \langle 1|\gamma^\mu |2]\langle 3|\gamma_\mu |4]=2\cbrak{13}{24}
+\end{equation}
+will be used in several times.
 In amplitude calculations, \textbf{momentum conservation} is imposed on n particles as $\sum_{i=1}^{n}p_i^\mu=0$(here we consider all particles ingoing). Translating by 
@@
 \begin{equation}
-    \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}{a_3}).
+    \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}T^{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}T^{a_3}).
 \end{equation}
@@
 \begin{equation}
-    \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})+\text{perms of } (234) )
+    \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})+\text{perms of } (234) )
 \end{equation}
@@
     \mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})
+    \label{2.29}
 \end{equation}
@@
 \end{enumerate}
+
+The trace basis \eqref{2.29} is overcomplete implies that there are further linear relations among these subamplitudes, which are called 
+\textit{\textbf{Kleiss - Kuiff(KK) relations}} 
+\begin{equation}
+    A_n[1,\{\alpha\},n,\{\beta\}]=(-1)^{|\beta|}\sum_{\sigma\in \text{OP}(\{\alpha\},\{\beta^T\}) }A_n[1,\sigma,n]
+\end{equation}
+where $\beta^T$ denotes the reverse ordering of the labels $\{\beta\}$  and the sum is over ordered
+permutations “OP”, means permutations of the labels in the joined set $\{\alpha\}\cup \{\beta^T\}$ in which 
+the ordering within $\{\alpha\}$ and $\{\beta\}^T$ is preserved.
+
+Consider a 5-point case as an example. Taking the LHS to be $A_5[1,\{2\},5,\{3,4\}]$, we have $\{\alpha\}\cup \{\beta^T\}=\{2\}\cup \{4,3\}$, so the 
+ordered permutations $\sigma$ refers to $\{243\},\{423\},\{432\}$. Thus the KK relation reads
+\begin{equation}
+    A_5[12534]=A_5[12435]+A_5[14235]+A_5[114325].
+\end{equation}
+
+The KK relations combine with cyclic, reflection, and $U(1)$ decoupling identities reduce the number of independent
+basis to $(n-2)!$. However, there are further linear relations called $\textit{\textbf{BCJ relations}}$ -- named after Bern, Carrasco and Johansson, which further
+reduce the number to $(n-3)!$.
+
+Although I will not show the derivation of BCJ relations, I would like to give some examples
+\begin{gather}
+    s_{14}A_4[1234]-s_{13}A_4[1243]=0,\\
+    s_{12}A_5[21345]s_{23}A_5[13245]-(s_{23}+s_{24})A_5[13425]=0.
+\end{gather}
+\subsection{Little group scalling}
+The rich structure of scattering amplitudes can be originated from a fundamental question — “What is a particle?” — which relates directly to Wigner’s Little group notation,
+characterizing how particles transform under Lorentz symmetry. Following this thought, we think particle as a unitary representation of 
+Poincar$\acute{e}$ group, which is the symmetry group of our spacetime. We use two labels to denote a one-particle state, one is the momentum $p^\mu$, another is $\sigma$ representing
+other labels the particle ca carry.
+
+We start from a one-particle state $\aket{k;\sigma}$ with reference momentum $k$.
+Another momentum $p$ is related by the lorentz transformation $L(p;k)$, $p=L(p;k)k$.
+Obviously, this Lorentz transformation is
+not unique because there exist Lorentz transformations keeping p invariant, called ``Little group transformation''.  We assume that there exist a 
+unitary representation for the Lorentz group, the operator in Hillbert space are denoted like $U(\Lambda)$.
+
+Then we simply \textit{define} the one-particle state with momentum p as 
+\begin{equation}
+    \aket{p;\sigma}=U(L(p;k))\aket{k;\sigma}.
+\end{equation}
+Having made this definition, we can compute how the state transformed under a general Lorentz transformation
+\begin{equation}
+    U(\Lambda)|p,\sigma\rangle = U(\Lambda) U(L(p;k))|k,\sigma \rangle = U(L(\Lambda p;k)) U(L^{-1}(\Lambda p;k) \Lambda L(p;k)) |k,\sigma \rangle\,.
+\end{equation}
+here we use the fact $U(\Lambda_1\Lambda_2)=U(\Lambda_1)U(\Lambda_2)$.
+Notice that $W(\Lambda,p,k)$ is not a general transformation but keep the momentum k invariant $Wk=k$. This subgroup of Lorentz group is called little group.
+Thus we must have 
+\begin{equation}
+    U(W(\Lambda,p,k))\aket{k;\sigma}=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{k,\sigma^{'}},
+\end{equation} 
+where $D_{\sigma\sigma^{'}}$ is the representation for little group. Then, p should transformed like
+\begin{equation}
+     U(\Lambda)|p,\sigma\rangle=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{\Lambda p,\sigma^{'}}
+\end{equation}
+
+The scattering amplitudes for n particle should keep invariant under Poincar$\acute{e}$ transformation -- translation invariance and Lorentz invariance
+\begin{gather}
+    \mathcal{M}(p_a,\sigma_a)=\delta^D(p_1^\mu+\cdots +p_n^\mu)\mathcal{M}(p_a,\sigma_a)\\
+    \mathcal{M}^\Lambda(p_a,\sigma_a)=\prod_{a}(D_{\sigma\sigma^{'}})\mathcal{M}((\Lambda p)_a,\sigma_a^{'})
+    \label{2.43}
+\end{gather}
+
+In D spacetime dimensions, the little group for massive particles is $SO(D-1)$. For massless
+particles the little group is the the group of Euclidean symmetries in (D−2) dimensions, which
+is $SO(D-2)$.In this article, we mainly discuss massless particles scattering in 4 dimension spacetime, so the little group is $SO(2)\backsimeq U(1)$.
+
+Then from the definition of spinor-helicity variable\eqref{2.1}, we can notice that there is an ambiguity here.
+The momentum is invariant under the following redefinition
+    \begin{equation}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
+    \end{equation}
+    same for
+    \begin{equation}
+        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+    \end{equation}.
+This scale perfectly matches the $U(1)$ little group transformation, so we can identify this rescale as the little group transformation.
+The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling like \eqref{2.43}, so
+\begin{equation}
+    \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
+    \label{2.46}
+\end{equation}
+where $h_i$ refers to the helicity of particles.
+As an example, consider the QED amplitude, $A_3(f^-\bar{f}^+\gamma^-)=e\frac{\avg{13}^2}{\avg{12}}$. For the negative helicity photon (particle 3), we obtain $t_3^{-2}=t_3^{2(-1)}$.
+We will see that little group scaling plays a significant role in 3-particle amplitudes.
+
+\noindent
+\textbf{3-particle amplitudes}
+
+\noindent
+By 3-particle special kinematics, we have known that on-shell 3-point amplitudes depends on either square brackets or
+angle brackets. We suppose that it only depends on angle brackets. We can write down the general ansatz
+\begin{equation}
+     A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
+\end{equation}
+where c is just a constant. Little group scaling \eqref{2.46} tell us that
+\begin{equation}
+    t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
+\end{equation}
+We can obtain
+    \begin{equation}
+        2h_1=-x_{12}-x_{13}
+    \end{equation}
+    Similarly, we can also obtain
+    \begin{equation}
+        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
+    \end{equation}
+    Then all index can be solved from this system of equations, so that
+ \begin{align}
+    A_3^{h_1h_2h_3} &= c\langle12\rangle^{h_3-h_1-h_2} \langle31\rangle^{h_2-h_1-h_3} \langle23\rangle^{h_1-h_2-h_3}
+    && \quad h_1 + h_2 + h_3 < 0 \label{2.51}\\[0.5em] 
+    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+    && \quad h_1 + h_2 + h_3 > 0 \label{2.52}
+\end{align}
+This means that \textit{\textbf{all massless 3-point amplitudes are completely fixed by little group scaling!}}
+
+We have shown the 3-point QED amplitudes. So now we can consider something different -- 3-point gluon amplitudes with 2 same helicities and 1 different helicity.
+Then we can determine the amplitudes from \eqref{2.51} \eqref{2.52}
+\begin{equation}
+    A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}, \quad A_3(g_1^+,g_2^+,g_3^-)=g\frac{[12]^3}{[23][31]} \label{2.53}
+\end{equation}
+
+Here it need some efforts to explain about the condition after equation \eqref{2.51} and \eqref{2.52}.If we assume the amplitude
+$A_3(g_1^-,g_2^-,g_3^+)$ depending on square brackets, so can obtain a different expression
+\begin{equation}
+    A_3(g_1^-,g_2^-,g_3^+)=g^{'}\frac{[31][23]}{[12]^3},
+    \label{2.54}
+\end{equation}
+to distinguish these two possibilities, we need to use \textbf{dimension analysis}. From \eqref{2.7}, we can know that both square brackets and angle brackets have mass-dimension 1. 
+Thus the kinematic factor of amplitude \eqref{2.53} has mass-dimension 1, compatible with the interaction term $AA\partial A$ in $\mathrm{Tr}F_{\mu\nu}F^{\mu\nu}$. But the mass-dimension 
+of kinematic factor in \eqref{2.54} is (-1), so it should come from the interaction term like $g^{'}AA\frac{1}{\square }A$. Here, we only consider the local field theory, so this kind of interaction
+should be discarded.
+
+The combination of \tif{little group scaling} and \tif{locality} uniquely fixes the massless 3-point amplitudes. In general, 
+\begin{equation}
+    \text{An n-point amplitude in D=4 spacetime have mass-dimension 4 - n.}
+\end{equation}
+Although we discard the amplitude \eqref{2.54}, the coupling s¥constant $g^{'}$ have mass-dimension 2, so \eqref{2.54} has the correct mass-dimension as \eqref{2.53}.
+
+How about the gluon amplitude with all minus helicities? The formula \eqref{2.51} immediately tells that it should equal to
+\begin{equation}
+    A_3(g_1^-,g_2^-,g_3^-)=g^{''}\mdavg{12}{23}\!\avg{31}.
+\end{equation}
+The kinematic part has mass-dimension 3 and reveals that: 
+\begin{enumerate}
+    \item The coupling constant $g^{''}$ must have mass-dimension -2.
+    \item This must come from an interaction term with 3 derivatives like $(\partial A)^3$.
+\end{enumerate}
+Furthermore, kinematic part has the antisymmetry under the exchange of gluon momenta, so the coupling constant should 
+also have this antisymmetry in order to satisfy the Bose statics as is of course the pure Yang-Mills case. 
+The natural candidate of this amplitude is a dimension 6 operator $\mathrm{Tr}F^\mu_\nu F^\nu_\lambda F^\lambda _\mu$.
+
+\subsection{MHV Classification}
+It has been well known that the all-plus tree-level gluon amplitudes vanish
+\begin{equation}
+    \text{tree-level gluon amplitues}: \quad A_n[1^+,2^+,\cdots,n^+]=0 \quad\text{and}\quad A_n[1^+,2^+,\cdots,n^-]=0
+\end{equation}
+This conclusion holds for the case with all helicities flipped:
+\begin{equation}
+    \text{tree-level gluon amplitues}: \quad A_n[1^-,2^-,\cdots,n^-]=0 \quad\text{and}\quad A_n[1^-,2^-,\cdots,n^+]=0
+\end{equation}
+In supersymmetric Yang-Mills theories, these results hold for all loop order, so actually it is a special case for SYM.
+
+If we flip one more helicit, the situation becomes quite different. Amplitudes $A_n[1^-,2^-,3^+,\cdots,n^+]$ does not equal to 0 and is quite important called \textbf{MHV amplitudes}.
+The gluon amplitudes with two negative helicities and n - 2 positive helicities are called
+\tif{maximally helicity violating} – or simply \tif{MHV} for short. The concept ``maximally helicity violating'' comes from thinking a $2\rightarrow n-2$ scattering process. 
+Because of crossing symmetry, the outgoing particle with positive(negtive) helicity is equivalent with an ingoing particle with negative(positive) helicty.
+So if we consider the process $A_n[1^+,2^+,\cdots,n^+]$ with
+all particle ingoing.
+It crosses over to $1^+2^-+\rightarrow 3^-\cdots n^-$ with two ingoing particles and n-2 outgoing particles, that's the reason we call it ``helicity violating''.
+We have known that the process in which the most we can violate helicity
+is $1^+2^+\rightarrow 3^+4^+5^-\cdots n^-$, which is equivalent to amplitudes $A_n[1^+2^+3^-4^-5^+\cdots n^+]$, therefore it is the \textit{maximally helicity violating} process.
+
+As we have shown in the last subsection, the MHV gluon tree amplitudes are given by Parke - Talyor formula
+\begin{equation}
+    A_n[1^+\cdots i^-\cdots j^- \cdots n^+]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\avg{n1}}
+\end{equation}
+The MHV amplitudes are the important blocks for scattering amplitudes in (super)Yang-Mills theory. They are simplest amplitudes, and the next-to simplest
+are called \textbf{Next-to-MHV} amplitudes, or just \textbf{NMHV}. This refers to scattering process for which two 2 positive gluons scatter into 3 positive gluons and n-5 negative gluons. 
+Similarly, we can define \textbf{$N^k$MHV} amplitudes. For anti-MHV amplitudes with all helicities flipping, we have a formula
+\begin{equation}
+    A_n[1^-\cdots i^+\cdots j^+ \cdots n^-]=\frac{[ij]^4}{[12][23]\cdots[n1]}.
+\end{equation}
 \subsection{BCFW recursion relation}
+The BCFW recursion relation was introduced in 2005 by Britto, Cachazo, and Feng, and later extended with Witten. It provided a novel way to compute tree-level scattering amplitudes by 
+analytically continuing external momenta into the complex plane and expressing higher-point amplitudes recursively in terms of lower-point ones. This on-shell approach uncovered surprising 
+simplicity in gauge theory amplitudes and offered an alternative to the traditional Feynman diagram expansion. The method was inspired in part by Witten's twistor string theory and the MHV 
+diagram program. In parallel, off-shell recursion relations were also being explored, especially in background field methods and Berends-Giele recursion, which organize amplitudes based on 
+off-shell currents. While off-shell methods remain useful in certain computational frameworks, the BCFW recursion highlighted the power of staying strictly on-shell, leading to a deeper understanding 
+of symmetry, analyticity, and the geometry of scattering processes. It has since become a cornerstone of modern amplitude research.
+
+Beyond BCFW, other on-shell recursion relations have also emerged—for instance, the KLT relations linking gauge and gravity amplitudes, and the double copy structure as well as recursion 
+for theories with special helicity configurations or massive particles.
+Together, these developments form the foundation of modern amplitude methods, emphasizing physical principles like unitarity, analyticity,
+and factorization over traditional Lagrangian-based techniques.
+
+\subsubsection{Complex shift and Relation from Simple Cauchy's Theorem}
+An on-shell amplitude(each external leg satisfies on-shell condition) is labeled by their external momentum $p_\mu$ and hilicity $h_i$.
+Here we only consider the massless particles $p_i^2=0$, for $i=1,2,\cdots,n$. And momentum conservation $\sum_{i=1}^{n}p_i^\mu=0$ should hold.
+
+First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
+\begin{itemize}
+    \item $\sum_{i=1}^{n}r_i^\mu=0$,
+    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
+    \item $p_i\cdot r_i=0$ for each i(no sum).
+\end{itemize}
+These vectors $r_i$ are used to define n shifted momentum
+\begin{equation}
+    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
+\end{equation}
+Note that, by imposing these constraints,
+\begin{itemize}
+    \item Momentum conservation holds for the shifted momentum:
+\end{itemize}
 

### 2025-05-13 Master Thesis/thesis.tex
New

@@
 \usepackage{xcolor}
+\usepackage{float}
 \numberwithin{equation}{section}
@@
 In D spacetime dimensions, the little group for massive particles is $SO(D-1)$. For massless
-particles the little group is the the group of Euclidean symmetries in (D−2) dimensions, which
+particles the little group is the the group of Euclidean symmetries in (D - 2) dimensions, which
 is $SO(D-2)$.In this article, we mainly discuss massless particles scattering in 4 dimension spacetime, so the little group is $SO(2)\backsimeq U(1)$.
@@
 \begin{itemize}
-    \item Momentum conservation holds for the shifted momentum:
+    \item Momentum conservation holds for the shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
+    \item We have $\hat{p}_i^2=0$, so each shifted momentum still keep on-shell
+    \item For a non-trival \footnote{non-trival here means at least two and no more than n-2 such that $P_I^2\neq 0$} subset of momentum $\{p_i\}_{i\in I}$,
+    define $P_i^\mu=\sum_{i\in I}p_i^\mu$. Then $\hat{P}_I^2$ is \textbf{linear} in z:
+    \begin{equation}
+        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I)
+    \end{equation}
+    beacuse the $z^2$ term vanishes. We can write 
+    \begin{equation}
+        \hat{P}_I^2=-\frac{P_I^2}{z_I}(z-z_I)\quad \text\quad {with} z_I=\frac{P_I^2}{2P_I\cdot k}
+        \label{2.63}
+    \end{equation}
 \end{itemize}
+If we consider the original amplitude $A_n$ in terms of the shifted momentum $\hat{p}_i^\mu$ instead of original momentum. Then the amplitude can be seen as 
+a holomorphic function of z. Actually, if we set $z=0$, we can obtain the origin ampltide $A_n=\hat{A}_n(z=0)$.
 
+In this paper, we only focus on the tree-level scatterung amplitudes, in which case the analytic structure becomes quite simple. The tree amplitudes does not have any branch cuts -- there are no 
+logs, no square roots, etc.. The tree-level amplitude is a rational function of Lorentz invariant kinematic quantities, like the contraction between momentum or momentum and polarization vector. 
+Therefore, the analytic structure can be completely captured by its single poles in the complex z plane. To see that all of the poles are single, we just need to notice 
+that we can only ontain poles from propagators. But we have seen that all of the poles can be dertermined by  \eqref{2.63}. 
+So $1/\hat{P}_I^2$ gives a single pole at $z_I$, and for generic momentum, $P_I^2\neq 0$(propagator is off-shell) so $z_I\neq 0$. Hence, 
+$\hat{A}_n(z)$ only has single poles away from the orignal poine $z=0$.\footnote{Here we need to impose locality to ensure all of the poles can be determined by the propagators.}
+
+Then let us turn to define a new holomorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane. We can pick a contour surrounding the original point 
+$z=0$ which is a single pole of this function. The residue of this single pole can be easily computed
+\begin{equation}
+    \mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(z=0)=A_n,
+\end{equation}
+It is just the unshifted amplitude what we want to compute at the begining.
+
+Also, we can choose another countour surrounding all single poles, then Cauchy's theorem just tell us 
+\begin{equation}
+    A_n = - \sum_{z_I} \mathrm{Res}_{z=z_I} \frac{\hat{A}_n(z)}{z}  + B_n\,,
+\end{equation}
+where the $B_n$ is the residue at $z=\infty$ infinity, called bounday term. By taking $z\rightarrow 1/\omega$, it is easy to notice that
+$B_n$ is the $O(z^0)$ term in the $z\rightarrow \infty$ expansion of $A_n$.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Cau.png} % 调整为所需大小
+    \caption{Cauchy Theorem}
+\end{figure}
+
+Now, at the position of $z_I$ pole, the propagator $1/\hat{P}_I^2$ gose on-shell. The unitarity has a tight relation with I poles in the S-matrix with on-shell intermediate
+states.
+\begin{equation}
+    G_n(p_1, \ldots, p_n) = (2\pi)^4 \, \delta^4\left(\sum p\right) 
+\frac{i}{p_\Psi^2 - m_\Psi^2 + i\varepsilon} 
+\mathcal{M}_\Psi^{1,r} \, \mathcal{M}_\Psi^{r+1,n\dagger} + \text{extra}
+\end{equation}
+where “extra” refers to anything else that contributes. This equation says that Green’s
+functions always have poles when on-shell intermediate particles can be produced.
+
+Then, in the on-shell limit, the shifted amplitude \textit{factorizes} into two on-shell parts
+\begin{equation}
+     \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+\end{equation}
+
+This makes it easy to compute the residue at $z=z_I$
+\begin{equation}
+    -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=-(z-z_I)\frac{z_I}{z(z-z_I)}|_{z=z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+\end{equation}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{recrel1.pdf} % 调整为所需大小
+    \caption{factorization}
+\end{figure}
+
+Note that, as opposed to Feynman diagrams for which the intermediate propagator does not equal to 0, here the intertal line $\hat{P}_I^2$ of Figure 2 does equal to 0.
+And the blobs which refer to subamplitudes are \tif{on-shell amplitudes}. In the diagrammatic representation Figure 2, the internal line is assigned the usual scalar propagator 
+$1/P_I^2$, evaluated using unshifted momenta. Since each subamplitude involves fewer than 
+n external particles, all the residues at finite z can be expressed entirely in terms of lower-point on-shell amplitudes. 
+This fundamental idea underlies the construction of the recursion relations.
+
+The contribution $B_n$ does affect a lot, and it has no similar general expression in trems of lower-point amplitudes. Although in some cases, the boundary term
+$B_n$ can be computed, but there is not a general method to compute it. Thus, in most applications, we always assumes, or better, prove that $B_n=0$. This is often modified
+by demonstrating stronger statement that 
+\begin{equation}
+    \hat{A}_n(z) \to 0 ~~~~ \text{for} ~~~~ z \to \infty. 
+    \label{2.69}
+\end{equation}
+If \eqref{2.69} holds, we state the shift is \tif{valid}.
+
+For a valid shift, the n-point amplitudes can be recursively computed interms of lower-point amplitude
+\begin{equation}
+     A_n ~= \sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
+    \,\frac{1}{P_I^2}\,
+    \hat{A}_\text{R}(z_I)
+       ~~=
+   \sum_{\text{diagrams}~I}
+   \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1}}
+   \,.
+\end{equation}
+where I means all possible factorization channels. We did not use any $D=4$ spacetime property, so this recursion relation can be 
+utilized to general D dimension spacetime.
+
+\subsubsection{BCFW recursion relation}
+In the last section, we introduce the recursion relation with all momentum shifted. But actually, some of the shift vectors $r_i^\mu$ can be choose to 0.
+The BCFW shift is a kind of special shift for which only two momentum are shifted, called i and j. In D=4 spacetime diension, the shift is implemented 
+\begin{equation}
+    \hat{p}_i(z)=p_i-zq,\qquad \hat{p}_j(z)=p_j+zq
+    \label{2.71}
+\end{equation}
+so momentum conservation is kept and the hold for on-shell condition require ot impose
+\begin{equation}
+    q^2=q\cdot p_i=q\cdot p_j=0 \, .
+\end{equation}
+This shift can be implemented in terms of spinor-helicity variable as
+\begin{equation}
+    |\hat{i}] = |i] - z\,|j]\,,   
+  ~~~~~~
+  |\hat{j}] = |j]\,,   
+  ~~~~~~
+  |\hat{i}\rangle = |i\rangle\,,
+  ~~~~~~
+  |\hat{j}\rangle = |j\rangle + z |i\rangle \,.
+\end{equation}
+No other spinors are shifted, this kind of shift are called $[i,j\rangle$ shift(it is worth to mention that $[i,j\rangle$ shift 
+is completely different with $[j,i\rangle$ shift). In the literature, the BCFW
+deformation is usually written in the above spinor form. However, the momentum form \eqref{2.71} provides
+another perspective.
+
+The BCFW recursion relation takes the form
+\begin{equation}
+     A_n ~= \sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
+    \,\frac{1}{P_I^2}\,
+    \hat{A}_\text{R}(z_I)
+       ~~=
+   \sum_{\text{diagrams}~I}
+   \raisebox{-5.8mm}{\includegraphics[height=1.4cm]{recrel.2.png}}
+   \,.
+\end{equation}
+
+Beforing going into the apllication of BCFW, let us first consider the large-z behavior. 
+In pure Yang-Mills case, it has been proved that the color-ordered gluon tree-level amplitudes behave like the following manner\cite{Arkani-Hamed:2001kyx}
+$$ 
+\begin{array}{cccccc}
+   [i,j\rangle & [-,-\rangle & [-,+\rangle & [+,+\rangle & [+,-\rangle &
+   \\[2mm]
+   \hat{A}_n(z) \sim 
+   &  \frac{1}{z} &  \frac{1}{z} &  \frac{1}{z} & z^3
+   \end{array}
+$$
+If i,j are not adjacent, one obtains an extra $1/z$ in each case. Thus any one of shifts $,[-,-\rangle,[-,+\rangle,[+,+\rangle$ are valid
+but $[+,-\rangle$ is not valid. This is a quite non-trival result.
+
+\newpage
 \bibliographystyle{unsrt}

### 2025-05-14 Master Thesis/thesis.tex
New

@@
 \usepackage{float}
+\usepackage{tikz}
+\usepackage{bm}
 \numberwithin{equation}{section}
@@
 No other spinors are shifted, this kind of shift are called $[i,j\rangle$ shift(it is worth to mention that $[i,j\rangle$ shift 
-is completely different with $[j,i\rangle$ shift). In the literature, the BCFW
+is completely different with $[j,i\rangle$ shift).Note that $[\hat{i}k]$ and $\avg{\hat{j}k}$ are linear in $z$ for $k \neq i, j$, while 
+$\avg{\hat{i}\hat{j}}=\avg{ij}$, $[\widehat{i}\, \widehat{j}] = [ij]$, 
+$\avg{\hat{i}k}=\avg{ik}$, and $[\hat{j}k] = [jk]$ remain unshifted. In the literature, the BCFW
 deformation is usually written in the above spinor form. However, the momentum form \eqref{2.71} provides
@@
 but $[+,-\rangle$ is not valid. This is a quite non-trival result.
+If we consider more general case\cite{Feng:2011np}
+\begin{equation*}
+\begin{aligned}
+p_i(z) &= p_i + z \lambda_i \tilde{\lambda}_j, \quad
+p_j(z) = p_j - z \lambda_i \tilde{\lambda}_j, 
+\Rightarrow
+\begin{cases}
+A(z) \to z^{-2}, & i, j \text{ not nearby} \\
+A(z) \to z^{-1}, & i, j \text{ nearby}
+\end{cases} \\
+\\
+p_i(z) &= p_i + z \lambda_i \tilde{\lambda}_k \ (k \neq j), \quad
+p_k(z) = p_k - z \lambda_i \tilde{\lambda}_k,
+\Rightarrow
+\begin{cases}
+A(z) \to z^{-2}, & i, k \text{ not nearby} \\
+A(z) \to z^{-1}, & i, k \text{ nearby}
+\end{cases}
+\end{aligned}
+\end{equation*}
+\begin{equation}
+\begin{aligned}
+p_i(z) &= p_i + z \lambda_k \tilde{\lambda}_i \ (k \neq j), \quad
+p_k(z) = p_k - z \lambda_k \tilde{\lambda}_i,
+\Rightarrow
+\begin{cases}
+A(z) \to z^2, & i, k \text{ not nearby} \\
+A(z) \to z^3, & i, k \text{ nearby}
+\end{cases} \\
+\\
+p_k(z) &= p_k + z \lambda_l \tilde{\lambda}_k, \quad
+p_l(z) = p_l - z \lambda_l \tilde{\lambda}_k, \quad
+k, l \neq i,j
+\Rightarrow
+\begin{cases}
+A(z) \to z^{-2}, & l, k \text{ not nearby} \\
+A(z) \to z^{-1}, & l, k \text{ nearby}
+\end{cases}
+\end{aligned}
+\end{equation}
+where $i,j$ are negetive helicities. Then we can go forward to the provement of Parke - Talyor formula by using BCFW recursion relation. First, we can notice that the formula
+\begin{equation}
+    A_n[1^+\cdots i^-\cdots j^- \cdots n^+]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\avg{n1}}
+    \label{2.76}
+\end{equation}
+holds for $n=3$ case, and we start the provement by induction from 3-point.
+For specific n, we suppose \eqref{2.76} holds for amplitudes with external legs less than n.
+Then we can writte down the n-point amplitude $A_n[1^-2^-3^+\cdots n^-]$ with BCFW shift $[1,2\rangle$
+\begin{align}
+    A_n[1^-2^-3^+\dots n^+] 
+    &= 
+        \sum_{k=4}^{n}~~
+        \raisebox{-6.5mm}{\includegraphics[height=1.6cm]{recrel2}} \notag \\[1ex]
+    &= \sum_{k=4}^{n} \sum_{h_I = \pm} 
+        \hat{A}_{n-k+3}\big[ \hat{1}^-, \hat{P}_I^{h_I} , k^+ \ldots , n^+\big] 
+        \,\frac{1}{P_I^2} \notag \\[0.5ex]
+    &\quad\quad \times \hat{A}_{k-1}\big[ -\hat{P}_I^{-h_I} ,  \hat{2}^-, 3^+ \ldots , (k-1)^+\big] \,.
+    \label{2.77}
+\end{align}
+The internal momentum can be evaluated as $P_I=p_2+p_3+\cdots+p_{k-1}$ and $\hat{P}_I=\hat{p}_2+p_3+\cdots +p_{k-1}$ if we choos $k=4,5,\cdots,n$.
+Notice that there are no such diagrams in which the $\hat{p_1}$ and $\hat{p}_2$ locate at the same side, whereby there are no z independence, so that we can not obtain any single pole in the complex plane.
+And because we are computing the color-ordered amplitudes, only diagrams that preserve the color-ordering of the external states are included.
+Note that we explicitly include the sum over all possible helicity assignments for the particle exchanged on the on-shell internal line.
+Specifically, if the exchanged gluon appears as an outgoing particle with negative helicity in the left subamplitude, it will correspondingly appear as an outgoing gluon with positive helicity in the right subamplitude.
 
-\newpage
+We have known that the color-amplitudes $A_n[-++c\cdots+]$ equals to 0, except for $n=3$ case. So \eqref{2.77} can be computed like
+\begin{align}
+    A_n[1^- 2^- 3^+ \ldots n^+]
+      &= 
+        \raisebox{-6.7mm}{\includegraphics[height=1.6cm]{recrel3a}}
+        ~~+~~
+        \raisebox{-6.9mm}{\includegraphics[height=1.6cm]{recrel3b}} 
+        \notag \\[2mm]
+      &=
+        \hat{A}_{3}\big[ \hat{1}^-, -\hat{P}_{1n}^{+}, n^+\big] 
+        \,\frac{1}{P_{1n}^2}\,
+        \hat{A}_{n-1}\big[ \hat{P}_{1n}^{-},  \hat{2}^-, 3^+ \ldots (n-1)^+\big] 
+        \notag \\[1mm]
+      &\quad
+        +~
+        \hat{A}_{n-1}\big[ \hat{1}^-, \hat{P}_{23}^{-}, 4^+ \ldots , n^+\big] 
+        \,\frac{1}{P_{23}^2}\,
+        \hat{A}_{3}\big[ -\hat{P}_{23}^{+},  \hat{2}^-, 3^+\big] \,.
+        \label{2.78}
+\end{align}
+Notice that in the first diagram of \eqref{2.78}, there is a 3-point subamplitude
+\begin{equation}
+    \hat{A}_{3}\big[ \hat{1}^-, -\hat{P}_{1n}^{+}\, , n^+\big]
+   ~=~ \frac{[\hat{P}_{1n} \,n]^3}{[n \hat{1}][\hat{1} \hat{P}_{1n}]} \,.
+   \label{2.79}
+\end{equation}
+here we take the convention of analytic continuation like
+\begin{equation}
+   \aket{-p}=-\aket{p},\qquad \sket{-\!p}=+\sket{p}.
+\end{equation}
+Because the propagator satisfies the on-shell condition, so we can obtain
+\begin{equation}
+    \hat{P}_{1n}^2=0=2\hat{p}_1\cdot p_n=\cbrak{\hat{1}n}{n\hat{1}},
+\end{equation}
+because we take the $[1,2\rangle$ shift, so that $\aket{\hat{1}}=\aket{1}$. And the angle bracket $\avg{1n}$ can not equal to 0, so that
+\begin{equation}
+    [\hat{1}n]=0 \qquad \Longrightarrow \qquad z=\frac{[1n]}{[2n]},
+\end{equation}
+so the potion of pole is determined by the on-shell propagator. Also, we can compute like
+\begin{equation}
+    \aket{\hat{P}_{1n}} [  \hat{P}_{1n}\,n] = -\hat{P}_{1n}|n] \,=\, -(\hat{p}_1 + p_n) |n] \,=\, \aket{1} [\hat{1}n] \,=\, 0\, , 
+\end{equation}
+we can conclude $ [  \hat{P}_{1n}\,n]=0$ because of $[\hat{1}n]=0$ and $\aket{\hat{P}_{1n}}\neq 0$.
+So the 3-point amplitude \eqref{2.79} has both a vanishing numerator and denominator, with the numerator vanishing one order faster.
+We conclude that
+special 3-point kinematics force $\hat{A}_{3}\big[ \hat{1}^-, -\hat{P}_{1n}^{+}\, , n^+\big]$. So the contribution from the first
+diagram in \eqref{2.78}vanishes.
+
+For the second diagram in \eqref{2.78}, we will not obtain the vanishing result, because it is an anti-MHV amplitude with angle spinor $\aket{2}$ shifted.
+Henceforth, the seemingly complicated summation \eqref{2.78} redeuce to a single diagram.
+This is one merit of BCFW recursion relation.
+Then the amplitude can be evaluated like
+\begin{align}
+A_n[1^- 2^- 3^+ \ldots n^+]
+  &= 
+    \raisebox{-6.9mm}{\includegraphics[height=1.6cm]{recrel3b}} \notag \\[1mm]
+  &=
+    \hat{A}_{n-1}\big[ \hat{1}^-, \hat{P}_{23}^{-}, 4^+, \ldots , n^+\big] 
+    \,\frac{1}{P_{23}^2}\,
+    \hat{A}_{3}\big[ -\hat{P}_{23}^{+},  \hat{2}^-, 3^+\big]\,.
+\end{align}
+By using the lower point Parke - Talyor formula which assune to hold, the amplitude can be written like
+\begin{equation}
+    A_n[1^- 2^- 3^+ \ldots n^+]
+  ~=~
+  \frac{\avg{\hat{1}\hat{P}_{23}}^4}{\avg{\hat{1}\hat{P}_{23}}\avg{\hat{P}_{23}\, 4}\avg{45}\cdots\avg{n\hat{1}}}
+  \times\frac{1}{\avg{23}[23]}\times
+  \frac{[3 \hat{P}_{23}]^3}{[\hat{P}_{23}\,\hat{2}][\hat{2} 3]}\,.
+\end{equation}
+This formula can be further simplified by using 
+\begin{equation}
+    \cbrak{\hat{1}\hat{P}_{23}}{3\hat{P}_{23}}=-\cbrak{\hat{1}\hat{P}_{23}}{\hat{P}_{23}3}=-\langle 1|\hat{p}_2+p_3|3]=-\langle 1|\hat{p}_2|3]=\cbrak{12}{32}
+\end{equation}
+here we use the fact $\aket{\hat{1}}=\aket{1}$ and $\avg{1\hat{2}}=\avg{12}$.
+And similarly , for the demoninator we have the similar result
+\begin{equation}
+    \avg{\hat{P}_{23}4}[\hat{P}_{23}\hat{2}]=-\avg{4\hat{P}_{23}}[\hat{P}_{23}\hat{2}]=-\langle 4|\hat{p}_2+p_3|2]=\cbrak{34}{32}
+\end{equation}
+here we use the fact $\sket{\hat{2}}=\sket{2}$.
+
+Then the full amplitude equals to
+\begin{align}
+    A_n[1^- 2^- 3^+ \ldots n^+]&=\frac{\avg{12}^3[32]^3}{\cbrak{34}{32}\cbrak{23}{23}[23]\avg{45}\cdots \avg{n1}}\\
+    &=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\avg{n1}}
+\end{align}
+so we finish the provement of Parke - Talyor formula by utlizing BCFW recursion relation.
+
+Notice that this formula only holds for MNH anplitudes.
+For NMHV amplitudes, of coure we can still use BCFW recusion relation to similarly compute them.
+Here, I only show the result of 6-gluon NMHV tree amplitude.
+\begin{align}
+    A_6[1^- 2^- 3^- 4^+ 5^+ 6^+]
+  ~&=~
+    \raisebox{-8.5mm}{\includegraphics[height=1.8cm]{recrel-6pt-A1}}
+  ~~~+~~~
+  \raisebox{-8.5mm}{\includegraphics[height=1.8cm]{recrel-6pt-A2}} \\
+  ~&=~ \frac{\langle 3|1+2|6]^3}{P_{126}^2[21][16]\mdavg{34}{45}\langle 5|1+6|2]}+\frac{\langle 1|5+6|4]^3}{P_{156}^2[23][34]\mdavg{56}{62}\langle 5|1+6|2]}
+\end{align}
+Color-ordered tree amplitudes can exhibit physical poles only when the sum of momenta of adjacent external lines goes on-shell.
+As previously noted, MHV gluon amplitudes feature only two-particle poles and do not possess multi-particle poles.
+In contrast, you have now seen that six-gluon NMHV amplitudes contain both two- and three-particle poles.
+Interestingly, in the BCFW representation, each diagram contributes a peculiar denominator factor of the form $\langle 5|1+6|2]$.
+This term does not correspond to any physical pole of the scattering amplitude—it is known as a \tif{spurious pole}.
+The residue associated with this unphysical pole must vanish, and indeed it does: the spurious contributions cancel out when summing over all relevant BCFW diagrams.
+
+\noindent
+\textbf{When does it work?}
+\begin{itemize}
+    \item Yang - Mills theory and gluon scattering.
+    \item Scalar - QED. 
+    \item Scalar theory $\lambda \phi^4$.
+    \item $\mathcal{N} =4$ super Yang - Mills theory.
+    \item Gravity. 
+\end{itemize}
+
+\section{(De)Constructed Gauge Theory}
+\subsection{Motivation}
+Our four-dimensional description of spacetime may only be an effective low-energy approximation.
+While the observable universe appears four-dimensional — with one time and three spatial directions — it is possible that additional spatial dimensions exist but are hidden at quite small scales beyond our current experimental realm.
+A simple and widely reasearched realization of this thought involves compact extra dimensions, where fields propagate on a higher-dimensional spacetime with some dimensions compactified to small radius.
+At energies much lower than the compactification scale, such theories reduce to four-dimensional physics as an effetive theory, but at higher energies, the influence of these extra dimensions become manifest, for example, the appearance of Kaluza - Klein excitations(KK modes).
+
+Theoretical interest in extra dimensions arises not only from string theory but also from the desire to better understand the ultraviolet behavior of field theories.
+Unfortunately, traditional higher-dimensional field theories are nonrenormalizable and contain dimensionful couplings, requiring a cutoff and becoming strongly coupled in the UV.
+This poses a major obstacle to fully understanding their high-energy behavior.
+
+In response to this, Arkani-Hamed, Cohen, and Georgi proposed the idea of (De)constructed dimensions, in which higher-dimensional behavior emerges dynamically from a renormalizable four-dimensional theory.
+Their construction discretizes the extra dimension using a chain of gauge groups and link fields, producing a low-energy spectrum that mimics a compactified fifth dimension.
+Crucially, the theory remains perturbative and controllable in the UV, making it an ideal framework to study phenomena associated with extra dimensions—such as KK mode scattering—without running into the usual ultraviolet issues.
+
+This paper is motivated by this (De)constructed approach.
+We focus on computing tree-level scattering amplitudes in the simplest two-site model, employing modern amplitude techniques such as the BCFW recursion relation, spinor-helicity formalism, and color ordering.
+\subsection{$SU(m)\times SU(n)$ \textit{Moose}}
+At first, we consider four-dimensional field theories that contain gauge fields and fermions.
+These theories can be conveniently illustrated using a type of diagram known as a “moose” or “quiver” diagram\footnote{Sorry for the ambiguity of different terminology.
+In this paper, the term ``quiver'', ``moose'' and ``(De)construction'' mainly represent the same meaning}.
+In such diagrams, gauge groups are represented by open circles, and fermions are shown as single arrows (directed lines) attached to those circles.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{The-quiver-diagram-for-the-2d-N-0-2-theory-corresponds-to-the-surface-defect-S-r.jpg}
+    \caption{Example of quiver diagram}
+\end{figure}
+
+An arrow pointing away from a circle represents a set of Weyl fermions transforming under the fundamental representation of that gauge group.
+Conversely, an arrow pointing toward a circle corresponds to fermions transforming in the complex conjugate of fundamental representation.
+
+We will focus on a specific example: a moose diagram shaped like an N-sided polygon, where each node and connection encodes the field content and gauge structure of the theory with gauge group $SU(m)^N\times SU(n)^N$
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Moose.png}
+    \caption{Moose diagram}
+\end{figure}
+
+We impose a \textit{cyclic symmetry} on the theory so that all $SU(m)$ gauge couplings are set equal to a common value $g$, and all $SU(n)$ gauge couplings are set equal to $g_s$.
+Through \textit{dimensional transmutation}, the theory can equivalently be described by two corresponding \textit{dimensionful parameters}, $\Lambda$ and $\Lambda_s$, which characterize the strong coupling scales of the respective gauge groups.
+
+Each \textit{side of the polygon} in the moose diagram represents two types of fermions, each transforming under the three gauge groups associated with that side: $SU_i(m) \times SU_i(n) \times SU_{i+1}(m)$.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Side.png}
+\end{figure}
+\begin{gather}
+    \chi_{i,i}\qquad \text{transformed under}\quad (m,\bar{n},1)\\
+    \psi_{i,i+1}\qquad \text{transformed under}\quad (1,n,\bar{m}) 
+\end{gather}
+where $m,n$ refer to the fundamental representation of gauge group $SU(m)$ and $Su(n)$, $\bar{m},\bar{n}$ refer to the conjugate of fundamental representation, and $1$ just represent the trival representation.
+
+\paragraph{Low-energy behavior.}
+
+\textbf{What does the theory look like at longer distances?} In the regime where $\Lambda_s \gg \Lambda$, the low-energy behavior of the theory becomes relatively simple.
+At energy scales around $\Lambda_s$, the $SU(m)$ gauge couplings remain weak and can be treated perturbatively.
+In contrast, each $SU(n)$ gauge group becomes strongly coupled at this scale, leading to \tif{fermion condensation}.
+
+Specifically, pairs of fermions associated with each strong gauge group condense, forming nonzero vacuum expectation values:
+\[
+\avg{\chi_{i,i} \psi_{i,i+1}} \sim 4\pi f^3\, U_{i,i+1}, \quad i = 1,\dots, N
+\]
+Here, $f \sim \Lambda_s / (4\pi)$ is the characteristic scale of the condensate, and $U_{i,i+1}$ is an $m \times m$ unitary matrix that encodes the orientation of the condensate in field space.
+And in thefollowing part, we will focus on the model after condensation.
+
+We use a similar condensed - moose diagram to represent this condensed theory:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Moosed.jpeg}
+    \caption{Condensed Moosed diagram}
+\end{figure}
+It is described by the following Lagrangian
+\begin{equation}
+    \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{N}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
+    \label{3.3}
+\end{equation}
+here $F_i$ refers to the ith gauge field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
+    \begin{equation}
+        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iA_{i\mu}\Phi_i+ig_{i+1}\Phi_i A_{i+1\mu}.
+    \end{equation}
+    Here, gauge field and scalar field transformed like
+    \begin{equation}
+        \bm{A_{i\mu}}\rightarrow U_i(x) \bm{A_{i\mu}} U_i^-(x)-\frac{i}{g_i}(\partial_\mu U)U^{-1},\qquad \Phi_i\rightarrow U_i(x)\Phi_i U_{i+1}^-(x)
+    \end{equation}
+    It is easy to confirm that this theory is invariant under $\prod_1^N SU(m)$ gauge group.
+
+    The action is similar to the non-linear sigma model, in which the non-lenear sigma fields effectively connects gauge fields at neighboring sites.
+In fact, equation \eqref{3.3} can be interpreted as a discretized version of a five-dimensional gauge theory with gauge group $SU(m)$, where only the fifth dimension is latticized.
+The non-linear sigma model fields play the role of \tif{link variables} in a lattice gauge theory, and the condensed moose diagram effectively represents the fifth dimension.
+
+    It is quite striking that the moose diagram, which was originally just a tool to keep track of fields and interactions in a four-dimensional theory, \tif{takes on a new physical meaning at low energies}: it effectively describes an extra spatial dimension.
+
+We can higgs the scalar field $U_{i,i+1}$ making the gauge group down to the diagonal subgroup.
+Its eigenvalues can be easily computed, yielding a discrete mass spectrum labeled by an integer $k$ satisfying $-N/2 < k \leq N/2$.
+The mass of each mode is given by:
+\begin{equation}
+M_k^2 = 4g^2 f_s^2 \sin^2\left( \frac{\pi k}{N} \right)
+\equiv \left( \frac{2}{a} \right)^2 \sin^2\left( \frac{p_5 a}{2} \right),
+\end{equation}
+where $p_5 \equiv 2\pi k / R$ is the discretized momentum along the fifth dimension. The corresponding eigenvectors take the form $\psi^m \sim \exp(i m p_5 a)$.
+
+In the regime $|k| \ll N/2$, the spectrum becomes approximately linear, and the masses simplify to:
+\begin{equation}
+M_k \simeq |p_k| = \frac{2\pi |k|}{R}.
+\end{equation}
+
+This exactly matches the \tif{Kaluza-Klein spectrum} for a five-dimensional gauge boson compactified on a circle of circumference $R$.
+The effective four-dimensional gauge coupling of the diagonal subgroup is given by $g_4^2 = g^2 / N$.
+Using the earlier relation in equation (2.7), this implies:
+\begin{equation}
+\frac{1}{g_4^2} = \frac{R}{g_5^2},
+\end{equation}
+which is the standard relation between the gauge couplings in five and four dimensions.
+
+\subsection{2\,-\,site model}
+For simplicity, in this paper we only focus on the smallest block in this condensed moose theory -- 2-site model, which can be represented by the following diagram 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.3\textwidth]{2-site.png}
+    \caption{2-site model}
+\end{figure}
+\noindent
+Here we choose a slightly different model, of which the two gauge group are different.
+
 \bibliographystyle{unsrt}

### 2025-05-15 Master Thesis/thesis.tex
New

@@
     \item Gravity. 
+    \item $\cdots\cdots$
 \end{itemize}
@@
 
-\subsection{2\,-\,site model}
+\section{Scattering ampliyudes in 2\,-\,site model}
 For simplicity, in this paper we only focus on the smallest block in this condensed moose theory -- 2-site model, which can be represented by the following diagram 
@@
 \noindent
-Here we choose a slightly different model, of which the two gauge group are different.
+Here we choose a slightly different model, of which the two gauge group are different. The lagrangiian can be written like 
+\begin{equation}
+    \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
+\end{equation}
+The amplitudes are classified by their multiplicity:
+
+\vspace{1em}
+\begin{table}[ht]
+\centering
+\renewcommand{\arraystretch}{1.3}
+\setlength{\tabcolsep}{6pt}
+\begin{tabular}{|c|c|c|c|}
+    \hline
+    \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
+    \hline
+    $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
+    $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
+    $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
+    $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
+     & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
+     & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
+     & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
+     & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
+    \hline
+\end{tabular}
+\caption{Classification}
+\end{table}
+\subsection{3-point building block}
+We have known that the on-shell 3-point amplitudes can be completely determined by the little group scaling, according to the following formulas
+\begin{align*}
+    A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+    \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+    \quad & h_1+h_2+h_3 > 0
+\end{align*}
+Because of the specialty of this kind of 2 site gauge theory, there are no direct interaction between gauge boson and scalar, so there are only two kinds of 3-point amplitudes.
+\begin{itemize}
+    \item 2 scalar 1 gauge boson
+    \begin{equation}
+        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\mdavg{23}{31}}{\avg{12}}
+    \end{equation}
+    \item 3 gauge boson
+    \begin{equation}
+        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\mdavg{45}{53}}
+    \end{equation}
+\end{itemize}
+If there are no exceptions, 1 and 2 always represent the scalar and antiscalar respectively, other number represent the gauge boson.
+
+\subsection{Gauge boson sector}
+In this section, we will show how to build the gauge boson scattering. Because there's no direct interaction between gauge boson 1 and gauge boson 2, so we only need to compute one of them.
+And although we have already known the formulas for MHV color-ordered amplitudes for gluon scattering -- Parke-Talyor Formula 
+\begin{equation}
+    A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\mdavg{n-1,n}{n1}}
+\end{equation}
+also for the anti-MHV amplitudes
+\begin{equation}
+    A[\cdots,i^+,\cdots,j^+,\cdots]=\frac{[ij]^4}{[12][34]\cdots[n-1,n][n1]}
+\end{equation}
+Here, we will give an concrete example to show how to use BCFW to compute the 4-point amplitudes $A[3^+,4^+,5^-,6^-]$
+
+\begin{figure}[H]
+    \centering
+    \includegraphics{4ptg.pdf}
+    \caption{4pt gluon}
+\end{figure}
+We choose the $[3,4\rangle$ shift, and it has been proved that $[+,+\rangle$ shift is valid
+\begin{gather}
+    \sket{\hat{3}}=\sket{3}-z\sket{4},\qquad \qquad \aket{\hat{4}}=\aket{4}+z\aket{3} \notag\\
+    \aket{\hat{3}}=\aket{3}, \qquad \sket{\hat{4}}=\sket{4}.
+\end{gather}
+The first diagram can be evaluated 
+\begin{equation}
+    A_1=\frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}\times\frac{1}{s_{36}}\times\frac{\avg{5\hat{I}}^3}{\mdavg{\hat{I}\hat{4}}{\hat{4}5}}
+\end{equation}
+The point here is that 
+\begin{equation}
+    \text{Pole position}:\quad \hat{P}_{34}^2=0=\avg{36}[6\hat{3}]\quad \Rightarrow  \quad [6\hat{3}]=0,
+\end{equation}
+for the similar reason, we can obtain $[\hat{I}6]=[6\hat{3}]=0$, so we conclude that the left part
+\begin{equation}
+    \frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}=0
+\end{equation}
+so the first channel is vanishing.
+
+The second diagram can be similarly evaluated
+\begin{align}
+    A_2&=\frac{\avg{\hat{I}6}^3}{\mdavg{6\hat{3}}{\hat{3}\hat{I}}}\times\frac{1}{s_{36}}\times\frac{[\hat{I}\hat{4}]^3}{[\hat{4}5][5\hat{I}]}\notag \\
+       &=\frac{[34]^3}{[34][45][56][61]}
+\end{align}
+From this, we can conclude that the color-ordered amplitude equals to
+\begin{equation}
+    A[3^+,4^+,5^-,6^-]=\frac{[34]^3}{[34][45][56][63]}.
+\end{equation}
+and it can also be expressed by angle brackets interchangeably
+\begin{equation}
+    A[3^+,4^+,5^-,6^-]=\frac{\avg{56}^3}{\mdavg{34}{45}\!\mdavg{56}{63}}
+\end{equation}
+Then, 5-point , 6-point can be recursively computed by using BCFW recursion relation.
+
+\subsection{SQCD like sector}
+\subsubsection{4-point case}
+First we explain the color decomposition in this sector by 4 point amplitude $\Phi^\dagger V_1V_1\Phi$
+    \begin{figure}[htbp]
+        \centering
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{sch.pdf}
+            \caption{s channel}
+        \end{minipage}
+        \hfill
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{uch.pdf}
+            \caption{u channel}
+        \end{minipage}
+        \hfill
+        \begin{minipage}[t]{0.32\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{tch.pdf}
+            \caption{t channel}
+        \end{minipage}
+    \end{figure}
+
+    The color factor can be written respectively as following
+    \begin{equation*}
+        r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\quad r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\quad
+        r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
+    \end{equation*}
+    We can easily obtain a similar Jacobbi relation
+    \begin{equation}
+        r_t=r_s-r_u
+    \end{equation}
+    Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.
+
+    For example, in the 4pt. case, the full amplitude can be decomposed to the following form
+        \begin{align}
+            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\notag \\
+            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\notag\\
+            &=(A_s+A_t)r_s+(A_u-A_t)r_u
+        \end{align}
+        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
+        \textcolor{red}{[1,2,4,3]} respectively.
+        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
+
+    If there is no special case, we always choose the following BCFW shift
+        \begin{gather}
+            \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\notag\\
+            \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
+        \end{gather}
+    where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.
+
+    We start from the 4-point color-ordered $A[1,2,3^+,4^-]$ again
+    \begin{center}
+    \begin{minipage}{0.45\textwidth}
+        \begin{align*}
+        A[1,2,3^+,4^-] &= \sum_{h}
+        \end{align*}
+        \end{minipage}
+        \hspace{-3em}
+        \begin{minipage}{0.45\textwidth}
+        \raisebox{-1em}{\scalebox{0.8}{\includegraphics{4pt1.pdf}}}
+        \end{minipage}
+    \end{center}
+
+    $\hspace{13.7em} =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$
+
+    For the same reason, the contribution from the second diagram is vanishing, so we only need to compute the firt one
+    \begin{align}
+        A_1&=\frac{\avg{\hat{2}\hat{I}}\avg{\hat{I}1}}{\avg{1\hat{I}}}\times \frac{1}{s_{12}}\times \frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\notag\\
+        &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+    \end{align}
+    where we use the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the \textcolor{red}{Fierz Identity}
+    \begin{equation}
+        [ij][kl]+[il][jk]+[ik][lj]=0
+    \end{equation}
+
+    Here we can prove a nonus relation $\textcolor{red}{A[1,2,3^+,4^+]=0}$. Because of the vanishing of 3 gluon amplitude $A[+,+,+]$, so we only have one channel
+    \begin{figure}[H]
+        \centering
+        \includegraphics{4pt+.pdf}
+        \caption{All plus}
+    \end{figure}
+
+    Similarly, beacuse of the on-shell pole, we obtain
+    \begin{equation}
+        [\hat{2}\hat{I}]=[\hat{I}1]=[1\hat{2}]=0,
+    \end{equation}
+    so the contribution from the left part
+    \begin{equation}
+        \frac{[\hat{2}\hat{I}][\hat{I}1]}{[1\hat{2}]}=0,
+    \end{equation}
+    then we can conclude that
+    \begin{equation}
+        \textcolor{red}{A[1,2,3^+,4^+]=0}
+    \end{equation}
+
+\subsubsection{5-point case}
+
+\noindent
+Still, from the 4-point amplitude, we can first obtain 
+\begin{equation}
+    \textcolor{red}{A[1,2,3^+,4^+,5^+]=0}.
+\end{equation}
+For the 5-point MHV case, here we only consider the $(+,+,-)$ case. 
+\begin{align}
+    A[1,2,3^+,4^+,5^+]&=\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.1.pdf}}}+\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.2.pdf}}}\notag\\
+    &=0+\frac{\avg{2\hat{5}}^2\avg{15}}{\avg{12}\!\mdavg{2\hat{I}}{\hat{I}5}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}3]}
+\end{align}
+then we use
+\begin{equation}
+    \cbrak{2\hat{I}}{\hat{I3}}=\cbrak{24}{43},\quad \acbrak{4\hat{I}}{\hat{I}5}=\acbrak{43}{\hat{3}5}
+\end{equation}
+from the pole position
+\begin{gather}
+    \hat{P}_{34}^2=0=\cbrak{\hat{3}4}{43}\quad \Rightarrow \quad \avg{\hat{3}4}=0\\
+    \avg{34}+z\avg{24}=0\qquad\Rightarrow\quad z=-\frac{\avg{34}}{\avg{24}}
+\end{gather}
+so
+\begin{equation}
+    \avg{\hat{3}5}=\frac{\mdavg{32}{54}}{\avg{24}}
+\end{equation}
+Then the color-ordered amplitude equals to 
+\begin{equation}
+    A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+\end{equation}
+\subsubsection{6 - point case}
+Similarly, we can obtain all - plus(minus) amplitude equals to 0
+\begin{equation}
+    A_6[1,2,3^+,4^+,5^+,6^+]=A_6[1,2,3^-,4^-,5^-,6^-]=0.
+\end{equation}
+
+For the 6-point MHV amplitude $A_6[1,2,3^+,4^+,5^+,6^-]$, here are the corresponding diagrams
+\begin{figure}[H]
+    \centering
+    \includegraphics[]{6pt1.pdf}
+    \caption{6-point MHV}
+\end{figure}
+For the second diagram of Figure 12, there are pure gauge boson subamplitude $A_4[3^+,4^+,5^+,6^-]=0$, so we conclude the second diagram gives vanishing contribution. For the third diagram, 
+\begin{equation}
+    \hat{P}_{12}^2=0=2p_1\cdot\hat{p}_2=\cbrak{1\hat{2}}{\hat{2}1}=\cbrak{12}{\hat{2}1}=0 \qquad \Rightarrow \qquad [\hat{2}1]=0
+\end{equation}
+and similarly
+\begin{equation}
+    [\hat{2}\hat{I}]=[1\hat{I}]=0.
+\end{equation}
+The third diagram equals to
+\begin{equation}
+    A=\frac{[\hat{2}\hat{I}][\hat{I}]1}{[1\hat{2}]}\times\frac{1}{s_{12}}\times A_5[\hat{3}^+,4^+,5^+,6^-,\hat{I}^-]=0.
+\end{equation}
+The only non-vanishing comes from the first diagram equaling to
+\begin{align}
+    A&=\frac{\avg{\hat{2}6}^2\avg{61}^2}{\mdavg{1\hat{2}}{\hat{2}\hat{I}}\mdavg{\hat{I}5}{56}\avg{61}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}3]}\notag\\
+    &=\frac{\avg{26}^2\avg{61}}{\mdavg{12}{2\hat{I}}\!\mdavg{\hat{I}5}{56}}\times\frac{1}{s_{34}}\times \frac{[34]^3}{[4\hat{I}][\hat{I}]3}
+\end{align}
+and we have the following equalities
+\begin{equation}
+    \cbrak{2\hat{I}}{\hat{I}3}+\cbrak{24}{43},\qquad \acbrak{4\hat{I}}{\hat{I}5}=\acbrak{43}{\hat{3}5}
+\end{equation}
+$\avg{\hat{3}5}$ can be obtained from the on-shell propagator
+\begin{equation}
+    \hat{P}_{34}^2=0=\cbrak{\hat{3}4}{4\hat{3}}=\cbrak{\hat{3}4}{43}\qquad \Rightarrow\qquad \avg{\hat{3}4}=0,
+\end{equation}
+then it can be derived that
+\begin{equation}
+    \avg{\hat{3}5}=\frac{\mdavg{23}{45}}{\avg{24}}.
+\end{equation}
+Finally, we can conclude that
+\begin{align}
+    A_6[1,2,3^+,4^+,5^+,6^-]&=\frac{\avg{26}^2\avg{61}\cancel{[34]^3}\cancel{\avg{24}}}{\mdavg{12}{56}\cancel{\avg{24}}\cancel{[43]}\cancel{[43]}\mdavg{23}{45}\cancel{[34]}\avg{43}}\notag\\
+    &=(-1)\frac{\avg{26}^2\avg{61}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\mdavg{56}{61}}.
+\end{align}
+
+Here, we need to notice that in 6-point case, we will first meet the NMHV amplitudes like $A_6[1,2,3^+,4^+,5^-,6^-]$.
+Although we can still compute it by samely utlizing BCFW recursion relaiton, but it is quite messy.
+\subsubsection{n-point case}
+It is not so hard to generallize these results to general case, here we only provide the compact formula, and the negligible sign are neglected
+\begin{equation*}
+    A[1,2,\cdots,n^-]=\frac{\avg{1n}^2\avg{2n}^2}{\mdavg{12}{23}\cdots\mdavg{n-1,1}{n,1}}
+\end{equation*} 
+\subsection{Pure 2-site sector}
+\subsubsection{4-point case}
+The color structure for this kind of amplitude has special form, like
+\begin{equation}
+    (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
+\end{equation}
+Here we start from the 4-point case with the color factor
+\begin{equation}
+    (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
+\end{equation}
+It is more straightforward to observe the color structure in terms of double line notation as follows 
+\vspace{0.5em}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
+\begin{center}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da7604191870446242] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
+%Straight Lines [id:da7895005569652712] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
+%Straight Lines [id:da19217218880843812] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
+%Straight Lines [id:da7866299736623521] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
+%Straight Lines [id:da5667542352395977] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
+%Straight Lines [id:da33701635654582174] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
+%Straight Lines [id:da7076492571881566] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
+%Straight Lines [id:da3803886589182971] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
+%Straight Lines [id:da696489944746132] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
+%Straight Lines [id:da24340791537710427] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
+%Straight Lines [id:da7298898466192736] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
+%Straight Lines [id:da3460055698725] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
+%Straight Lines [id:da4507056480848969] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
+%Straight Lines [id:da6544383915955476] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
+%Straight Lines [id:da03624471669725382] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
+%Straight Lines [id:da34280653261510274] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;
+
+% Text Node
+\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+% Text Node
+\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+
+\end{tikzpicture}
+\end{center}
+For the 4-point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
+configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
+\begin{figure}[htbp]
+    \centering
+    \includegraphics{4pt.eps}
+    \caption{4pt.}
+    \label{1}
+\end{figure}
+
+Because we choose $[2,3\rangle$ shift here, so there is only one valid BCFW channel
+\begin{align*}
+    A[1,2,3_1^+,4_2^-]&=\frac{\mdavg{\hat{2}4}{4\hat{I}}}{\avg{\hat{I}\hat{2}}}\times\frac{1}{s_{24}}\times\frac{[\hat{I}\hat{3}][\hat{3}1]}{[1\hat{I}]}\\
+    &=\frac{[13][23]}{[14][24]}
+\end{align*}
+it seems that this amplitude is different from others before, because it is expressed solely in terms of angle brackets, but of course it can be rewritten to another form.
+\begin{align*}
+    \frac{[13][23]}{[14][24]}&=\frac{\cbrak{23}{31}}{\cbrak{23}{41}}\times \frac{\acbrak{23}{31}}{\acbrak{24}{31}}\\
+    &=-\frac{\cbrak{24}{\bcancel{41}}}{\avg{23}\bcancel{[41]}}\times(-1)\frac{\bcancel{[24]}\avg{41}}{\bcancel{[24]}\avg{31}}\\
+    &=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+\end{align*}
+Also, we can compute it from direct gluing. For the first diagram, the residue equals to
+\begin{equation*}
+    \mathrm{Res}|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
+\end{equation*}
+Similarly, the second one is
+\begin{equation*}
+    \mathrm{Res}|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
+\end{equation*}
+
+Then we can conclude that the four-point color-ordered amplitude $A[1,2,3^+,4^-]$ equals to
+\begin{equation*}
+    A[1,2,3^+,4^-]=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23][42]\avg{24}}=\frac{\avg{24}\avg{14}}{\avg{13}\avg{23}}
+\end{equation*}
+
+\textcolor{red}{$\star Bonus$}
+
+It is still necessary to prove the color-ordered amplitude $A[1,2,3^+,4^+]$ equals to 0. Here we can use the color ordered Feynman rules to show the result.
+\begin{equation*}
+    A[1,2,3^+,4^+]\propto \frac{\left(\epsilon_3\cdot p_2\right)\left(\epsilon_4\cdot p_1\right)}{s_{23}}+\frac{\left(\epsilon_4\cdot p_2\right)\left(\epsilon_3\cdot p_1\right)}{s_{24}} 
+\end{equation*}
+Here we can utilize the spinor-helicity variable to express polarization vector
+\begin{equation*}
+    \epsilon_2^{+\mu}=\frac{\langle r_1 | \gamma^\mu | 3 ]}{\sqrt{2}\avg{r_13}},\qquad \epsilon_4^{+\mu}=\frac{\left <r_2|\gamma^\mu|4\right ]}{\sqrt{2}\avg{r_24}}
+\end{equation*}
+here $r_1$ and $r_2$ represent the reference spinor.
+
+We can freely choose $r_1=r_2=1$ or 2, then $\avg{r_1 2}$,$\avg{r_2 1}$,$\avg{r_1 1}$,$\avg{r_2 2}$, two of them equal to 0, so we can conclude that
+\begin{equation*}
+    A[1,2,3^+,4^+]=0
+\end{equation*}
+\subsubsection{5-point case}
+For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
+we always consider the MHV (Maximal helicity violation) amplitude.
+
+Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 
+of this kind of gauge theory, the color structure is invariant under the OPP (Order Preserving Permutation), in this case, for example,
+\begin{equation}
+    (3_1^+,4_1^+,5_2^-)\qquad (3_1^+,5_2^-,4_1^+)\qquad(5_2^-,3_1^+,4_1^+)
+\end{equation}
+give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude. We can draw all diagrams contributing to the BCFW process, the first two are following
+\par
+\begin{figure}[H]
+    \centering
+    \includegraphics{5pt1.eps}
+    \caption{5pt. 1}
+    \label{2}
+\end{figure}
+It is obvious that the second diagram in Figure 13 equals to 0, because there are no interaction between the two gauge bosons.
+Similarly, another two diagrams equal to 0 for the same reason
+\begin{figure}[H]
+    \centering
+    \includegraphics{5pt2.eps}
+    \caption{5pt. 2}
+    \label{3}
+\end{figure}
+\par
+The last diagram still gives 0 contribution because it includes a subamplitude $A[1,\hat{I},\hat{3}^+,4^+]=0$.
+\par
+\begin{figure}[H]
+    \centering
+    \includegraphics{5pt3.eps}
+    \caption{5pt. 3}
+    \label{4}
+\end{figure}
+Above all. only the first diagram in Figure 1 has non-vanishing contributions, so the full color ordered amplitude equals to
+\begin{align}
+    A[1,2,3_1^+,4_1^+,5_2^-]&=A[1,2,\hat{I}^+,5^-]\times\frac{1}{s_{34}}\times A[\hat{3}^+,4^+,\hat{I}^-]\notag\\
+    &=\frac{\mdavg{15}{25}}{\mdavg{1\hat{I}}{2\hat{I}}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
+    &=\frac{\mdavg{15}{25}\bcancel{[34]^3}}{\mdavg{14}{23}\avg{43}\bcancel{[43][43][34]}}\\
+    &=\frac{\mdavg{15}{25}}{\mdavg{23}{34}\avg{41}}\notag\\
+    &=\frac{(-1)\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align}
+where we use the fact $|\hat{3}\rangle=|\hat{3}\rangle$ and following identities
+\begin{equation}
+    \cbrak{1\hat{I}}{\hat{I}3}=\cbrak{14}{43},\quad \cbrak{2\hat{I}}{\hat{I}3}=\cbrak{24}{43}
+\end{equation}
+and also
+\begin{align}
+    \frac{[\hat{I}3]}{[4\hat{I}]}&=-\frac{\acbrak{3\hat{I}}{\hat{I}2}}{\acbrak{4\hat{I}}{\hat{I}2}}=-\frac{\acbrak{34}{42}}{\acbrak{43}{\hat{3}2}},\quad(\avg{\hat{3}2}=\avg{32}+z\avg{22}=\avg{32})\notag\\
+    &=\frac{\avg{42}}{\avg{32}}
+\end{align}
+here green refers to the particle with (-) helicity, red refers to particles belong to gauge group 1, red refers to particles belong to gauge group 2.
+\par
+Similarly, it is very easy to obtain another color-ordered amplitude $A[1,2,3_1^+,4_1^-,5_2^+]$
+\begin{align}
+    A[1,2,3_1^+,4_1^-,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{4}}^2\!\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{align}
+and also $A[1,2,3_1^-,4_1^+,5_2^+]$ equals to
+\begin{equation}
+    A[1,2,3_1^-,4_1^+,5_2^+]=
+    \frac{(-1)\avg{2\textcolor{green}{3}}^2\!\avg{1\textcolor{green}{3}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+\end{equation}
+But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5^+ \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
+\subsubsection{6-point case}
+Here we consider $(V_2V_2\Phi^\dagger V_1V_1 \Phi)$ case, the corresponding color-ordered amplitude is $A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]$.
+Similarly, the fowwling orders all give us the same color factor
+\begin{gather}
+    (3_1^+,4_1^+,5_2^+,6_2^-)\qquad(3_1^+,5_2^+,4_1^+,6_2^-)\qquad (3_1^+,5_2^+,6_2^-,4_1^+)\notag\\
+    (5_2^+,3_1^+,4_1^+,6_2^-)\qquad(5_2^+,3_1^+,6_2^-,4_1^+)\qquad (5_2^+,6_2^-,3_1^+,4_1^+)
+\end{gather}
+Only two diagrams have semmingly non-zero contribution,
+\par
+\begin{figure}[H]
+    \centering
+    \includegraphics{6pt.eps}
+    \caption{6pt.}
+    \label{5}
+\end{figure}
+so the full color ordered amplitude equals to
+\begin{align}
+    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
+    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
+    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
+    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
+\end{align}
+where we have used the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the following identities
+\begin{equation}
+    \cbrak{2\hat{I}}{\hat{I}3}=\cbrak{24}{43}, \qquad \acbrak{4\hat{I}}{\hat{I}1}=\acbrak{43}{\hat{3}1}
+\end{equation}
+The point here is that we first $\avg{\hat{3}1}$ which does not appear in 5-point case, so we nned to compute it carefully
+\begin{gather}
+    \text{pole position}: \quad \hat{P_{34}}^2=0=2P_3\cdot P_4=\cbrak{4\hat{3}}{34}\qquad\Rightarrow \qquad \avg{4\hat{3}}=0\notag\\
+    \avg{43}+z\avg{42}=0\qquad \Rightarrow \qquad z=-\frac{43}{42}
+\end{gather}
+then
+\begin{align}
+    \avg{\hat{3}1}=\avg{31}+z\avg{21}&=\avg{31}-\frac{\avg{43}}{\avg{42}}\avg{21}\notag\\
+    &=\frac{\mdavg{42}{31}-\mdavg{43}{21}}{42}\notag\\
+    &=\frac{\mdavg{41}{32}}{\avg{42}}
+\end{align}
+where we have used the Fierz identity
+\begin{equation}
+    \mdavg{42}{31}+\mdavg{41}{23}+\mdavg{43}{12}=0.
+\end{equation}
+Simiraly, we can compute the second diagram
+\begin{equation}
+    A_2=\frac{[\hat{2}5][5\hat{I}]}{[\hat{I}\hat{2}]}\times\frac{1}{s_{25}}\times \frac{(-1)\asqu{16}\asqu{\hat{I}6}}{\mdavg{\hat{I}\hat{3}}{\hat{3}4}
+    \!\mdavg{41}{\hat{I}6}\!\avg{61}}
+\end{equation}
+but from the pole position
+\begin{equation}
+    \hat{P_{25}}^2=0=2P_2\cdot P_5=\cbrak{52}{\hat{2}5}\qquad\Rightarrow \qquad [\hat{2}5]=0,
+\end{equation}
+and simiraly
+\begin{equation}
+    [\hat{2}\hat{I}]=[5\hat{I}]=0.
+\end{equation}
+Then we can conclude that the left part of the amplitude equals to 0 so $A_2=0$. Finally, we obtain the color-ordered amplitude 
+\begin{equation}
+    A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=A_1+A_2=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}.
+\end{equation}
+\subsection{n-point case}
+Here, we first propose a compact formula for the color-ordered amplitude
+\begin{equation}
+    A=\frac{\asqu{2a}\!\asqu{1a}}{\underbrace{\avg{2\star}\cdots \avg{\star 1}}_{SU(N_1)}\underbrace{\avg{2\ast }\cdots \avg{\ast 1}}_{SU(N_2)}}
+\end{equation}
+where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
+refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
+\par
+The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.
+
+\section{Summary and Outlook}
+
+In this paper, we have explored scattering amplitudes within the framework of (De)construc-ted gauge theories, focusing specifically on the simplest 2 - site model.
+Considering the well-known limitations of conventional Feynman diagram methods — particularly their complexity in handling huge number of gauge redundancies and their failure to naturally exhibit hidden symmetries like dual conformal invariance, so that modern amplitude techniques, such as the BCFW recursion relation, provide powerful alternatives.
+By leveraging complex momentum shifts, BCFW recursion effectively reduces higher-point scattering amplitudes to simpler lower-point amplitudes, offering substantial analytical and computational simplifications.
+
+Our work applied the BCFW recursion relation alongside related modern amplitude methods, including color-ordering and spinor-helicity formalisms, to investigate tree-level scattering processes within this simplest two-site scenario.
+This model serves as an ideal testing ground due to its renormalizability and clear connection to higher-dimensional physics, specifically Kaluza-Klein (KK) modes emerging dynamically through dimensional deconstruction.
+
+Looking forward, several promising directions arise naturally from our current study.
+Firstly, it is compelling to extend the two-site model analysis systematically to more intricate configurations, such as three-site or general $n$-site models.
+Increasing the number of sites allows for richer dynamical behavior and a more realistic representation of higher-dimensional gauge theories.
+Introducing massive scalar or gauge bosons into the model could further enhance realism, closely mimicking genuine KK spectra as encountered in phenomenological models of compactified extra dimensions.
+
+Another intriguing avenue of future research involves incorporating gravity into this (De)constructed framework.
+Developing a gravitational analogue through a similar deconstruction procedure, or applying the double-copy technique to our existing gauge-theoretic amplitudes, could yield novel gravitational amplitudes.
+Such gravitational models would enable the investigation of analogous cancellations observed in KK scattering, potentially offering insights into the intricate interplay between gauge theories and gravity.
+
+In conclusion, the results presented here set the foundation for future explorations into more complex (De)constructed models and their gravitational counterparts.
+These studies promise to deepen our understanding of amplitude structures, dimensional emergence, and the broader implications of gauge-gravity dualities.
 

### 2025-05-16 Master Thesis/thesis.tex
New

@@
     \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
+    \label{2.61}
 \end{equation}
@@
 Although we can still compute it by samely utlizing BCFW recursion relaiton, but it is quite messy.
+So it is better to introduce another method named CSW expansion.
+
+We introduce the general shift in section 2.4.1 like \eqref{2.61} and specialize to BCFW shift in section 2.4.2 like \eqref{2.71}.
+Here, I will introduce another kind of recursion relation.
+Consider a shift which is implemented by a ``holomorphic'' square spinor shift:
+\begin{equation}
+    \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{i}=\aket{i},
+    \label{4.37}
+\end{equation}
+Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n}c_i\aket{i}=0$.
+Notice that this equation can be always solved and the shift spinors also satisfy momentum conservation and on-shell condition.
+
+We consider here a situation where all $c_i \neq 0$ so that all momentum lines are shifted via\eqref{4.37} – this is an all-line shift.
+And the large - z behavior of all-line shift can be found in this paper\cite{Cohen:2010mi}.
+As shown in \cite{Elvang:2008vz}, N$^{K}$MHV gluon tree amplitudes fall off as $1/z^K$ under an all-line shift in the large-$z$ limit.
+This implies that all tree-level gluon amplitudes---except the MHV case with $K = 0$---can be fully constructed using the all-line shift recursion relations.
+
+The critical point here is that the MHV amplitudes depend only on angle spinors, so the only way we can know about the square-spinor
+shift is arrording to the internal line angle spinors $\aket{\hat{P}_I}$, and this $\aket{\hat{P}_I}$ can be written in a wise manner
+\begin{equation}
+    \aket{\hat{P}_I}\frac{[\hat{P}_I X]}{[\hat{P}_I X]}=\hat{P}_I\sket{X}\frac{1}{[\hat{P}_IX]}=P_I\sket{X}\frac{1}{[\hat{P}_IX]},
+\end{equation}
+where we can drop the hat upon the shifted momentum $\hat{P}_I$ because the shift is proportional to $\sket{X}$, so that it will become 0 when contracting with itself.
+And other point is there are same number of $\aket{P}_I$ appearing in the numerator and demoninator as there's no helicity dependence on internal propagator, so that all of $\frac{1}{[\hat{P}_IX]}$ can be canceled with other.
+
+Then for each diagram we can use the following prescription
+\begin{equation}
+    \aket{P}_I \quad \rightarrow \quad P_I\sket{X}, 
+\end{equation}
+
+For example
+\begin{equation}
+    \raisebox{-5.5mm}{\includegraphics[height=1.5cm]{csw-6pt-A2}}
+   ~=~ 
+\frac{\langle 1|P_{156}|X]^4}{\langle 1|P_{156}|X]\langle 5|P_{156}|X]\langle 56\rangle \langle 61\rangle}
+\cdot \frac{1}{P_{156}^2}
+\cdot \frac{\langle 23\rangle^4}{\langle 23\rangle \langle 34\rangle \langle 4|P_{156}|X]\langle 2|P_{156}|X]}
+\end{equation}
+
+In general, individual diagrams exhibit an explicit dependence on the reference spinor $\sket{X}$.
+However, the full tree-level amplitude must remain independent of this arbitrary choice.The expansion of amplitudes using MHV vertex diagrams extends naturally beyond the NMHV level.
+More generally, an N$^K$MHV tree-level amplitude can be expressed as a sum over all tree diagrams containing exactly $K + 1$ MHV vertices.
+Henceforth, this method is called \tif{MHV vertex expansion}.
+But actually, this method was discovered by Cachazo, Svrcek, and Witten \cite{Cachazo:2004kj} befor introducing complex shift, so it is also named \tif{CSW expansion}.
 \subsubsection{n-point case}
@@
 \end{gather}
-Only two diagrams have semmingly non-zero contribution,
+Evey OPP corresponds different BCFW diagrams, here for concreteness, we list all of the diagrams as following 
+\begin{itemize}
+    \item $(3_1^+,4_1^+,5_2^+,6_2^-)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_1.pdf}
+        \caption{Order $(3_1^+,4_1^+,5_2^+,6_2^-)$}
+    \end{figure}
+    \item $(3_1^+,5_2^+,4_1^+,6_2^-)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_2.pdf}
+        \caption{Order $(3_1^+,5_2^+,4_1^+,6_2^-$}
+    \end{figure}
+    \item $(3_1^+,5_2^+,6_2^-,4_1^+)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_3.pdf}
+        \caption{Order $(3_1^+,5_2^+,6_2^-,4_1^+)$}
+    \end{figure}
+    \item $(5_2^+,3_1^+,4_1^+,6_2^-)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_4_1.pdf}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt_1_4_2.pdf}
+        \caption{Order $(5_2^+,3_1^+,4_1^+,6_2^-)$}
+    \end{figure}
+    \item $(5_2^+,3_1^+,6_2^-,4_1^+)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_5_1.pdf}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt1_5_2.pdf}
+        \caption{Oredr $(5_2^+,3_1^+,6_2^-,4_1^+)$}
+    \end{figure}
+    \item $(5_2^+,6_2^-,3_1^+,4_1^+)$
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt_1_6_1.pdf}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt_1_6_2.pdf}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics{6pt_1_6_3.pdf}
+        \caption{Order $(5_2^+,6_2^-,3_1^+,4_1^+)$}
+    \end{figure}
+\end{itemize}
+
+Most of them equal to 0 because of there are no interaction between two gauge bosons or special helicity configuration.
+And some of the nonvanishing diagrams have same structure under OPP so they conly contribute once.
+Finally, only two diagrams have semmingly non-zero contribution,
 \par

### 2025-05-27 Master Thesis/thesis.tex
New

@@
 \newcommand{\tif}[1]{\textit{\textbf{#1}}}
+\newcommand{\asbra}[3]{\langle #1 | #2 |#3 ]}
 \onehalfspacing
@@
 \normalsize
-This paper mainly show the computation for scattering amplitudes in a kind of (De)Constructed gauge theory, by using the so called on shell method. As we have known,
-under the conventional quantum field theory frame, Feynman proposed a brilliant method -- Feynman diagrams, to help us perturbatively compute scattering amplitude by a
-diagrammatic method. However, this method faces many challenges during the improvements of physical theory and complexity of construction for model building, there are many
-amplitudes hard to compute by hand or even impossible to compute. Hence, it is quite necessary to introduce a new method.      
+This thesis explores tree-level scattering amplitudes in (De)constructed gauge theories using modern on-shell methods.
+Traditional Feynman diagram techniques, though systematic, become increasingly cumbersome in theories with gauge redundancies and high multiplicity.
+Motivated by these limitations, we adopt a framework based on analyticity, factorization, and gauge invariance, applying the BCFW recursion relation and related spinor-helicity techniques.
+
+Our analysis focuses on the two-site model, the simplest (De)constructed scenario, which provides a renormalizable four-dimensional realization of dimensional deconstruction and naturally generates Kaluza-Klein (KK)-like spectra.
+Tree-level color-ordered amplitudes involving massive and massless vector bosons are computed using the BCFW recursion, revealing significant simplifications and cancellation patterns, especially in longitudinal gauge boson scattering.
+To access non-MHV sectors, we further employ the Cachazo-Svrček-Witten (CSW) expansion, which efficiently constructs NMHV amplitudes from MHV vertices, offering a complementary perspective to BCFW recursion.
+
+Our results demonstrate that on-shell methods remain powerful even in semi-realistic settings with broken gauge symmetry and massive states.
+The structural simplicity of the resulting amplitudes suggests potential geometric interpretations and invites extensions to loop-level processes.
+
+Future directions include applying generalized unitarity and BCFW-based recursion at loop level, incorporating double-copy constructions to study gravitational analogues, and exploring formulations via the CHY formalism, scattering forms, or positive geometry such as the amplituhedron.
+These approaches promise deeper insight into the unifying principles behind quantum field theories and the emergence of higher-dimensional behavior from four-dimensional dynamics.
+
+\textbf{Keywords:} scattering amplitudes, on-shell methods, BCFW recursion,  (De)constructed gauge theory
+
 \end{abstract}
@@
 The residue associated with this unphysical pole must vanish, and indeed it does: the spurious contributions cancel out when summing over all relevant BCFW diagrams.
+More wisely, Hodges introduced the momentum twistor formalism to eliminate spurious poles \cite{Hodges:2009hk} and the introduction of momentum twistors laid the foundation for the development of the amplituhedron \cite{Arkani-Hamed:2013jha}, providing a natural coordinate system for its geometric formulation.
 
@@
 \end{equation}
+
+Here, for the 6-point amplitude $A_6[1,2,3^+,4^-,5^+,6^-]$, we can computing by this method 
+\begin{align}
+    A_6[1,2,3^+,4^-,5^+,6^-] = &\frac{\avg{24}^2\langle 4|P_{234}|X]}{\langle 2|P_{234}|X]\mdavg{23}{34}}\times \frac{1}{s_{12}}\times \frac{\langle 6|P_{156}|x]^2\avg{61}}{\langle 1|P_{156}|x]\mdavg{25}{56}}\notag \\
+    &+\frac{\avg{24}^2\asbra{4}{P_{61}}{X}^2}{\asbra{5}{P_{61}}{X}\asbra{2}{P_{61}}{X}\mdavg{23}{34}\!\avg{45}}\times\frac{1}{s_{61}}\times\frac{\avg{61}\asbra{6}{P_{61}}{X}}{\asbra{1}{P_{61}}{X}}\notag \\
+    &+\frac{\asbra{1}{P_{123}}{X}^2\asbra{2}{P_{123}}{X}}{\asbra{3}{P_{123}}{X}\mdavg{13}{21}}\times\frac{1}{s_{123}}\times \frac{\avg{46}^4}{\asbra{4}{P_{456}}{X}\asbra{6}{P_{456}}{X}\mdavg{45}{56}}\notag \\
+    &+\frac{\avg{14}^2\avg{24}^2}{\asbra{4}{P_{56}}{X}\asbra{1}{P_{56}}{X}\mdavg{23}{34}}\times \frac{1}{s_{56}}\times\frac{\asbra{6}{P_{56}}{X}^3}{\asbra{5}{P_{56}}{X}\avg{56}}
+\end{align}
+
+In principle, there is another diagram contributing to this amplitude
+\begin{figure}[H]
+    \centering
+    \includegraphics{sqcd6.pdf}
+    \caption{MHV $\times$ anti-MHV}
+\end{figure}
+but because of the 3 particle special kinematics, the 3-point anti-MHV part gives vanishing contributtion, this diagram actually equals to 0.
+This is why we called this method MHV expansion in the following.
 
@@
 \end{equation}
+
+For the NMHV ampitudes $A[1,2,3_1^+,4_1^-,5_2^+,6_2^-]$, we can obtain the following equation
+\begin{align}
+    A[1,2,3_1^+,4_1^-,5_2^+,6_2^-] =& \frac{\avg{24}\asbra{4}{P_{234}}{X}}{\avg{24}\asbra{3}{P_{234}}{X}}\times\frac{1}{s_{234}}\times\frac{\avg{61}\asbra{6}{P_{156}}{X}}{\avg{51}\asbra{5}{P_{156}}{X}}\notag\\
+    &+\frac{\avg{26}\asbra{6}{P_{256}}{X}}{\avg{25}\asbra{5}{P_{256}}{X}}\times\frac{1}{s_{256}}\times\frac{\avg{14}\asbra{4}{P_{134}}{X}}{\avg{13}\asbra{3}{P_{134}}{X}}\notag\\
+    &+\frac{\avg{26}^2\avg{61}}{\mdavg{25}{56}\asbra{2}{P_{34}}{X}\asbra{1}{P_{34}}{X}}\times\frac{1}{s_{34}}\times\frac{\asbra{4}{P_{34}}{X}^3}{\avg{34}\asbra{3}{P_{34}}{X}}\notag\\
+    &+\frac{\avg{24}^2\avg{41}}{\mdavg{23}{36}\asbra{2}{P_{56}}{X}\asbra{1}{P_{56}}{X}}\times\frac{1}{s_{56}}\times\frac{\asbra{6}{P_{56}}{X}^3}{\avg{56}\asbra{5}{P_{56}}{X}}.
+\end{align}
+
 \subsection{n-point case}
@@
 \section{Summary and Outlook}
-
-In this paper, we have explored scattering amplitudes within the framework of (De)construc-ted gauge theories, focusing specifically on the simplest 2 - site model.
-Considering the well-known limitations of conventional Feynman diagram methods — particularly their complexity in handling huge number of gauge redundancies and their failure to naturally exhibit hidden symmetries like dual conformal invariance, so that modern amplitude techniques, such as the BCFW recursion relation, provide powerful alternatives.
+In this paper, we have explored scattering amplitudes within the framework of (De)constructed gauge theories, focusing specifically on the simplest 2-site model.
+Considering the well-known limitations of conventional Feynman diagram methods — particularly their complexity in handling the vast gauge redundancies and their failure to naturally exhibit hidden symmetries such as dual conformal invariance — modern amplitude techniques, such as the BCFW recursion relation, provide powerful alternatives.
 By leveraging complex momentum shifts, BCFW recursion effectively reduces higher-point scattering amplitudes to simpler lower-point amplitudes, offering substantial analytical and computational simplifications.
@@
 
+In addition to BCFW recursion, we have also incorporated the Cachazo-Svrček-Witten (CSW) expansion to compute next-to-maximally helicity-violating (NMHV) amplitudes.
+The CSW approach, based on the MHV vertex expansion, re-expresses amplitudes as connected diagrams built from on-shell MHV amplitudes and scalar propagators, offering an efficient alternative to traditional Feynman rules for nontrivial helicity sectors.
+Within our (De)constructed setup, the CSW framework enables a transparent decomposition of NMHV tree amplitudes and facilitates comparison with results obtained from BCFW, serving as a valuable complementary computational tool.
+
 Looking forward, several promising directions arise naturally from our current study.
-Firstly, it is compelling to extend the two-site model analysis systematically to more intricate configurations, such as three-site or general $n$-site models.
+Firstly, it is compelling to extend the two-site model analysis systematically to more intricate configurations, such as three-site or general \( n \)-site models.
 Increasing the number of sites allows for richer dynamical behavior and a more realistic representation of higher-dimensional gauge theories.
@@
 
+Within the broader landscape of modern amplitude methods and higher-dimensional theories, various directions remain to be explored.
+
+First, one natural extension is to apply on-shell techniques beyond the tree level.
+Loop amplitudes in gauge and gravity theories present formidable computational challenges when approached via traditional Feynman methods.
+However, modern on-shell approaches — such as generalized unitarity and integrand reduction — have proven to be powerful tools in reconstructing loop integrands from on-shell tree amplitudes~\cite{Bern:1994zx}.
+Notably, certain extensions of BCFW recursion relations have also been proposed for one-loop amplitudes~\cite{Kharel:2011vz}, where under carefully chosen complex momentum shifts, the integrands of loop-level diagrams can be constructed recursively using forward limits of tree amplitudes.
+These developments not only enable efficient computation but also reveal hidden structures in multi-loop amplitudes, such as iterative patterns and dual conformal invariance.
+
+Secondly, the double-copy correspondence between gauge and gravity theories~\cite{Bern:2010ue} opens a compelling avenue for constructing gravitational amplitudes from gauge-theoretic data.
+Applying double-copy techniques to (De)constructed gauge amplitudes may allow the generation of corresponding gravitational amplitudes, potentially illuminating novel relations between dimensional deconstruction and the emergence of semi-classical gravity.
+
+Another important frontier is the celestial amplitude program~\cite{Pasterski:2017kqt}, which reinterprets flat-space S-matrix elements as conformal correlators on the celestial sphere.
+Translating amplitudes from our (De)constructed framework into this basis may uncover new conformal structures and clarify connections to soft theorems and asymptotic symmetries, particularly in the context of dimensional emergence.
+
+On-shell techniques have also begun to play a central role in understanding the classical dynamics of gravitating systems.
+Recent studies have demonstrated how scattering amplitudes can be used to compute classical observables, such as deflection angles and radiation profiles, in black hole encounters~\cite{Guevara:2019fsj,Neill:2013wsa}.
+In particular, the use of amplitude-based methods to study black hole mergers and angular momentum transfer has gained traction~\cite{Aoki:2024boe}.
+Extending our methods to incorporate spinning particles or KK black hole analogs within (De)constructed frameworks may provide novel insights into the classical gravitational limit of higher-dimensional gauge systems.
+
+Beyond computational techniques, recent advances have revealed that scattering amplitudes possess remarkably rich mathematical structures that transcend their Feynman diagram origins.
+The Cachazo-He-Yuan (CHY) formalism~\cite{Cachazo:2013gna}~\cite{Cachazo:2013hca}~\cite{Cachazo:2013iea} reformulates tree-level amplitudes in a variety of theories — including gauge theory, gravity, and scalar theory — as contour integrals over the moduli space of punctured Riemann spheres, localized on solutions to the so-called scattering equations.
+This approach unifies diverse theories into a single geometric framework and suggests a deep connection between worldsheet models and field theory amplitudes.
+
+Building on such geometric insights, the notion of scattering forms~\cite{Arkani-Hamed:2017mur} encodes amplitudes as differential forms on kinematic spaces or moduli spaces.
+These forms have logarithmic singularities only on physical poles, and their residues capture consistent factorization properties.
+Scattering forms provide a natural language for organizing amplitudes independently of specific Feynman representations, with close ties to positive geometry and canonical forms.
+
+Most strikingly, in planar \( \mathcal{N}=4 \) super Yang-Mills theory, the amplituhedron offers a geometric reformulation in which the integrand of scattering amplitudes is interpreted as the canonical form on a positive region of the Grassmannian.
+This picture bypasses locality and unitarity as input, instead deriving them from global geometric consistency.
+These developments highlight a profound shift: scattering amplitudes may ultimately be understood as emergent from geometry and combinatorics, rather than traditional Lagrangian dynamics.
+
+Altogether, these directions — from higher-loop gauge and gravity amplitudes, to celestial reformulations, to classical black hole dynamics — point to a broad and rich landscape where modern amplitude techniques can deepen our understanding of spacetime, duality, and quantum gravity.
+The present work lays foundational steps toward the future goals within the context of (De)constructed quantum field theories or another different directions.
+
 In conclusion, the results presented here set the foundation for future explorations into more complex (De)constructed models and their gravitational counterparts.

### 2025-05-29 Master Thesis/thesis.tex
New

@@
 \normalsize
+\noindent
+Name: Su Yingze
+
+\noindent
+Student number: 262309017
+
 This thesis explores tree-level scattering amplitudes in (De)constructed gauge theories using modern on-shell methods.
@@
 \section{Introduction}
-As we have known,
-under the conventional quantum field theory frame, Richard Feynman proposed a brilliant method -- Feynman diagrams, to help us perturbatively compute scattering amplitude by a
-diagrammatic method. However, this method faces many challenges during the improvements of physical theory and complexity of construction for model building, there are many
-amplitudes hard to compute by hand or even impossible to compute. In gauge theory, there are huge number of gauge redundancies, making the computation quite complicated.
-We need to address with this kind of unphysical degree of freedom, otherwise we can not obtain the correct physical quantities.
-Also, we have to address with kinematic factor and color factor simultaneously in the nonabelian gauge theory.
-And it has been known that the amplitudes in $\mathcal{N}=4$ super Yang-Mills theory obtain the symmetry -- dual superconformal symmetry\cite{Drummond:2008vq}, which is not reflected in conventional Feynman diagram method.
-
-Hence, all of these factors impetus physicists to propose something new, then the BCFW recursion relation is the first product as a new method to compute amplitudes .
-Historically, the original recursion relation is for gluon scattering amplitudes, coming from Britto, Cachazo and Feng \cite{Britto:2004ap},
-and it can be seen as the first breakthrough for modern amplitude method.
-They explored the analytic properties of amplitudes when extended into complex momentum space.
-In particular, they considered deforming two external momenta by a complex parameter z, in such a way that the on-shell conditions and momentum conservation are preserved.
-Through this deformation, they observed that tree-level amplitudes exhibit simple pole structures in the complex 
-z-plane, corresponding to internal propagators going on-shell. This analytic structure allowed them to derive a recursion relation that expresses an 
-n-point amplitude in terms of lower-point amplitudes.
-Edward Witten subsequently noticed that his Twistor String Theory\cite{Witten:2003nn}, which reveals the hidden symmetry and geometry structure of amplitude, implied that the scattering amplitudes has stronger
-analytic property.
-Their collaboration led to a general formulation of the recursion relations, now known as the BCFW recursion relations\cite{Britto:2005fq}, named after Ruth Britto, Freddy Cachazo, Bo Feng, and Edward Witten.
-In particular, Witten helped clarify the large -- z behavior of the amplitudes under complex momentum shifts --- a crucial condition ensuring the validity of the recursion.
-
-The starting point comes from the precise cancellation in scattering for longitudinal modes of massive spin-2 Kaluza-Klein(KK) states.
-While individual contributions grow as $\mathcal{O}(s^5)$, $\mathcal{O}(s^4)$, $\mathcal{O}(s^3)$ and $\mathcal{O}(s^2)$, it has been proved that these contributions are cancelled with
-each other in a quite intricate way\cite{SekharChivukula:2019yul}, and the final results only grow as $\mathcal{O}(s)$.
-But it is quite difficult to compute this kind of scattering amplitudes, so if we can obtain some clues for this KK scattering amplitudes from other aspects, it may help us to
-understand this cancellation in another way.
-This paper is motivated by a kind of (De)constructed gauge theory, proposed by Nima, Cohen and Georgi\cite{Arkani-Hamed:2001kyx}.
-They constructed a renormalizable, asymptotically free, four dimension gauge theories that dynamically generate a fifth dimension.
-In this paper, the authors proposed that the “ Condensed '' theory actually discretized a five dimension gauge theory with gauge group $SU(m)$.
-After higgsing, the Kaluza-Klein spectrum for $S^1$ compactification appears.
-It encourages to compute scattering amplitudes in this model.
-This paper mainly contributes to the
-computation for scattering amplitudes in the simplest 2-site model by utilizing BCFW recursion relation and other related method, such as color-ordered amplitudes, spinor-helicity formalism, etc.
+As we have known, under the conventional quantum field theory framework, Richard Feynman introduced an elegant method—Feynman diagrams—to perturbatively compute scattering amplitudes through diagrammatic expansions.
+Despite their intuitive and systematic nature, these diagrams quickly become complicated as the complexity of physical theories grows, particularly in gauge theories.
+When dealing with non-Abelian gauge fields such as gluons, an enormous number of redundant gauge degrees of freedom often arises, significantly increasing computational complexity.
+This redundancy requires meticulous handling to ensure correct and gauge-invariant results.
+Furthermore, traditional Feynman diagrams obscure underlying symmetries, such as the dual superconformal symmetry observed explicitly in N = 4 super Yang-Mills theory, making it difficult to identify and exploit these hidden structures.
+
+These challenges have strongly motivated physicists to develop alternative, more efficient methods.
+Among these, the BCFW recursion relation represents a pivotal breakthrough.
+Originating from the work of Britto, Cachazo, and Feng, and later generalized in collaboration with Edward Witten, the BCFW recursion provides a powerful method to compute amplitudes by analytically continuing external momenta into the complex plane.
+By deforming two external momenta with a complex parameter, while maintaining momentum conservation and on-shell conditions, the amplitudes exhibit simplified pole structures, enabling recursive computation from lower-point amplitudes.
+This method not only streamlines calculations but also naturally reveals hidden symmetries and analytic properties that are invisible through traditional approaches.
+
+Motivated by insights from dimensional deconstruction, this thesis investigates a simplified yet rich class of gauge theories—the (De)constructed gauge theories—where higher-dimensional theories emerge dynamically from four-dimensional renormalizable setups.
+Proposed initially by Arkani-Hamed, Cohen, and Georgi, these models discretize additional spatial dimensions into gauge groups linked by scalar fields.
+Specifically, we focus on the simplest example, the two-site model, which dynamically generates Kaluza-Klein-like states.
+One intriguing phenomenon in these models is the subtle cancellation of amplitudes involving longitudinal modes of massive gauge bosons, which mimics the behavior observed in genuine higher-dimensional gauge theories.
+
+In this work, we apply modern amplitude techniques, such as the BCFW recursion relation and the spinor-helicity formalism, to compute tree-level amplitudes within this two-site framework.
+By exploring both maximally helicity violating (MHV) and next-to-MHV (NMHV) configurations using the Cachazo-Svrček-Witten (CSW) expansion, we demonstrate significant simplifications and uncover intricate cancellation patterns.
+These results not only validate the effectiveness of modern on-shell methods in theories with massive and massless gauge fields but also suggest deeper geometric interpretations.
+
+This thesis serves as the foundational step in my research journey, equipping me with essential knowledge and skills and broadening my perspective in scattering amplitude computations.
+Through this initial exploration of (De)constructed gauge theories using modern on-shell methods, I have established a robust understanding of tree-level amplitudes and gained familiarity with pivotal tools like the BCFW recursion relation and the spinor-helicity formalism.
+This groundwork will enable me to efficiently transition into further research directions, facilitating deeper inquiries into various topics in theoretical physics.
+
+The structure of this thesis is organized as follows: Chapter 2 provides a comprehensive review of essential theoretical background, including the color structure of gauge theory and modern amplitude techniques such as BCFW recursion, spinor-helicity formalism, and CSW expansions.
+Chapter 3 introduces the general (De)constructed gauge theory framework, discussing the overall structure and fundamental concepts relevant to the model.
+Chapter 4 focuses specifically on detailed computations within the two-site (De)constructed gauge model, presenting thorough analyses of tree-level scattering amplitudes, significant simplifications, and cancellation phenomena.
+Finally, Chapter 5 summarizes key findings, emphasizing their implications and potential applications, while also identifying future research opportunities inspired by this work.
 
@@
 \end{align}
-
-\subsection{n-point case}
+where I do not cancel the dependence of spinor X explicitly, but it is not quite complicated to do.
+\subsubsection{n-point case}
 Here, we first propose a compact formula for the color-ordered amplitude
@@
 
+\subsection{Pure scalar case}
+Before going to the computation of pure scalar amplitudes in the 2-site model, it is necessary to review a quite similar amplitude -- scalar QED.
+There are two feynman diagrams corresponding to 4 scalar scattering process 
+\begin{figure}[H]
+    \centering
+    \includegraphics{s4pt.pdf}
+    \caption{4 scalar scattering}
+\end{figure}
+First we can use the feynman rule to compute them like
+\begin{align}
+    i\mathcal{A}&=(-ie)^2(-i)\times\frac{(p_1-p_2)(p_3-p_4)}{(p_1+p_2)^2}+(-ie)^2(-i)\frac{(p_1-p_4)(p_3-p_2)}{(p_1+p_4)^2}\notag\\
+    &=ie^2\left(\frac{u-t}{s}+\frac{u-s}{t}\right)\notag\\
+    &=-2ie^2-2ie^2\left(\frac{t}{s}+\frac{s}{t}\right)
+\end{align}
+where the Mandelstam variables are defined as 
+\begin{equation}
+    s=(p_1+p_2)^2,\quad t=(p_1+p_4)^2,\quad u=(p_1+p_3)^2.
+\end{equation}
+We can rewrite this formula in terms of spinor-helicity variables
+\begin{equation}
+    s=\cbrak{12}{21}=\cbrak{34}{43},\quad t=\cbrak{14}{41}=\cbrak{23}{32},\quad u=\cbrak{13}{31}=\cbrak{24}{42}.
+\end{equation}
+then the amplitudes can be rewritten like
+\begin{equation}
+    \mathcal{A}=-2e^2-2e^2\left(\frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}\right)
+\end{equation}
+The second term can be written further as
+\begin{align}
+    \frac{\mdavg{14}{23}}{\mdavg{12}{34}}+\frac{\mdavg{12}{34}}{\mdavg{14}{23}}&=\frac{\avg{14}^2\avg{23}^2+\avg{12}^2\avg{34}^2}{\mdavg{14}{23}\!\mdavg{12}{34}}=\frac{(\mdavg{14}{23}+\mdavg{12}{34})^2-2\mdavg{14}{23}\!\mdavg{12}{34}}{\mdavg{14}{23}\!\mdavg{12}{34}}\notag\\
+    &=-\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}-2
+\end{align}
+then the final form of amplitudes can be read as
+\begin{equation}
+    \mathcal{A}=\underbrace{2e^2}_{\text{boundary term}}+2e^2\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+    \label{4.68}
+\end{equation}
+where the meaning of boundary term can be understood later.
+
+If we use BCFW to compute the same amplitude, can we obtain the same result? We choose the normal $[1,3\rangle$ shift and it corresponds two following BCFW channel
+\begin{figure}[H]
+    \centering
+    \includegraphics{s4pt1.pdf}
+\end{figure}
+It can be computed like
+\begin{align}
+    \mathcal{A}&=\frac{\mdavg{\hat{1}\hat{I}}{\hat{I}2}}{\avg{\hat{1}2}}\times\frac{1}{s_{12}}\times\frac{[4\hat{I}][\hat{I}3]}{[\hat{3}4]}+\frac{\mdavg{\hat{1}\hat{I}}{\hat{I}4}}{\avg{4\hat{1}}}\times\frac{1}{s_{14}}\times\frac{[\hat{3}\hat{I}][\hat{I}2]}{[2\hat{3}]}\notag\\
+    &=\frac{\mdavg{13}{24}}{\mdavg{14}{23}}+\frac{\mdavg{13}{24}}{\mdavg{12}{34}}\notag\\
+    &=(-1)g^2\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+\end{align}
+so if we choose $g=\sqrt{2}e$, we can notice that BCFW actually reproduce partial part of the full amplitude.If we compute the large-z behavior for equation \eqref{4.68}, we can find that
+\begin{equation}
+    \mathcal{A}|_{z\rightarrow \infty}=2e^2
+\end{equation}
+this is why we called it boundary term before. More geneally, if we consider a sclar QED action including a $\phi^4$
+term like
+\begin{align}
+  \mathcal{L} 
+  &= - \frac{1}{4} F_{\mu\nu}F^{\mu\nu} - |D\varphi|^2 - \frac{1}{4} \lambda |\varphi|^4 \notag\\
+  &= - \frac{1}{4} F_{\mu\nu}F^{\mu\nu} - |\partial_\mu \varphi|^2
+     + i e A^\mu \left[ (\partial_\mu \varphi^*) \varphi - \varphi^* \partial_\mu \varphi \right]- e^2 A^\mu A_\mu \varphi^* \varphi - \frac{1}{4} \lambda |\varphi|^4
+\end{align}
+
+The 4-pt amplitude can be computed like
+\begin{equation}
+    A_4(\varphi\, \varphi^* \varphi\, \varphi^*)
+  ~=~
+  -\lambda + \tilde{e}^2 
+  \bigg( 
+     1+\frac{\avg{13}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+  \bigg) \,,
+\end{equation}
+so actually we compute ta special case in which the parameter $\lambda$ are choosed as $\lambda=2e^2$, so that the boundary are eliminated. 
+\subsubsection{Attempt to massive scalar}
 \section{Summary and Outlook}
@@
 
+\addcontentsline{toc}{section}{References}
 \bibliographystyle{unsrt}

### 2025-05-29 Master Defense/Defense.tex
New

\documentclass{beamer}
\usetheme{metropolis}
% 防止目录变灰或消失
\setbeamercolor{section in toc}{fg=black,bg=white}
\setbeamercolor{section in toc shaded}{fg=black,bg=white}
\setbeamercolor{subsection in toc shaded}{fg=black,bg=white}
\setbeamercolor{alerted text}{fg=black}

% 禁用 shaded 效果
\setbeamertemplate{section in toc shaded}[default]
\setbeamertemplate{subsection in toc shaded}[default]

% ========= 字体 & 数学 =========
\usepackage{newtxtext,newtxmath}

% ========= 图像 & 物理包 =========
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{tikz-feynman}
\usepackage{physics}

% ========= 修复 Metropolis 的变灰问题 =========

% ========= 标题信息 =========
\title{On-Shell Methods for Tree-Level Amplitudes\\ in (De)Constructed Gauge Theory}
\subtitle{Application of BCFW Recursion Relation}

\author[Su Yingze]{
  Su Yingze\\
  Supervisor: Prof. Tanabashi Masaharu
}

\institute{Theoretical Particle Physics Laboratory, Nagoya University}
\date{\today}

% ========= 标题页右下角校徽 =========
\titlegraphic{
  \vspace*{4.5cm}
  \hfill
  \includegraphics[width=2.5cm]{Nagoya.png}
  \vspace*{-2cm}
}

% ========= 正文开始 =========
\begin{document}

% ===== 封面 =====
\maketitle

% ===== 总目录页 =====
\begin{frame}{Outline}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents[currentsection]
\end{frame}

% ===== 每章开始时显示当前目录页（可选）=====

% ===== 1. Motivation =====
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy experiments such as the LHC
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as integrability or AdS/CFT correspondence
    \end{itemize}
  \end{enumerate}
\end{frame}
\begin{frame}
    \frametitle{Struggles of Traditional Approaches}

\end{frame}

% ===== 2. Model =====
\section{Model}
\begin{frame}{(De)constructed Gauge Theory}
  \begin{itemize}
    \item Based on discretizing extra dimensions
    \item Multiple gauge groups + link scalar fields
    \item Focus: a general $n$-site structure and 2-site limit
  \end{itemize}
\end{frame}

% ===== 3. Methods =====
\section{Methods} 
\begin{frame}{Modern Amplitude Techniques}
  \begin{itemize}
    \item BCFW recursion: complex deformation of momenta
    \item Spinor-helicity formalism: simplifies massless amplitudes
    \item CSW expansion: handles NMHV amplitudes
  \end{itemize}
  \pause
  \[
  A_n = \sum_{\text{partitions}} \frac{A_L A_R}{P^2}
  \]
\end{frame}

% ===== 4. Results =====
\section{Results}
\begin{frame}{Key Results}
  \begin{itemize}
    \item Computed tree-level amplitudes for various helicity configurations
    \item Verified KK-mode cancellation patterns
    \item Demonstrated efficiency over traditional Feynman diagrams
  \end{itemize}
\end{frame}

% ===== 5. Outlook =====
\section{Outlook}
\begin{frame}{Future Directions}
  \begin{itemize}
    \item Extension to $n$-site models and loop-level amplitudes
    \item Application to black hole scattering (on-shell gravity)
    \item Exploration of geometric frameworks (amplituhedron, CHY)
  \end{itemize}
\end{frame}

% ===== 致谢 =====
\begin{frame}{Acknowledgement}
  \centering
  Thanks to my advisor, lab colleagues, and audience!
\end{frame}

\end{document}

### 2025-05-29 Master Thesis/thesis.tex
New

@@
 \begin{equation}
-    \mathrm{Tr}\{T^aA\}\mathrm{Tr}\{T^aB\}=\mathrm{Tr}\{AB\}-\frac{1}{N}\{A\}\mathrm{Tr}\{B\},
+    \mathrm{Tr}\{T^aA\}\mathrm{Tr}\{T^aB\}=\mathrm{Tr}\{AB\}-\frac{1}{N}\mathrm{Tr}\{A\}\mathrm{Tr}\{B\},
 \end{equation}
@@
         &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+        \label{4.16}
     \end{align}
@@
 so actually we compute ta special case in which the parameter $\lambda$ are choosed as $\lambda=2e^2$, so that the boundary are eliminated.
-\subsubsection{Attempt to massive scalar}
+
+Similarly, if we consider four sclar scattering in 2-site model $\Phi\Phi^\dagger\Phi\Phi^\dagger$, we have the same Feynman diagram but with two different gauge boson propagating in the internal line
+\begin{figure}[H]
+    \centering
+    \includegraphics{4ptt1.pdf}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics{4ptt2.pdf}
+\end{figure}
+These diagrams correspond to two different amplitudes
+\begin{align}
+    \mathcal{A}_1&=g_1^2\left(\frac{-2t-s}{s}\right)r_s+g_1^2\left(\frac{-2s-t}{t}\right)r_t\notag\\
+    &=g_1^2\left(-1-2\frac{t}{s}\right)r_s+g_1^2\left(-1-2\frac{s}{t}\right)r_t\notag\\
+    &=-g_1^2(r_s+r_t)-2g_1^2\left(\frac{t}{s}r_s+\frac{s}{t}r_t\right)
+\end{align}
+\subsection{Attempt to massive scalar}
+It is quite intriguing to investigate what is the situation if we change the scalar to be massive.
+Without doubt, the BCFW shift should change and here we just refer to the method from \cite{Ballav:2020ese}.
+The shift are choosen like 
+\begin{gather}
+    \aket{\hat{2^I}}=\aket{2^I},\qquad \sket{\hat{2^I}}=\sket{2^I}-\frac{z}{m}\sket{3}[2^I3]\\
+    \aket{\hat{3}}=\aket{3}+\frac{z}{m}p_2\sket{3},\qquad \sket{\hat{3}}=\sket{3}.
+\end{gather}
+For the massive particle with same mass, it is necessary to introduce a x factor as \cite{Arkani-Hamed:2017jhn}. Here the x factor equals to
+\begin{gather}
+    x\lambda_{3\alpha}=\frac{p_{1\alpha\dot{\alpha}}}{m}\tilde{\lambda}_3^{\dot{\alpha}}\quad \Rightarrow \quad x\avg{\xi 3 }=\frac{\asbra{\xi}{p_1}{3}}{m}\qquad x=\frac{\asbra{\xi}{p_1}{3}}{m\avg{\xi 3}}\\
+    \frac{\tilde{\lambda}_3^{\dot{\alpha}}}{x}=\frac{p_1^{\dot{\alpha \alpha}}\lambda_{3\alpha}}{m}\quad \Rightarrow \quad \frac{1}{x}[\xi3]=\frac{\asbra{3}{p_1}{\xi}}{m}\qquad \frac{1}{x}=\frac{\asbra{3}{p_1}{\xi}}{m[3\xi]} ~\text{or}~ x=\frac{m[\xi3]}{\asbra{3}{p_1}{\xi}}
+\end{gather}
+Then, from the 3-point building block
+\begin{equation}
+    M^{\text{min},+1}=x\frac{\avg{\textbf{12}}^{2s}}{m^{2s-1}},\qquad M^{\text{min,-1}}=\frac{1}{x}\frac{[\textbf{12}]^{2s}}{m^{2s-1}}
+\end{equation}
+here min means the minimal coupling. The amplitudes can be similarly computed by utlizing BCFW with some more efforts
+\begin{align}
+    A[\textbf{1},\textbf{2},3^+,4^+]&=g^2m \hat{x}_{12}\times\frac{1}{s_{12}}\times \frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
+    &=g^2m^2\frac{[4\hat{I}]}{\asbra{\hat{I}}{p_1}{4}}\times\frac{1}{s_{12}}\times \frac{[34]^3}{[4\hat{I}][\hat{I}\hat{3}]}
+\end{align}
+and
+\begin{equation}
+    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}
+\end{equation}
+can be computed as following
+\begin{align}
+    -[3\hat{I}]\asbra{\hat{I}}{p_1}{4}&=-[3|(p_3+p_4)p_1|4]=[3|p_3p_1|4]-[3|p_4p_1|4]=-[3|p_4p_1|4]\notag\\
+    &=-p_{4\mu} p_{1\nu}[3|(\bar{\sigma}^\mu)^{\dot{\alpha}\beta}(\sigma^\nu)_{\beta\dot{\gamma}}|4]\notag\\
+    &=[3|p_1p_4|4]-2p_1\cdot p_4[34]=-2p_1\cdot p_4[34]
+\end{align}
+here we use the formula
+\begin{equation}
+    (\sigma^\mu\bar{\sigma}^\nu+\sigma^\nu\bar{\sigma}^\mu)_\alpha^{\phantom{a}\beta}=2\eta^{\mu\nu}\delta_\alpha^{\phantom{a}\beta}
+\end{equation}
+and the term $2p_1\cdot p_4$ can be extracted from
+\begin{equation}
+    (p_1+p_4)^2=(p_2+p_3)^2=s_{23}
+\end{equation}
+The final result for this amplitude is 
+\begin{equation}
+    A[\textbf{1},\textbf{2},3^+,4^+]=\frac{[34]^3}{s_{34}(s_{23}-m^2)[43]}=m^2g^2\frac{[34]}{\avg{43}(s_{23}-m^2)}
+\end{equation}
+If we take the high energy limit so that the m can be chose to 0, then the amplitude becomes 0, which is consistent with our previous analysis.
+
+For another helicity configuration, we can compute similarly
+\begin{align}
+    A[\textbf{1},\textbf{2},3^+,4^-]&=g^2m\frac{1}{\hat{x}_{12}}\times\frac{1}{s_{12}}\times\frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\notag\\
+    &=g^2m\frac{\asbra{\hat{I}}{p_1}{3}}{m[\hat{I}3]}\times\frac{[\hat{I}3]^3}{[34][4\hat{I}]}=g^2\frac{\asbra{\hat{I}}{p_1}{3}[\hat{I}3]^2}{[34][4\hat{I}]s_{34}}
+\end{align}
+aftering the similar computation, the final result can be obtained as 
+\begin{equation}
+    A[\textbf{1},\textbf{2},3^+,4^-]=g^2\frac{\asbra{4}{p_1}{3}^2}{(s_{14}-m^2)s_{34}}
+\end{equation}
+We can also take the high energy limit and check if it is consistent with our previous result. Aftering some subtle computation, it can be proved that the amplitude can be written like 
+\begin{equation}
+    A=\frac{\cbrak{13}{24}\acbrak{14}{32}}{\acbrak{23}{32}\acbrak{12}{21}}=\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+\end{equation}
+which is perfectly math to the equation \eqref{4.16}.(We neglect the negligible $\pm$ sign)
+
+For the higher point case, in principle, there is no big difference from the computaion before, except the computaion for massive spinor-helicty variable.
 \section{Summary and Outlook}

### 2025-05-30 Master Thesis/thesis.tex
New

@@
 \usepackage{bm}
+\usepackage{esvect} % 在导言区加入
+
 \numberwithin{equation}{section}
@@
 \newcommand{\asbra}[3]{\langle #1 | #2 |#3 ]}
+\newcommand{\casbra}[3]{[ #1 | #2 | #3 \rangle]}
+\newcommand{\bra}[1]{\langle #1|}
 \onehalfspacing
@@
     \textbf{Affiliation:} \\
+    Theoretical Elementary Particle Physics Laboratory\\
     Department of Physics, Faculty of Science \\
@@
 These studies promise to deepen our understanding of amplitude structures, dimensional emergence, and the broader implications of gauge-gravity dualities.
-
+\newpage
+\appendix
+\section{Conventions}
+
+In this paper we follow the mostly minus convention $(+, -, -, -)$, and an on-shell momentum satisfies $p^2 = m^2$. The sigma matrix are defined as
+\begin{equation}
+    \sigma^\mu=(1,\vec{\sigma}),\qquad \bar{\sigma}^\mu=(1,-\vec{\sigma}).
+\end{equation}
+The corressponding matrix form can be written like 
+\begin{equation}
+    p_{\alpha\dot{\alpha}}=p_\mu \sigma^\mu=\begin{pmatrix}
+        E-p_3 & -p_1+ip_2 \\
+        -p_1-ip_2 & E+p_3
+    \end{pmatrix}
+\end{equation}
+and 
+\begin{equation}
+    p^{\dot{\alpha}\alpha}=p_\mu \bar{\sigma}^\mu=\begin{pmatrix}
+        E+p_3 & p_1-ip_2 \\
+        p_1+ip_2 & E-p_3
+    \end{pmatrix}.
+\end{equation}
+Then it is easy to obtain their product 
+\begin{align}
+    p_{\alpha\dot{\alpha}}\cdot p^{\dot{\alpha}\beta}&=\begin{pmatrix}
+        E-p_3 & -p_1+ip_2 \\
+        -p_1-ip_2 & E+p_3
+    \end{pmatrix}
+    \begin{pmatrix}
+        E+p_3 & p_1-ip_2 \\
+        p_1+ip_2 & E-p_3
+    \end{pmatrix}\notag\\
+    &=\begin{pmatrix}
+        E-p^2 & 0 \\
+        0 & E-p^2 
+    \end{pmatrix}=m^2\delta_\alpha^\beta,
+    \label{A.4}
+\end{align}
+and 
+\begin{equation}
+    \mathrm{det}p_{\alpha\dot{\alpha}}=m^2.
+\end{equation}
+We list the following properties for sigma matrix
+\begin{gather}
+    (\bar{\sigma})^{\dot{\alpha}\alpha}=\varepsilon^{\alpha\beta}\varepsilon^{\dot{\alpha}\dot{\beta}}(\sigma)_{\beta\dot{\beta}}\\
+    (\sigma)_{\alpha\dot{\alpha}}(\sigma)_{\beta\dot{\beta}}=2\varepsilon_{\alpha\beta}\varepsilon_{\dot{\alpha}\dot{\beta}}\\
+    (\sigma^\mu\bar{\sigma}^\nu+\sigma^\nu\bar{\sigma}^\mu)_\alpha^{\phantom{a}\beta}=2\eta^{\mu\nu}\delta_\alpha^{\phantom{a}\beta}\\
+    \mathrm{Tr}(\sigma^\mu\bar{\sigma}^\nu)=\mathrm{Tr}(\bar{\sigma}^\mu\sigma^\nu)=2\eta^{\mu\nu} \label{A.9} 
+\end{gather}
+
+The Gamma matrices are defined like
+\begin{equation}
+    \gamma^\mu=\begin{pmatrix}
+        0 & (\sigma)_{\alpha\dot{\alpha}}\\
+        (\bar{\sigma})^{\dot{\alpha}\alpha} & 0 
+    \end{pmatrix}, \qquad \{\gamma^\mu,\gamma^\nu\}=2\eta^{\mu\nu}
+\end{equation}
+The $\mathrm{SL}(2,\mathbb{C})$ and $\mathrm{SU}_L(2)$ indices are raised and lowered as
+\begin{equation}
+    \psi_\alpha = \psi^\beta \varepsilon_{\alpha\beta}, \quad
+    \psi^\alpha = \varepsilon^{\alpha\beta} \psi_\beta, \quad
+    \varepsilon^{\alpha\beta} \varepsilon_{\beta\gamma} = \delta^\alpha_\gamma
+\end{equation}
+where the $\psi$ refers to a Weyl spinor belonging to $SU(2)_L$ representation (left-handed spinor), and it is same for $SU(2)_R$ (right-handed spinor).
+We use $\varepsilon_{\alpha\beta} = -\varepsilon^{\alpha\beta} = \begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix}$, the anti-symmetric tensor, to rasie and lower the index.
+More general for eqution \eqref{A.4}, two different spinor contraction can be converted to vector contraction following
+\begin{equation}
+    p_1^{\alpha \dot\alpha} p_{2 \alpha \dot\alpha} = 2 p_1^\mu p_{2\mu}, 
+\end{equation}
+where we use the formula \eqref{A.9} and hence for massive momenta, $p^{\alpha\dot\alpha} p_{\alpha\dot\alpha} = 2m^2$, it can also be noticed from \eqref{A.4}.
+The vector indices are converted to spinorial ones for massive case as:
+\begin{equation}
+    \gamma^\mu =
+    \begin{pmatrix}
+        0 & \sigma^\mu_{\alpha\dot\beta} \\
+        \bar{\sigma}^\mu{}^{\dot\alpha\beta} & 0
+    \end{pmatrix}
+    \quad \rightarrow \quad 
+    (\bcancel{p} + m) =
+    \begin{pmatrix}
+        m \delta^\beta_\alpha & p_{\alpha \dot\beta} \\
+        p^{\dot\alpha \beta} & m \delta^{\dot\alpha}_{\dot\beta}
+    \end{pmatrix}
+\end{equation}
+
+For convenience, we also collect some useful identities for spinor-helicity variable:
+\begin{gather}
+    [p|_{\dot{\alpha}}=\varepsilon _{\dot{\alpha}\dot{\beta}}\sket{p}^{\dot{\beta}},\qquad \langle p|^\alpha=\varepsilon^{\alpha\beta}\aket{p}_{\beta}, \notag \\
+    \sket{p}^{\dot{\alpha}}=\varepsilon^{\dot{\alpha}\dot{\beta}}[p|_{\dot{\beta}},\qquad \aket{p}_\alpha=\varepsilon^{\alpha\beta}\langle p|_\beta, \notag \\
+    p_{\alpha\dot{\alpha}}=\aket{p}_\alpha[p|_{\dot{\alpha}},\qquad p^{\dot{\alpha}\alpha}=\sket{p}^{\dot{\alpha}}\langle p|^{\alpha}, \notag \\
+    \bcancel{p}=\aket{p}_\alpha[p|_{\dot{\alpha}}+\sket{p}^{\dot{\alpha}}\langle p|^{\alpha}, \notag \\
+    \avg{pq}=\langle p|^{\alpha}\aket{q}_{\alpha},\qquad [pq]=[p|_{\dot{\alpha}}\sket{q}^{\dot{\alpha}}, \notag \\
+    \cbrak{pq}{qp}=2p\cdot q= (p+q)^2 \quad , \notag \\
+    (\text{the last equality only holds for massless particle}) \notag \\
+    \casbra{k}{\sigma^\mu}{p}=\asbra{p}{\sigma^\mu}{k},\qquad \casbra{k}{\sigma^\mu}{p}=\asbra{k}{\sigma^\mu}{p} ~(\text{for real moemnta}), \notag \\
+    \asbra{p}{P}{k}=\langle p|^\alpha P_{\alpha\dot{\alpha}}|k]^{\dot{\alpha}},\qquad \avg{p|y_1y_2|k}=\langle p|^\alpha y_{1\alpha\dot{\alpha}}y_2^{\dot{\alpha}\beta}|p\rangle_\beta, \notag \\
+    \asbra{p}{q}{k}=\cbrak{pq}{qk},\qquad \langle 1 | \gamma^\mu | 2 ] \langle 3 | \gamma_\mu | 4 ] = 2 \langle 13 \rangle [24].
+\end{gather}
+
+ The analytic continuation are choosen like 
+ \begin{equation}
+    \aket{-p}=-\aket{p},\qquad \sket{-p}=+\sket{p}.
+ \end{equation}
+
+ The angle spinor and square spinor are related by complex conjugation:
+ \begin{equation}
+        [p|_{\dot{\alpha}}=(\aket{p}_\alpha)^*,\qquad \langle p|^{\alpha}=(\sket{p}^{\dot{\alpha}})^*
+ \end{equation}
+for real momenta $p$.
+
+\section{Polarization Vectors}
+In quantum field theory, the quantities computed directly from Feynman diagrams, such as \( M^\mu(p, \cdots) \), are Lorentz tensors.
+However, these objects by themselves do not possess the correct transformation properties to be regarded as physical scattering amplitudes.
+In particular, they fail to transform appropriately under the little group associated with massless particles.
+
+To bridge this gap, we introduce \emph{polarization vectors} \( \epsilon^\mu_\sigma(p) \), whose role is to carry the correct little group behavior.
+These vectors transform under Lorentz transformations as
+\[
+\epsilon^\mu_\sigma(\Lambda p) = \Lambda^\mu_{\ \nu} \, \epsilon^\nu_{\sigma'}(p) \, D_{\sigma'\sigma}(W),
+\]
+where \( D(W) \) is the representation of the little group element \( W \) associated with the Lorentz transformation \( \Lambda \). In this way, the contraction
+\[
+\epsilon^\mu_\sigma(p) \, M_\mu(p, \cdots)
+\]
+transforms correctly as a scalar (or spinor/tensor) amplitude under both Lorentz and little group actions.
+
+It is important to emphasize that in modern amplitude formulations—particularly those employing spinor-helicity variables or on-shell recursion relations—polarization vectors are not fundamental ingredients.
+Rather, they serve as auxiliary tools to extract the physical content from intermediate Feynman tensor structures.
+The true scattering amplitude is inherently a little group covariant object, and in spinor-helicity language, this structure is built directly into the helicity-spinor formalism.
+In fact, as demonstrated in the main text, one can carry out the entire computation without ever introducing polarization vectors.
+Nevertheless, in certain contexts, particularly when comparing with Feynman diagrammatic results or for pedagogical clarity, their use remains convenient and insightful.
+
+The external line rule for an outgoing massless spin-1 vector boson is implemented by contracting the amplitude with its polarization vector.
+In the spinor-helicity formalism, the polarization vectors can be expressed as:
+\begin{equation}
+\epsilon_-^\mu(p; q) = -\frac{\bra{p} \gamma^\mu \sket{q}}{\sqrt{2} [q\,p]}, \qquad
+\epsilon_+^\mu(p; q) = -\frac{\bra{q} \gamma^\mu \sket{p}}{\sqrt{2} \langle q\,p \rangle},
+\end{equation}
+where \( q \neq p \) is an arbitrary reference spinor. The choice of reference spinor encodes gauge redundancy, and the physical amplitude remains unchanged under shifts of the form
+\[
+\epsilon^\mu_\pm(p) \to \epsilon^\mu_\pm(p) + C\, p^\mu.
+\]
+
+The Weyl equation for massless spinors ensures that \( p_\mu \epsilon^\mu_\pm(p) = 0 \). In practice, the polarization vectors are often written in a spinor outer-product form:
+\begin{equation}
+\bcancel{\epsilon}_-(p; q) = \frac{\sqrt{2}}{[q\,p]}\left( \sket{p}[q| + \sket{q}[p| \right), \qquad
+\bcancel{\epsilon}_+(p; q) = \frac{\sqrt{2}}{\langle q\,p \rangle}\left( \sket{p}\bra{q} + \sket{q}\bra{p} \right).
+\end{equation}
+
+This freedom in choosing the reference spinor reflects gauge invariance.
+It does not affect on-shell amplitudes, due to the Ward identity \( p_\mu A_n^\mu = 0 \).
+For each external gluon (or massless vector),
+one can freely choose a \( q_i \neq p_i \) for defining its polarization.
+However, consistency requires that the same \( q_i \) be used across all diagrams within a given process.
+Importantly, the full physical amplitude remains independent of the reference spinors after summing over diagrams.
+
+We consider a massless four-momentum given by
+\[
+p^\mu = \left( E,\, E \sin\theta \cos\phi,\, E \sin\theta \sin\phi,\, E \cos\theta \right),
+\]
+which corresponds to a particle moving at an angle \(\theta\) from the \(z\)-axis and azimuthal angle \(\phi\) in spherical coordinates.
+In Exercise 2.1, the spinor-helicity variables \(\sket{p}\) and \([p|\) associated with this momentum were constructed explicitly.
+
+In this context, we now relate the spinor-helicity polarization vectors from the previous section to the conventional polarization vectors defined in coordinate space.
+The standard helicity eigenstate vectors take the form:
+\[
+\tilde{\epsilon}_\pm^\mu(p) = \pm \frac{e^{\mp i\phi}}{\sqrt{2}}
+\left( 0,\; \cos\theta \cos\phi \pm i \sin\phi,\; \cos\theta \sin\phi \mp i \cos\phi,\; -\sin\theta \right).
+\]
+
+These expressions clearly show the transverse nature of the polarization with respect to the direction of motion.
+In the special case where \(\theta = \phi = 0\), i.e., the particle moves along the \(z\)-axis, the polarization vectors reduce to
+\[
+\tilde{\epsilon}_\pm^\mu(p) = \pm \frac{1}{\sqrt{2}}(0,\, 1,\, \mp i,\, 0),
+\]
+which correspond to circular polarization in the \(xy\)-plane.
+
+\textbf{Example.} Consider the 3-point QED amplitude \( A_3(f^{h_1} \bar{f}^{h_2} \gamma^{h_3}) \), where \( f = e^- \) and \( \bar{f} = e^+ \) denote the outgoing massless electron and positron, respectively.
+Let us take the helicities to be \( h_1 = -\tfrac{1}{2} \), \( h_2 = +\tfrac{1}{2} \), and \( h_3 = -1 \).
+The corresponding Feynman amplitude is given by:
+
+\[
+i A_3(f^- \bar{f}^+ \gamma^-) = \bar{u}_-(p_1) \, (ie \gamma_\mu) \, v_+(p_2) \, \epsilon_-^\mu(p_3; q)
+\]
+
+Using spinor-helicity variables, this becomes:
+
+\[
+= ie \bra{1} \gamma_\mu \sket{2}  \frac{ [3| \gamma^\mu \sket{q} }{ \sqrt{2} [3 q] }
+= \sqrt{2} i e \frac{ \langle 13 \rangle [2 q] }{ [3 q] }
+\]
+where we have applied the Fierz identity in the last step to simplify the spinor contractions.
+
+Hence, the amplitude reduces to:
+
+\[
+A_3(f^- \bar{f}^+ \gamma^-) = \tilde{e} \, \frac{ \langle 13 \rangle [2 q] }{ [3 q] }
+\]
+with the shorthand coupling \( \tilde{e} \equiv \sqrt{2} e \) absorbing the normalization factor into the definition of the coupling constant.
+This is the reason why we use $\tilde{e}$ instead of e in the main context.
+
+Without doubt, the physical amplitude should not depend on arbitrary reference spinor $q$.
+To eliminate the reference spinor \( |q] \) appearing in the denominator, we first multiply the amplitude by the identity factor \( \langle 12 \rangle / \langle 12 \rangle \).
+This transforms the numerator as follows:
+\[
+\langle 13 \rangle \langle 12 \rangle [2q].
+\]
+
+Next, using momentum conservation \( p_2 = -p_1 - p_3 \) and the massless Dirac equation \( \bra{1} p_2 = -\bra{1} (p_1 + p_3) \), we compute:
+\[
+\langle 12 \rangle [2q] = -\bra{1} p_2 \rvert q] = \bra{1} (p_1 + p_3) \rvert q] = \bra{13} q] = \langle 13 \rangle [3q].
+\]
+
+Thus, the numerator becomes \( \langle 13 \rangle^2 [3q] \), and the factor of \( [3q] \) cancels with the same term in the denominator of the original expression.
+
+We are therefore left with a compact expression:
+\[
+A_3(f^- \bar{f}^+ \gamma^-) = \tilde{e} \, \frac{ \langle 13 \rangle^2 }{ \langle 12 \rangle },
+\]
+which is manifestly independent of the arbitrary reference spinor \( q \).
+
+\newpage
 \addcontentsline{toc}{section}{References}

### 2025-06-01 Master Thesis/thesis.tex
New

@@
 \usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black
+}
 \usepackage{setspace}
@@
 
-    \textbf{Major:} \\
-    Theoretical Physics \\[1cm]
+    \textbf{Student number:} \\
+    262309017 \\[1cm]
 
@@
 \end{figure}
+\noindent
 but because of the 3 particle special kinematics, the 3-point anti-MHV part gives vanishing contributtion, this diagram actually equals to 0.
@@
 \end{equation}
-where a refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
+where $a$ refer to the particle with - helicity, whichever gauge group it belongs to. And, `$\star$' refers to the ordering for the first gauge group, `$\ast$'
 refers to the ordering for the second gauge group. We suppose there are $n_1$ gauge boson 1, $n_2$ gauge boson 2, so the n-point means that $n=n_1+n_2+2$.
@@
 The usual way to prove this kind of compact formula is induction. First we suppose that all of the amplitudes with external point lower than n satisfy the compact formula.
-
+Here, we denote the permutation $\star ~ \ast$ as $\sigma$ and $\tau$ respectively. It includes many kinds of channels as following
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{npt1.jpg}
+    \caption{First type}
+\end{figure}
+The first channel can be computed like 
+\begin{equation}
+    A_1=\frac{\avg{\hat{2}a}^2\avg{1a}^2}{\avg{2\sigma(5)}\avg{\sigma(5)\sigma(6)}\cdots\avg{2\tau(n_1+1)}\cdots}\times\frac{1}{s_{\sigma(3)\sigma(4)}}\times\frac{[\hat{\sigma(3)}\sigma(4)]^3}{[\sigma(4)\hat{I}][\hat{I}\hat{\sigma(4)}]}
+    \label{4.63}
+\end{equation}
+We also have other BCFW channels like
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{npt2.jpg}
+    \caption{Second type}
+\end{figure}
+but this kind of channel always have a all-plus subamplitude, so it equals to 0.
+
+And another channel can also be drawn like
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{npt3.jpg}
+    \caption{Third type}
+\end{figure}
+\noindent
+in which we still have an vanishing subamplitude in the right part.
+
+The last one looks like 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{npt4.jpg}
+    \caption{Fourth type}
+\end{figure}
+\noindent
+and obviously, either the left or right part will offer a all-plus subamplitude, so that it equals to 0.
+
+The equation \eqref{4.63} can be easily evaluated in the similar manner, and it actually gives us the form
+\begin{equation}
+    A=\frac{\asqu{2a}\!\asqu{1a}}{\avg{2\star}\cdots \avg{\star 1}\avg{2\ast }\cdots \avg{\ast 1}}
+\end{equation}
+so we accomplish the prove although it seems a little rough.
 \subsection{Pure scalar case}
@@
 \end{align}
+It can also be found that the large-z behavior looks like
+\begin{equation}
+    \mathcal{A}_1|_{z\rightarrow\infty}=-g_1^2(r_s+r_t)
+\end{equation}
+if we choose $[1,3\rangle$ shift.
+
+The color facor $r_s$ can be written like
+\begin{equation}
+    \mathrm{Tr}\{\Phi_1\Phi_2^\dagger T^a\}\mathrm{Tr}\{\Phi_3\Phi_4^\dagger T^a\}=\mathrm{Tr}\{\Phi_1\Phi_2^\dagger\Phi_3\Phi_4^\dagger\}-\frac{1}{N}\mathrm{Tr}\{\Phi_1\Phi_2^\dagger\}\mathrm{Tr}\{\Phi_3\Phi_4^\dagger\},
+\end{equation}
+where the subscript $i$ can be understood as the label of external particle. These two terms can remind that it is possible to introduce two independent operators into the Lagrangian:
+\begin{equation}
+    \mathcal{L}_{\text{4pt}}=\lambda_1\mathrm{Tr}\{\Phi\Phi^\dagger\Phi\Phi^\dagger\}+\lambda_2\mathrm{Tr}\{\Phi\Phi^\dagger\}\mathrm{Tr}\{\Phi\Phi^\dagger\}
+\end{equation}
+which can contribute to $r_s$ and $r_t$ at the same time. Therefore, if we choose the parameter
+\begin{equation}
+    \lambda_1=g_1^2,\qquad \lambda_2=\frac{g_2^2}{N}.
+\end{equation}
+The boundary term can be canceled so that we get a valid large-z behavior, then BCFW recursion relation can be utilized.
+
+Unfortunately, if we consider the 3-site, in which there are two scalars, the pure scalar ampitudes will become quite complicated, so till now we postphone the discussion about that. 
 \subsection{Attempt to massive scalar}

### 2025-06-05 Master Thesis/thesis.tex
New

@@
 \noindent
+Title: On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory
+
+\noindent
 Name: Su Yingze
@@
 
-This thesis explores tree-level scattering amplitudes in (De)constructed gauge theories using modern on-shell methods.
-Traditional Feynman diagram techniques, though systematic, become increasingly cumbersome in theories with gauge redundancies and high multiplicity.
-Motivated by these limitations, we adopt a framework based on analyticity, factorization, and gauge invariance, applying the BCFW recursion relation and related spinor-helicity techniques.
-
-Our analysis focuses on the two-site model, the simplest (De)constructed scenario, which provides a renormalizable four-dimensional realization of dimensional deconstruction and naturally generates Kaluza-Klein (KK)-like spectra.
-Tree-level color-ordered amplitudes involving massive and massless vector bosons are computed using the BCFW recursion, revealing significant simplifications and cancellation patterns, especially in longitudinal gauge boson scattering.
-To access non-MHV sectors, we further employ the Cachazo-Svrček-Witten (CSW) expansion, which efficiently constructs NMHV amplitudes from MHV vertices, offering a complementary perspective to BCFW recursion.
-
-Our results demonstrate that on-shell methods remain powerful even in semi-realistic settings with broken gauge symmetry and massive states.
-The structural simplicity of the resulting amplitudes suggests potential geometric interpretations and invites extensions to loop-level processes.
-
-Future directions include applying generalized unitarity and BCFW-based recursion at loop level, incorporating double-copy constructions to study gravitational analogues, and exploring formulations via the CHY formalism, scattering forms, or positive geometry such as the amplituhedron.
-These approaches promise deeper insight into the unifying principles behind quantum field theories and the emergence of higher-dimensional behavior from four-dimensional dynamics.
+This thesis studies how to calculate scattering amplitudes in a class of simplified gauge theories known as (De)constructed models, using modern on-shell techniques.
+In traditional quantum field theory, Feynman diagrams provide a systematic way to compute these amplitudes, but the calculations often become very complicated — especially in gauge theories with many particles or redundant degrees of freedom.
+
+To overcome these difficulties, we use on-shell methods that rely on general principles like momentum conservation, unitarity, and analyticity, rather than directly computing every diagram.
+A key tool is the BCFW recursion relation, which builds complicated amplitudes from simpler ones by shifting external momenta.
+We also use the spinor-helicity formalism, which rewrites particle momenta in terms of spinors, making many expressions simpler and more symmetric.
+To further reduce complexity, we organize our calculations using color ordering, which separates the physics from the gauge group structure.
+
+Our main focus is on the two-site model, a simple setup that mimics extra - dimensional physics using only four-dimensional fields.
+In this model, we compute various tree-level amplitudes involving both massless and massive gauge bosons.
+We find interesting simplifications and cancellations, especially in processes involving longitudinal polarization, and confirm that these effects match expectations from higher-dimensional theories.
+For more complex helicity configurations (beyond MHV), we apply the CSW expansion, which reconstructs amplitudes using MHV building blocks.
+
+Our results show that on-shell techniques are powerful even in models with massive particles and broken symmetries.
+These compact results hint at deeper geometric structures behind quantum field theory.
+
+Looking forward, this work lays the foundation for further studies, including loop-level calculations, connections to gravity via the double-copy approach, and exploring deeper structures like the CHY formalism, scattering forms, and the amplituhedron, which aim to reformulate quantum field theory in a more elegant and unified way.
 

### 2025-06-05 MasterDefense/main.tex
New

--- 2025-04-19 Intermediate report/main.tex
@@
 \usepackage{amsmath}
+\usepackage{enumitem}
 \usepackage{bm}
@@
 \usepackage{mathtools}
-\usepackage{enumitem}
 \usepackage{subcaption}
@@
 \usepackage[most]{tcolorbox}
+
+\setlist[enumerate]{label=\arabic*.}
+\setlist[itemize]{label=\textbullet}  % 标准 bullet 点
 \tcbset{
@@
 }
-\setlist[itemize]{label=\textbullet}
 \usetikzlibrary{decorations.pathreplacing}
@@
 \newcommand{\asqu}[1]{{\langle#1\rangle}^2}
+\newcommand{\tif}[1]{\textit{\textbf{#1}}}
 \AtBeginSection[]{
@@
 }
-\title[Application of BCFW]{Tree level scattering amplitude in (De)constructed gauge theory}
-\author{Su Yingze}
-\institute{Nagoya University}
-\date[4 21st 2025]{April 21st 2025}
+\title[Application of BCFW]{\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}
+\author[Su Yingze]{
+  \textbf{Su Yingze}\\[0.2em]
+  \small Supervisor: \tif{Prof. Tanabashi Masaharu}
+}
+
+\institute[E Lab]{
+  \normalsize Theoretical Elementary Particle Physics Laboratory\\[-0.3em]
+  Nagoya University
+}
+
+\date[$11^{\text{th}}$ June]{June 11th, 2025}
 
 \begin{document}
-\frame{\titlepage}
-\section{Why we need new method?}
+\setbeamertemplate{itemize item}{\normalsize\textbullet}
+\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
+  \titlepage
+\end{frame}
+\section{Motivation}
+\begin{frame}{Why We Study Scattering Amplitudes?}
+  \begin{enumerate}
+    \item \textbf{Bridge between theory and experiment}
+    \begin{itemize}
+      \item Core prediction targets for high-energy collider experiments such as the LHC
+      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
+    \end{itemize}
+    \pause
+    \item \textbf{Reveal deep structures of quantum field theory}
+    \begin{itemize}
+      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
+      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
+    \end{itemize}
+  \end{enumerate}
+\end{frame}
+
 \begin{frame}
-    \frametitle{Why we need new method?}
-Feynman diagram is a brilliant method without doubt, helping us compute the scattering process pertubatively.
+    \frametitle{Challenges we face befor}
 \begin{center}
@@
 \vspace{-2.3em}
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\hline
+$n=$ & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+\hline
+     & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
+\hline
+\end{tabular}
+\end{center}
+\pause
 
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Shape: Spring [id:dp43786797179465176] 
-\draw   (216.4,104.97) ..
-controls (219.03,103.2) and (222.94,102.68) ..
-(226.33,106.02) ..
-controls (233.1,112.72) and (224.24,121.49) ..
-(220.86,118.14) ..
-controls (217.47,114.8) and (226.33,106.02) ..
-(233.1,112.72) ..
-controls (239.87,119.41) and (231.01,128.19) ..
-(227.63,124.84) ..
-controls (224.24,121.49) and (233.1,112.72) ..
-(239.87,119.41) ..
-controls (246.64,126.11) and (237.78,134.88) ..
-(234.4,131.53) ..
-controls (231.01,128.19) and (239.87,119.41) ..
-(246.64,126.11) ..
-controls (253.41,132.8) and (244.56,141.58) ..
-(241.17,138.23) ..
-controls (237.78,134.88) and (246.64,126.11) ..
-(253.41,132.8) ..
-controls (254.2,133.59) and (254.78,134.4) ..
-(255.18,135.22) ;
-%Shape: Ellipse [id:dp10564067273276767] 
-\draw  [fill={rgb, 255:red, 196; green, 189; blue, 189 }  ,fill opacity=1 ] (252.25,146.07) ..
-controls (252.25,135.17) and (261.17,126.33) ..
-(272.19,126.33) ..
-controls (283.2,126.33) and (292.12,135.17) ..
-(292.12,146.07) ..
-controls (292.12,156.97) and (283.2,165.8) ..
-(272.19,165.8) ..
-controls (261.17,165.8) and (252.25,156.97) ..
-(252.25,146.07) -- cycle ;
-%Shape: Spring [id:dp8051072896719512] 
-\draw   (202.57,146.94) ..
-controls (203.45,144.19) and (206.11,141.62) ..
-(210.87,142.09) ..
-controls (220.4,143.03) and (219.26,154.27) ..
-(214.5,153.79) ..
-controls (209.74,153.32) and (210.87,142.09) ..
-(220.4,143.03) ..
-controls (229.92,143.98) and (228.78,155.21) ..
-(224.02,154.74) ..
-controls (219.26,154.27) and (220.4,143.03) ..
-(229.92,143.98) ..
-controls (239.44,144.92) and (238.31,156.15) ..
-(233.54,155.68) ..
-controls (228.78,155.21) and (229.92,143.98) ..
-(239.44,144.92) ..
-controls (248.97,145.87) and (247.83,157.1) ..
-(243.07,156.63) ..
-controls (238.31,156.15) and (239.44,144.92) ..
-(248.97,145.87) ..
-controls (250.08,145.98) and (251.05,146.23) ..
-(251.89,146.59) ;
-%Shape: Spring [id:dp24229359788253813] 
-\draw   (291.38,147.82) ..
-controls (292.02,144.73) and (294.46,141.66) ..
-(299.24,141.73) ..
-controls (308.81,141.87) and (308.63,154.27) ..
-(303.84,154.2) ..
-controls (299.06,154.13) and (299.24,141.73) ..
-(308.81,141.87) ..
-controls (318.38,142.01) and (318.2,154.41) ..
-(313.41,154.34) ..
-controls (308.63,154.27) and (308.81,141.87) ..
-(318.38,142.01) ..
-controls (327.95,142.15) and (327.77,154.55) ..
-(322.98,154.48) ..
-controls (318.2,154.41) and (318.38,142.01) ..
-(327.95,142.15) ..
-controls (337.52,142.28) and (337.34,154.69) ..
-(332.55,154.62) ..
-controls (327.77,154.55) and (327.95,142.15) ..
-(337.52,142.28) ..
-controls (338.64,142.3) and (339.63,142.49) ..
-(340.49,142.8) ;
-%Shape: Spring [id:dp1840306550125722] 
-\draw   (290.58,139.13) ..
-controls (289.05,136.36) and (288.91,132.46) ..
-(292.6,129.45) ..
-controls (299.99,123.43) and (307.96,133) ..
-(304.26,136.01) ..
-controls (300.57,139.02) and (292.6,129.45) ..
-(299.99,123.43) ..
-controls (307.38,117.41) and (315.35,126.98) ..
-(311.65,129.99) ..
-controls (307.96,133) and (299.99,123.43) ..
-(307.38,117.41) ..
-controls (314.77,111.38) and (322.73,120.96) ..
-(319.04,123.97) ..
-controls (315.35,126.98) and (307.38,117.41) ..
-(314.77,111.38) ..
-controls (322.16,105.36) and (330.12,114.94) ..
-(326.43,117.95) ..
-controls (322.73,120.96) and (314.77,111.38) ..
-(322.16,105.36) ..
-controls (323.02,104.66) and (323.9,104.17) ..
-(324.76,103.85) ;
-%Shape: Spring [id:dp21851269782703253] 
-\draw   (271.73,127.44) ..
-controls (268.6,126.81) and (265.5,124.41) ..
-(265.56,119.67) ..
-controls (265.68,110.2) and (278.2,110.35) ..
-(278.14,115.09) ..
-controls (278.08,119.82) and (265.56,119.67) ..
-(265.68,110.2) ..
-controls (265.79,100.73) and (278.32,100.88) ..
-(278.26,105.61) ..
-controls (278.2,110.35) and (265.68,110.2) ..
-(265.79,100.73) ..
-controls (265.91,91.25) and (278.44,91.4) ..
-(278.38,96.14) ..
-controls (278.32,100.88) and (265.79,100.73) ..
-(265.91,91.25) ..
-controls (266.03,81.78) and (278.55,81.93) ..
-(278.5,86.67) ..
-controls (278.44,91.4) and (265.91,91.25) ..
-(266.03,81.78) ..
-controls (266.04,80.67) and (266.23,79.69) ..
-(266.54,78.84) ;
-%Shape: Spring [id:dp05024762380258474] 
-\draw   (224.2,195.95) ..
-controls (222.44,193.32) and (221.96,189.44) ..
-(225.37,186.13) ..
-controls (232.21,179.5) and (240.98,188.36) ..
-(237.56,191.68) ..
-controls (234.14,194.99) and (225.37,186.13) ..
-(232.21,179.5) ..
-controls (239.05,172.87) and (247.82,181.73) ..
-(244.4,185.05) ..
-controls (240.98,188.36) and (232.21,179.5) ..
-(239.05,172.87) ..
-controls (245.88,166.24) and (254.65,175.1) ..
-(251.24,178.42) ..
-controls (247.82,181.73) and (239.05,172.87) ..
-(245.88,166.24) ..
-controls (252.72,159.61) and (261.49,168.47) ..
-(258.07,171.79) ..
-controls (254.65,175.1) and (245.88,166.24) ..
-(252.72,159.61) ..
-controls (253.52,158.83) and (254.35,158.27) ..
-(255.18,157.88) ;
-%Shape: Spring [id:dp9217960437924791] 
-\draw   (283.39,161.81) ..
-controls (286.03,160.03) and (289.94,159.51) ..
-(293.32,162.86) ..
-controls (300.09,169.56) and (291.24,178.33) ..
-(287.85,174.98) ..
-controls (284.47,171.64) and (293.32,162.86) ..
-(300.09,169.56) ..
-controls (306.86,176.25) and (298.01,185.03) ..
-(294.62,181.68) ..
-controls (291.24,178.33) and (300.09,169.56) ..
-(306.86,176.25) ..
-controls (313.63,182.95) and (304.78,191.72) ..
-(301.39,188.37) ..
-controls (298.01,185.03) and (306.86,176.25) ..
-(313.63,182.95) ..
-controls (320.4,189.64) and (311.55,198.42) ..
-(308.17,195.07) ..
-controls (304.78,191.72) and (313.63,182.95) ..
-(320.4,189.64) ..
-controls (321.2,190.43) and (321.78,191.24) ..
-(322.17,192.06) ;
-
-% Text Node
-\draw (254.1,174.78) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
-% Text Node
-\draw (354,136) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Can we really compute this by hand?}};
-
-\end{tikzpicture}
-
-\end{frame}
-\begin{frame}
-    \frametitle{From Frynman diagram to On-shell method}
 The answer is On-shell method.
@@
 \end{tikzpicture}
-
 \end{center}
-
-    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
-    Specifically, there are many ingredients under this frame
-    \begin{itemize}
-        \item The analytic continuation for S-matrix.
-        \item The color-ordered amplitudes.
-        \item The BCFW recursion relation.
-        \item The spinor helicity discription for amplitudes.
-    \end{itemize}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{A brief introduction to BCFW}
-BCFW helps us solve one of the problems
-\vspace{-1em}
+    \frametitle{Conventional VS. Modern}
+    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
+\begin{equation*}
+    \begin{aligned}
+&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
+&\quad \times \Big\{ 
+-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
++ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
+&\quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
++ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* \\
+&\quad + 4\, \epsilon_1 \cdot \epsilon_4^* \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot p_4 
+- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_4 \, \epsilon_4^* \cdot p_1 \\
+&\quad - 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_3 \, \epsilon_3^* \cdot \epsilon_4^*
++ \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_2 \cdot p_3 \\
+&\quad + 4\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot \epsilon_3^* \, \epsilon_4^* \cdot p_3 
+- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_2 \, \epsilon_4^* \cdot p_3 \\
+&\quad + 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_4 \, \epsilon_3^* \cdot \epsilon_4^* 
+- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_4 \cdot p_2 \\
+&\quad + 2\, \epsilon_1 \cdot p_3 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* 
+- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_1 \cdot p_3 
+\Big\}.
+\end{aligned}
+\end{equation*}
+\end{frame}
+\begin{frame}
+    If you consider 5point case, it will become worser:
+\begin{center}
+    \textcolor{red}{$\bigstar$ There are nearly 10000 terms!}
+\end{center}
+\begin{columns}[T,onlytextwidth]
+    % 左侧：传统图像
+    \column{0.48\textwidth}
+    \textbf{传统费曼图计算：}
     \begin{figure}
         \centering
-    \includegraphics[width=0.5\textwidth]{BCFW.png}
+        \includegraphics[width=\linewidth]{5pt.png}
     \end{figure}
-\vspace{-1em}
-with the cost of introducing \textcolor{red}{complexed momentum}.
-
-BCFW is a method to compute amplitudes recursively, proposed by 
-\begin{itemize}
-    \item Britto, Cachazo, Feng, arXiv: hep-th/0412308
-    \item Britto, Cachazo, Feng, Witten, arXiv: hep-th/0501052
-
-\end{itemize}
-
-\begin{center}
-
- \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
- \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
- %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
- %Shape: Ellipse [id:dp47704771803228196] 
- \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (179.79,126.94) ..
-controls (179.79,120.82) and (184.73,115.86) ..
-(190.81,115.86) ..
-controls (196.89,115.86) and (201.82,120.82) ..
-(201.82,126.94) ..
-controls (201.82,133.06) and (196.89,138.02) ..
-(190.81,138.02) ..
-controls (184.73,138.02) and (179.79,133.06) ..
-(179.79,126.94) -- cycle ;
- %Straight Lines [id:da8859462256956995] 
- \draw    (163,96.75) -- (182.27,118.91) ;
- %Straight Lines [id:da980370255241411] 
- \draw    (201.82,126.94) -- (232.38,126.66) ;
- %Straight Lines [id:da41368612060172827] 
- \draw    (182.82,135.52) -- (165.75,153.25) ;
- %Right Arrow [id:dp6770308298589597] 
- \draw   (240.37,124.24) -- (254.74,124.24) -- (254.74,121.68) -- (264.32,126.8) -- (254.74,131.92) -- (254.74,129.36) -- (240.37,129.36) -- cycle ;
- %Shape: Ellipse [id:dp9789947232756657] 
- \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (277.26,126.94) ..
-controls (277.26,120.82) and (282.19,115.86) ..
-(288.27,115.86) ..
-controls (294.35,115.86) and (299.28,120.82) ..
-(299.28,126.94) ..
-controls (299.28,133.06) and (294.35,138.02) ..
-(288.27,138.02) ..
-controls (282.19,138.02) and (277.26,133.06) ..
-(277.26,126.94) -- cycle ;
- %Straight Lines [id:da15853752019875] 
- \draw    (263.22,98.41) -- (279.74,118.91) ;
- %Straight Lines [id:da28595275955528565] 
- \draw    (299.28,126.94) -- (329.84,126.66) ;
- %Straight Lines [id:da7505788363123894] 
- \draw    (280.29,135.52) -- (263.22,153.25) ;
- %Shape: Ellipse [id:dp870376485686725] 
- \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (351.87,126.66) ..
-controls (351.87,120.54) and (346.94,115.58) ..
-(340.86,115.58) ..
-controls (334.77,115.58) and (329.84,120.54) ..
-(329.84,126.66) ..
-controls (329.84,132.78) and (334.77,137.74) ..
-(340.86,137.74) ..
-controls (346.94,137.74) and (351.87,132.78) ..
-(351.87,126.66) -- cycle ;
- %Straight Lines [id:da5791423310908868] 
- \draw    (363.43,98.97) -- (349.94,118.91) ;
- %Straight Lines [id:da5454664407915119] 
- \draw    (349.43,134.42) -- (365.28,152.14) ;
- %Right Arrow [id:dp848095583389827] 
- \draw   (368.11,124.79) -- (382.49,124.79) -- (382.49,122.23) -- (392.07,127.35) -- (382.49,132.48) -- (382.49,129.92) -- (368.11,129.92) -- cycle ;
-
- % Text Node
- \draw (393.76,120.95) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
-
- \end{tikzpicture}
-\end{center}
-
+    \pause 
+    % 右侧：PT表达式
+    \column{0.48\textwidth}
+    \vspace{1.5em}
+    \qquad \textbf{Parke–Taylor Formula:}
+    \begin{gather*}
+        \textcolor{red}{A_5(1^-,2^-,3^+,4^+,5^+)} =\\
+        \textcolor{red}{\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}
+    \end{gather*}
+\end{columns}
+\vspace{2em}
+\textcolor{red}{$\bigstar$ \Large It becomes quite simple and compact!}
 \end{frame}
-\begin{frame}
-    \frametitle{From real to complex -- Analytic Continuation}
-    \textbf{Why can we conduct analytic continuation?}
-\begin{itemize}
-  \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
-  \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
-  \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
-\end{itemize}
-    \begin{center}
-    \tikz{
-      \draw[double equal sign distance, -Implies, line width=1pt] (0,0) -- (0,-1.2);
-    }
-    \end{center}
-\vspace{0.5em}
-\centering
-\textcolor{red}{Ampltudes can be shifted to complex plane}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Momentum Shift in BCFW}
-    \textbf{What did BCFW do to make the shift?}
-
-    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
-    \begin{equation*}
-        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
-    \end{equation*}
-    satisfying 
-    \begin{equation*}
-        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
-    \end{equation*}
-
-\begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Shape: Circle [id:dp47058391497271046] 
-\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) ..
-controls (266.75,112.19) and (277.94,101) ..
-(291.75,101) ..
-controls (305.56,101) and (316.75,112.19) ..
-(316.75,126) ..
-controls (316.75,139.81) and (305.56,151) ..
-(291.75,151) ..
-controls (277.94,151) and (266.75,139.81) ..
-(266.75,126) -- cycle ;
-%Straight Lines [id:da8759716500759761] 
-\draw    (249,78.25) -- (273.5,109.25) ;
-%Straight Lines [id:da2121821831988906] 
-\draw    (233.5,103.25) -- (266.5,120.75) ;
-%Straight Lines [id:da6378763431676462] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
-%Straight Lines [id:da7508961107891289] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
-%Straight Lines [id:da06317949320750826] 
-\draw    (237,155.25) -- (271.5,140.75) ;
-%Straight Lines [id:da403008866951158] 
-\draw    (261.5,180.25) -- (281.5,149.25) ;
-%Straight Lines [id:da8334043101335312] 
-\draw    (423,119.25) -- (457.5,104.75) ;
-%Straight Lines [id:da03451573841415356] 
-\draw    (418.5,109.75) -- (438.5,78.75) ;
-%Straight Lines [id:da025418352459996796] 
-\draw    (420,140.25) -- (453,157.75) ;
-%Straight Lines [id:da22879254297825424] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
-%Straight Lines [id:da2355772127149045] 
-\draw    (410.5,148.75) -- (435,179.75) ;
-%Shape: Rectangle [id:dp6752662310096104] 
-\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
-%Straight Lines [id:da4580921639862495] 
-\draw    (316.75,126) -- (373.5,125.75) ;
-%Shape: Circle [id:dp8699671429684472] 
-\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) ..
-controls (373.5,111.94) and (384.69,100.75) ..
-(398.5,100.75) ..
-controls (412.31,100.75) and (423.5,111.94) ..
-(423.5,125.75) ..
-controls (423.5,139.56) and (412.31,150.75) ..
-(398.5,150.75) ..
-controls (384.69,150.75) and (373.5,139.56) ..
-(373.5,125.75) -- cycle ;
-
-% Text Node
-\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
-% Text Node
-\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
-% Text Node
-\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
-% Text Node
-\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
-% Text Node
-\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
-% Text Node
-\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};
-
-\end{tikzpicture}
-    \end{minipage}
-    \hspace{1em}
-    \begin{minipage}{0.45\textwidth}
-        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
-    \begin{equation*}
-        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
-    \end{equation*}
-
-    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
-    \end{minipage}
-\end{figure} 
-\end{frame}
-
 \begin{frame}
@@
     \end{block}
-    Brief proof:
-
-    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
-    \begin{equation*}
-        A_n \longrightarrow \hat{A}_n(z)
-    \end{equation*}
-
-    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the single pole at the origin. 
-    \textcolor{red}{$\bigstar$ The most important point here is that}
-    \begin{equation*}
-        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
-    \end{equation*}
-    It means that the original amplitude equals to the residue at origin.
-\end{frame}
-\begin{frame}
-    From Cauchy Theorem, we can ontain
-    \begin{equation*}
-        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
-    \vspace{-1em}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width=0.3\textwidth]{CT.png}
-    \end{figure}
-    \vspace{-1.5em}
-    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
-    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
-    \begin{equation*}
-        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
-    \end{equation*}
-    This makes it easy to evaluate the residue at $z=z_I$
-    \begin{equation*}
-        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Large z behavior}
-    In the BCFW formula, the boundary term $B_n$ affects a lot
-    \begin{equation*}
-        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
-    \begin{equation*}
-        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
-    \end{equation*}
-    Here I show the large z behavior for gluon scattering 
-    \begin{center}
-        \begin{tabular}{lrc}
-            \toprule
-            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
-            \midrule
-            $+$ & $1/z$ & $z^3$ \\
-            $-$ & $1/z$ & $1/z$ \\
-            \bottomrule
-          \end{tabular}
-    \end{center}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Spinor-Helicity formalisim}
-In the part of introduction to BCFW
-\begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[height=4em]{recrel1.pdf} 
-    \end{minipage}
-    \hspace{0.01em}
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \(
-        \vcenter{\hbox{$\rightarrow$}} \quad \text{No helicity appears here}
-        \)
-    \end{minipage}
-\end{figure}
-
-but the S-matrix is a function of moentum $p_i$ and helicity $h_i$
-\begin{center}
-
+\vspace*{1em}
+\pause
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
@@
 
-%Shape: Circle [id:dp6973592945628315] 
-\draw  [color={rgb, 255:red, 248; green, 0; blue, 0 }  ,draw opacity=1 ] (302.8,146.93) ..
-controls (302.81,142.78) and (306.18,139.44) ..
-(310.32,139.45) ..
-controls (314.47,139.46) and (317.81,142.83) ..
-(317.8,146.97) ..
-controls (317.79,151.11) and (314.42,154.46) ..
-(310.28,154.45) ..
-controls (306.14,154.44) and (302.79,151.07) ..
-(302.8,146.93) -- cycle ;
-%Straight Lines [id:da7518027963985391] 
-\draw [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ]   (310.28,154.45) -- (296.03,178.04) ;
-\draw [shift={(295,179.75)}, rotate = 301.13] [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
+%Shape: Circle [id:dp714548377068662] 
+\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (226.5,142.5) ..
+controls (226.5,135.6) and (232.1,130) ..
+(239,130) ..
+controls (245.9,130) and (251.5,135.6) ..
+(251.5,142.5) ..
+controls (251.5,149.4) and (245.9,155) ..
+(239,155) ..
+controls (232.1,155) and (226.5,149.4) ..
+(226.5,142.5) -- cycle ;
+%Straight Lines [id:da2774899580018806] 
+\draw    (205.75,111.25) -- (228.5,135) ;
+%Straight Lines [id:da9722977180083648] 
+\draw    (206.25,170.75) -- (229.5,151.5) ;
+%Straight Lines [id:da6995788762725553] 
+\draw    (283,142.5) -- (251.5,142.5) ;
+%Shape: Circle [id:dp5472781658369114] 
+\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (338.5,142) ..
+controls (338.5,135.1) and (344.1,129.5) ..
+(351,129.5) ..
+controls (357.9,129.5) and (363.5,135.1) ..
+(363.5,142) ..
+controls (363.5,148.9) and (357.9,154.5) ..
+(351,154.5) ..
+controls (344.1,154.5) and (338.5,148.9) ..
+(338.5,142) -- cycle ;
+%Straight Lines [id:da00014298672423462833] 
+\draw    (317.75,110.75) -- (340.5,134.5) ;
+%Straight Lines [id:da9890078833503395] 
+\draw    (317.25,169.75) -- (341.5,151) ;
+%Straight Lines [id:da6144558640267263] 
+\draw    (395,142) -- (363.5,142) ;
+%Right Arrow [id:dp2461212615941556] 
+\draw  [fill={rgb, 255:red, 241; green, 80; blue, 80 }  ,fill opacity=1 ] (289.75,140.31) -- (304.3,140.31) -- (304.3,138.25) -- (314,142.38) -- (304.3,146.5) -- (304.3,144.44) -- (289.75,144.44) -- cycle ;
+%Shape: Circle [id:dp17520461351076555] 
+\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (395,142) ..
+controls (395,135.1) and (400.6,129.5) ..
+(407.5,129.5) ..
+controls (414.4,129.5) and (420,135.1) ..
+(420,142) ..
+controls (420,148.9) and (414.4,154.5) ..
+(407.5,154.5) ..
+controls (400.6,154.5) and (395,148.9) ..
+(395,142) -- cycle ;
+%Straight Lines [id:da6771243917531791] 
+\draw    (417.25,132.75) -- (440.25,111.75) ;
+%Straight Lines [id:da9753272478311303] 
+\draw    (419.25,149.75) -- (440.75,167.75) ;
+%Right Arrow [id:dp8085176402619464] 
+\draw  [fill={rgb, 255:red, 241; green, 80; blue, 80 }  ,fill opacity=1 ] (444.25,137.81) -- (458.8,137.81) -- (458.8,135.75) -- (468.5,139.88) -- (458.8,144) -- (458.8,141.94) -- (444.25,141.94) -- cycle ;
 
 % Text Node
-\draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt]    {$\mathcal{M}( p_{i} ,h_{i})$};
+\draw (82,133.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\small More understandable:}}};
 % Text Node
-\draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 247; green, 13; blue, 13 }  ,opacity=1 ] [align=left] {How can we catch the information of helicity?};
+\draw (473.5,130.9) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
+% Text Node
+\draw (224,164.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize 3 point}}};
+% Text Node
+\draw (363.5,162) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize 4 point}}};
+% Text Node
+\draw (479,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize higher point}}};
+
+\end{tikzpicture}
+
+\vspace{1em}
+
+\textcolor{red}{$\bigstar $ ~ From lower point to higher point!!}
+
+\end{frame}
+\begin{frame}{Spinor-Helicity Formalism}
+\begin{block}{Helicity}
+\textbf{Helicity} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
+\[
+h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
+\]
+\end{block}
+\pause
+% 文本说明（点击1出现）
+\only<1->{
+S-matrix is a function of momentum $p_i$ and helicity $h_i$
+}
+
+\vspace{0.8em}
+
+% TikZ 图（点击1显示公式，点击2后补图形）
+\begin{center}
+\tikzset{every picture/.style={line width=0.75pt}}        
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+
+  % 点击1：显示公式
+  \only<1>{
+    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
+          {$\mathcal{M}( p_{i} ,h_{i})$};
+  }
+
+  % 点击2及后：公式 + 圈箭头
+  \only<2->{
+    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
+          {$\mathcal{M}( p_{i} ,\textcolor{red}{h_{i}})$};
+
+    % 圆圈
+    \draw  [color=red, draw opacity=1] 
+      (302.8,146.93) .. controls (302.81,142.78) and (306.18,139.44) .. (310.32,139.45)
+      .. controls (314.47,139.46) and (317.81,142.83) .. (317.8,146.97)
+      .. controls (317.79,151.11) and (314.42,154.46) .. (310.28,154.45)
+      .. controls (306.14,154.44) and (302.79,151.07) .. (302.8,146.93) -- cycle;
+
+    % 箭头
+    \draw [color=red, draw opacity=1] 
+      (310.28,154.45) -- (296.03,178.04);
+    \draw [shift={(295,179.75)}, rotate=301.13, color=red, draw opacity=1][line width=0.75pt] 
+      (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0)
+      .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29);
+
+    % 注释文字
+    \draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  
+      [font=\small,color=red,opacity=1] [align=left] 
+      {How can we catch the information of helicity?};
+  }
 
@@
 \end{center}
-The answer is \textbf{Spinor-Helicity formalism} 
-\(
-\xrightarrow{\text{}} 
-\)
-Catch \(p_i\) and \(h_i\) at the same time.
+
+% 点击3：Massless Case（用 uncover 保持排版稳定）
+\uncover<3->{
+\vspace{-1em}
+\textbf{Massless Case:}
+\begin{itemize}
+  \item Momenta in spinor form:
+    \[
+      p_{\mu}\sigma^{\mu} = p_{\alpha\dot{\alpha}} = p_\alpha \tilde{p}_{\dot{\alpha}} = \aket{p}[p|
+    \]
+\end{itemize}
+}
 
 \end{frame}
-\begin{frame}
-\frametitle{Spinor-helicity formalism}
-    \begin{itemize}
-        \item $\textbf{\text{Massless Case}}$\\
+
+\section{Model and Computation}
+
+\begin{frame}{Introduction of quiver gauge theory}
+\vspace{1em}
+\begin{columns}[c]
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moose.png}
+
+    \column{0.14\textwidth}
+    \centering
+    \begin{tikzpicture}[scale=0.8]
+        \draw[->, line width=1pt] (0,0) -- (1.5,0)
+            node[midway, above] {\footnotesize Condensation}; % ← 加文字
+    \end{tikzpicture}
+
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moosed.jpeg}
+\end{columns}
+
+\pause
+\raggedright
+The Lagrangian can be written like
 \begin{equation*}
-        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \mathcal{L} = -\sum_{i=1}^{N} \frac{1}{2} \mathrm{Tr}(F_i^2)
+    + \sum_{i=1}^{N} \mathrm{Tr}\left[(D_\mu \Phi_i)^\dagger (D^\mu \Phi_i)\right],
 \end{equation*}
-    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
+here $F_i$ refers to the $i$th gauge field strength. The scalar field $\Phi_i$ transforms under the \textcolor{red}{bi-fundamental} representation, and the covariant derivative equals to
 \begin{equation*}
-        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
+    D_\mu \Phi_i = \partial_\mu \Phi_i - i g_i A_{i\mu} \Phi_i + i g_{i+1} \Phi_i A_{i+1\mu}.
 \end{equation*}
-    same for
-    \begin{equation*}
-        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
-    \end{equation*}
-    The scattering amplitudes should transform covariantly under little group scaling:
-    \begin{equation*}
-        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
-    \end{equation*}
-    \end{itemize}
-\vspace{-2em}
-    \begin{itemize}
-    \item \textbf{Massive Case}\\
-    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
-    \end{itemize}
+
 \end{frame}
@@
 \begin{frame}
-    \frametitle{ On-shell 3-point can be completely determined}
-    \textbf{On-shell 3-point for real momentum}
-
-    Because of the constrain from momentum conservation and on-shell condition
-    \begin{equation*}
-        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
-    \end{equation*}
-    All of the contribution 
-    \begin{equation*}
-        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
-    \end{equation*}
-    In terms of Spinor- Helicity variable, we have 
-    \begin{equation*}
-        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
-    \end{equation*}
-    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}
-
-    Of coure, you can introduce non-minimal interaction
-    \begin{equation*}
-        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
-    \end{equation*}
-    but it still equals to 0 under the on-shell condition.
-\end{frame}
-
-\begin{frame}
-    \textbf{Another necessarity to introduce complex momentum}
-
-    If the momentum is complexed, we have 
-    \begin{equation*}
-        \avg{12}\neq[21]^*
-    \end{equation*}
-    Then we can obtain
-    \begin{equation*}
-        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
-    \end{equation*}
-    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
-    \begin{equation*}
-        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
-    \end{equation*}
-    Little group scaling tells us that
-    \begin{equation*}
-        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
-    \end{equation*}
-    We can obtain
-    \begin{equation*}
-        2h_1=-x_{12}-x_{13}
-    \end{equation*}
-    Similarly, we can also obtain
-    \begin{equation*}
-        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    Then all index can be solved from this system of equations, so that
-    \[
-    \boxed{
-    \begin{aligned}
-        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
-        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
-        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
-        \quad & h_1+h_2+h_3 > 0
-    \end{aligned}
-        }
-    \]
-
-    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
-
-    \textbf{Example}: 3-gluon amplitude\\
-    \begin{equation*}
-        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
-    \end{equation*}
-    There's another possibility 
-    \begin{equation*}
-        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
-    \end{equation*}
-    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
-\end{frame}
-\section{Introduction of quiver gauge theory}
-\begin{frame}
-    \frametitle{Introduction of Quiver or Moose gauge theory}
-    \begin{figure}
-        \centering
-        \begin{minipage}{0.45\textwidth}
-        Quiver: A container for carring arrows\\
-        Moose: A kind of deer with large horns 
-    \end{minipage}
+    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
+    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
+     \vspace{1em} % 图与文字之间的间距
+    \begin{center}
     \begin{minipage}{0.45\textwidth}
         \centering
-        \includegraphics[width=0.3\linewidth]{Quiver.jpg}
-        \hspace{1em}
-        \includegraphics[width=0.3\textwidth]{Moose.jpeg}
-
+        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
     \end{minipage}
-\end{figure}
-
-    In the language of field theories, quiver gauge theories contain gauge fields and bi-fundamental scalars, summarized in a pictotial representaion.
-    \begin{figure}
-        \centering
+    \hspace{0.05\textwidth}
     \begin{minipage}{0.45\textwidth}
         \centering
-            \includegraphics[width=0.6\textwidth]{Moosed.jpeg}
-            \caption*{Moose diagram}
+        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
     \end{minipage}
-        \hspace{1em}
-        \begin{minipage}{0.3\textwidth}
-            \begin{gather*}
-                N\text{-sided polygon}\\
-                G: \text{gauge group} \quad SU(m)\\
-                \rightarrow : \text{Unitary scalar fields}\quad \Phi_{ij} 
-            \end{gather*}
-        \end{minipage}
-
-    \end{figure}
-\end{frame}
-\begin{frame}
-    \frametitle{Why we foucs on quiver gauge theory?}
-    The lagrangian can be written like
-    \begin{equation*}
-        \mathcal{L}=-\sum_{i=1}^{N}\frac{1}{2}\mathrm{Tr}(F_i)^2+\sum_{i=1}^{N}\mathrm{Tr}[(D_\mu\Phi_i)^\dagger(D^\mu\Phi_i)],
-    \end{equation*}
-    here $F_i$ refers to the ith gauge field strength, scalar field $\Phi_i$ transformed under the \textcolor{red}{bi-fundamental} representation and the covariant derivative equals to
-    \begin{equation*}
-        D_\mu \Phi_i=\partial_\mu \Phi_i -ig_iA_{i\mu}\Phi_i+ig_{i+1}\Phi_i A_{i+1\mu}.
-    \end{equation*}
-    Here, gauge field and scalar field transformed like
-    \begin{equation*}
-        \bm{A_{i\mu}}\rightarrow U_i(x) \bm{A_{i\mu}} U_i^-(x)-\frac{i}{g_i}(\partial\mu U)U^{-1},\qquad \Phi_i\rightarrow U_i(x)\Phi_i U_{i+1}^-(x)
-    \end{equation*}
-    It is easy to confirm that this theory is invariant under $\prod_1^N SU(m)$ gauge group.
-\end{frame}
-\begin{frame}
-    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
-    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
-    \begin{itemize}
-        \item If $SU(m)_1$ and $SU(m)_N$ are connected $\longrightarrow$ $S^2$ compactification
-        \item If not connected $\longrightarrow$ $\mathrm{Interval}$ compactification
-    \end{itemize}
+    \end{center}
+    \pause
     After higgsing the scalar field, we can obtain a spectrum
@@
 \begin{frame}
-    {What is relation to scattering amplitude?}
-    The critical point is \textcolor{red}{locality}. 
-    \begin{itemize}
-        \item Space-Time Locality $\longrightarrow$ local field theories
-        \item Theory Space Locality $\longrightarrow$ Discretized theory space
-    \end{itemize}
-
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
-\begin{center}
-    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-        %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-        %Shape: Ellipse [id:dp8504954329776364] 
-        \draw   (104,129.25) ..
-controls (104,123.31) and (108.57,118.5) ..
-(114.2,118.5) ..
-controls (119.84,118.5) and (124.4,123.31) ..
-(124.4,129.25) ..
-controls (124.4,135.19) and (119.84,140) ..
-(114.2,140) ..
-controls (108.57,140) and (104,135.19) ..
-(104,129.25) -- cycle ;
-        %Shape: Ellipse [id:dp885507200032482] 
-        \draw   (219.1,129.25) ..
-controls (219.1,123.31) and (223.66,118.5) ..
-(229.3,118.5) ..
-controls (234.93,118.5) and (239.5,123.31) ..
-(239.5,129.25) ..
-controls (239.5,135.19) and (234.93,140) ..
-(229.3,140) ..
-controls (223.66,140) and (219.1,135.19) ..
-(219.1,129.25) -- cycle ;
-        %Shape: Ellipse [id:dp7989991915217867] 
-        \draw   (180.38,129.25) ..
-controls (180.38,123.31) and (184.95,118.5) ..
-(190.58,118.5) ..
-controls (196.22,118.5) and (200.79,123.31) ..
-(200.79,129.25) ..
-controls (200.79,135.19) and (196.22,140) ..
-(190.58,140) ..
-controls (184.95,140) and (180.38,135.19) ..
-(180.38,129.25) -- cycle ;
-        %Shape: Ellipse [id:dp013562751387628191] 
-        \draw   (142.71,129.25) ..
-controls (142.71,123.31) and (147.28,118.5) ..
-(152.92,118.5) ..
-controls (158.55,118.5) and (163.12,123.31) ..
-(163.12,129.25) ..
-controls (163.12,135.19) and (158.55,140) ..
-(152.92,140) ..
-controls (147.28,140) and (142.71,135.19) ..
-(142.71,129.25) -- cycle ;
-        %Straight Lines [id:da15611587109210845] 
-        \draw    (124.4,129.25) -- (142.71,129.25) ;
-        %Straight Lines [id:da9794450917549196] 
-        \draw    (163.12,129.25) -- (181.43,129.25) ;
-        %Straight Lines [id:da4720621582644091] 
-        \draw    (200.79,129.25) -- (219.1,129.25) ;
-
-        % Text Node
-        \draw (103,93.4) node [anchor=north west][inner sep=0.75pt]    {$G_{1}$};
-        % Text Node
-        \draw (142,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
-        % Text Node
-        \draw (180,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
-        % Text Node
-        \draw (220,94.4) node [anchor=north west][inner sep=0.75pt]    {$G_{4}$};
-        % Text Node
-        \draw (124,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
-        % Text Node
-        \draw (164,140.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
-        % Text Node
-        \draw (203,141.4) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
-        \end{tikzpicture}
-\end{center}
-If we change this to a scattering diagram, and compute the large-z behavior
-\begin{figure}
-    \centering
-\begin{minipage}{0.4\textwidth}
-
-    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-    %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-    %Shape: Inductor (Air Core) [id:dp932367781299785] 
-    \draw   (274.98,130.32) -- (281.77,130.32) ..
-controls (281.87,128.3) and (282.81,126.57) ..
-(284.14,125.97) ..
-controls (285.47,125.36) and (286.92,126.01) ..
-(287.8,127.59) ..
-controls (288.47,128.82) and (288.75,130.41) ..
-(288.55,131.96) ..
-controls (288.55,132.56) and (288.21,133.05) ..
-(287.8,133.05) ..
-controls (287.38,133.05) and (287.04,132.56) ..
-(287.04,131.96) ..
-controls (286.85,130.41) and (287.12,128.82) ..
-(287.8,127.59) ..
-controls (288.58,126.27) and (289.67,125.53) ..
-(290.81,125.53) ..
-controls (291.95,125.53) and (293.05,126.27) ..
-(293.83,127.59) ..
-controls (294.5,128.82) and (294.78,130.41) ..
-(294.58,131.96) ..
-controls (294.58,132.56) and (294.24,133.05) ..
-(293.83,133.05) ..
-controls (293.41,133.05) and (293.07,132.56) ..
-(293.07,131.96) ..
-controls (292.88,130.41) and (293.16,128.82) ..
-(293.83,127.59) ..
-controls (294.61,126.27) and (295.7,125.53) ..
-(296.84,125.53) ..
-controls (297.99,125.53) and (299.08,126.27) ..
-(299.86,127.59) ..
-controls (300.53,128.82) and (300.81,130.41) ..
-(300.61,131.96) ..
-controls (300.61,132.56) and (300.28,133.05) ..
-(299.86,133.05) ..
-controls (299.44,133.05) and (299.11,132.56) ..
-(299.11,131.96) ..
-controls (298.91,130.41) and (299.19,128.82) ..
-(299.86,127.59) ..
-controls (300.73,126.01) and (302.18,125.36) ..
-(303.52,125.97) ..
-controls (304.85,126.57) and (305.79,128.3) ..
-(305.89,130.32) -- (312.67,130.32) ;
-    %Straight Lines [id:da12934086227313735] 
-    \draw    (239.95,129.92) -- (274.98,129.92) ;
-    %Straight Lines [id:da483410968594159] 
-    \draw    (274.98,130.32) -- (275.43,159.86) ;
-    %Shape: Inductor (Air Core) [id:dp1480868197800882] 
-    \draw   (339.72,130.32) -- (346.51,130.32) ..
-controls (346.6,128.3) and (347.55,126.57) ..
-(348.88,125.97) ..
-controls (350.21,125.36) and (351.66,126.01) ..
-(352.54,127.59) ..
-controls (353.21,128.82) and (353.48,130.41) ..
-(353.29,131.96) ..
-controls (353.29,132.56) and (352.95,133.05) ..
-(352.54,133.05) ..
-controls (352.12,133.05) and (351.78,132.56) ..
-(351.78,131.96) ..
-controls (351.59,130.41) and (351.86,128.82) ..
-(352.54,127.59) ..
-controls (353.32,126.27) and (354.41,125.53) ..
-(355.55,125.53) ..
-controls (356.69,125.53) and (357.78,126.27) ..
-(358.57,127.59) ..
-controls (359.24,128.82) and (359.52,130.41) ..
-(359.32,131.96) ..
-controls (359.32,132.56) and (358.98,133.05) ..
-(358.57,133.05) ..
-controls (358.15,133.05) and (357.81,132.56) ..
-(357.81,131.96) ..
-controls (357.62,130.41) and (357.89,128.82) ..
-(358.57,127.59) ..
-controls (359.35,126.27) and (360.44,125.53) ..
-(361.58,125.53) ..
-controls (362.72,125.53) and (363.81,126.27) ..
-(364.6,127.59) ..
-controls (365.27,128.82) and (365.55,130.41) ..
-(365.35,131.96) ..
-controls (365.35,132.56) and (365.01,133.05) ..
-(364.6,133.05) ..
-controls (364.18,133.05) and (363.84,132.56) ..
-(363.84,131.96) ..
-controls (363.65,130.41) and (363.92,128.82) ..
-(364.6,127.59) ..
-controls (365.47,126.01) and (366.92,125.36) ..
-(368.26,125.97) ..
-controls (369.59,126.57) and (370.53,128.3) ..
-(370.63,130.32) -- (377.41,130.32) ;
-    %Straight Lines [id:da6722655237119544] 
-    \draw    (311.79,129.92) -- (339.72,129.92) ;
-    %Straight Lines [id:da3803917060459867] 
-    \draw    (339.72,130.32) -- (340.17,159.86) ;
-    %Straight Lines [id:da9202776931220129] 
-    \draw    (377.41,130.32) -- (377.86,159.86) ;
-    %Straight Lines [id:da09703581803647143] 
-    \draw    (377.41,129.92) -- (412.44,129.92) ;
-
-    % Text Node
-    \draw (219.64,120.92) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
-    % Text Node
-    \draw (264.87,163) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{1}$};
-    % Text Node
-    \draw (279.95,102.3) node [anchor=north west][inner sep=0.75pt]    {$G_{2}$};
-    % Text Node
-    \draw (311.87,103.11) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
-    % Text Node
-    \draw (330.5,163) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{2}$};
-    % Text Node
-    \draw (348.23,102.3) node [anchor=north west][inner sep=0.75pt]    {$G_{3}$};
-    % Text Node
-    \draw (368.63,161.38) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
-    % Text Node
-    \draw (413.86,121.72) node [anchor=north west][inner sep=0.75pt]    {$\Phi _{3}$};
-
-    \end{tikzpicture}
-
-\end{minipage}
-\hspace{1em}
-\begin{minipage}{0.4\textwidth}
+    \frametitle{Scattering Amplitudes from BCFW}
+    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
     \begin{equation*}
-        \sim 1/z^{\textcolor{red}{\textcircled{\textcolor{black}{4}}}}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
     \end{equation*}
-\end{minipage}
-\end{figure}
-\end{frame}
-\section{Scattering amplitudes from BCFW}
-\begin{frame}
-    \frametitle{Classification of Scattering Amplitudes}
-    \centering
-    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$. The amplitudes are classified by their multiplicity:
-
-    \vspace{1em}
-
-    \renewcommand{\arraystretch}{1.3}
-    \setlength{\tabcolsep}{6pt}
-    \begin{tabular}{|c|c|c|c|}
-        \hline
-        \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
-        \hline
-        $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
-        $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
-        $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
-        $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
-        & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
-        & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
-        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
-        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
-        \hline
-    \end{tabular}
+We only foucus on the following amplitudes:
+\begin{equation*}
+    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
+\end{equation*}
+here n can be any positive integer.
 \end{frame}
@@
 \end{frame}
-\section{Summary and Outlook}
+\section{Summary}
 \begin{frame}
@@
     \begin{itemize}
-        \item Introduce the on-shell method, including BCFW recursion relation, color-ordered amplitudes. etc.
+        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
         \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
-        \item The locality plays an important role to relate the spacetime locality and field space locality.
         \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
     \end{itemize}
-\end{frame}
-\begin{frame}
-    \frametitle{Possible future work}
-
-\begin{center}
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Shape: Circle [id:dp9858548351804828] 
-\draw   (351.75,140.5) ..
-controls (351.75,130.84) and (359.59,123) ..
-(369.25,123) ..
-controls (378.91,123) and (386.75,130.84) ..
-(386.75,140.5) ..
-controls (386.75,150.16) and (378.91,158) ..
-(369.25,158) ..
-controls (359.59,158) and (351.75,150.16) ..
-(351.75,140.5) -- cycle ;
-%Straight Lines [id:da97880204376832] 
-\draw    (382.75,152.5) -- (418.61,189.81) ;
-\draw [shift={(420,191.25)}, rotate = 226.13] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da40380915410006823] 
-\draw    (381.25,128) -- (416.59,92.66) ;
-\draw [shift={(418,91.25)}, rotate = 135] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da3536680968554168] 
-\draw    (356.5,127.75) -- (312.17,98.36) ;
-\draw [shift={(310.5,97.25)}, rotate = 33.55] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da43484293892230164] 
-\draw    (356.75,154) -- (311.61,187.07) ;
-\draw [shift={(310,188.25)}, rotate = 323.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da7682811881365084] 
-\draw    (351.75,140.5) -- (298.5,140.26) ;
-\draw [shift={(296.5,140.25)}, rotate = 0.26] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da38096838344174566] 
-\draw    (386.75,140.5) -- (439.5,140.26) ;
-\draw [shift={(441.5,140.25)}, rotate = 179.74] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-
-% Text Node
-\draw (353.25,133) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Now}};
-% Text Node
-\draw (371.25,194.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Including gravity?}};
-% Text Node
-\draw (370.25,69.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont BCJ double copy?}};
-% Text Node
-\draw (249.75,57) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Massive scalar or}\\{\fontfamily{ptm}\selectfont  gauge boson?}};
-% Text Node
-\draw (262.75,191) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 3 or 4 site?}};
-% Text Node
-\draw (276.75,132) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont ??}};
-% Text Node
-\draw (443.75,132.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont ??}};
-
-\end{tikzpicture}
-\end{center}
 \end{frame}
@@
 \appendix
-\section{Appendix}
-\begin{frame}
-    \frametitle{Color structure}
-    \begin{itemize}
-        \item n$ V_1$ or n$V_2$\\
-        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
-        existing results.
-        \begin{equation*}
-            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
-        \end{equation*}
-        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
-    \end{itemize}
-\end{frame}
 
 \begin{frame}
-    \begin{itemize}
-        \item $\Phi^\dagger V_1V_1\Phi$
-        \begin{figure}
-            \centering
-            \begin{subfigure}{0.3\textwidth}
-              \includegraphics[width=\linewidth]{sch.pdf}
-              \caption{s channel}
-            \end{subfigure}
-            \hfill
-            \begin{subfigure}{0.3\textwidth}
-              \includegraphics[width=\linewidth]{uch.pdf}
-              \caption{u channel}
-            \end{subfigure}
-            \hfill
-            \begin{subfigure}{0.3\textwidth}
-              \includegraphics[width=\linewidth]{tch.pdf}
-              \caption{t channel}
-            \end{subfigure}
-          \end{figure}
-        The color factor can be written respectively as following
+
+    \textbf{Brief explaination}: We choose two momentum to be shifted oppositely 
     \begin{equation*}
-            r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\,r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\,
-            r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
     \end{equation*}
-        We can easily obtain a similar Jacobbi relation
+    satisfying 
     \begin{equation*}
-            r_t=r_s-r_u
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
     \end{equation*}
-        Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.
-    \end{itemize}
-\end{frame}
 
-\begin{frame}
-    \begin{itemize}
-        \item[] For example, in the 4pt. case, the full amplitude can be decomposed to the following form
-        \begin{align*}
-            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\\
-            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\\
-            &=(A_s+A_t)r_s+(A_u-A_t)r_u
-        \end{align*}
-        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
-        \textcolor{red}{[1,2,4,3]} respectively.
-
-        \vspace{0.5em}
-        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.
-        It should be noticed that the order only has the relation with the order of external gluon line.
+    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
     \begin{equation*}
-            [1,2,\sigma(3),\sigma(4),\cdots,\sigma(n)]
+        A_n \longrightarrow \hat{A}_n(z)
     \end{equation*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item $\Phi V_2 \Phi^\dagger V_1$\\
-        The color structure for this kind of amplitude has special form, like
+    \pause
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane.
+    From Cauchy Theorem, we can ontain
     \begin{equation*}
-            (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
+        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
     \end{equation*}
-        It is more straightforward to observe the color structure in terms of double line notation as follows 
-        \vspace{0.5em}
-
-        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-        \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Straight Lines [id:da7604191870446242] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
-%Straight Lines [id:da7895005569652712] 
-\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
-%Straight Lines [id:da19217218880843812] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
-%Straight Lines [id:da7866299736623521] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
-%Straight Lines [id:da5667542352395977] 
-\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
-%Straight Lines [id:da33701635654582174] 
-\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
-%Straight Lines [id:da7076492571881566] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
-%Straight Lines [id:da3803886589182971] 
-\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
-%Straight Lines [id:da696489944746132] 
-\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
-%Straight Lines [id:da24340791537710427] 
-\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
-%Straight Lines [id:da7298898466192736] 
-\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
-%Straight Lines [id:da3460055698725] 
-\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
-\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
-%Straight Lines [id:da4507056480848969] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
-%Straight Lines [id:da6544383915955476] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
-%Straight Lines [id:da03624471669725382] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
-%Straight Lines [id:da34280653261510274] 
-\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
-\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;
-
-% Text Node
-\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
-% Text Node
-\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
-% Text Node
-\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
-% Text Node
-\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
-% Text Node
-\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
-% Text Node
-\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
-% Text Node
-\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
-% Text Node
-\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
-
-        \end{tikzpicture}
-
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{OPP(Order preserving permutation)}
-    From the 4 point case, we have known that the relative order between gauge boson 1 and gauge boson 2 does not affect the color structure. 
-    Thus, it is necessary to introduce the \textbf{OPP(Order preserving permutation)}. For example:
-    \begin{equation*}
-        (3_1,4_1,5_2) \quad (3_1,5_2,4_1) \quad (5_2,3_1,4_1)
-    \end{equation*}
-    These three permutations are different OPP for $(3_1,4_1,5_2)$, so that give us the same color factor.
+    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
 \end{frame}
 \begin{frame}
-    \frametitle{Basic building block -- 3-point}
-    From the previous section, we have known that there are only two kinds of 3 point amplitude
-    \begin{gather*}
-        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
-        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5_+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
-    \end{gather*}
-    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
-\end{frame}
 
-\begin{frame}
-    \frametitle{4 point from BCFW}
-    $\bullet \, \Phi^\dagger V_1V_1\Phi$\\
-    Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
-    \begin{gather*}
-        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
-        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
-    \end{gather*}
-    \begin{minipage}{0.5\textwidth}
+    \vspace{-1em}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=0.3\textwidth]{CT.png}
+    \end{figure}
+    \vspace{-1.5em}
+    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
+    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
+   \textcolor{red}{$\bigstar$ The most important point here is that}
     \begin{equation*}
-        A[1,2,3^+,4^-] = \sum_{h}
+        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
     \end{equation*}
-        \end{minipage}
-        \hspace{-3em}
-        \begin{minipage}{0.45\textwidth}
-        \scalebox{0.7}{\includegraphics{4pt1.pdf}}
-        \end{minipage}
-\end{frame}
-
-\begin{frame}
-    $\qquad =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$
-    \vspace{0.5em}
-
-    We denote these two different BCFW channels as $A_1$ and $A_2$, then 
-    \begin{align*}
-        A_1&=\frac{\avg{\hat{2}\hat{I}}\avg{\hat{I}1}}{\avg{1\hat{I}}}\times \frac{1}{s_{12}}\times \frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\\
-        &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
-    \end{align*}
-    where we use the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the \textcolor{red}{Fierz Identity}
+    and 
 \begin{equation*}
-        [ij][kl]+[il][jk]+[ik][lj]=0
+    \mathrm{Res}|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
 \end{equation*}
@@
 \begin{frame}
-    Similarly, we can obtain
+    \frametitle{Large z behavior}
+    In the BCFW formula, the boundary term $B_n$ affects a lot
     \begin{equation*}
-        A[1,2,3^-,4^+]=(-1)\frac{\avg{13}^2\avg{23}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
+        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
     \end{equation*}
-    \textcolor{red}{$\bigstar$ Bonus relation}
+    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
     \begin{equation*}
-        A[1,2,3^+,4^+]=A[1,2,3^-,4^-]=0
+        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
+    \end{equation*}
+    Here I show the large z behavior for gluon scattering 
+    \begin{center}
+        \begin{tabular}{lrc}
+            \toprule
+            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
+            \midrule
+            $+$ & $1/z$ & $z^3$ \\
+            $-$ & $1/z$ & $1/z$ \\
+            \bottomrule
+          \end{tabular}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{ On-shell 3-point can be completely determined}
+    For the complex momentum, we have 
+    \begin{equation*}
+        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
+    \end{equation*}
+    \[
+    \boxed{
+    \begin{aligned}
+        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+        \quad & h_1+h_2+h_3 > 0
+    \end{aligned}
+        }
+    \]
+
+    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
+
+    \textbf{Example}: 3-gluon amplitude\\
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
     \end{equation*}
 \end{frame}
-\begin{frame}
-    \frametitle{Fantasitic result from Cauchy Theorem}
-    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
-    \begin{equation*}
-        A_n \longrightarrow \hat{A}_n(z)
-    \end{equation*}
-    and we have known the possible positions of single poles, $z_I$, different propagators give 
-    us different single poles in the z-plane. 
-    \par
-    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
-    \textcolor{red}{$\bigstar$ The most important point here is that}
-    \begin{equation*}
-        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
-    \end{equation*}
-    It means that the original amplitude equals to the residue at origin.
-\end{frame}
-
 \end{document}

### 2025-06-05 MasterDefense/main.tex
New

@@
 \begin{frame}
-    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
+    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
     only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.

### 2025-06-09 MasterDefense/main.tex
Newest

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{enumitem}
@@
 \usepackage[most]{tcolorbox}
+\usepackage{tikz}
+\usetikzlibrary{calc}
+\usetikzlibrary{arrows.meta, positioning}
 
@@
 \begin{frame}
-    \frametitle{Challenges we face befor}
+    \frametitle{Challenges we face before}
 \begin{center}
@@
 \hline
-$n=$ & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+$n$ pt. amplitudes & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
 \hline
-     & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
+\# of diag.      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
 \hline
@@
 \pause
+\centering
+\textcolor{red}{The number of Feyman diagrams grow quite rapidly!}
 
+\end{frame}
+
+\begin{frame}
+\frametitle{Conventional Computation}
+\hypertarget{conv}{}
+    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
+\begin{figure}
+  \centering
+  \includegraphics[height=2.5cm]{4ptt2.pdf} \hfill
+  \includegraphics[height=2.8cm]{4ptt2_1.pdf}
+\end{figure}
+
+\vspace{-2em}
+\hyperlink{helicity}{
+\begin{flushleft}
+$
+\begin{aligned}
+&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
+&\quad \times \Big\{ 
+-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
++ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
+& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
++ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
+\end{aligned}
+$
+\end{flushleft}
+}
+\end{frame}
+
+\begin{frame}
+If you consider 5point case, it will become worse:
+\begin{center}
+    \textcolor{red}{$\bigstar$ We have 25 diagrams and nearly 10000 terms!}
+\end{center}
+\vspace{-2em}
+    % 左侧：传统图像
+
+    \textbf{传统费曼图计算：}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.5\linewidth]{5pt.png}
+    \end{figure}
+\vspace{-1.5em}
+\pause
+\begin{center}
+\hspace*{-0.5em}\includegraphics[width=1.05\textwidth]{structure.png}
+\end{center}
+\vspace{-1.5em}
+\pause
+\hspace*{-0.5em}\textcolor{red}{We need to cancel many useless information because of gauge redundancies!}
+
+\end{frame}
+\section{Preliminary}
+\begin{frame}
+\frametitle{Modern Amplitude Method} 
  The answer is On-shell method.
@@
 \draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
-
 \end{tikzpicture}
 \end{center}
+\vspace{-1em}
+\pause
+$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{perms}$ ,\quad$+,-$ : helicity
+
+    % 右侧：PT表达式
+
+    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
+    \begin{gather*}
+        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
+        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
+        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
+    \end{gather*}
+    \vspace{-3em}
+    \pause
+    \begin{gather*}
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}_\alpha[\lambda|_{\dot{\alpha}},\quad \sigma^\mu=(1,\vec{\sigma}),\\
+        \aket{\lambda},\sket{\lambda}: \text{Weyl Spinors}
+    \end{gather*}
 \end{frame}
-\section{Preliminary}
+
 \begin{frame}
-    \frametitle{Conventional VS. Modern}
-    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
-\begin{equation*}
-    \begin{aligned}
-&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
-&\quad \times \Big\{ 
--4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
-+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
-&\quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
-+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* \\
-&\quad + 4\, \epsilon_1 \cdot \epsilon_4^* \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot p_4 
-- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_4 \, \epsilon_4^* \cdot p_1 \\
-&\quad - 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_3 \, \epsilon_3^* \cdot \epsilon_4^*
-+ \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_2 \cdot p_3 \\
-&\quad + 4\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot \epsilon_3^* \, \epsilon_4^* \cdot p_3 
-- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_2 \, \epsilon_4^* \cdot p_3 \\
-&\quad + 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_4 \, \epsilon_3^* \cdot \epsilon_4^* 
-- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_4 \cdot p_2 \\
-&\quad + 2\, \epsilon_1 \cdot p_3 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* 
-- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_1 \cdot p_3 
-\Big\}.
-\end{aligned}
-\end{equation*}
+    \frametitle{Modern Amplitude Method} 
+ The answer is On-shell method.
+    \begin{center}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da5445374886882226] 
+\draw    (276.25,137) -- (457.5,136.26) ;
+\draw [shift={(459.5,136.25)}, rotate = 179.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
+% Text Node
+\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
+% Text Node
+\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
+\end{tikzpicture}
+\end{center}
+\vspace{-1em}
+    % 右侧：PT表达式
+    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
+    \begin{gather*}
+        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
+        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
+        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
+    \end{gather*}
+    \vspace{-2em}
+    \begin{gather*}
+        {A_5[1^-,2^-,3^-,4^-,5^-]=0}\\
+        {A_5[1^+,2^-,3^-,4^-,5^-]=0}\\
+        \textcolor{red}{A_5[1^+,2^+,3^-,4^-,5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
+    \end{gather*}
 \end{frame}
+
 \begin{frame}
-    If you consider 5point case, it will become worser:
-\begin{center}
-    \textcolor{red}{$\bigstar$ There are nearly 10000 terms!}
-\end{center}
-\begin{columns}[T,onlytextwidth]
-    % 左侧：传统图像
-    \column{0.48\textwidth}
-    \textbf{传统费曼图计算：}
-    \begin{figure}
-        \centering
-        \includegraphics[width=\linewidth]{5pt.png}
-    \end{figure}
-    \pause 
-    % 右侧：PT表达式
-    \column{0.48\textwidth}
-    \vspace{1.5em}
-    \qquad \textbf{Parke–Taylor Formula:}
-    \begin{gather*}
-        \textcolor{red}{A_5(1^-,2^-,3^+,4^+,5^+)} =\\
-        \textcolor{red}{\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}
-    \end{gather*}
-\end{columns}
-\vspace{2em}
-\textcolor{red}{$\bigstar$ \Large It becomes quite simple and compact!}
-\end{frame}
-\begin{frame}
-    \frametitle{Fantasitic result from Cauchy Theorem}
+    \frametitle{The Power of BCFW Recursion Relation}
     %First, I will show the most important part in this report.
@@
 
-\textcolor{red}{$\bigstar $ ~ From lower point to higher point!!}
+\textcolor{red}{$\bigstar $ ~ From lower point on-shell amp. to higher point on-shell amp.!!}
 
 \end{frame}
+
+\begin{frame}
+    More specifically,
+
+\begin{center}
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da4236245229594603] 
+\draw    (259,91.9) -- (308,92.24) ;
+\draw [shift={(310,92.25)}, rotate = 180.39] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da22408043084764206] 
+\draw    (341.2,91.9) -- (391,91.76) ;
+\draw [shift={(393,91.75)}, rotate = 179.83] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Straight Lines [id:da5239716133788715] 
+\draw    (421.7,91.3) -- (477,91.73) ;
+\draw [shift={(479,91.75)}, rotate = 180.45] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+
+% Text Node
+\draw (231.8,83.1) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 3pt.}};
+% Text Node
+\draw (313.5,83) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 4pt.}};
+% Text Node
+\draw (396.9,83.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 5pt.}};
+% Text Node
+\draw (482.4,85.2) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
+% Text Node
+\draw (214,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle12\rangle\langle 23\rangle \langle 31\rangle }$};
+% Text Node
+\draw (279.25,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle 12\rangle \langle 23\rangle \langle 34\rangle \langle 41\rangle }$};
+% Text Node
+\draw (370.75,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle 12\rangle \langle 23\rangle \langle 34\rangle \langle 45\rangle \langle 51\rangle }$};
+
+\end{tikzpicture}
+\end{center}
+
+\pause
+\begin{equation*}
+    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-,(i+1)^+\cdots~j^-\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+\end{equation*}
+
+\vspace*{2em}
+\textcolor{red}{$\bigstar$ \Large This is the power of BCFW recursion relation.}
+\end{frame}
+\begin{frame}{From Review to Applications}
+
+\begin{columns}[T]
+  % 左列：当前已完成
+  \begin{column}{0.48\textwidth}
+    \begin{block}{\centering\large \textbf{So far: Foundations}}
+      \begin{itemize}[left=1em]
+        \item Reviewed the structure of \textbf{BCFW recursion relation}
+        \item Applied to:
+          \begin{itemize}[left=0.1em]
+            \item \textbf{Pure Yang-Mills} theory
+            \item Tree-level MHV amplitudes
+            \item Color-ordered partial amplitudes
+          \end{itemize}
+      \end{itemize}
+    \end{block}
+  \end{column}
+\pause
+  % 右列：研究目标
+  \begin{column}{0.48\textwidth}
+    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
+      \begin{itemize}[left=1em]
+        \item Move beyond massless gauge theory
+        \item Consider:
+          \begin{itemize}[left=0.1em]
+            \item \textbf{(De)constructed gauge theories}
+          \end{itemize}
+        \item Key questions:
+          \begin{itemize}[left=0.1em]
+            \item Can BCFW still apply?
+            \item How to choose momentum shift?
+            \item What new structures emerge?
+          \end{itemize}
+      \end{itemize}
+    \end{block}
+  \end{column}
+\end{columns}
+
+\end{frame}
+
+\section{Model and Computation}
+
+\begin{frame}{Introduction of quiver gauge theory}
+\vspace{1em}
+\begin{columns}[c]
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moose.png}
+
+    \column{0.14\textwidth}
+    \centering
+    \begin{tikzpicture}[scale=0.8]
+        \draw[->, line width=1pt] (0,0) -- (1.5,0)
+            node[midway, above] {\footnotesize Condensation}; % ← 加文字
+    \end{tikzpicture}
+
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moosed.jpeg}
+\end{columns}
+
+\pause
+\raggedright
+The Lagrangian can be written like
+\begin{equation*}
+    \mathcal{L} = -\sum_{i=1}^{N} \frac{1}{2} \mathrm{Tr}(F_i^2)
+    + \sum_{i=1}^{N} \mathrm{Tr}\left[(D_\mu \Phi_i)^\dagger (D^\mu \Phi_i)\right],
+\end{equation*}
+here $F_i$ refers to the $i$th gauge field strength. The scalar field $\Phi_i$ transforms under the \textcolor{red}{bi-fundamental} representation, and the covariant derivative equals to
+\begin{equation*}
+    D_\mu \Phi_i = \partial_\mu \Phi_i - i g_i A_{i\mu} \Phi_i + i g_{i+1} \Phi_i A_{i+1\mu}.
+\end{equation*}
+
+\end{frame}
+
+\begin{frame}
+    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
+    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
+     \vspace{1em} % 图与文字之间的间距
+    \begin{center}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
+    \end{minipage}
+    \hspace{0.05\textwidth}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
+    \end{minipage}
+    \end{center}
+    \pause
+    After higgsing the scalar field, we can obtain a spectrum
+    \begin{equation*}
+        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
+    \end{equation*}
+    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^1$ compactification. 
+\end{frame}
+
+\begin{frame}
+    \frametitle{Amplitudes from BCFW}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.5\textwidth]{2-site.png}
+    \end{figure}
+    \vspace{-1em}
+    From the previous section, we have known that there are only two kinds of 3 point amplitude
+    \begin{gather*}
+        A[1^\Phi,2^{\Phi^\dagger},3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi,2^{\Phi^\dagger},3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
+        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
+    \end{gather*}
+    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
+\end{frame}
+\begin{frame}
+    \frametitle{Gauge boson sector}
+    \begin{itemize}
+        \item n$ V_1$ or n$V_2$\\
+        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
+        existing results.
+        \begin{equation*}
+            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+        \end{equation*}
+        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{SQCD like sector}
+    \begin{itemize}
+        \item $\Phi^\dagger V_1V_1\Phi$\\
+        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
+        \begin{gather*}
+        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
+        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
+        \end{gather*}
+        The amplitudes can be computed 
+        \begin{align*}
+            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
+        \end{align*}
+        \item $\Phi^\dagger V_1V_1V_1\Phi$
+            \begin{equation*}
+                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+            \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item $\Phi^\dagger (nV_1)\Phi$
+            \begin{equation*}
+                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
+            \end{equation*}
+            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
+                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
+        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pure 2-site amplitude}
+    \begin{itemize}
+        \item $\Phi V_2 \Phi^\dagger V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+        \end{equation*}
+        \item $\Phi V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+        \end{equation*}
+        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
+        \end{equation*}       
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item Compact formula for general case
+        \begin{equation*}
+            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
+        \end{equation*} 
+        \begin{minipage}{0.7\textwidth}
+            \raggedright  % 或者 \centering 或 \raggedleft
+            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
+            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
+            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
+            $\star$: \,Order for gauge group 1\\
+            $\ast$: \,Order for gauge group 2 
+            \end{minipage}
+
+    \end{itemize}
+    \pause
+    For example, if we want to compute $A[1,2,5_1^+,3_1^+,4_1^-,7_2^+,6_2^+,8_2^+]$:
+    \begin{equation*}
+        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
+    \end{equation*}
+\end{frame}
+\section{Summary}
+\begin{frame}
+    \frametitle{Summary}
+    \begin{itemize}
+        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
+        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
+        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
+    \end{itemize}
+\end{frame}
+\begin{frame} 
+    \centering
+    \Huge Thanks for your attention!
+\end{frame} 
+\appendix
 \begin{frame}{Spinor-Helicity Formalism}
+    \hypertarget{helicity}{}
 \begin{block}{Helicity}
-\textbf{Helicity} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
+\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
 \[
@@
 \end{frame}
-
-\section{Model and Computation}
-
-\begin{frame}{Introduction of quiver gauge theory}
-\vspace{1em}
-\begin{columns}[c]
-    \column{0.43\textwidth}
-    \centering
-    \includegraphics[width=100pt]{Moose.png}
-
-    \column{0.14\textwidth}
-    \centering
-    \begin{tikzpicture}[scale=0.8]
-        \draw[->, line width=1pt] (0,0) -- (1.5,0)
-            node[midway, above] {\footnotesize Condensation}; % ← 加文字
-    \end{tikzpicture}
-
-    \column{0.43\textwidth}
-    \centering
-    \includegraphics[width=100pt]{Moosed.jpeg}
-\end{columns}
-
-\pause
-\raggedright
-The Lagrangian can be written like
-\begin{equation*}
-    \mathcal{L} = -\sum_{i=1}^{N} \frac{1}{2} \mathrm{Tr}(F_i^2)
-    + \sum_{i=1}^{N} \mathrm{Tr}\left[(D_\mu \Phi_i)^\dagger (D^\mu \Phi_i)\right],
-\end{equation*}
-here $F_i$ refers to the $i$th gauge field strength. The scalar field $\Phi_i$ transforms under the \textcolor{red}{bi-fundamental} representation, and the covariant derivative equals to
-\begin{equation*}
-    D_\mu \Phi_i = \partial_\mu \Phi_i - i g_i A_{i\mu} \Phi_i + i g_{i+1} \Phi_i A_{i+1\mu}.
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}
-    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
-    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
-     \vspace{1em} % 图与文字之间的间距
-    \begin{center}
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
-        \par\vspace{0.5em}
-    \end{minipage}
-    \hspace{0.05\textwidth}
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
-        \par\vspace{0.5em}
-    \end{minipage}
-    \end{center}
-    \pause
-    After higgsing the scalar field, we can obtain a spectrum
-    \begin{equation*}
-        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
-    \end{equation*}
-    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification. 
-\end{frame}
-\begin{frame}
-    \frametitle{Scattering Amplitudes from BCFW}
-    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
-    \begin{equation*}
-        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
-    \end{equation*}
-We only foucus on the following amplitudes:
-\begin{equation*}
-    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
-\end{equation*}
-here n can be any positive integer.
-\end{frame}
-\begin{frame}
-    \frametitle{Basic building block -- 3-point}
-    From the previous section, we have known that there are only two kinds of 3 point amplitude
-    \begin{gather*}
-        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
-        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
-    \end{gather*}
-    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
-\end{frame}
-\begin{frame}
-    \frametitle{Gauge boson sector}
-    \begin{itemize}
-        \item n$ V_1$ or n$V_2$\\
-        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
-        existing results.
-        \begin{equation*}
-            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
-        \end{equation*}
-        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{SQCD like sector}
-    \begin{itemize}
-        \item $\Phi^\dagger V_1V_1\Phi$\\
-        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
-        \begin{gather*}
-        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
-        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
-        \end{gather*}
-        The amplitudes can be computed 
-        \begin{align*}
-            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
-        \end{align*}
-        \item $\Phi^\dagger V_1V_1V_1\Phi$
-            \begin{equation*}
-                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
-            \end{equation*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item $\Phi^\dagger (nV_1)\Phi$
-            \begin{equation*}
-                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
-            \end{equation*}
-            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
-                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
-        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pure 2-site amplitude}
-    \begin{itemize}
-        \item $\Phi V_2 \Phi^\dagger V_1$
-        \begin{equation*}
-            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
-        \end{equation*}
-        \item $\Phi V_2 \Phi^\dagger V_1V_1$
-        \begin{equation*}
-            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
-        \end{equation*}
-        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
-        \begin{equation*}
-            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
-        \end{equation*}       
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item Compact formula for general case
-        \begin{equation*}
-            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
-        \end{equation*} 
-        \begin{minipage}{0.7\textwidth}
-            \raggedright  % 或者 \centering 或 \raggedleft
-            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
-            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
-            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
-            $\star$: \,Order for gauge group 1\\
-            $\ast$: \,Order for gauge group 2 
-            \end{minipage}
-
-    \end{itemize}
-\end{frame}
-\section{Summary}
-\begin{frame}
-    \frametitle{Summary}
-    \begin{itemize}
-        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
-        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
-        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
-    \end{itemize}
-\end{frame}
-\begin{frame}
-    \centering
-    \Huge Thanks for your attention!
-\end{frame} 
-\appendix
 
@@
 \end{frame}
+
+\begin{frame}
+    \frametitle{Scattering Amplitudes from BCFW}
+    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
+    \begin{equation*}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
+    \end{equation*}
+We only foucus on the following amplitudes:
+\begin{equation*}
+    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
+\end{equation*}
+here n can be any positive integer.
+\end{frame}
+
 \end{document}

### 2025-06-12 MasterDefense/main.tex
New

@@
     \begin{itemize}
-      \item Core prediction targets for high-energy collider experiments such as the LHC
+      \item Core prediction targets for high-energy collider experiments such as the LHC , especially for high multiplicity amplitudes.
       \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
@@
 \vspace{-2.3em}
+\pause
 \begin{center}
@@
 \hline
-\# of diag.      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
+\# of diagrams      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
 \hline
@@
 \end{center}
-\pause
 \centering
@@
 \frametitle{Conventional Computation}
-\hypertarget{conv}{}
+
     Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
@@
 \vspace{-2em}
-\hyperlink{helicity}{
+
 \begin{flushleft}
@@
 \end{flushleft}
-}
+
 \end{frame}
@@
 \end{center}
-\vspace{-1.5em}
-\pause
-\hspace*{-0.5em}\textcolor{red}{We need to cancel many useless information because of gauge redundancies!}
 
@@
 % Text Node
-\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
+\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Helicity Amplitude}}};
 % Text Node
@@
 \pause
-$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{perms}$ ,\quad$+,-$ : helicity
+$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{permutations}$
 
@@
     \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
+    \begin{align*}
+    A_5[1^+2^+3^+4^+5^+] &= 0 
+    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
+    A_5[1^-2^+3^+4^+5^+] &= 0 
+    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
+    \end{align*}
+    \pause
+    \vspace{-3em}
+    \hypertarget{conv}{}
     \begin{gather*}
-        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
-        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
-        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
-    \end{gather*}
-    \vspace{-3em}
-    \pause
-    \begin{gather*}
-        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}_\alpha[\lambda|_{\dot{\alpha}},\quad \sigma^\mu=(1,\vec{\sigma}),\\
-        \aket{\lambda},\sket{\lambda}: \text{Weyl Spinors}
+    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]= 
+    \frac{\langle 1 2 \rangle^4}
+         {\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle45 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trivial one})\\[1em]
+    (p_{i\mu} \sigma^\mu)_{\alpha\dot{\alpha}}=(\aket{p_i})_\alpha([p_i|)_{\dot{\alpha}},\quad \aket{p_i}=\aket{i}\\
+    \quad \sigma^\mu=(1,\vec{\sigma}),\quad \aket{i},\sket{i}: \text{Weyl Spinors}\\
+    \avg{ij}=\langle i |^\alpha \aket{j}_\alpha=\varepsilon^{\alpha\beta}\aket{i}_\beta\aket{j}_\alpha,\quad \varepsilon^{\alpha\beta}: \text{antisymmetric tensor}
     \end{gather*}
@@
     \begin{gather*}
-        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
-        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
-        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
+        {A_5[1^+2^+3^+4^+5^+]=0}\\
+        {A_5[1^-2^+3^+4^+5^+]=0}\\
+        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
     \end{gather*}
-    \vspace{-2em}
+    \vspace{-3em}
     \begin{gather*}
-        {A_5[1^-,2^-,3^-,4^-,5^-]=0}\\
-        {A_5[1^+,2^-,3^-,4^-,5^-]=0}\\
-        \textcolor{red}{A_5[1^+,2^+,3^-,4^-,5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
+        {A_5[1^-2^-3^-4^-5^-]=0}\\
+        {A_5[1^+2^-3^-4^-5^-]=0}\\
+        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
     \end{gather*}
@@
 \begin{frame}
-    More specifically,
+    More specifically, it helps us to prove P. T. formula
 
@@
 
+\vspace{-2em}
 \pause
 \begin{equation*}
-    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-,(i+1)^+\cdots~j^-\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-(i+1)^+\cdots~j^-(j+1)^+\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
 \end{equation*}
@@
             \item Can BCFW still apply?
-            \item How to choose momentum shift?
             \item What new structures emerge?
@@
 
-\begin{frame}{Introduction of quiver gauge theory}
+\begin{frame}{Introduction of (De)Constructed gauge theory}
 \vspace{1em}
@@
     \vspace{-1em}
-    From the previous section, we have known that there are only two kinds of 3 point amplitude
+    From the Lagrangian, we have known that there are only two kinds of 3 point amplitude ($+,-:$ helicity\qquad $\Phi,\Phi^\dagger: \text{charge of scalar}$)
     \begin{gather*}
-        A[1^\Phi,2^{\Phi^\dagger},3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi,2^{\Phi^\dagger},3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
-        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
+        A[1^\Phi2^{\Phi^\dagger}3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi2^{\Phi^\dagger}3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
+        A[3^+4^+5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-4^-5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
     \end{gather*}
@@
         \begin{equation*}
-            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots i^-\cdots j^-\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
         \end{equation*}
@@
     \frametitle{SQCD like sector}
+    The amplitudes can be computed like 
     \begin{itemize}
-        \item $\Phi^\dagger V_1V_1\Phi$\\
-        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
-        \begin{gather*}
-        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
-        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
-        \end{gather*}
-        The amplitudes can be computed 
+        \item $\Phi^\dagger V_1V_1\Phi$
         \begin{align*}
-            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
+            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
         \end{align*}
@@
             \begin{equation*}
-                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
             \end{equation*}
@@
             \begin{equation*}
-                A[1,2,\cdots,(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
+                A[1^\Phi2^{\Phi^\dagger}\cdots(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
             \end{equation*}
             \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
-                A[1,2,3^+,4^+]=0\quad \Rightarrow  \quad A[1,2,3^+,\cdots,n^+]=0 \end{equation*}}
+                A[1^\Phi2^{\Phi^\dagger}3^+4^+]=0\quad \Rightarrow  \quad A[1^\Phi2^{\Phi^\dagger}3^+\cdots n^+]=0 \end{equation*}}
         For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
@@
         \begin{equation*}
-            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
         \end{equation*}
@@
         \begin{equation*}
-            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
         \end{equation*}
@@
         \begin{equation*}
-            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
         \end{equation*}       
@@
     \pause
-    For example, if we want to compute $A[1,2,5_1^+,3_1^+,4_1^-,7_2^+,6_2^+,8_2^+]$:
+    For example, if we want to compute $A[1^\Phi2^{\Phi^\dagger}5_1^+3_1^+4_1^-7_2^+6_2^+8_2^+]$:
     \begin{equation*}
@@
     \end{equation*}
+    If you use Feynman diagrams, it may take sevral days to accomplish the computation.
 \end{frame}

### 2025-06-23 2nd report/2report.tex
New

--- 2025-06-12 MasterDefense/main.tex
@@
 \newcommand{\tif}[1]{\textit{\textbf{#1}}}
+\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
+\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
 \AtBeginSection[]{
@@
 \end{frame}
+\begin{frame}
+    \frametitle{Momentum Shift in BCFW}
+    \textbf{What did BCFW do to make the shift?}
+
+    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
+    \begin{equation*}
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
+    \end{equation*}
+    satisfying 
+    \begin{equation*}
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
+    \end{equation*}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Circle [id:dp47058391497271046] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) ..
+controls (266.75,112.19) and (277.94,101) ..
+(291.75,101) ..
+controls (305.56,101) and (316.75,112.19) ..
+(316.75,126) ..
+controls (316.75,139.81) and (305.56,151) ..
+(291.75,151) ..
+controls (277.94,151) and (266.75,139.81) ..
+(266.75,126) -- cycle ;
+%Straight Lines [id:da8759716500759761] 
+\draw    (249,78.25) -- (273.5,109.25) ;
+%Straight Lines [id:da2121821831988906] 
+\draw    (233.5,103.25) -- (266.5,120.75) ;
+%Straight Lines [id:da6378763431676462] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
+%Straight Lines [id:da7508961107891289] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
+%Straight Lines [id:da06317949320750826] 
+\draw    (237,155.25) -- (271.5,140.75) ;
+%Straight Lines [id:da403008866951158] 
+\draw    (261.5,180.25) -- (281.5,149.25) ;
+%Straight Lines [id:da8334043101335312] 
+\draw    (423,119.25) -- (457.5,104.75) ;
+%Straight Lines [id:da03451573841415356] 
+\draw    (418.5,109.75) -- (438.5,78.75) ;
+%Straight Lines [id:da025418352459996796] 
+\draw    (420,140.25) -- (453,157.75) ;
+%Straight Lines [id:da22879254297825424] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
+%Straight Lines [id:da2355772127149045] 
+\draw    (410.5,148.75) -- (435,179.75) ;
+%Shape: Rectangle [id:dp6752662310096104] 
+\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
+%Straight Lines [id:da4580921639862495] 
+\draw    (316.75,126) -- (373.5,125.75) ;
+%Shape: Circle [id:dp8699671429684472] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) ..
+controls (373.5,111.94) and (384.69,100.75) ..
+(398.5,100.75) ..
+controls (412.31,100.75) and (423.5,111.94) ..
+(423.5,125.75) ..
+controls (423.5,139.56) and (412.31,150.75) ..
+(398.5,150.75) ..
+controls (384.69,150.75) and (373.5,139.56) ..
+(373.5,125.75) -- cycle ;
+
+% Text Node
+\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
+% Text Node
+\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
+% Text Node
+\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
+% Text Node
+\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
+% Text Node
+\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
+% Text Node
+\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};
+
+\end{tikzpicture}
+    \end{minipage}
+    \hspace{1em}
+    \begin{minipage}{0.45\textwidth}
+        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
+    \begin{equation*}
+        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
+    \end{equation*}
+
+    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
+    \end{minipage}
+\end{figure} 
+\end{frame}
+
+\begin{frame}
+
+    \textbf{Brief explaination}: We choose two momentum to be shifted oppositely 
+    \begin{equation*}
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
+    \end{equation*}
+    satisfying 
+    \begin{equation*}
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
+    \end{equation*}
+
+    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
+    \begin{equation*}
+        A_n \longrightarrow \hat{A}_n(z)
+    \end{equation*}
+    \pause
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane.
+    From Cauchy Theorem, we can ontain
+    \begin{equation*}
+        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
+\end{frame}
+
+\begin{frame}
+
+    \vspace{-1em}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=0.3\textwidth]{CT.png}
+    \end{figure}
+    \vspace{-1.5em}
+    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
+    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
+   \textcolor{red}{$\bigstar$ The most important point here is that}
+    \begin{equation*}
+        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
+    \end{equation*}
+    and 
+\begin{equation*}
+    \mathrm{Res}|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+\end{equation*}
+\end{frame}
 
@@
 \end{frame}
+\begin{frame}
+\frametitle{Spinor-helicity formalism}
+    \begin{itemize}
+        \item $\textbf{\text{Massless Case}}$\\
+    \begin{equation*}
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \end{equation*}
+    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
+    \begin{equation*}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
+    \end{equation*}
+    same for
+    \begin{equation*}
+        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+    \end{equation*}
+    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
+    \begin{equation*}
+        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
+    \end{equation*}
+    \end{itemize}
+\vspace{-2em}
+    \begin{itemize}
+    \item \textbf{Massive Case}\\
+    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{ On-shell 3-point can be completely determined}
+    \textbf{On-shell 3-point for real momentum}
+
+    Because of the constrain from momentum conservation and on-shell condition
+    \begin{equation*}
+        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
+    \end{equation*}
+    All of the contribution 
+    \begin{equation*}
+        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
+    \end{equation*}
+    In terms of Spinor- Helicity variable, we have 
+    \begin{equation*}
+        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
+    \end{equation*}
+    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}
+
+    Of coure, you can introduce non-minimal interaction
+    \begin{equation*}
+        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
+    \end{equation*}
+    but it still equals to 0 under the on-shell condition.
+\end{frame}
+
+\begin{frame}
+    \textbf{Another necessarity to introduce complex momentum}
+
+    If the momentum is complexed, we have 
+    \begin{equation*}
+        \avg{12}\neq[21]^*
+    \end{equation*}
+    Then we can obtain
+    \begin{equation*}
+        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
+    \end{equation*}
+    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
+    \begin{equation*}
+        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
+    \end{equation*}
+    Little group scaling tells us that
+    \begin{equation*}
+        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
+    \end{equation*}
+    We can obtain
+    \begin{equation*}
+        2h_1=-x_{12}-x_{13}
+    \end{equation*}
+    Similarly, we can also obtain
+    \begin{equation*}
+        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    Then all index can be solved from this system of equations, so that
+    \[
+    \boxed{
+    \begin{aligned}
+        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+        \quad & h_1+h_2+h_3 > 0
+    \end{aligned}
+        }
+    \]
+
+    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
+
+    \textbf{Example}: 3-gluon amplitude\\
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
+    \end{equation*}
+    There's another possibility 
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
+    \end{equation*}
+    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
+\end{frame}
+
 \begin{frame}{From Review to Applications}
@@
     \vspace{-1em}
+    \begin{equation*}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
+    \end{equation*}
     From the Lagrangian, we have known that there are only two kinds of 3 point amplitude ($+,-:$ helicity\qquad $\Phi,\Phi^\dagger: \text{charge of scalar}$)
@@
 \end{frame}
+\section{Some problems and extends}
+\begin{frame}
+    \frametitle{How about NMHV?}
+    First, let us review the NMHV amplitudes for gluon scattering.
+
+    Still we begin with the simplest case -- \textbf{Split-helicity} NMHV like \mbox{\( A_6[1^-\, 2^-\, 3^-\, 4^+\, 5^+\, 6^+] \)}.%
+
+    Here we choose $[1,2\rangle$ shift
+\vspace{-1em}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\textwidth]{6ptNMHV.png}
+\end{figure}
+\pause
+\begin{itemize}
+    \item Diagram B includes a propagator $1/P_{156}^2$, so there is a 3-particle pole $P_{156}^2=0$. But by inspecting the external order,
+    it seems that there's no difference between $(-++)$ channel 561 and 345. We should expect the amplitude to have a pole also at 
+    $P_{345}^2=0$. 
+    \begin{equation*}
+        \text{diagram A}=\frac{\avg{\hat{1}\hat{P}_{16}}^3}{\avg{\hat{P}_{16}6}\avg{6\hat{1}}}\times\frac{1}{P_{16}^2}\times\frac{\avg{\hat{2}3}^3}{\mdavg{34}{45}\!\mdavg{5\hat{P}_{16}}{\hat{P}_{16}2}}
+    \end{equation*}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+    \item[] $$\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3} = \avg{21}[\hat{1}3] + \avg{\hat{2}6}[63]$$
+    It follows from $\hat{P}_{16}^2=0$ that $z_{16}=-\frac{[16]}{[26]}$, so
+    \[
+\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3}
+= -\frac{[36]}{[26]}
+\left( \avg{12}[12] + \avg{16}[16] + \avg{26}[26] \right)
+= -\frac{[36]}{[26]} P_{126}^2
+\]
+\textcolor{red}{The 3-particle pole $P_{126}^2$ is encoded inside the BCFW channel !}
+    \item Full expression 
+    \begin{align*}
+        A_6[1^-\,2^-\,3^-\,4^+\,5^+\,6^+] =&
+        \frac{ \langle 3|1+2|6]^3}{P_{126}^2 [21][16] \langle 34 \rangle \langle 45 \rangle \langle 5|1+6|2]}\\
+        &+\frac{ \langle 1|5+6|4]^3}{P_{156}^2 [23][34] \langle 56 \rangle \langle 61 \rangle \langle 5|1+6|2]}.
+    \end{align*}
+    The factor $\langle 5|1+6|2]$ does not correspond to a physical pole of the scattering amplitude: it is a \textbf{spurious pole}.
+    %You will also note that there is a strange denominator-factor $\langle 5|1+6|2]$ in the result from each BCFW diagram. 
+    %It is typical that BCFW packs the information of the amplitudes into compact
+    %expressions, but the cost is the appearance of spurious poles; this means that in the BCFW
+    %representation the locality of the underlying field theory is not manifest.
+    %The spurious pole should cancel in the sum of the two BCFW diagrams.
+
+    There has been interesting paper investigating how to systematically cancel the spurious poles,
+    like "A. Hodges, JHEP 1305, 35 (2013) [arXiv:0905.1473 [hep-th]]." 
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item We utilize the $[1,2\rangle$ shift before, what happens if we change to $[2,1\rangle$ shift?
+    \end{itemize}
+    \begin{figure}
+            \centering
+            \includegraphics[width=1\textwidth]{6ptNMHV2.png}
+        \end{figure}
+    \begin{itemize}
+        \item[] diagram A' = $\mathrm{anti\text{-}MHV} \times \mathrm{NMHV}$, as opposed to diagram A = $\mathrm{MHV}\times \mathrm{MHV}$. 
+        \vspace{1em}
+
+        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
+        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{CSW expansion}
+    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
+    \begin{equation*}
+        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
+    \end{equation*}
+    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
+
+\end{frame}
+
 \section{Summary}
@@
 \begin{frame}
-
-    \textbf{Brief explaination}: We choose two momentum to be shifted oppositely 
-    \begin{equation*}
-        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
-    \end{equation*}
-    satisfying 
-    \begin{equation*}
-        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
-    \end{equation*}
-
-    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
-    \begin{equation*}
-        A_n \longrightarrow \hat{A}_n(z)
-    \end{equation*}
-    \pause
-    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane.
-    From Cauchy Theorem, we can ontain
-    \begin{equation*}
-        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
-\end{frame}
-\begin{frame}
-
-    \vspace{-1em}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width=0.3\textwidth]{CT.png}
-    \end{figure}
-    \vspace{-1.5em}
-    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
-    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
-   \textcolor{red}{$\bigstar$ The most important point here is that}
-    \begin{equation*}
-        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
-    \end{equation*}
-    and 
-\begin{equation*}
-    \mathrm{Res}|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
-\end{equation*}
-\end{frame}
-
-\begin{frame}
     \frametitle{Large z behavior}

### 2025-06-24 2nd report/2report.tex
New

@@
 \usepackage{tikz}
+\usepackage{cancel}
 \usetikzlibrary{calc}
@@
 &\quad \times \Big\{ 
--4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
-+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
-& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
-+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
+-4\, (\epsilon_1 \cdot \epsilon_3^*) \, (\epsilon_2 \cdot p_1) \, (\epsilon_4^* \cdot p_3) 
++ 2\, (\epsilon_1 \cdot \epsilon_2) \, (\epsilon_3^* \cdot p_1) \, (\epsilon_4^* \cdot p_3) \\
+& \quad - 2\, (\epsilon_1 \cdot p_4) \, (\epsilon_2 \cdot p_1) \, (\epsilon_3^* \cdot \epsilon_4^*)
++ (\epsilon_1 \cdot \epsilon_2) \, (p_4 \cdot p_1) \, (\epsilon_3^* \cdot \epsilon_4^*)  + \text{10 terms}\big\}
 \end{aligned}
@@
     \end{gather*}
-\end{frame}
-\begin{frame}
-    \frametitle{Momentum Shift in BCFW}
-    \textbf{What did BCFW do to make the shift?}
-
-    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
-    \begin{equation*}
-        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
-    \end{equation*}
-    satisfying 
-    \begin{equation*}
-        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
-    \end{equation*}
-
-\begin{figure}
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Shape: Circle [id:dp47058391497271046] 
-\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) ..
-controls (266.75,112.19) and (277.94,101) ..
-(291.75,101) ..
-controls (305.56,101) and (316.75,112.19) ..
-(316.75,126) ..
-controls (316.75,139.81) and (305.56,151) ..
-(291.75,151) ..
-controls (277.94,151) and (266.75,139.81) ..
-(266.75,126) -- cycle ;
-%Straight Lines [id:da8759716500759761] 
-\draw    (249,78.25) -- (273.5,109.25) ;
-%Straight Lines [id:da2121821831988906] 
-\draw    (233.5,103.25) -- (266.5,120.75) ;
-%Straight Lines [id:da6378763431676462] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
-%Straight Lines [id:da7508961107891289] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
-%Straight Lines [id:da06317949320750826] 
-\draw    (237,155.25) -- (271.5,140.75) ;
-%Straight Lines [id:da403008866951158] 
-\draw    (261.5,180.25) -- (281.5,149.25) ;
-%Straight Lines [id:da8334043101335312] 
-\draw    (423,119.25) -- (457.5,104.75) ;
-%Straight Lines [id:da03451573841415356] 
-\draw    (418.5,109.75) -- (438.5,78.75) ;
-%Straight Lines [id:da025418352459996796] 
-\draw    (420,140.25) -- (453,157.75) ;
-%Straight Lines [id:da22879254297825424] 
-\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
-%Straight Lines [id:da2355772127149045] 
-\draw    (410.5,148.75) -- (435,179.75) ;
-%Shape: Rectangle [id:dp6752662310096104] 
-\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
-%Straight Lines [id:da4580921639862495] 
-\draw    (316.75,126) -- (373.5,125.75) ;
-%Shape: Circle [id:dp8699671429684472] 
-\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) ..
-controls (373.5,111.94) and (384.69,100.75) ..
-(398.5,100.75) ..
-controls (412.31,100.75) and (423.5,111.94) ..
-(423.5,125.75) ..
-controls (423.5,139.56) and (412.31,150.75) ..
-(398.5,150.75) ..
-controls (384.69,150.75) and (373.5,139.56) ..
-(373.5,125.75) -- cycle ;
-
-% Text Node
-\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
-% Text Node
-\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
-% Text Node
-\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
-% Text Node
-\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
-% Text Node
-\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
-% Text Node
-\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};
-
-\end{tikzpicture}
-    \end{minipage}
-    \hspace{1em}
-    \begin{minipage}{0.45\textwidth}
-        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
-    \begin{equation*}
-        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
-    \end{equation*}
-
-    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
-    \end{minipage}
-\end{figure} 
-\end{frame}
-
-\begin{frame}
-
-    \textbf{Brief explaination}: We choose two momentum to be shifted oppositely 
-    \begin{equation*}
-        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
-    \end{equation*}
-    satisfying 
-    \begin{equation*}
-        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
-    \end{equation*}
-
-    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
-    \begin{equation*}
-        A_n \longrightarrow \hat{A}_n(z)
-    \end{equation*}
-    \pause
-    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane.
-    From Cauchy Theorem, we can ontain
-    \begin{equation*}
-        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
-\end{frame}
-
-\begin{frame}
-
-    \vspace{-1em}
-    \begin{figure}[htbp]
-        \centering
-        \includegraphics[width=0.3\textwidth]{CT.png}
-    \end{figure}
-    \vspace{-1.5em}
-    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
-    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
-   \textcolor{red}{$\bigstar$ The most important point here is that}
-    \begin{equation*}
-        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
-    \end{equation*}
-    and 
-\begin{equation*}
-    \mathrm{Res}|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
-\end{equation*}
 \end{frame}
@@
 \begin{frame}
+    \frametitle{Momentum Shift in BCFW}
+    \textbf{What did BCFW do to make the shift?}
+
+    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
+    \begin{equation*}
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
+    \end{equation*}
+    satisfying 
+    \begin{equation*}
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
+    \end{equation*}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Shape: Circle [id:dp47058391497271046] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) ..
+controls (266.75,112.19) and (277.94,101) ..
+(291.75,101) ..
+controls (305.56,101) and (316.75,112.19) ..
+(316.75,126) ..
+controls (316.75,139.81) and (305.56,151) ..
+(291.75,151) ..
+controls (277.94,151) and (266.75,139.81) ..
+(266.75,126) -- cycle ;
+%Straight Lines [id:da8759716500759761] 
+\draw    (249,78.25) -- (273.5,109.25) ;
+%Straight Lines [id:da2121821831988906] 
+\draw    (233.5,103.25) -- (266.5,120.75) ;
+%Straight Lines [id:da6378763431676462] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
+%Straight Lines [id:da7508961107891289] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
+%Straight Lines [id:da06317949320750826] 
+\draw    (237,155.25) -- (271.5,140.75) ;
+%Straight Lines [id:da403008866951158] 
+\draw    (261.5,180.25) -- (281.5,149.25) ;
+%Straight Lines [id:da8334043101335312] 
+\draw    (423,119.25) -- (457.5,104.75) ;
+%Straight Lines [id:da03451573841415356] 
+\draw    (418.5,109.75) -- (438.5,78.75) ;
+%Straight Lines [id:da025418352459996796] 
+\draw    (420,140.25) -- (453,157.75) ;
+%Straight Lines [id:da22879254297825424] 
+\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
+%Straight Lines [id:da2355772127149045] 
+\draw    (410.5,148.75) -- (435,179.75) ;
+%Shape: Rectangle [id:dp6752662310096104] 
+\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
+%Straight Lines [id:da4580921639862495] 
+\draw    (316.75,126) -- (373.5,125.75) ;
+%Shape: Circle [id:dp8699671429684472] 
+\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) ..
+controls (373.5,111.94) and (384.69,100.75) ..
+(398.5,100.75) ..
+controls (412.31,100.75) and (423.5,111.94) ..
+(423.5,125.75) ..
+controls (423.5,139.56) and (412.31,150.75) ..
+(398.5,150.75) ..
+controls (384.69,150.75) and (373.5,139.56) ..
+(373.5,125.75) -- cycle ;
+
+% Text Node
+\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
+% Text Node
+\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
+% Text Node
+\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
+% Text Node
+\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
+% Text Node
+\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
+% Text Node
+\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};
+
+\end{tikzpicture}
+    \end{minipage}
+    \hspace{1em}
+    \begin{minipage}{0.45\textwidth}
+        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
+    \begin{equation*}
+        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
+    \end{equation*}
+
+    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
+    \end{minipage}
+\end{figure} 
+\end{frame}
+
+\begin{frame}
+
+    \textbf{Brief explaination}: We choose two momentum to be shifted oppositely 
+    \begin{equation*}
+        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
+    \end{equation*}
+    satisfying 
+    \begin{equation*}
+        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
+    \end{equation*}
+
+    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
+    \begin{equation*}
+        A_n \longrightarrow \hat{A}_n(z)
+    \end{equation*}
+    \pause
+    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane.
+    From Cauchy Theorem, we can ontain
+    \begin{equation*}
+        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
+\end{frame}
+
+\begin{frame}
+    From Cauchy Theorem, we can ontain
+    \begin{equation*}
+        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
+    \vspace{-1em}
+    \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=0.3\textwidth]{CT.png}
+    \end{figure}
+    \vspace{-1.5em}
+    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
+    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
+    \begin{equation*}
+        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+    \end{equation*}
+    This makes it easy to evaluate the residue at $z=z_I$
+    \begin{equation*}
+        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+\frametitle{Little group scaling}
+    \begin{itemize}
+        \item $\textbf{\text{Massless Case}}$\\
+    \begin{equation*}
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \end{equation*}
+    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
+    \begin{equation*}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
+    \end{equation*}
+    same for
+    \begin{equation*}
+        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+    \end{equation*}
+    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
+    \begin{equation*}
+        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
+    \end{equation*}
+    \end{itemize}
+\vspace{-2em}
+    \begin{itemize}
+    \item \textbf{Massive Case}\\
+    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{ On-shell 3-point can be completely determined}
+    \textbf{Another necessarity to introduce complex momentum}
+    If the momentum is complexed, we have 
+    \begin{equation*}
+        \avg{12}\neq[21]^*
+    \end{equation*}
+    Then we can obtain
+    \begin{equation*}
+        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
+    \end{equation*}
+    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
+    \begin{equation*}
+        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
+    \end{equation*}
+    Little group scaling tells us that
+    \begin{equation*}
+        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
+    \end{equation*}
+    We can obtain
+    \begin{equation*}
+        2h_1=-x_{12}-x_{13}
+    \end{equation*}
+    Similarly, we can also obtain
+    \begin{equation*}
+        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    Then all index can be solved from this system of equations, so that
+    \[
+    \boxed{
+    \begin{aligned}
+        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+        \quad & h_1+h_2+h_3 > 0
+    \end{aligned}
+        }
+    \]
+
+    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
+
+    \textbf{Example}: 3-gluon amplitude\\
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
+    \end{equation*}
+    There's another possibility 
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
+    \end{equation*}
+    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
+\end{frame}
+
+\begin{frame}{From Review to Applications}
+
+\begin{columns}[T]
+  % 左列：当前已完成
+  \begin{column}{0.48\textwidth}
+    \begin{block}{\centering\large \textbf{So far: Foundations}}
+      \begin{itemize}[left=1em]
+        \item Reviewed the structure of \textbf{BCFW recursion relation}
+        \item Applied to:
+          \begin{itemize}[left=0.1em]
+            \item \textbf{Pure Yang-Mills} theory
+            \item Tree-level MHV amplitudes
+            \item Color-ordered partial amplitudes
+          \end{itemize}
+      \end{itemize}
+    \end{block}
+  \end{column}
+\pause
+  % 右列：研究目标
+  \begin{column}{0.48\textwidth}
+    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
+      \begin{itemize}[left=1em]
+        \item Move beyond massless gauge theory
+        \item Consider:
+          \begin{itemize}[left=0.1em]
+            \item \textbf{(De)constructed gauge theories}
+          \end{itemize}
+        \item Key questions:
+          \begin{itemize}[left=0.1em]
+            \item Can BCFW still apply?
+            \item What new structures emerge?
+          \end{itemize}
+      \end{itemize}
+    \end{block}
+  \end{column}
+\end{columns}
+
+\end{frame}
+
+\section{Model and Computation}
+
+\begin{frame}{Introduction of (De)Constructed gauge theory}
+\vspace{1em}
+\begin{columns}[c]
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moose.png}
+
+    \column{0.14\textwidth}
+    \centering
+    \begin{tikzpicture}[scale=0.8]
+        \draw[->, line width=1pt] (0,0) -- (1.5,0)
+            node[midway, above] {\footnotesize Condensation}; % ← 加文字
+    \end{tikzpicture}
+
+    \column{0.43\textwidth}
+    \centering
+    \includegraphics[width=100pt]{Moosed.jpeg}
+\end{columns}
+
+\pause
+\raggedright
+The Lagrangian can be written like
+\begin{equation*}
+    \mathcal{L} = -\sum_{i=1}^{N} \frac{1}{2} \mathrm{Tr}(F_i^2)
+    + \sum_{i=1}^{N} \mathrm{Tr}\left[(D_\mu \Phi_i)^\dagger (D^\mu \Phi_i)\right],
+\end{equation*}
+here $F_i$ refers to the $i$th gauge field strength. The scalar field $\Phi_i$ transforms under the \textcolor{red}{bi-fundamental} representation, and the covariant derivative equals to
+\begin{equation*}
+    D_\mu \Phi_i = \partial_\mu \Phi_i - i g_i A_{i\mu} \Phi_i + i g_{i+1} \Phi_i A_{i+1\mu}.
+\end{equation*}
+
+\end{frame}
+
+\begin{frame}
+    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
+    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
+     \vspace{1em} % 图与文字之间的间距
+    \begin{center}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
+    \end{minipage}
+    \hspace{0.05\textwidth}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
+        \par\vspace{0.5em}
+    \end{minipage}
+    \end{center}
+    \pause
+    After higgsing the scalar field, we can obtain a spectrum
+    \begin{equation*}
+        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
+    \end{equation*}
+    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^1$ compactification. 
+\end{frame}
+
+\begin{frame}
+    \frametitle{Amplitudes from BCFW}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.5\textwidth]{2-site.png}
+    \end{figure}
+    \vspace{-1em}
+    \begin{equation*}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
+    \end{equation*}
+    From the Lagrangian, we have known that there are only two kinds of 3 point amplitude ($+,-:$ helicity\qquad $\Phi,\Phi^\dagger: \text{charge of scalar}$)
+    \begin{gather*}
+        A[1^\Phi2^{\Phi^\dagger}3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi2^{\Phi^\dagger}3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
+        A[3^+4^+5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-4^-5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
+    \end{gather*}
+    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
+\end{frame}
+\begin{frame}
+    \frametitle{Gauge boson sector}
+    \begin{itemize}
+        \item n$ V_1$ or n$V_2$\\
+        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
+        existing results.
+        \begin{equation*}
+            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots i^-\cdots j^-\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
+        \end{equation*}
+        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{SQCD like sector}
+    The amplitudes can be computed like 
+    \begin{itemize}
+        \item $\Phi^\dagger V_1V_1\Phi$
+        \begin{align*}
+            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
+        \end{align*}
+        \item $\Phi^\dagger V_1V_1V_1\Phi$
+            \begin{equation*}
+                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
+            \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item $\Phi^\dagger (nV_1)\Phi$
+            \begin{equation*}
+                A[1^\Phi2^{\Phi^\dagger}\cdots(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
+            \end{equation*}
+            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
+                A[1^\Phi2^{\Phi^\dagger}3^+4^+]=0\quad \Rightarrow  \quad A[1^\Phi2^{\Phi^\dagger}3^+\cdots n^+]=0 \end{equation*}}
+        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pure 2-site amplitude}
+    \begin{itemize}
+        \item $\Phi V_2 \Phi^\dagger V_1$
+        \begin{equation*}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
+        \end{equation*}
+        \item $\Phi V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
+        \end{equation*}
+        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
+        \begin{equation*}
+            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
+        \end{equation*}       
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    Here I show the concrete computation process 
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{6pt.eps}
+    \end{figure}
+    \vspace{-1em}
+    \begin{align*}
+    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
+    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
+    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
+    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
+    \end{align*}
+\end{frame}
+\begin{frame}
+    \begin{itemize}
+        \item Compact formula for general case
+        \begin{equation*}
+            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
+        \end{equation*} 
+        \begin{minipage}{0.7\textwidth}
+            \raggedright  % 或者 \centering 或 \raggedleft
+            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
+            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
+            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
+            $\star$: \,Order for gauge group 1\\
+            $\ast$: \,Order for gauge group 2 
+            \end{minipage}
+
+    \end{itemize}
+    \pause
+    For example, if we want to compute $A[1^\Phi2^{\Phi^\dagger}5_1^+3_1^+4_1^-7_2^+6_2^+8_2^+]$:
+    \begin{equation*}
+        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
+    \end{equation*}
+    If you use Feynman diagrams, it may take sevral days to accomplish the computation.
+\end{frame}
+\section{Some problems and extends}
+\begin{frame}
+    \frametitle{How about NMHV?}
+    First, let us review the NMHV amplitudes for gluon scattering.
+
+    Still we begin with the simplest case -- \textbf{Split-helicity} NMHV like \mbox{\( A_6[1^-\, 2^-\, 3^-\, 4^+\, 5^+\, 6^+] \)}.%
+
+    Here we choose $[1,2\rangle$ shift
+\vspace{-1em}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\textwidth]{6ptNMHV.png}
+\end{figure}
+\pause
+\begin{itemize}
+    \item Diagram B includes a propagator $1/P_{156}^2$, so there is a 3-particle pole $P_{156}^2=0$. But by inspecting the external order,
+    it seems that there's no difference between $(-++)$ channel 561 and 345. We should expect the amplitude to have a pole also at 
+    $P_{345}^2=0$. 
+    \begin{equation*}
+        \text{diagram A}=\frac{\avg{\hat{1}\hat{P}_{16}}^3}{\avg{\hat{P}_{16}6}\avg{6\hat{1}}}\times\frac{1}{P_{16}^2}\times\frac{\avg{\hat{2}3}^3}{\mdavg{34}{45}\!\mdavg{5\hat{P}_{16}}{\hat{P}_{16}2}}
+    \end{equation*}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+    \item[] $$\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3} = \avg{21}[\hat{1}3] + \avg{\hat{2}6}[63]$$
+    It follows from $\hat{P}_{16}^2=0$ that $z_{16}=-\frac{[16]}{[26]}$, so
+    \[
+\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3}
+= -\frac{[36]}{[26]}
+\left( \avg{12}[12] + \avg{16}[16] + \avg{26}[26] \right)
+= -\frac{[36]}{[26]} P_{126}^2
+\]
+\textcolor{red}{The 3-particle pole $P_{126}^2$ is encoded inside the BCFW channel !}
+    \item Full expression 
+    \begin{align*}
+        A_6[1^-\,2^-\,3^-\,4^+\,5^+\,6^+] =&
+        \frac{ \langle 3|1+2|6]^3}{P_{126}^2 [21][16] \langle 34 \rangle \langle 45 \rangle \langle 5|1+6|2]}\\
+        &+\frac{ \langle 1|5+6|4]^3}{P_{156}^2 [23][34] \langle 56 \rangle \langle 61 \rangle \langle 5|1+6|2]}.
+    \end{align*}
+    The factor $\langle 5|1+6|2]$ does not correspond to a physical pole of the scattering amplitude: it is a \textbf{spurious pole}.
+    %You will also note that there is a strange denominator-factor $\langle 5|1+6|2]$ in the result from each BCFW diagram. 
+    %It is typical that BCFW packs the information of the amplitudes into compact
+    %expressions, but the cost is the appearance of spurious poles; this means that in the BCFW
+    %representation the locality of the underlying field theory is not manifest.
+    %The spurious pole should cancel in the sum of the two BCFW diagrams.
+
+    There has been interesting paper investigating how to systematically cancel the spurious poles,
+    like "A. Hodges, JHEP 1305, 35 (2013) [arXiv:0905.1473 [hep-th]]." 
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{itemize}
+        \item We utilize the $[1,2\rangle$ shift before, what happens if we change to $[2,1\rangle$ shift?
+    \end{itemize}
+    \begin{figure}
+            \centering
+            \includegraphics[width=1\textwidth]{6ptNMHV2.png}
+        \end{figure}
+    \begin{itemize}
+        \item[] diagram A' = $\mathrm{anti\text{-}MHV} \times \mathrm{NMHV}$, as opposed to diagram A = $\mathrm{MHV}\times \mathrm{MHV}$. 
+        \vspace{1em}
+
+        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
+        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
+    \end{itemize}
+\end{frame}
+\begin{frame}
+    \frametitle{CSW(Cachazo-Svrcek-Witten) expansion}
+    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
+    \begin{equation*}
+        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
+    \end{equation*}
+    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
+    %Here we consider the situation where all $c_i\neq 0$, so that all momentum are shifted, called all-line shift.
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.7\textwidth]{NMHV.png}
+    \end{figure}
+    There are two possibilities: $\mathrm{anti\text{-}MHV_3}(=0)\times \mathrm{NMHV}$ ~or~ $\mathrm{MHV}\times\mathrm{MHV}$.
+\end{frame}
+
+\begin{frame}
+    For example, the 6pt split NMHV amplitude
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\textwidth]{6ptSpNMHV.png}
+    \end{figure}
+
+    \begin{minipage}{0.33\textwidth}
+    \centering
+    \includegraphics[width=1\textwidth]{exNMHV.png}
+\end{minipage}
+\hfill
+\begin{minipage}{0.66\textwidth}
+    \centering
+    \[
+    = \frac{\avg{1\hat{P}_I}^4}{\avg{1\hat{P}_I} \avg{\hat{P}_I 5} \avg{56} \avg{61}}
+    \frac{1}{P_{156}^2}
+    \frac{\avg{23}^4}{\avg{23} \avg{34} \avg{4\hat{P}_I} \avg{\hat{P}_I 2}} \,.
+    \]
+\end{minipage}
+\pause
+
+We can write 
+\begin{equation*}
+    \aket{\hat{P}_I}\frac{[\hat{P}_IX]}{[\hat{P}_IX]}=\hat{P}_I\sket{X}\frac{1}{[\hat{P}_IX]}=P_I\sket{X}\frac{1}{[\hat{P}_IX]}
+\end{equation*}
+\end{frame}
+\begin{frame}
+    We can use the prescription
+    \begin{equation*}
+        \aket{\hat{P}_I}\rightarrow P_I \sket{X}
+    \end{equation*}
+    \begin{minipage}{0.38\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{FinalNMHV.png}
+\end{minipage}
+\hfill
+\begin{minipage}{0.62\textwidth}
+    \centering
+    \[
+= \frac{\langle 1|P_{156}|X]^4}{\langle 1|P_{156}|X] \langle 5|P_{156}|X] \langle 56\rangle \langle 61\rangle}
+\cdot \frac{1}{P_{156}^2}
+\cdot \frac{\langle 23\rangle^4}{\langle 23\rangle \langle 34\rangle \langle 4|P_{156}|X] \langle 2|P_{156}|X]} \,.
+\]
+
+\end{minipage}
+
+\end{frame}
+
+\section{Summary}
+\begin{frame}
+    \frametitle{Summary}
+    \begin{itemize}
+        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
+        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
+        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
+    \end{itemize}
+\end{frame}
+\begin{frame} 
+    \centering
+    \Huge Thanks for your attention!
+\end{frame} 
+\appendix
+\begin{frame}{Spinor-Helicity Formalism}
+    \hypertarget{helicity}{}
+\begin{block}{Helicity}
+\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
+\[
+h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
+\]
+\end{block}
+\pause
+% 文本说明（点击1出现）
+\only<1->{
+S-matrix is a function of momentum $p_i$ and helicity $h_i$
+}
+
+\vspace{0.8em}
+
+% TikZ 图（点击1显示公式，点击2后补图形）
+\begin{center}
+\tikzset{every picture/.style={line width=0.75pt}}        
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+
+  % 点击1：显示公式
+  \only<1>{
+    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
+          {$\mathcal{M}( p_{i} ,h_{i})$};
+  }
+
+  % 点击2及后：公式 + 圈箭头
+  \only<2->{
+    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
+          {$\mathcal{M}( p_{i} ,\textcolor{red}{h_{i}})$};
+
+    % 圆圈
+    \draw  [color=red, draw opacity=1] 
+      (302.8,146.93) .. controls (302.81,142.78) and (306.18,139.44) .. (310.32,139.45)
+      .. controls (314.47,139.46) and (317.81,142.83) .. (317.8,146.97)
+      .. controls (317.79,151.11) and (314.42,154.46) .. (310.28,154.45)
+      .. controls (306.14,154.44) and (302.79,151.07) .. (302.8,146.93) -- cycle;
+
+    % 箭头
+    \draw [color=red, draw opacity=1] 
+      (310.28,154.45) -- (296.03,178.04);
+    \draw [shift={(295,179.75)}, rotate=301.13, color=red, draw opacity=1][line width=0.75pt] 
+      (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0)
+      .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29);
+
+    % 注释文字
+    \draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  
+      [font=\small,color=red,opacity=1] [align=left] 
+      {How can we catch the information of helicity?};
+  }
+
+\end{tikzpicture}
+\end{center}
+
+% 点击3：Massless Case（用 uncover 保持排版稳定）
+\uncover<3->{
+\vspace{-1em}
+\textbf{Massless Case:}
+\begin{itemize}
+  \item Momenta in spinor form:
+    \[
+      p_{\mu}\sigma^{\mu} = p_{\alpha\dot{\alpha}} = p_\alpha \tilde{p}_{\dot{\alpha}} = \aket{p}[p|
+    \]
+\end{itemize}
+}
+
+\end{frame}
+
+\begin{frame}
+    \frametitle{Large z behavior}
+    In the BCFW formula, the boundary term $B_n$ affects a lot
+    \begin{equation*}
+        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
+    \begin{equation*}
+        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
+    \end{equation*}
+    Here I show the large z behavior for gluon scattering 
+    \begin{center}
+        \begin{tabular}{lrc}
+            \toprule
+            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
+            \midrule
+            $+$ & $1/z$ & $z^3$ \\
+            $-$ & $1/z$ & $1/z$ \\
+            \bottomrule
+          \end{tabular}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+        \textbf{On-shell 3-point for real momentum}
+
+    Because of the constrain from momentum conservation and on-shell condition
+    \begin{equation*}
+        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
+    \end{equation*}
+    All of the contribution 
+    \begin{equation*}
+        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
+    \end{equation*}
+    In terms of Spinor- Helicity variable, we have 
+    \begin{equation*}
+        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
+    \end{equation*}
+    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}
+
+    Of coure, you can introduce non-minimal interaction
+    \begin{equation*}
+        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
+    \end{equation*}
+    but it still equals to 0 under the on-shell condition.
+\end{frame}
+
+\begin{frame}
+    \frametitle{ On-shell 3-point can be completely determined}
+    For the complex momentum, we have 
+    \begin{equation*}
+        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
+    \end{equation*}
+    \[
+    \boxed{
+    \begin{aligned}
+        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
+        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
+        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
+        \quad & h_1+h_2+h_3 > 0
+    \end{aligned}
+        }
+    \]
+
+    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
+
+    \textbf{Example}: 3-gluon amplitude\\
+    \begin{equation*}
+        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Scattering Amplitudes from BCFW}
+    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
+    \begin{equation*}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
+    \end{equation*}
+We only foucus on the following amplitudes:
+\begin{equation*}
+    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
+\end{equation*}
+here n can be any positive integer.
+\end{frame}
+
+\begin{frame}
     More specifically, it helps us to prove P. T. formula
@@
 \end{frame}
-\begin{frame}
-\frametitle{Spinor-helicity formalism}
-    \begin{itemize}
-        \item $\textbf{\text{Massless Case}}$\\
-    \begin{equation*}
-        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
-    \end{equation*}
-    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
-    \begin{equation*}
-        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
-    \end{equation*}
-    same for
-    \begin{equation*}
-        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
-    \end{equation*}
-    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
-    \begin{equation*}
-        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
-    \end{equation*}
-    \end{itemize}
-\vspace{-2em}
-    \begin{itemize}
-    \item \textbf{Massive Case}\\
-    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{ On-shell 3-point can be completely determined}
-    \textbf{On-shell 3-point for real momentum}
-
-    Because of the constrain from momentum conservation and on-shell condition
-    \begin{equation*}
-        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
-    \end{equation*}
-    All of the contribution 
-    \begin{equation*}
-        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
-    \end{equation*}
-    In terms of Spinor- Helicity variable, we have 
-    \begin{equation*}
-        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
-    \end{equation*}
-    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}
-
-    Of coure, you can introduce non-minimal interaction
-    \begin{equation*}
-        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
-    \end{equation*}
-    but it still equals to 0 under the on-shell condition.
-\end{frame}
-
-\begin{frame}
-    \textbf{Another necessarity to introduce complex momentum}
-
-    If the momentum is complexed, we have 
-    \begin{equation*}
-        \avg{12}\neq[21]^*
-    \end{equation*}
-    Then we can obtain
-    \begin{equation*}
-        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
-    \end{equation*}
-    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
-    \begin{equation*}
-        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
-    \end{equation*}
-    Little group scaling tells us that
-    \begin{equation*}
-        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
-    \end{equation*}
-    We can obtain
-    \begin{equation*}
-        2h_1=-x_{12}-x_{13}
-    \end{equation*}
-    Similarly, we can also obtain
-    \begin{equation*}
-        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    Then all index can be solved from this system of equations, so that
-    \[
-    \boxed{
-    \begin{aligned}
-        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
-        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
-        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
-        \quad & h_1+h_2+h_3 > 0
-    \end{aligned}
-        }
-    \]
-
-    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
-
-    \textbf{Example}: 3-gluon amplitude\\
-    \begin{equation*}
-        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
-    \end{equation*}
-    There's another possibility 
-    \begin{equation*}
-        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
-    \end{equation*}
-    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
-\end{frame}
-
-\begin{frame}{From Review to Applications}
-
-\begin{columns}[T]
-  % 左列：当前已完成
-  \begin{column}{0.48\textwidth}
-    \begin{block}{\centering\large \textbf{So far: Foundations}}
-      \begin{itemize}[left=1em]
-        \item Reviewed the structure of \textbf{BCFW recursion relation}
-        \item Applied to:
-          \begin{itemize}[left=0.1em]
-            \item \textbf{Pure Yang-Mills} theory
-            \item Tree-level MHV amplitudes
-            \item Color-ordered partial amplitudes
-          \end{itemize}
-      \end{itemize}
-    \end{block}
-  \end{column}
-\pause
-  % 右列：研究目标
-  \begin{column}{0.48\textwidth}
-    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
-      \begin{itemize}[left=1em]
-        \item Move beyond massless gauge theory
-        \item Consider:
-          \begin{itemize}[left=0.1em]
-            \item \textbf{(De)constructed gauge theories}
-          \end{itemize}
-        \item Key questions:
-          \begin{itemize}[left=0.1em]
-            \item Can BCFW still apply?
-            \item What new structures emerge?
-          \end{itemize}
-      \end{itemize}
-    \end{block}
-  \end{column}
-\end{columns}
-
-\end{frame}
-
-\section{Model and Computation}
-
-\begin{frame}{Introduction of (De)Constructed gauge theory}
-\vspace{1em}
-\begin{columns}[c]
-    \column{0.43\textwidth}
-    \centering
-    \includegraphics[width=100pt]{Moose.png}
-
-    \column{0.14\textwidth}
-    \centering
-    \begin{tikzpicture}[scale=0.8]
-        \draw[->, line width=1pt] (0,0) -- (1.5,0)
-            node[midway, above] {\footnotesize Condensation}; % ← 加文字
-    \end{tikzpicture}
-
-    \column{0.43\textwidth}
-    \centering
-    \includegraphics[width=100pt]{Moosed.jpeg}
-\end{columns}
-
-\pause
-\raggedright
-The Lagrangian can be written like
-\begin{equation*}
-    \mathcal{L} = -\sum_{i=1}^{N} \frac{1}{2} \mathrm{Tr}(F_i^2)
-    + \sum_{i=1}^{N} \mathrm{Tr}\left[(D_\mu \Phi_i)^\dagger (D^\mu \Phi_i)\right],
-\end{equation*}
-here $F_i$ refers to the $i$th gauge field strength. The scalar field $\Phi_i$ transforms under the \textcolor{red}{bi-fundamental} representation, and the covariant derivative equals to
-\begin{equation*}
-    D_\mu \Phi_i = \partial_\mu \Phi_i - i g_i A_{i\mu} \Phi_i + i g_{i+1} \Phi_i A_{i+1\mu}.
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}
-    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
-    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
-     \vspace{1em} % 图与文字之间的间距
-    \begin{center}
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
-        \par\vspace{0.5em}
-    \end{minipage}
-    \hspace{0.05\textwidth}
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
-        \par\vspace{0.5em}
-    \end{minipage}
-    \end{center}
-    \pause
-    After higgsing the scalar field, we can obtain a spectrum
-    \begin{equation*}
-        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
-    \end{equation*}
-    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^1$ compactification. 
-\end{frame}
-
-\begin{frame}
-    \frametitle{Amplitudes from BCFW}
-    \begin{figure}
-        \centering
-        \includegraphics[width=0.5\textwidth]{2-site.png}
-    \end{figure}
-    \vspace{-1em}
-    \begin{equation*}
-        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
-    \end{equation*}
-    From the Lagrangian, we have known that there are only two kinds of 3 point amplitude ($+,-:$ helicity\qquad $\Phi,\Phi^\dagger: \text{charge of scalar}$)
-    \begin{gather*}
-        A[1^\Phi2^{\Phi^\dagger}3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi2^{\Phi^\dagger}3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
-        A[3^+4^+5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-4^-5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
-    \end{gather*}
-    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
-\end{frame}
-\begin{frame}
-    \frametitle{Gauge boson sector}
-    \begin{itemize}
-        \item n$ V_1$ or n$V_2$\\
-        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
-        existing results.
-        \begin{equation*}
-            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots i^-\cdots j^-\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
-        \end{equation*}
-        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{SQCD like sector}
-    The amplitudes can be computed like 
-    \begin{itemize}
-        \item $\Phi^\dagger V_1V_1\Phi$
-        \begin{align*}
-            A[1^\Phi2^{\Phi^\dagger}3^+4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
-        \end{align*}
-        \item $\Phi^\dagger V_1V_1V_1\Phi$
-            \begin{equation*}
-                A[1^\Phi2^{\Phi^\dagger}3^+4^+5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
-            \end{equation*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item $\Phi^\dagger (nV_1)\Phi$
-            \begin{equation*}
-                A[1^\Phi2^{\Phi^\dagger}\cdots(n+2)^-]=(-1)^{n+1}\frac{\avg{1,n+2}^2\avg{2,n+2}^2}{\mdavg{12}{23}\cdots\mdavg{n+1,n+2}{n+2,1}}
-            \end{equation*}
-            \textcolor{red}{$\star$ Bonus relation: \begin{equation*}
-                A[1^\Phi2^{\Phi^\dagger}3^+4^+]=0\quad \Rightarrow  \quad A[1^\Phi2^{\Phi^\dagger}3^+\cdots n^+]=0 \end{equation*}}
-        For the amplitude $\Phi (nV_2)\Phi^\dagger$, we can obtain nearly the same expression.
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pure 2-site amplitude}
-    \begin{itemize}
-        \item $\Phi V_2 \Phi^\dagger V_1$
-        \begin{equation*}
-            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
-        \end{equation*}
-        \item $\Phi V_2 \Phi^\dagger V_1V_1$
-        \begin{equation*}
-            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
-        \end{equation*}
-        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
-        \begin{equation*}
-            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
-        \end{equation*}       
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item Compact formula for general case
-        \begin{equation*}
-            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
-        \end{equation*} 
-        \begin{minipage}{0.7\textwidth}
-            \raggedright  % 或者 \centering 或 \raggedleft
-            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
-            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
-            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
-            $\star$: \,Order for gauge group 1\\
-            $\ast$: \,Order for gauge group 2 
-            \end{minipage}
-
-    \end{itemize}
-    \pause
-    For example, if we want to compute $A[1^\Phi2^{\Phi^\dagger}5_1^+3_1^+4_1^-7_2^+6_2^+8_2^+]$:
-    \begin{equation*}
-        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
-    \end{equation*}
-    If you use Feynman diagrams, it may take sevral days to accomplish the computation.
-\end{frame}
-\section{Some problems and extends}
-\begin{frame}
-    \frametitle{How about NMHV?}
-    First, let us review the NMHV amplitudes for gluon scattering.
-
-    Still we begin with the simplest case -- \textbf{Split-helicity} NMHV like \mbox{\( A_6[1^-\, 2^-\, 3^-\, 4^+\, 5^+\, 6^+] \)}.%
-
-    Here we choose $[1,2\rangle$ shift
-\vspace{-1em}
-\begin{figure}
-    \centering
-    \includegraphics[width=1\textwidth]{6ptNMHV.png}
-\end{figure}
-\pause
-\begin{itemize}
-    \item Diagram B includes a propagator $1/P_{156}^2$, so there is a 3-particle pole $P_{156}^2=0$. But by inspecting the external order,
-    it seems that there's no difference between $(-++)$ channel 561 and 345. We should expect the amplitude to have a pole also at 
-    $P_{345}^2=0$. 
-    \begin{equation*}
-        \text{diagram A}=\frac{\avg{\hat{1}\hat{P}_{16}}^3}{\avg{\hat{P}_{16}6}\avg{6\hat{1}}}\times\frac{1}{P_{16}^2}\times\frac{\avg{\hat{2}3}^3}{\mdavg{34}{45}\!\mdavg{5\hat{P}_{16}}{\hat{P}_{16}2}}
-    \end{equation*}
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-    \item[] $$\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3} = \avg{21}[\hat{1}3] + \avg{\hat{2}6}[63]$$
-    It follows from $\hat{P}_{16}^2=0$ that $z_{16}=-\frac{[16]}{[26]}$, so
-    \[
-\cbrak{\hat{2} \hat{P}_{16}}{\hat{P}_{16} 3}
-= -\frac{[36]}{[26]}
-\left( \avg{12}[12] + \avg{16}[16] + \avg{26}[26] \right)
-= -\frac{[36]}{[26]} P_{126}^2
-\]
-\textcolor{red}{The 3-particle pole $P_{126}^2$ is encoded inside the BCFW channel !}
-    \item Full expression 
-    \begin{align*}
-        A_6[1^-\,2^-\,3^-\,4^+\,5^+\,6^+] =&
-        \frac{ \langle 3|1+2|6]^3}{P_{126}^2 [21][16] \langle 34 \rangle \langle 45 \rangle \langle 5|1+6|2]}\\
-        &+\frac{ \langle 1|5+6|4]^3}{P_{156}^2 [23][34] \langle 56 \rangle \langle 61 \rangle \langle 5|1+6|2]}.
-    \end{align*}
-    The factor $\langle 5|1+6|2]$ does not correspond to a physical pole of the scattering amplitude: it is a \textbf{spurious pole}.
-    %You will also note that there is a strange denominator-factor $\langle 5|1+6|2]$ in the result from each BCFW diagram. 
-    %It is typical that BCFW packs the information of the amplitudes into compact
-    %expressions, but the cost is the appearance of spurious poles; this means that in the BCFW
-    %representation the locality of the underlying field theory is not manifest.
-    %The spurious pole should cancel in the sum of the two BCFW diagrams.
-
-    There has been interesting paper investigating how to systematically cancel the spurious poles,
-    like "A. Hodges, JHEP 1305, 35 (2013) [arXiv:0905.1473 [hep-th]]." 
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \begin{itemize}
-        \item We utilize the $[1,2\rangle$ shift before, what happens if we change to $[2,1\rangle$ shift?
-    \end{itemize}
-    \begin{figure}
-            \centering
-            \includegraphics[width=1\textwidth]{6ptNMHV2.png}
-        \end{figure}
-    \begin{itemize}
-        \item[] diagram A' = $\mathrm{anti\text{-}MHV} \times \mathrm{NMHV}$, as opposed to diagram A = $\mathrm{MHV}\times \mathrm{MHV}$. 
-        \vspace{1em}
-
-        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
-        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
-    \end{itemize}
-\end{frame}
-\begin{frame}
-    \frametitle{CSW expansion}
-    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
-    \begin{equation*}
-        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
-    \end{equation*}
-    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
-
-\end{frame}
-
-\section{Summary}
-\begin{frame}
-    \frametitle{Summary}
-    \begin{itemize}
-        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
-        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
-        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
-    \end{itemize}
-\end{frame}
-\begin{frame} 
-    \centering
-    \Huge Thanks for your attention!
-\end{frame} 
-\appendix
-\begin{frame}{Spinor-Helicity Formalism}
-    \hypertarget{helicity}{}
-\begin{block}{Helicity}
-\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
-\[
-h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
-\]
-\end{block}
-\pause
-% 文本说明（点击1出现）
-\only<1->{
-S-matrix is a function of momentum $p_i$ and helicity $h_i$
-}
-
-\vspace{0.8em}
-
-% TikZ 图（点击1显示公式，点击2后补图形）
-\begin{center}
-\tikzset{every picture/.style={line width=0.75pt}}        
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-
-  % 点击1：显示公式
-  \only<1>{
-    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
-          {$\mathcal{M}( p_{i} ,h_{i})$};
-  }
-
-  % 点击2及后：公式 + 圈箭头
-  \only<2->{
-    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
-          {$\mathcal{M}( p_{i} ,\textcolor{red}{h_{i}})$};
-
-    % 圆圈
-    \draw  [color=red, draw opacity=1] 
-      (302.8,146.93) .. controls (302.81,142.78) and (306.18,139.44) .. (310.32,139.45)
-      .. controls (314.47,139.46) and (317.81,142.83) .. (317.8,146.97)
-      .. controls (317.79,151.11) and (314.42,154.46) .. (310.28,154.45)
-      .. controls (306.14,154.44) and (302.79,151.07) .. (302.8,146.93) -- cycle;
-
-    % 箭头
-    \draw [color=red, draw opacity=1] 
-      (310.28,154.45) -- (296.03,178.04);
-    \draw [shift={(295,179.75)}, rotate=301.13, color=red, draw opacity=1][line width=0.75pt] 
-      (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0)
-      .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29);
-
-    % 注释文字
-    \draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  
-      [font=\small,color=red,opacity=1] [align=left] 
-      {How can we catch the information of helicity?};
-  }
-
-\end{tikzpicture}
-\end{center}
-
-% 点击3：Massless Case（用 uncover 保持排版稳定）
-\uncover<3->{
-\vspace{-1em}
-\textbf{Massless Case:}
-\begin{itemize}
-  \item Momenta in spinor form:
-    \[
-      p_{\mu}\sigma^{\mu} = p_{\alpha\dot{\alpha}} = p_\alpha \tilde{p}_{\dot{\alpha}} = \aket{p}[p|
-    \]
-\end{itemize}
-}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Large z behavior}
-    In the BCFW formula, the boundary term $B_n$ affects a lot
-    \begin{equation*}
-        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
-    \begin{equation*}
-        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
-    \end{equation*}
-    Here I show the large z behavior for gluon scattering 
-    \begin{center}
-        \begin{tabular}{lrc}
-            \toprule
-            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
-            \midrule
-            $+$ & $1/z$ & $z^3$ \\
-            $-$ & $1/z$ & $1/z$ \\
-            \bottomrule
-          \end{tabular}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{ On-shell 3-point can be completely determined}
-    For the complex momentum, we have 
-    \begin{equation*}
-        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
-    \end{equation*}
-    \[
-    \boxed{
-    \begin{aligned}
-        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
-        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
-        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
-        \quad & h_1+h_2+h_3 > 0
-    \end{aligned}
-        }
-    \]
-
-    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}
-
-    \textbf{Example}: 3-gluon amplitude\\
-    \begin{equation*}
-        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Scattering Amplitudes from BCFW}
-    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
-    \begin{equation*}
-        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
-    \end{equation*}
-We only foucus on the following amplitudes:
-\begin{equation*}
-    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
-\end{equation*}
-here n can be any positive integer.
-\end{frame}
 

### 2025-06-24 2nd report/2report.tex
New

@@
     \end{align*}
-    \pause
     \vspace{-3em}
     \hypertarget{conv}{}
-    \begin{gather*}
-    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]= 
-    \frac{\langle 1 2 \rangle^4}
-         {\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle45 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trivial one})\\[1em]
-    (p_{i\mu} \sigma^\mu)_{\alpha\dot{\alpha}}=(\aket{p_i})_\alpha([p_i|)_{\dot{\alpha}},\quad \aket{p_i}=\aket{i}\\
-    \quad \sigma^\mu=(1,\vec{\sigma}),\quad \aket{i},\sket{i}: \text{Weyl Spinors}\\
-    \avg{ij}=\langle i |^\alpha \aket{j}_\alpha=\varepsilon^{\alpha\beta}\aket{i}_\beta\aket{j}_\alpha,\quad \varepsilon^{\alpha\beta}: \text{antisymmetric tensor}
-    \end{gather*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Modern Amplitude Method} 
- The answer is On-shell method.
-    \begin{center}
-
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Straight Lines [id:da5445374886882226] 
-\draw    (276.25,137) -- (457.5,136.26) ;
-\draw [shift={(459.5,136.25)}, rotate = 179.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-
-% Text Node
-\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
-% Text Node
-\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
-% Text Node
-\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
-\end{tikzpicture}
-\end{center}
-\vspace{-1em}
-    % 右侧：PT表达式
-    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
-    \begin{gather*}
-        {A_5[1^+2^+3^+4^+5^+]=0}\\
-        {A_5[1^-2^+3^+4^+5^+]=0}\\
-        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
-    \end{gather*}
-    \vspace{-3em}
+    \pause
     \begin{gather*}
@@
     \end{gather*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Color-ordering for Yang-Mills}
+    Consider the Yang-Mills lagrangian
+    \begin{equation*}
+        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_{\mu\nu}F^{\mu\nu})
+    \end{equation*}
+    The 3 point and 4 point vertices include $\tilde{f}^{abc}$ and $\tilde{f}^{abe}\tilde{f}^{cde}+\text{perms}$.
+
+    (With a different convention,$\textrm{Tr}[T^aT^b]=\delta^{ab}$ and $[T^a,T^b]=i\tilde{f}^{abc}T^c$)
+
+    We have 
+    \begin{equation*}
+        c_s=\tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4},\quad c_t=\tilde{f}^{a_4a_1b}\tilde{f}^{ba_2a_3},\quad c_u=\tilde{f}^{a_1a_3b}\tilde{f}^{ba_2a_4}
+    \end{equation*}
+    and the color factor can be rewritten by the trace of product of generators
+    \begin{equation*}
+        i\tilde{f}^{abc}=\mathrm{Tr}([T^a,T^b]T^c),
+    \end{equation*}
+    Moreover, in $SU(N)$, we have a Fierz identity
+    \begin{equation}
+        \sum_{a}T^a_{ij}T^a_{kl}=\delta_{il}\delta_{kj}-\frac{1}{N}\delta_{ij}\delta_{kl}.
+    \end{equation}
+\end{frame}
+
+\begin{frame}
+    This identity is easier understood as matrix form like 
+    \begin{align*}
+    \mathrm{Tr}\{T^aA\}\mathrm{Tr}\{T^aB\}=\mathrm{Tr}\{AB\}-\frac{1}{N}\mathrm{Tr}\{A\}\mathrm{Tr}\{B\},\\
+    \mathrm{Tr}\{AT^aBT^a\}=\mathrm{Tr}\{A\}\mathrm{Tr}\{B\}-\frac{1}{N}\mathrm{Tr}\{AB\}.
+    \end{align*}
+    So, the 4 gluon s-channel gives us
+    \begin{align*}
+        \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}T^{a_4})\\
+        -\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}T^{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}T^{a_3}).
+    \end{align*}
+    Therefore, the full 4-point amplitude can be rewritten like
+    \begin{equation*}
+        \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})+\text{perms of } (234) )
+    \end{equation*}
+    here the subamplitudes $A_4[1234],A_4[1243]$, etc. are called \textbf{color-ordered ampltitudes}. This concept can be easily generalized to tree-level n-point case
+    \begin{equation*}
+        \textcolor{red}{\mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})}
+    \end{equation*}
 \end{frame}
@@
     \begin{equation*}
-        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
-    \end{equation*}
+        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\frac{(z-z_I)z_I}{z(z-z_I)}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Large z behavior}
+    In the BCFW formula, the boundary term $B_n$ affects a lot
+    \begin{equation*}
+        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
+    \end{equation*}
+    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
+    \begin{equation*}
+        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
+    \end{equation*}
+    Here I show the large z behavior for gluon scattering 
+    \begin{center}
+        \begin{tabular}{lrc}
+            \toprule
+            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
+            \midrule
+            $+$ & $1/z$ & $z^3$ \\
+            $-$ & $1/z$ & $1/z$ \\
+            \bottomrule
+          \end{tabular}
+    \end{center}
+    proved by using background field expansion ~\textcolor{green}{(N.~Arkani-Hamed and J.~Kaplan,
+%``On Tree Amplitudes in Gauge Theory and Gravity,''
+[arXiv:0801.2385 [hep-th]].)}
 \end{frame}
@@
     \frametitle{SQCD like sector}
+    The color factor in this sector looks like
+    \begin{equation*}
+        (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
+    \end{equation*}
+    so we we need to notice is just the order of gauge boson.
+
     The amplitudes can be computed like 
@@
     \frametitle{Pure 2-site amplitude}
+    The straightforward way to observe the color structure in this case  is double line notation as follows 
+        \vspace{-0.8em}
+    \begin{center}
+        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+        \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=0.8,xscale=0.8]
+
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Straight Lines [id:da7604191870446242] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
+%Straight Lines [id:da7895005569652712] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
+%Straight Lines [id:da19217218880843812] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
+%Straight Lines [id:da7866299736623521] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
+%Straight Lines [id:da5667542352395977] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
+%Straight Lines [id:da33701635654582174] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
+%Straight Lines [id:da7076492571881566] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
+%Straight Lines [id:da3803886589182971] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
+%Straight Lines [id:da696489944746132] 
+\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
+%Straight Lines [id:da24340791537710427] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
+%Straight Lines [id:da7298898466192736] 
+\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
+%Straight Lines [id:da3460055698725] 
+\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
+\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
+%Straight Lines [id:da4507056480848969] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
+%Straight Lines [id:da6544383915955476] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
+%Straight Lines [id:da03624471669725382] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
+%Straight Lines [id:da34280653261510274] 
+\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
+\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;
+
+% Text Node
+\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+% Text Node
+\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
+% Text Node
+\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
+
+        \end{tikzpicture}
+    \end{center}
     \begin{itemize}
@@
             A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
-        \end{equation*}
-        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
-        \begin{equation*}
-            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^+6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
         \end{equation*}  
@@
 
-        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
-        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
+        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem} \textcolor{green}{(N.
+Arkani-Hamed, F.
+Cachazo, C.
+Cheung, and J.
+Kaplan, [arXiv:0907.5418 [hep-th]].)} \textcolor{red}{and Grassmannian.}
     \end{itemize}

### 2025-06-24 2nd report/2report.tex
New

@@
       \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
-      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
+      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or holographic principle (celestial duality).
     \end{itemize}
@@
     \end{center}
+    The color factor here have special form like
+    \begin{equation*}
+         (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
+    \end{equation*}
+     we can notice that the relative order between two gauge group do not affect the color structure, but the
+    order inside the gauge group matters.
+\end{frame}
+
+\begin{frame}
+    So we introduce the \textbf{OPP (Order Preserving Permutation)}
     \begin{itemize}
@@
 \end{frame}
-
 \begin{frame}

### 2025-06-25 2nd report/2report.tex
New

@@
 \usepackage{cancel}
+\usepackage{newtxtext,newtxmath}
 \usetikzlibrary{calc}
@@
 \author[Su Yingze]{
-  \textbf{Su Yingze}\\[0.2em]
-  \small Supervisor: \tif{Prof. Tanabashi Masaharu}
+  \textbf{Su Yingze}
 }
@@
 \institute[E Lab]{
-  \normalsize Theoretical Elementary Particle Physics Laboratory\\[-0.3em]
-  Nagoya University
+  \normalsize E Lab, Nagoya University
 }
 
-\date[$11^{\text{th}}$ June]{June 11th, 2025}
+\date[$1^{\text{st}}$ July]{July 1st, 2025}
 
@@
 \begin{frame}
+    \frametitle{Analyticity}
+    Amplitudes are analytic functions
+    \begin{itemize}
+        \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
+        \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
+        \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
+\end{itemize}
+Historically, when people consider 4-point scattering 
+\begin{equation*}
+    p_1,p_2,p_3,p_4, \quad \text{satisfying}\quad p_i^2=0 \quad\text{and}\quad \sum_{i=1}^{4}p_i=0
+\end{equation*}
+\begin{equation*}
+    \text{d.o.f}=4n-4-n=3n-4\quad \text{independent complexed d.o.f}
+\end{equation*}
+This seems to be too much, so people change to use Mandelstam variables
+\begin{equation*}
+    s,t,u(\text{for}~~\pi\pi~~\text{scattering})\quad\text{satisfying}\quad s+t+u=0
+\end{equation*}
+\end{frame}
+
+\begin{frame}
+    Also for earliest String Amplitude (Venezaino Amplitude)
+    \begin{equation*}
+        A_{\text{open}}(s, t) = g^2 \frac{\Gamma(-\alpha' s)\, \Gamma(-\alpha' t)}{\Gamma(-\alpha' s - \alpha' t)}
+    \end{equation*}
+   But the problem is that Mandelstam variables only apply to 2$\rightarrow$2 scattering, how about higher point?
+   \begin{equation*}
+    \text{single complexed variable like}\quad A(z) 
+   \end{equation*}
+   This is the starting point of BCFW recursion relation!
+\end{frame}
+
+\begin{frame}
+    \frametitle{Poincaré Invariance and Little Group Scaling }
+    We consider a Poincaré invariant field theory.
+    The one-particle state are defined from a reference momentum k like this  
+    \begin{equation*}
+         \aket{p;\sigma}=U(L(p;k))\aket{k;\sigma}
+    \end{equation*}
+    Then the general Lorentz transformation acts like
+    \begin{align*}
+        U(\Lambda)|p,\sigma\rangle &= U(\Lambda) U(L(p;k))|k,\sigma \rangle \\
+        &= U(L(\Lambda p;k)) U(L^{-1}(\Lambda p;k) \Lambda L(p;k)) |k,\sigma \rangle\
+    \end{align*}
+    here $W=L^{-1}(\Lambda p;k) \Lambda L(p;k)$ is not a general transformation but keep k invariant, called little group.
+    Thus we have 
+    \begin{equation*}
+         U(W(\Lambda,p,k))\aket{k;\sigma}=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{k,\sigma^{'}}
+    \end{equation*}
+    so one-particle state with momentum p transformed like 
+    \begin{equation*}
+        \textcolor{red}{U(\Lambda)|p,\sigma\rangle=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{\Lambda p,\sigma^{'}}}
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    \textcolor{red}{One-particle state transformed under the little group!}
+
+    For massless particle, the little group is $SO(2)\backsimeq U(1)$, so the representation matrix is just a phase.
+    The Poincaré invariance of S-matrix requires 
+    \begin{equation*}
+        \mathcal{M}^\Lambda(p_a,\sigma_a)=\prod_{a}(D_{\sigma\sigma^{'}})\mathcal{M}((\Lambda p)_a,\sigma_a^{'})
+    \end{equation*}
+      \begin{itemize}
+        \item $\textbf{\text{Massless Case}}$\\
+    \begin{equation*}
+        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
+    \end{equation*}
+    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
+    \begin{equation*}
+        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
+    \end{equation*}
+    same for
+    \begin{equation*}
+        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
+    \end{equation*}
+    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
+    \begin{equation*}
+        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
+    \end{equation*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Crossing Symmetry and MHV Classification}
+    Crossing symmetry is a result from analyticity, unitarity and Lorentz invariance. 
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{CrossingSYM.png}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
 \frametitle{Modern Amplitude Method} 
@@
     \begin{align*}
-    A_5[1^+2^+3^+4^+5^+] &= 0 
+    A_5[1^+2^+3^+4^+5^+] =& 0 
     \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
-    A_5[1^-2^+3^+4^+5^+] &= 0 
+    A_5[1^-2^+3^+4^+5^+] =& 0 
     \qquad 1,2,\cdots,n:~\text{particle labels}) \\
+    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]} &=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle  \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}\quad (\text{first non-trival one})
     \end{align*}
-    \vspace{-3em}
+    \vspace{-1em}
     \hypertarget{conv}{}
@@
     \frametitle{Color-ordering for Yang-Mills}
-    Consider the Yang-Mills lagrangian
+    Consider the Yang-Mills Lagrangian
     \begin{equation*}
@@
 \begin{frame}
-    From Cauchy Theorem, we can ontain
-    \begin{equation*}
-        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
-    \end{equation*}
-    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
+   The most important point here is that
+    \begin{equation*}
+        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
+    \end{equation*}
+    It means that the original amplitude equals to the residue at origin.
     \vspace{-1em}
